### 2019-09-09 report - poc.Rmd
Adding initial report.

---
title: "Beta to Release Matching"
author: "Corey Dow-Hygelund, Mozilla Data Science"
date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    theme: cosmo
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r imports, message=FALSE, warning=FALSE, echo=FALSE}
load('data/4week/US/analysis_09072019.RData')
source('supporting_funcs.R')
library(cowplot)
```

```{r data_load, message=FALSE, warning=FALSE, echo=FALSE}
exp_4x_all.nearest.ma.df <- match.data(exp_4x_all.nearest.ma)

# single dataframe for plotting
df_f <- exp_4x.nearest.ma.df %>% 
  select(-c(distance, weights)) %>%
  filter(label == 'beta') %>%
  mutate(label =  'beta - matched') %>%
  rbind(df_4x_sm)
```

## tl;dr

[Statistical matching](https://en.wikipedia.org/wiki/Matching_(statistics)) methods were employed to investigate the posssibility of finding a subset of Beta clients that are representative of Release. The specific use-case of this proof-of-concept is utilizing engagement, configuration, and environment client fields (covariates) for matching. Validation of the matching is performed on a hold-out set of Firefox performance covariates, as an illustration of a potential real-world use-case. The following tables represent the relative difference between Beta and Release for the mean and median respectively. These initial results are promising and suggest that such techniques can work.

```{r tldr_summary, message=FALSE, warning=FALSE, echo=FALSE}

stats_pre <- calc_delta(df_4x_sm, NULL, holdout_covariates) %>%
  select(-'content_crashes')
stats_post <- calc_delta(exp_4x_all.nearest.ma.df, NULL, holdout_covariates) %>%
  select(-'content_crashes')

stats_mean <- stats_pre[1, ] %>% 
  rbind(stats_post[1, ]) %>%
  set_rownames(c('pre-matching', 'post-matching'))

stats_median <- stats_pre[2, ] %>% 
  rbind(stats_post[2, ]) %>%
  set_rownames(c('pre-matching', 'post-matching'))
```

### Beta-Release Difference: Mean
```{r tldr_summary_mean, message=FALSE, warning=FALSE, echo=FALSE}
library(kableExtra)

knitr::kable(stats_mean) %>%
  kable_styling() %>%
  scroll_box(width = "750px", height = "200px")
```

### Beta-Release Difference: Mean

```{r tldr_summary_median, message=FALSE, warning=FALSE, echo=FALSE}
knitr::kable(stats_median) %>%
  kable_styling() %>%
  scroll_box(width = "750px", height = "200px")
```

## Problem Statement
It is highly desirable to utilize the Beta versions of Firefox to determine the behaviour of Release before it is launched. However, it is well known that the Beta population has distinctly differently characteristics than Release, such as country distribution and having higher incidents of crashes. Therefore, directly utilizing Beta to inform Release is not statistical valid.

One possible approach to deal with this discrepency is to use statistical matching techniques to find a subset of Beta that is representative of Release. What connotates "representative" depends upon the desirec use-case (outcome), such as performance characteristics, or crash rates. In this work we focus on the application of performance metrics.

## Methodology
### Data Preparation
The code that exported the data is available [here](https://dbc-caf9527b-e073.cloud.databricks.com/#notebook/172123/command/172124). This work specifically focuses on desktop Firefox. The following filters are applied:

* Version 68
* Beta dates: last four weeks (06/04/2019 - 07/09/2019)
* Release dates: first four weeks (07/09/2019 - 08/06/2019)
* Two weeks of collection per profile, starting with first observed ping within date window
* en-US, en-GB locales
* US, GB countries

Preliminary work utilized all countries. However, the results of the statistical matching were poor. Therefore, the dominant two countries in Release were selected to reduce the problem scope. This significantly limited the available population for matching to ~100K.

### Covariates
The following covariates are collected. These are categorized under training, and hold-out. The former are used for training a statistical matching model. The latter are not included in training and are used for determining model performance. The covariates are further subcategorized as to the what they measure.

#### Training
The sum of <  > ....
(build markdown table)

#### Holdout
The following are the performance metrics used for validation. The

### Covariate Selection {#cov_sel}

As statistical matching typically trains a machine learning (ML) model for calculation of propensity scores, variable selection should be employed. However, the literature suggests that typical ML techniques of limiting covariates to those that best predict the response (i.e., Beta or Release) are not helpful for statistical matching. Rather, covariates that best describe the outcome (i.e., performance metrics) should be utilized. Please refer to the following papers for reference.

* [Variable Selection for Propensity Scores](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC1513192/) (Brookhart et al. 2007)
* [Variable Selectgion for Propensity Score Estimation via Balancing Covariates](https://journals.lww.com/epidem/FullText/2015/03000/Variable_Selection_for_Propensity_Score_Estimation.25.aspx) (Zhu et al. 2015)

In this work, due to time considerations, sets of covariates were manually chosen from each measure type that were not highly correlated. The following plot shows the correlation of the continuous covariates.

```{r corrplot, fig.width=14, fig.height=14, echo=FALSE}
corrplot(cor(df[, c(cont_log_covariates, cont_covariates)], use='complete.obs'), method = 'ellipse')
```

## Models
A range of statistical matching models were reviewed, using the _R_ library [Matchit](https://cran.r-project.org/web/packages/MatchIt/index.html):

* Coarsened Exact Matching (CEM)
* Nearest neighbor matching
* Nearest neighbor matching, with Mahalanobis distance measure

In addition, various sets of covariates were utilized, under the conditions described [above](#cov_sel).

Finally, a range of Beta overrepresentations were tested. In the following, 2x means there were twice as many Beta samples as Release.

* 1x Beta to Release
* 2x Beta to Release
* 4x Beta to Release

The best performing model was Nearest Neighbors with Mahalanobis distance measure, with 4x Beta to Release. This is in vein to the findings of [King et al. 2018](https://gking.harvard.edu/files/gking/files/psnot.pdf). However, this works finds that CEM is sub-optimal, with respect to Neight neighbors matching.

Mahalanobis distance matching requires continuous covariates. The following were found to be the most performant:

< covariates>

## Results

The following plots show the covariate distributions for the following subsets:

* Beta: pre-matching
* Beta: matched and subsetted
* Release

**NOTE**: Guiding lines have been added for the following:

* <span style="color:red">red</span> dashed: Release mean
* <span style="color:blue">blue</span> dashed: Release median
* <span style="color:green">green</span> dashed line: subsetted Beta _mean_.

### Covariates: Performance Holdout

The following plot shows the holdout performance metrics distributions for the following subsets. Overall, the matching greatly reduces the  differences in the distributions between Beta and Release. For several metrics, such as `CONTENT_PAINT_TIME_CONTENT`, the subsetting results in very comparable distributions. For cases such as `TIME_TO_DOM_CONTENT_LOADED_MS`, the improvement is significant, though differences between the two channels are significant.

However, for `MEMORY_TOTAL` and `startup_ms`, the improvement is marginal and the resultant matched distrubution are poor. `MEMORY_TOTAL` has the greatest observable difference between Beta and Release pre and post matching. `startup_ms` doesn't appear to be highly distinct across channels for these metrics.

Combined, these results suggest that matching can make small, but limited, improvements to the distributions.

```{r perf_holdout, fig.width=10, fig.height=100, echo=FALSE}
ho_other_cov <- c('content_crashes')
ho_log_cov <- holdout_covariates[!holdout_covariates %in% ho_other_cov]

stats <- calc_stats(exp_4x.nearest.ma.df, holdout_covariates, add_1 = TRUE)
plots <- list()

for (covariate in ho_log_cov) {
  stats_rel <- stats %>% filter(label == 'release') %>% select(covariate, metric)
  means <- stats_rel[stats_rel$metric == 'mean', covariate]
  medians <- stats_rel[stats_rel$metric == 'median', covariate]
  ho_means <- stats %>% filter(label == 'beta' & metric == 'mean') %>% select(covariate)

  plots[[covariate]] <- compare_log_cont(df_f, covariate, means, medians, as.numeric(ho_means), print=FALSE) 
}

plot_grid(plotlist = plots, ncol = 1)
```

### Covariates: Engagement Holdout

The following engagement covariates were not used training, as they are relatively correlated to those metrics used.

```{r engagment_plot, fig.width=10, fig.height=50, echo=FALSE}
stats <- calc_stats(exp_4x.nearest.ma.df, cont_log_covariates, add_1 = TRUE)
plots <- list()

model_covs <- c('search_count', 'daily_max_tabs', 'daily_num_sessions_started', 'num_addons', 
                                        'num_bookmarks', 'profile_age', 'timezone_offset', 'cpu_speed_mhz', 'memory_mb', 
                                        'cpu_cores')

for (covariate in cont_log_covariates[!cont_log_covariates %in% model_covs]) {
  stats_rel <- stats %>% filter(label == 'release') %>% select(covariate, metric)
  means <- stats_rel[stats_rel$metric == 'mean', covariate]
  medians <- stats_rel[stats_rel$metric == 'median', covariate]
  ho_means <- stats %>% filter(label == 'beta' & metric == 'mean') %>% select(covariate)

  plots[[covariate]] <- compare_log_cont(df_f, covariate, means, medians, as.numeric(ho_means), print=FALSE)

}

plot_grid(plotlist = plots, ncol = 1)
```

## Discussion

The matching did an adequate job in finding a representative subset of Beta, especially concerning the performance metrics task. There are many avenues to further this analsysis, in order to utilize such a methodology in a production setting:

* Covariate/ Variable selection
  * This needs to be actively researched, especially in regards to real-world Firefox use-cases. 
* Compare histogram distributions
  * Client means were utilized in this above analysis. Instead, aggregating the client distributions needs to be addressed.
* Feature generation
  * The covariates utilized above are limited subset. A much more rigorous analysis of covariates needs to be applied.
* All countries used in matching
  * This is required for most general uses of the Beta subset.
  * The US and GB Beta population is quite small. As noted above, overrepresentation of Beta in matching results in higher performant models. Therefore, to obtain greater training sample sizes requires at minimum for India to be considered.

### 2019-09-09 supporting_funcs.R
Updating with additional helpers and the like for report support.

@@ -1,34 +1,104 @@
 library(dplyr)
 library(ggplot2)
 library(corrplot)
+library(magrittr)
 library(tidyr)
 library(tidyselect)
 library(MatchIt)
 
-model_pipeline <- function(df, tr_cov, ho_cov, match_type, label, ...){
-  # Matching
-  formula <- as.formula(paste(label, paste(tr_cov, collapse="+")))
-  print(paste('Matching:', formula))
-  matcher <- matchit(formula, df, method = match_type, ...)
-  df.match <- match.data(matcher)
-  
+#### Helpers
+# TODO remove `tr_cov` arg
+calc_means <- function(df.match, tr_cov, ho_cov, add_1 = FALSE){
   # Validation
   ## Means: train
-  tr_mean <- df.match %>% 
-    select(tr_cov, label) %>% 
-    group_by(label) %>% 
-    summarise_all(mean)
-  print(tr_mean)
+  # tr_mean <- df.match %>% 
+  #   select(tr_cov, label) %>% 
+  #   group_by(label) %>% 
+  #   summarise_all(mean)
+  # print(tr_mean)
   ## Means: holdout
   ho_mean <- df.match %>% 
     select(ho_cov, label) %>% 
+    mutate_all(function(x) if(is.numeric(x) && add_1) x+1 else x) %>%
     group_by(label) %>% 
     summarise_all(mean)
-  print(ho_mean)
-  return(c(matcher, df.match))
+  return(ho_mean)
 }
 
+calc_medians <- function(df.match, tr_cov, ho_cov, add_1 = FALSE){
+  # Validation
+  ## medians: train
+  # tr_median <- df.match %>% 
+  #   select(tr_cov, label) %>% 
+  #   group_by(label) %>% 
+  #   summarise_all(median)
+  # print(tr_median)
+  ## medians: holdout
+  ho_median <- df.match %>% 
+    select(ho_cov, label) %>% 
+    mutate_all(function(x) if(is.numeric(x) && add_1) x+1 else x) %>%
+    group_by(label) %>% 
+    summarise_all(median)
+  # print(ho_median)
+  # return(list(train = tr_median, ho = ho_median))
+  return(ho_median)
+}
+
+calc_delta <- function(df.match, tr_cov, ho_cov){
+  perc_diff <- function(x) abs(x[1]-x[2])/x[2]
+  means <- calc_means(df.match, tr_cov, ho_cov) %>%
[…]

### 2019-09-11 modeling_poc.Rmd
Adding report markdown and supporting modeling file.

---
title: 'Beta to Release Matching: Modeling'
author: "Corey Dow-Hygelund"
date: "9/3/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## tl;dr

[Statistical matching](https://en.wikipedia.org/wiki/Matching_(statistics)) methods were employed to investigate the posssibility of finding a subset of Beta clients that are representative of Release. The specific use-case of this proof-of-concept is utilizing engagement, configuration, and environment covariates of the clients for matching. Validation of the matching is performed on a hold-out set of Firefox performance covariates. Such a a use-case has real-world analogies.

```{r, warning=FALSE, message=FALSE, echo=FALSE}
source('supporting_funcs.R')
```

## Data Loading/Preparation
```{r}
# define response field
label <- 'is_release'

# load up dataset
df <- read.csv('data/4week/US/df.csv') %>%
  select(-c(CONTENT_PAINT_TIME_PARENT, COMPOSITE_TIME_CONTENT, COMPOSITE_TIME_PARENT, CONTENT_FRAME_TIME_PARENT)) %>% # All NAs 
  select(-e10s_enabled) %>% # All True
  mutate(default_search_engine = as.factor(normalize_search_engine(default_search_engine))) %>%
  mutate(profile_age_cat = as.factor(normalize_profile_age(profile_age))) %>%
  mutate(distro_id_norm = as.factor(normalize_distro_id(distribution_id))) %>%
  mutate(timezone_cat = as.factor(normalize_timezone(timezone_offset))) %>%
  mutate(memory_cat = as.factor(normalize_memory(memory_mb))) %>% 
  mutate(cpu_speed_cat = as.factor(normalize_cpu_speed(cpu_speed_mhz))) %>% 
  mutate(cpu_cores_cat = as.factor(normalize_cpu_cores(cpu_cores))) %>% 
  mutate(!!label := case_when(
    label == 'beta' ~ FALSE,
    TRUE ~ TRUE)) %>%
  filter(startup_ms >= 0 & profile_age >= 0)
  # filter(country %in% c('US', 'GB'))

# complete cases (specifically targets perf metrics)
df_c <- df %>% na.omit()
```

```{r}
# Various sampling for beta overrepresentation
df_beta <- df_c %>% filter(is_release == FALSE)
df_rel <- df_c %>% filter(is_release == TRUE)
n_beta <- nrow(df_beta)

build_df <- function(multiple){
  df <- df_rel %>%
    sample_n(size = round(n_beta / multiple)) %>%
    rbind(df_beta)
}

df_1x <- build_df(1)
df_2x <- build_df(2)
df_4x <- build_df(4)

```

Downsample to allow nearest neighbors to complete within the year. 
```{r}
df_1x_sm <- df_1x %>% sample_n(size = 70000)
df_2x_sm <- df_2x %>% sample_n(size = 70000)
df_4x_sm <- df_4x %>% sample_n(size = 70000)
```

## Covariates

Define the covariates for modeling and validation.

```{r}
cont_log_covariates <- c('active_hours', 'daily_max_tabs', 'daily_tabs_opened', 'search_count', 'daily_unique_domains',
                     'num_bookmarks', 'num_addons', 'num_active_days', 'num_pages', 'uri_count', 'session_length')

cont_covariates <- c('profile_age', 'cpu_cores', 'cpu_speed_mhz', 'daily_num_sessions_started', 'timezone_offset')

cat_covariates <- c('country', 'timezone_cat', 'distribution_id', 'profile_age_cat')

holdout_covariates <- c("CONTENT_PAINT_TIME_CONTENT", "TIME_TO_DOM_CONTENT_LOADED_END_MS", 
                        "MEMORY_TOTAL", "TIME_TO_DOM_COMPLETE_MS", "FX_PAGE_LOAD_MS_2_PARENT", 
                        "FX_TAB_SWITCH_TOTAL_E10S_MS",
                        "CONTENT_FRAME_TIME_GPU", "COMPOSITE_TIME_GPU",
                        "TIME_TO_LOAD_EVENT_END_MS", 'startup_ms', 'content_crashes')
```

## Variable Selection
None performed at the moment. Literature suggests that using those related to outcome variables.

## Experiments
Groups of models to train. Complete alchemy at this point...

```{r}
exp_1 <- c('uri_count', 'daily_max_tabs', 'daily_num_sessions_started', 'num_addons', 'num_bookmarks',
           'profile_age_cat', 'is_wow64', 'fxa_configured', 'sync_configured', 'is_default_browser',
           'timezone_cat')

exp_2 <- c('uri_count', 'daily_max_tabs', 'daily_num_sessions_started', 'num_addons', 'num_bookmarks',
           'profile_age', 'is_wow64', 'fxa_configured', 'sync_configured', 'is_default_browser',
           'timezone_offset')

exp_3 <- c('uri_count', 'daily_max_tabs', 'daily_num_sessions_started', 'num_addons', 'num_bookmarks',
           'profile_age_cat', 'is_wow64', 'fxa_configured', 'sync_configured', 'is_default_browser',
           'timezone_cat', 'distro_id_norm')

exp_4 <- c('search_count', 'daily_max_tabs', 'daily_num_sessions_started', 'num_addons', 'num_bookmarks',
           'profile_age_cat', 'is_wow64', 'fxa_configured', 'sync_configured', 'is_default_browser',
           'timezone_cat', 'distro_id_norm') # causing errors when downsampling!, 'os')

exp_5 <- c('search_count', 'daily_max_tabs', 'daily_num_sessions_started', 'num_addons', 'num_bookmarks',
           'profile_age_cat','fxa_configured', 'sync_configured', 'is_default_browser',
           'timezone_cat', 'cpu_speed_mhz')

exp_6 <- c('search_count', 'daily_max_tabs', 'daily_num_sessions_started', 'num_addons', 'num_bookmarks',
           'profile_age_cat','fxa_configured', 'sync_configured', 'is_default_browser',
           'country', 'cpu_speed_mhz')

exp_7 <- c('search_count', 'daily_max_tabs', 'daily_num_sessions_started', 'num_addons', 'num_bookmarks',
           'profile_age_cat','fxa_configured', 'sync_configured', 'is_default_browser',
           'country', 'cpu_speed_mhz', 'memory_mb')

exp_8 <- c('search_count', 'daily_max_tabs', 'daily_num_sessions_started', 'num_addons', 'num_bookmarks',
           'profile_age_cat','fxa_configured', 'sync_configured', 'is_default_browser',
           'country', 'cpu_speed_mhz', 'memory_mb', 'cpu_cores')

exp_9 <- c('search_count', 'daily_max_tabs', 'daily_num_sessions_started', 'num_addons', 'num_bookmarks',
           'profile_age_cat','fxa_configured', 'sync_configured', 'is_default_browser',
           'country', 'cpu_speed_cat', 'memory_cat', 'cpu_cores_cat')

exp_10 <- c('search_count', 'daily_max_tabs', 'daily_num_sessions_started', 'num_addons', 'num_bookmarks',
           'profile_age_cat','fxa_configured', 'sync_configured', 'is_default_browser',
           'country', 'cpu_speed_cat', 'memory_cat', 'cpu_cores_cat', 'distro_id_norm')

exps <- list(exp_1 = exp_1, exp_2 = exp_2, exp_3 = exp_3, exp_4 = exp_4, exp_5 = exp_5, 
             exp_6 = exp_6, exp_7 = exp_7, exp_8 = exp_8, exp_9 = exp_9, exp_10 = exp_10)
```

## Modeling

### CEM: Small Dataset

#### 1x Oversampling
```{r}
cem_results_1x <- list()
cem_models_1x <- list()
for (exp in names(exps)){
  cem <- matchit(formula = generate_formula(exps[[exp]], label), df_1x_sm, 'cem')
  res <- match.data(cem) %>%
    calc_delta(tr_cov = exps[[exp]], ho_cov = holdout_covariates)
  cem_results_1x[[exp]] <- res
  cem_models_1x[[exp]] <- cem
  print(res)
}
```

#### 2x Oversampling
```{r}
cem_results_2x <- list()
cem_models_2x <- list()
for (exp in names(exps)){
  cem <- matchit(formula = generate_formula(exps[[exp]], label), df_2x_sm, 'cem')
  res <- match.data(cem) %>%
    calc_delta(tr_cov = exps[[exp]], ho_cov = holdout_covariates)
  cem_results_2x[[exp]] <- res
  cem_models_2x[[exp]] <- cem
  print(res)
}
```

#### 4x Oversampling
```{r}
cem_results_4x <- list()
cem_models_4x <- list()
for (exp in names(exps)){
  cem <- matchit(formula = generate_formula(exps[[exp]], label), df_4x_sm, 'cem')
  res <- match.data(cem) %>%
    calc_delta(tr_cov = exps[[exp]], ho_cov = holdout_covariates)
  cem_results_4x[[exp]] <- res
  cem_models_4x[[exp]] <- cem
  print(res)
}
```

```{r}
save.image('data/4week/US/analysis_09072019.RData')
```

**Observation**: Adding in environment metrics greatly helps!

### Nearest Neighbors: Small

#### 1x Oversampling
```{r}
nearest_results_1x <- list()
nearest_models_1x <- list()
for (exp in names(exps)){
  nearest <- matchit(formula = generate_formula(exps[[exp]], label), df_1x_sm, 'nearest', replace = TRUE)
  res <- match.data(nearest) %>%
    calc_delta(tr_cov = exps[[exp]], ho_cov = holdout_covariates)
  nearest_results_1x[[exp]] <- res
  nearest_models_1x[[exp]] <- nearest
  print(res)
}
```

#### 2x Oversampling
```{r}
nearest_results_2x <- list()
nearest_models_2x <- list()
for (exp in names(exps)){
  nearest <- matchit(formula = generate_formula(exps[[exp]], label), df_2x_sm, 'nearest')
  res <- match.data(nearest) %>%
    calc_delta(tr_cov = exps[[exp]], ho_cov = holdout_covariates)
  nearest_results_2x[[exp]] <- res
  nearest_models_2x[[exp]] <- nearest
  print(res)
}
```

#### 4x Oversampling
```{r}
nearest_results_4x <- list()
nearest_models_4x <- list()
for (exp in names(exps)){
  nearest <- matchit(formula = generate_formula(exps[[exp]], label), df_4x_sm, 'nearest')
  res <- match.data(nearest) %>%
    calc_delta(tr_cov = exps[[exp]], ho_cov = holdout_covariates)
  nearest_results_4x[[exp]] <- res
  nearest_models_4x[[exp]] <- nearest
  print(res)
}
```

```{r, echo=FALSE}
save.image('data/4week/US/analysis_09072019.RData')
```

### CEM: Full

#### 1x Oversampling
```{r}
cem_results_1x <- list()
cem_models_1x <- list()
for (exp in names(exps)){
  cem <- matchit(formula = generate_formula(exps[[exp]], label), df_1x, 'cem')
  res <- match.data(cem) %>%
    calc_delta(tr_cov = exps[[exp]], ho_cov = holdout_covariates)
  cem_results_1x[[exp]] <- res
  cem_models_1x[[exp]] <- cem
  print(res)
}
```

#### 2x Oversampling
```{r}
cem_results_2x <- list()
cem_models_2x <- list()
for (exp in names(exps)){
  cem <- matchit(formula = generate_formula(exps[[exp]], label), df_2x, 'cem')
  res <- match.data(cem) %>%
    calc_delta(tr_cov = exps[[exp]], ho_cov = holdout_covariates)
  cem_results_2x[[exp]] <- res
  cem_models_2x[[exp]] <- cem
  print(res)
}
```

#### 4x Oversampling
```{r}
cem_results_4x <- list()
cem_models_4x <- list()
for (exp in names(exps)){
  cem <- matchit(formula = generate_formula(exps[[exp]], label), df_4x, 'cem')
  res <- match.data(cem) %>%
    calc_delta(tr_cov = exps[[exp]], ho_cov = holdout_covariates)
  cem_results_4x[[exp]] <- res
  cem_models_4x[[exp]] <- cem
  print(res)
}
```

### Nearest Neighbors: Small - mahalanobis

Appears `distance = 'mahalanobis'` doesn't work with categorical (singular matrix). Bypassing issue by only using numeric covariates.

#### 1x Oversampling
```{r}
formula <- generate_formula(c('search_count', 'daily_max_tabs', 'daily_num_sessions_started', 'num_addons', 
                                        'num_bookmarks', 'profile_age', 'timezone_offset', 'cpu_speed_mhz', 'memory_mb', 
                                        'cpu_cores'), label = label)

exp_1x.nearest.ma<- matchit(formula, df_1x_sm, 'nearest', distance='mahalanobis', replace = TRUE)

exp_1x.res.nearest.ma <- match.data(exp_1x.nearest.ma) %>%
  calc_delta(tr_cov = exp_1, ho_cov = holdout_covariates)
exp_1x.res.nearest.ma
```

#### 2x Oversampling
```{r}
exp_2x.nearest.ma.1x<- matchit(formula, df_2x_sm, 'nearest', distance='mahalanobis')

exp_2x.res.nearest.ma <- match.data(exp_2x.nearest.ma) %>%
  calc_delta(tr_cov = exp_1, ho_cov = holdout_covariates)
exp_2x.res.nearest.ma
```

#### 4x Oversampling
```{r}
exp_4x.nearest.ma<- matchit(formula, df_4x_sm, 'nearest', distance='mahalanobis')

exp_4x.res.nearest.ma <- match.data(exp_4x.nearest.ma) %>%
  calc_delta(tr_cov = exp_1, ho_cov = holdout_covariates)
exp_4x.res.nearest.ma
```

```{r, echo=FALSE} 
save.image('data/4week/US/analysis_09072019.RData')
```

```{r}
stats <- calc_stats(df_4x_sm, holdout_covariates, add_1 = TRUE)

for (covariate in holdout_covariates) {
  stats_rel <- stats %>% filter(label == 'release') %>% select(covariate, metric)
  means <- stats_rel[stats_rel$metric == 'mean', covariate]
  medians <- stats_rel[stats_rel$metric == 'median', covariate]

  compare_log_cont(df_4x_sm, covariate, means, medians) 
}
```

```{r}
exp_4x.nearest.ma.df <- match.data(exp_4x.nearest.ma)
stats <- calc_stats(exp_4x.nearest.ma.df, holdout_covariates, add_1 = TRUE)

for (covariate in holdout_covariates) {
  stats_rel <- stats %>% filter(label == 'release') %>% select(covariate, metric)
  means <- stats_rel[stats_rel$metric == 'mean', covariate]
  medians <- stats_rel[stats_rel$metric == 'median', covariate]

  compare_log_cont(exp_4x.nearest.ma.df, covariate, means, medians) 
}
```

#### 4x: Kitchen Sink
All continuous covariates

```{r}
formula <- generate_formula(c(cont_log_covariates, cont_covariates), label = label)

exp_4x_all.nearest.ma<- matchit(formula, df_4x_sm, 'nearest', distance='mahalanobis')

exp_4x_all.res.nearest.ma <- match.data(exp_4x_all.nearest.ma) %>%
  calc_delta(tr_cov = exp_1, ho_cov = holdout_covariates)
exp_4x_all.res.nearest.ma
```

```{r}
save.image('data/4week/US/analysis_09072019.RData')
```

```{r}
stats <- calc_stats(df_4x_sm, holdout_covariates, add_1 = TRUE)

for (covariate in holdout_covariates) {
  stats_rel <- stats %>% filter(label == 'release') %>% select(covariate, metric)
  means <- stats_rel[stats_rel$metric == 'mean', covariate]
  medians <- stats_rel[stats_rel$metric == 'median', covariate]

  compare_log_cont(df_4x_sm, covariate, means, medians) 
}
```

```{r}
exp_4x_all.nearest.ma.df <- match.data(exp_4x_all.nearest.ma)
stats <- calc_stats(exp_4x_all.nearest.ma.df, holdout_covariates, add_1 = TRUE)

for (covariate in holdout_covariates) {
  stats_rel <- stats %>% filter(label == 'release') %>% select(covariate, metric)
  means <- stats_rel[stats_rel$metric == 'mean', covariate]
  medians <- stats_rel[stats_rel$metric == 'median', covariate]

  compare_log_cont(exp_4x_all.nearest.ma.df, covariate, means, medians) 
}
```

```{r}
save.image('data/4week/US/analysis_09072019.RData')
```

### 2019-09-11 report_poc.Rmd
Adding report markdown and supporting modeling file.

--- 2019-09-09 report - poc.Rmd
@@
   rbind(df_4x_sm)
+
+model_covs <- c('search_count', 'daily_max_tabs', 'daily_num_sessions_started', 'num_addons', 
+                                        'num_bookmarks', 'profile_age', 'timezone_offset', 'cpu_speed_mhz', 'memory_mb', 
+                                        'cpu_cores')
 ```
@@
 [Statistical matching](https://en.wikipedia.org/wiki/Matching_(statistics)) methods were employed to investigate the posssibility of finding a subset of Beta clients that are representative of Release.
-The specific use-case of this proof-of-concept is utilizing engagement, configuration, and environment client fields (covariates) for matching.
-Validation of the matching is performed on a hold-out set of Firefox performance covariates, as an illustration of a potential real-world use-case.
+The specific use-case of this proof-of-concept was to utilize engagement, configuration, and environment client fields (covariates) for matching.
+Validation of the matching was performed on a hold-out set of Firefox performance covariates, as an illustration of a potential real-world use-case.
 The following tables represent the relative difference between Beta and Release for the mean and median respectively.
@@
 ### Covariates
-The following covariates are collected.
-These are categorized under training, and hold-out.
-The former are used for training a statistical matching model.
+The following covariates were collected.
+These were categorized under training, and hold-out.
+The former were used for training a statistical matching model.
 The latter are not included in training and are used for determining model performance.
@@
 #### Training
-The sum of <  > ....
-(build markdown table)
+
+* Browser engagement
+    - uri_count
+    - search_count
+    - active_hours
+    - num_pages
+    - daily_max_tabs
+    - daily_unique_domains
+    - daily_num_sessions_started
+    - daily_tabs_opened
+* Frequency of Browser Usage
+    - num_active_days
+    - daily_num_sessions_started
+    - session_length
+    - profile_age
+* Environment
+    - cpu_cores
+    - cpu_speed_mhz
+    - memory_mb
+    - os
+    - os_version
+    - is_wow64
+    - distribution_id
+* Geo
+    - country
+    - timezone_offset
+* Settings
+    - num_bookmarks
+    - num_addons
+    - sync_configured
+    - is_default_browser
 
 #### Holdout
-The following are the performance metrics used for validation. The
+The following are the performance metrics used for validation.
+These were chosen to cover various aspects of [Firefox performance](https://docs.google.com/document/d/1W-EREsJLuRvTPvGXaW71FvuAGXkoLNDZmZl-sbaeMZM/edit#heading=h.xguata2qq3jz), in addition to their ease of accessbility in `main_summary`,
+
+* Page Load
+    - FX_PAGE_LOAD_MS_2_PARENT
+    - TIME_TO_DOM_COMPLETE_MS
+    - TIME_TO_DOM_CONTENT_LOADED_END_MS
+    - TIME_TO_LOAD_EVENT_END_MS
+* Responsiveness
+    - FX_TAB_SWITCH_TOTAL_E10S_MS    
+* Graphics
+    - COMPOSITE_TIME_GPU
+    - CONTENT_FRAME_TIME_GPU
+    - CONTENT_PAINT_TIME_CONTENT
+* Memory
+    - MEMORY_TOTAL
+* Startup
+    - startup_ms
+* Stability
+    - content_crashes
 
@@
 ## Models
-A range of statistical matching models were reviewed, using the _R_ library [Matchit](https://cran.r-project.org/web/packages/MatchIt/index.html):
+A range of statistical matching models were [reviewed](https://metrics.mozilla.com/protected/cdowhygelund/modeling_poc.Rmd), using the R library [Matchit](https://cran.r-project.org/web/packages/MatchIt/index.html):
 
@@
 
-Mahalanobis distance matching requires continuous covariates. The following were found to be the most performant:
-
-< covariates>
+Mahalanobis distance matching requires continuous covariates. The following were found to be the most performant: `r paste(model_covs, sep=', ', collapse = ', ')`.
 
@@
 
-However, for `MEMORY_TOTAL` and `startup_ms`, the improvement is marginal and the resultant matched distrubution are poor.
+However, for `MEMORY_TOTAL` and `startup_ms`, the improvement is marginal and the resultant matched distrubutions are poor.
 `MEMORY_TOTAL` has the greatest observable difference between Beta and Release pre and post matching.
@@
 
-Combined, these results suggest that matching can make small, but limited, improvements to the distributions.
+In all cases, the change in the metrics is always positive. Combined, these results suggest that matching can make significant, albeit limited, improvements to the distributions.
 
@@
 
-model_covs <- c('search_count', 'daily_max_tabs', 'daily_num_sessions_started', 'num_addons', 
-                                        'num_bookmarks', 'profile_age', 'timezone_offset', 'cpu_speed_mhz', 'memory_mb', 
-                                        'cpu_cores')
-
 for (covariate in cont_log_covariates[!cont_log_covariates %in% model_covs]) {
@@
 The matching did an adequate job in finding a representative subset of Beta, especially concerning the performance metrics task.
-There are many avenues to further this analsysis, in order to utilize such a methodology in a production setting:
+There are many avenues to further this analsysis, in order to utilize such a methodology in a production setting.
+The primary research investment that needs to be made is in feature generation and selection.
+These are typically the highest influential factos in ML/predictive modeling tasks.
+
+Additional next steps include:
 
@@
 * Compare histogram distributions
-  * Client means were utilized in this above analysis. Instead, aggregating the client distributions needs to be addressed.
+  * Client means were utilized in this above analysis. Instead, aggregating the client distributions should be addressed.
 * Feature generation
   * The covariates utilized above are limited subset. A much more rigorous analysis of covariates needs to be applied.
-* All countries used in matching
+* Additional countries used in matching
   * This is required for most general uses of the Beta subset.
-  * The US and GB Beta population is quite small.
-As noted above, overrepresentation of Beta in matching results in higher performant models.
-Therefore, to obtain greater training sample sizes requires at minimum for India to be considered.
+  * The US + GB Beta population is quite small.
+As noted above, overrepresentation of Beta in matching yields higher performant models.
+Therefore, to obtain greater training sample sizes requires additional countries, especially India, to be considered.

### 2019-09-11 report_poc.Rmd
Adding report.

@@
 The following tables represent the relative difference between Beta and Release for the mean and median respectively.
-These initial results are promising and suggest that such techniques can work.
+These initial results are promising and suggest that such techniques could be applied to Mozilla use-cases.
+A simple, but robust validation of the technique is to apply and compare the resultant Beta subset to subsequent Release versions.
 
@@
 
-### Beta-Release Difference: Mean
+### Beta-Release Difference: Median
 
@@
 It is highly desirable to utilize the Beta versions of Firefox to determine the behaviour of Release before it is launched.
-However, it is well known that the Beta population has distinctly differently characteristics than Release, such as country distribution and having higher incidents of crashes.
-Therefore, directly utilizing Beta to inform Release is not statistical valid.
+However, it is well known that the Beta population has distinctly different characteristics than Release, such as country distribution and having higher incidents of crashes.
+Therefore, directly utilizing Beta to inform Release is not statistically valid.
 
 One possible approach to deal with this discrepency is to use statistical matching techniques to find a subset of Beta that is representative of Release.
-What connotates "representative" depends upon the desirec use-case (outcome), such as performance characteristics, or crash rates.
+What connotates "representative" depends upon the desired use-case (outcome), such as performance characteristics, or crash rates.
 In this work we focus on the application of performance metrics.
@@
 Therefore, the dominant two countries in Release were selected to reduce the problem scope.
-This significantly limited the available population for matching to ~100K.
+This significantly limited the available Beta population for matching to ~100K.
 
@@
 The following are the performance metrics used for validation.
-These were chosen to cover various aspects of [Firefox performance](https://docs.google.com/document/d/1W-EREsJLuRvTPvGXaW71FvuAGXkoLNDZmZl-sbaeMZM/edit#heading=h.xguata2qq3jz), in addition to their ease of accessbility in `main_summary`,
+These were chosen to cover various aspects of [Firefox performance](https://docs.google.com/document/d/1W-EREsJLuRvTPvGXaW71FvuAGXkoLNDZmZl-sbaeMZM/edit#heading=h.xguata2qq3jz), in addition to their ease of accessbility in `main_summary` and `clients_daily`.
 
@@
 Rather, covariates that best describe the outcome (i.e., performance metrics) should be utilized.
-Please refer to the following papers for reference.
+Please refer to the following papers for reference:
 
@@
 2018](https://gking.harvard.edu/files/gking/files/psnot.pdf).
-However, this works finds that CEM is sub-optimal, with respect to Neight neighbors matching.
+However, this works finds that CEM is sub-optimal, with respect to Neirest neighbors matching.
 
@@
 The following engagement covariates were not used training, as they are relatively correlated to those metrics used.
+In the cases of `daily_tabs_opened`, `daily_unique_domains`, and `num_pages` the matching actually _increased_ differences between Beta and Release.
 
@@
 The matching did an adequate job in finding a representative subset of Beta, especially concerning the performance metrics task.
-There are many avenues to further this analsysis, in order to utilize such a methodology in a production setting.
+There are many avenues to further this analysis, in order to utilize such a methodology in a production setting.
 The primary research investment that needs to be made is in feature generation and selection.
-These are typically the highest influential factos in ML/predictive modeling tasks.
+These are typically the highest influential factors in ML/predictive modeling tasks.
+
+### Further Validation
+
+The general use-case is to find a subset that can be applied to _future_ releases.
+Therefore, a pertinent validation of the technique is to utilize the resultant Beta subset profiles in predicting the behavior of the next Firefox Release (i.e.
+69).
+For the technique to be applicable, the improvements seen in V68 Beta to Release comparisons should hold for V69 Beta to Release.
+
+### Additional Next Steps
 
@@
 * Covariate/ Variable selection
-  * This needs to be actively researched, especially in regards to real-world Firefox use-cases. 
+    - This needs to be actively researched, especially in regards to real-world Firefox use-cases. 
 * Compare histogram distributions
-  * Client means were utilized in this above analysis. Instead, aggregating the client distributions should be addressed.
+    - Client means were utilized in this above analysis. Instead, aggregating the client distributions should be addressed.
 * Feature generation
-  * The covariates utilized above are limited subset. A much more rigorous analysis of covariates needs to be applied.
+    - The covariates utilized above are limited subset. A much more rigorous analysis of covariates needs to be applied.
 * Additional countries used in matching
-  * This is required for most general uses of the Beta subset.
-  * The US + GB Beta population is quite small.
+    - This is required for most general uses of the Beta subset.
+    - The US + GB Beta population is quite small.
 As noted above, overrepresentation of Beta in matching yields higher performant models.

### 2019-09-24 supporting_funcs.R
Categorical methods generate order factor.

@@ -159,14 +159,15 @@ normalize_cpu_speed <- function(cpu_speed){
 }
 
 normalize_cpu_cores <- function(cpu_cores){
-  case_when(
+  levels <- c('1', '2', '< 4', '< 8', '< 16', '> 16')
+  factor(case_when(
     cpu_cores <= 1 ~ "1",
     cpu_cores <= 2 ~ "2",
     cpu_cores <= 4 ~ "< 4",
     cpu_cores <= 8 ~ "< 8",
     cpu_cores <= 16 ~ "< 16",
     TRUE ~ "> 16"
-  )
+  ), levels = levels, ordered = TRUE)
 }
 
 #### Diagnostics
@@ -202,7 +203,7 @@ compare_cont <- function(df, covariate){
   print(p)
 }
 
-compare_cat <- function(df, covariate, limit = NULL, plot=TRUE){
+compare_cat <- function(df, covariate, limit = NULL, plot=TRUE, add_legend=TRUE){
   # reshape for plotting
   df_c <- df %>% 
     count(get(covariate), label) %>%
@@ -224,9 +225,11 @@ compare_cat <- function(df, covariate, limit = NULL, plot=TRUE){
   
   p <- ggplot(df_c, aes(category, density)) +
     geom_bar(aes(fill = label), position = "dodge", stat="identity") +
-    theme_bw() + 
+    theme_bw() +
+    theme(legend.position = c(0.2, 0.8)) +
     labs(x = covariate)
   
+  if (!add_legend) p <- p + guides(fill=FALSE)
   if (plot) print(p)
   return(p)
   # return(df_c)

### 2019-09-24 report_validation.Rmd
Adding report on validation and supporting files.

---
title: 'Beta to Release Matching: Method Validation'
author: "Corey Dow-Hygelund, Mozilla Data Science"
date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    theme: cosmo
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r data_load, message=FALSE, warning=FALSE, echo=FALSE}
load('data/Validation/analysis_09182019_corr.RData')
```

```{r imports, message=FALSE, warning=FALSE, echo=FALSE}
source('supporting_funcs.R')
library(cowplot)
library(kableExtra)
library(pander)
```

# tl;dr

This work expands upon the Beta to Release matching [proof-of-concept](https://metrics.mozilla.com/protected/cdowhygelund/beta_subset_release.html), by validating the technique across versions. The matching model was trained on v67 Desktop Firefox versions, matching Beta profiles that were representative of Release. Comparisons were made against these matched profiles and Release for v68 performance and engagement metrics. The results for v68 are similar to those observed in v67. This suggests this methodology can be used to calculate additional Firefox Release Health metrics derived from the Beta populations.

```{r tldr_summary, message=FALSE, warning=FALSE, echo=FALSE}
stats_pre <- calc_delta(df_validate, NULL, holdout_covariates) %>%
  select(-'content_crashes')
stats_post <- calc_delta(df_validate_matched, NULL, holdout_covariates) %>%
  select(-'content_crashes')

stats_pre_v67 <- calc_delta(df_train, NULL, holdout_covariates) %>%
  select(-'content_crashes')
stats_post_v67 <- calc_delta(df_matched, NULL, holdout_covariates) %>%
  select(-'content_crashes')

rows <- c('pre-matching: v67', 'post-matching: v67', 'pre-matching: v68', 'post-matching: v68')

stats_mean <- stats_pre_v67[1, ] %>% 
  rbind(stats_post_v67[1, ]) %>%
  rbind(stats_pre[1, ]) %>%
  rbind(stats_post[1, ]) %>%
  set_rownames(rows)

stats_median <- stats_pre_v67[2, ] %>% 
  rbind(stats_post_v67[2, ]) %>%
  rbind(stats_pre[2, ]) %>%
  rbind(stats_post[2, ]) %>%
  set_rownames(rows)
```

The following tables represent the relative difference between the Beta and Release train (v67) and validation (v68) datasets for the mean and median respectively.

## Beta-Release Difference: Mean

The following shows the 
```{r tldr_summary_mean, message=FALSE, warning=FALSE, echo=FALSE}
knitr::kable(stats_mean) %>%
  kable_styling() %>%
  scroll_box(width = "900px", height = "400px")
```

## Beta-Release Difference: Median

```{r tldr_summary_median, message=FALSE, warning=FALSE, echo=FALSE}

knitr::kable(stats_median) %>%
  kable_styling() %>%
  scroll_box(width = "900px", height = "400px")
```

# Problem Statement
There is significant utility in findiing representative Beta populations of Firefox that can give insight into Release before its launch. In a previous work, it was shown that [statistical matching](https://en.wikipedia.org/wiki/Matching_(statistics)) can find a subset of Beta that is representative of Release regarding performance metrics. However, a real world use-case is training the model on v67, finding matched clients, then applying to a subsequent version. This work attempts to further validate the technique, by following  this real-world use-case.

1. Train a statistical matching model on v67 Firefox data that matches Beta to Release profiles.
2. Extract the matched v67 Beta profiles.
3. Subset v68 Beta profiles by the matched v67 profiles.
4. Measure the difference in performance and engagement between between Beta and Release before and after matching.

# Methodology
## Data Preparation
The code that exported the data is available [here](https://dbc-caf9527b-e073.cloud.databricks.com/#notebook/175052/command/175053). Similar filters are applied as the previous work.

* Desktop Firefox
* Two weeks of collection per profile, starting with first observed ping within date window
* en-US, en-GB locales
* US, GB countries

### Training
The follows makes up the training dataset, used in statistical matching:

* Version 67
* Beta dates: last four weeks (06/04/2019 - 07/09/2019)
* Release dates: first four weeks (07/09/2019 - 08/06/2019)
* Composition:

```{r training_composition, message=FALSE, warning=FALSE, echo=FALSE}
knitr::kable(
  df_train_4x %>% 
  count(label) %>%
  rename(channel = label, count = n)
  ) %>%
  kable_styling() %>%
  scroll_box(width = "250px", height = "150px")
```

### Validation

The followings filters constitute the validation dataset:

* Version 68
* Beta dates: last four weeks (04/23/2019 - 05/21/2019)
* Release dates: first four weeks (05/21/2019 - 06/18/2019)
* Composition: _before_ matching and subsetting of Beta)

```{r validation_composition, message=FALSE, warning=FALSE, echo=FALSE}
knitr::kable(
  df_validate %>% 
  count(label) %>%
    rename(channel = label, count = n)
  ) %>%
  kable_styling() %>%
  scroll_box(width = "250px", height = "150px")
```

# Model

The [highest performant model](https://metrics.mozilla.com/protected/cdowhygelund/beta_subset_release.html#models) was trained on the [v67 dataset](https://metrics.mozilla.com/protected/cdowhygelund/modeling_validation.Rmd). The code the performed the modeling is available [here](https://metrics.mozilla.com/protected/cdowhygelund/method_validation.Rmd):

* Model: Nearest Neighbors with Mahalanobis distance measure
* Beta oversampling: 4x Beta to Release
* Covariates (Model Features): `r pander(model_covs)`

The final result of this model is a subset of Beta profiles most representative of Release.

# Validation

The next step is to subset the _validation_ v68 dataset by these matched Beta profiles. This reduces the Beta sample size used in the subsequent analysis:

* v67 Beta subset: `r df_matched %>% filter(label == 'beta') %>% count()` distinct profiles
* v68 Beta subset: `r df_validate_matched %>% filter(label == 'beta') %>% count()` distinct profiles

The following plots show the covariate distributions for the following subsets:

* Beta v68: pre-matching
* Beta v68: matched and subsetted
* Release v68

**NOTE**: Guiding lines have been added for the following:

* <span style="color:red">red</span> dashed: Release mean
* <span style="color:blue">blue</span> dashed: Release median
* <span style="color:green">green</span> dashed line: subsetted Beta _mean_.

## Holdout Covariates
The same set of [performance metrics as the previous analysis](https://metrics.mozilla.com/protected/cdowhygelund/beta_subset_release.html#covariates), were held out from matching model training and used as a model diagnostic:

```{r holdout_covs_list, echo=FALSE, results='asis'}
pander(as.list(holdout_covariates))
```

### Training Dataset: v67

```{r perf_holdout_training, fig.width=10, fig.height=50, echo=FALSE}
df_training_full <- df_matched %>% 
  select(-weights, -distance) %>%
  filter(label == 'beta') %>%
  mutate(label =  'beta - matched') %>%
  rbind(df_train) %>% 
  distinct()

stats <- calc_stats(df_training_full, holdout_covariates, add_1 = TRUE)

plots <- list()

for (covariate in holdout_covariates) {
  if (covariate == 'content_crashes') break
  stats_rel <- stats %>% filter(label == 'release') %>% select(covariate, metric)
  means <- stats_rel[stats_rel$metric == 'mean', covariate]
  medians <- stats_rel[stats_rel$metric == 'median', covariate]
  ho_means <- stats %>% filter(label == 'beta' & metric == 'mean') %>% select(covariate)

  plots[[covariate]] <- compare_log_cont(df_training_full, covariate, means, medians, as.numeric(ho_means), print=FALSE) 
}

plot_grid(plotlist = plots, ncol = 2)
```

### Validation Dataset: v68
```{r perf_holdout_validation, fig.width=10, fig.height=50, echo=FALSE}
df_validate_full <- df_validate_matched %>% 
  filter(label == 'beta') %>%
  mutate(label =  'beta - matched') %>%
  rbind(df_validate) %>% 
  distinct()

stats <- calc_stats(df_validate_full, holdout_covariates, add_1 = TRUE)

plots <- list()

for (covariate in holdout_covariates) {
  if (covariate == 'content_crashes') break
  stats_rel <- stats %>% filter(label == 'release') %>% select(covariate, metric)
  means <- stats_rel[stats_rel$metric == 'mean', covariate]
  medians <- stats_rel[stats_rel$metric == 'median', covariate]
  ho_means <- stats %>% filter(label == 'beta' & metric == 'mean') %>% select(covariate)

  plots[[covariate]] <- compare_log_cont(df_validate_full, covariate, means, medians, as.numeric(ho_means), print=FALSE) 
}

plot_grid(plotlist = plots, ncol = 2)
```

## Training Covariates

The following covariates were used in training the v67 model. Note that the environment covariates were trained on the numerical versions, but have been converted to categories for plotting.

```{r summary_training_covs, echo=FALSE, warning=FALSE}
stats_pre <- calc_delta(df_validate, NULL, cont_log_covariates) 
stats_post <- calc_delta(df_validate_matched, NULL, cont_log_covariates)

stats_pre_v67 <- calc_delta(df_train, NULL, cont_log_covariates)
stats_post_v67 <- calc_delta(df_matched, NULL, cont_log_covariates)

rows <- c('pre-matching: v67', 'post-matching: v67', 'pre-matching: v68', 'post-matching: v68')

stats_mean <- stats_pre_v67[1, ] %>% 
  rbind(stats_post_v67[1, ]) %>%
  rbind(stats_pre[1, ]) %>%
  rbind(stats_post[1, ]) %>%
  set_rownames(rows)

stats_median <- stats_pre_v67[2, ] %>% 
  rbind(stats_post_v67[2, ]) %>%
  rbind(stats_pre[2, ]) %>%
  rbind(stats_post[2, ]) %>%
  set_rownames(rows)
```

### Beta-Release Difference: Mean
```{r summary_training_covs_mean_tbl, echo=FALSE, warning=FALSE}
knitr::kable(stats_mean) %>%
  kable_styling() %>%
  scroll_box(width = "900px", height = "400px")
```

###  Beta-Release Difference: Median

```{r summary_training_covs_median_tbl, echo=FALSE, warning=FALSE}
knitr::kable(stats_median) %>%
  kable_styling() %>%
  scroll_box(width = "900px", height = "400px")
```

### Training Dataset Continuous Covariates: v67
```{r training_cont_log_cov_plots, fig.width=10, fig.height=50, echo=FALSE}
stats <- calc_stats(df_validate_full, cont_log_covariates, add_1 = TRUE)

plots <- list()

for (covariate in cont_log_covariates) {
  stats_rel <- stats %>% filter(label == 'release') %>% select(covariate, metric)
  means <- stats_rel[stats_rel$metric == 'mean', covariate]
  medians <- stats_rel[stats_rel$metric == 'median', covariate]
  ho_means <- stats %>% filter(label == 'beta' & metric == 'mean') %>% select(covariate)

  plots[[covariate]] <- compare_log_cont(df_validate_full, covariate, means, medians, as.numeric(ho_means), print=FALSE) 
}
```

```{r training_cont_log_cov_plotted, fig.width=10, fig.height=50, echo=FALSE}
plot_grid(plotlist = plots, ncol = 2)
```

### Training Dataset Categorical Covariates: v67

```{r training_cat_cov_orderder, echo=FALSE}
# Hacked due to not having foresight in ordering beforehand...

if (!'default_search_engine' %in% cat_covariates) {
  cat_covariates <- c(cat_covariates, 'default_search_engine')
}

df_training_full <- df_training_full %>%
  mutate(cpu_cores_cat = ordered(cpu_cores_cat, 
                                 levels <- c('1', '2', '< 4', '< 8', '< 16', '> 16'))) %>%
  mutate(cpu_speed_cat = ordered(cpu_speed_cat, 
                                 levels <- c("< 1GHz", "< 2GHz", "< 3GHz", "< 4GHz", "> 16GHz"))) %>% 
  mutate(memory_cat = ordered(memory_cat, 
                              levels <- c('< 1GB', '< 2GB', '< 4GB', '< 6GB', '< 16GB', '> 16GB'))) %>%
  mutate(profile_age_cat = ordered(profile_age_cat,
                                   levels <- c("< 1 week",  "< 1 month", 
                                               "< 6 months", "< 2 years", "< 5 years", "> 5 years")))
```

```{r training_cat_cov_plotted, fig.width=10, fig.height=20, echo=FALSE}
plots <- list()

for (i in 1:length(cat_covariates)) {
  covariate <- cat_covariates[i]
  if (i!=1) plots[[covariate]] <- compare_cat(df_training_full, covariate, 
                                              limit = 10, plot = FALSE, add_legend=FALSE)
  else plots[[covariate]] <- compare_cat(df_training_full, covariate, limit = 10, plot = FALSE)
}

plot_grid(plotlist = plots, ncol = 2)
```

### Validation Dataset Continuous Covariates: v68

```{r validation_cont_log_cov_plots, fig.width=10, fig.height=50, echo=FALSE}
stats <- calc_stats(df_validate_full, cont_log_covariates, add_1 = TRUE)

plots <- list()

for (covariate in cont_log_covariates) {
  stats_rel <- stats %>% filter(label == 'release') %>% select(covariate, metric)
  means <- stats_rel[stats_rel$metric == 'mean', covariate]
  medians <- stats_rel[stats_rel$metric == 'median', covariate]
  ho_means <- stats %>% filter(label == 'beta' & metric == 'mean') %>% select(covariate)

  plots[[covariate]] <- compare_log_cont(df_validate_full, covariate, means, medians, as.numeric(ho_means), print=FALSE) 
}
```

```{r validation_cont_log_cov_plotted, fig.width=10, fig.height=50, echo=FALSE}
plot_grid(plotlist = plots, ncol = 2)
```

### Validation Dataset Categorical Covariates: v68

```{r validation_cat_cov_orderder, echo=FALSE}
# Hacked due to not having foresight in ordering beforehand...
df_validate_full <- df_validate_full %>%
  mutate(cpu_cores_cat = ordered(cpu_cores_cat, 
                                 levels <- c('1', '2', '< 4', '< 8', '< 16', '> 16'))) %>%
  mutate(cpu_speed_cat = ordered(cpu_speed_cat, 
                                 levels <- c("< 1GHz", "< 2GHz", "< 3GHz", "< 4GHz", "> 16GHz"))) %>% 
  mutate(memory_cat = ordered(memory_cat, 
                              levels <- c('< 1GB', '< 2GB', '< 4GB', '< 6GB', '< 16GB', '> 16GB'))) %>%
  mutate(profile_age_cat = ordered(profile_age_cat,
                                   levels <- c("< 1 week",  "< 1 month", 
                                               "< 6 months", "< 2 years", "< 5 years", "> 5 years")))
```

```{r validation_cat_cov_plotted, fig.width=10, fig.height=20, echo=FALSE}
plots <- list()

for (i in 1:length(cat_covariates)) {
  covariate <- cat_covariates[i]
  if (i!=1) plots[[covariate]] <- compare_cat(df_validate_full, covariate, 
                                              limit = 10, plot = FALSE, add_legend=FALSE)
  else plots[[covariate]] <- compare_cat(df_validate_full, covariate, limit = 10, plot = FALSE)
}

plot_grid(plotlist = plots, ncol = 2)
```

# Discussion

The matching yielded a subset that was similarly representative to v67 as to v68 for most of the covariates reviewed. However, for a subset of covariates, the difference between channels actually increased (e.g., `profile_age`, `default_search_engine`), or are distinctly different than Release before and after matching, namely `MEMORY_TOTAL`. This latter covariate requires further investigation as why its distribution is significantly more spread to higher values than for Release.

## Next Steps
This methodology is an initial step towards providing an additional set of Firefox Release Heatlth metrics derived from the Beta release population. Additional work to realize this goal include:

* Address the full country and locale distributions 
* Investigate other model architectures that utilize nominal/categorical covariates
* Additional feature/covariate generation 
     - locale
     - additional environmental (e.g., HDD/SDD)
     - additional performance metrics 
          - Especially those influencing WebRender and Fission
     - crash
* Research into [covariate selection](https://metrics.mozilla.com/protected/cdowhygelund/beta_subset_release.html#covariate_selection) for matching models

### 2019-09-24 supporting_funcs.R

@@ -6,7 +6,7 @@ library(tidyr)
 library(tidyselect)
 library(MatchIt)
 
-#### Helpers
+#### Helpers ####
 # TODO remove `tr_cov` arg
 calc_means <- function(df.match, tr_cov, ho_cov, add_1 = FALSE){
   # Validation
@@ -121,13 +121,16 @@ normalize_distro_id <- function(distro_id){
 }
 
 normalize_profile_age <- function(profile_age){
-  case_when(
-    profile_age < 7 ~ "< 1 week",
-    profile_age < 31 ~ "< 1 month",
-    profile_age < 180 ~ "< 6 months",
-    profile_age < (365 * 2) ~ "< 2 years",
-    profile_age < (365 * 5) ~ "< 5 years",
-    TRUE ~ "> 5 years"
+  levels <- c("< 1 week",  "< 1 month", "< 6 months", "< 2 years", "< 5 years", "> 5 years")
+  factor(
+    case_when(
+      profile_age < 7 ~ levels[1],
+      profile_age < 31 ~ levels[2],
+      profile_age < 180 ~ levels[3],
+      profile_age < (365 * 2) ~ levels[4], 
+      profile_age < (365 * 5) ~ levels[5],
+      TRUE ~ levels[6]
+    ), levels = levels, ordered = TRUE
   )
 }
 
@@ -136,41 +139,49 @@ normalize_timezone <- function(timezone){
 }
 
 normalize_memory <- function(memory){
+  levels <- c('< 1GB', '< 2GB', '< 4GB', '< 6GB', '< 16GB', '> 16GB')
   gb <- memory / 1024
-  case_when(
-    gb <= 1 ~ "< 1GB",
-    gb <= 2 ~ "< 2GB",
-    gb <= 4 ~ "< 4GB",
-    gb <= 6 ~ "< 6GB",
-    gb <= 16 ~ "< 16GB",
-    TRUE ~ "> 16GB"
+  factor(
+    case_when(
+      gb <= 1 ~ levels[1],
+      gb <= 2 ~ levels[2],
+      gb <= 4 ~ levels[3],
+      gb <= 6 ~ levels[4],
+      gb <= 16 ~ levels[5],
+      TRUE ~ levels[6]
+    ), levels = levels, ordered = TRUE
   )
 }
 
 normalize_cpu_speed <- function(cpu_speed){
[…]

### 2019-09-24 report_validation.Rmd
Adding paragraph noting hold-out covariates and their utility.

@@
 
+The usage of a performance metrics hold-out set is not necessary, when applying the model across versions.
+However, [research has shown](https://metrics.mozilla.com/protected/cdowhygelund/beta_subset_release.html#covariate_selection) that optimal feature selection for statistical matching uses the effects (e.g., hold-out covariates) rather than the response (e.g., whether it is Beta or Release) typical of predictive modeling.
+Therefore, knowledge of the metrics of concern before matching occurs is key.
+
 ## Next Steps

### 2019-10-01 poc/method_validation.Rmd
Moving reports over

---
title: 'Beta to Release Matching: Method Validation'
author: "Corey Dow-Hygelund"
date: "9/19/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r imports, warning=FALSE, message=FALSE, echo=FALSE}
source('supporting_funcs.R')
library(kableExtra)
library(cowplot)
```

# Technique

* Apply same data cleaning, covariate/feature generation, and sampling as in [proof-of-concept](https://metrics.mozilla.com/protected/cdowhygelund/beta_subset_release.html)
    - Apply to v67 and v68 datasets
    - **NOTE** Should we sample clients from both versions? 
* Train model (apply matching) to v67
    - Review diagnostics
* Validated against v68
    1. Find all clients in v67 sample 
    2. Review diagnostics

# Data Loading

Follow the same protocol in the [previous work](https://metrics.mozilla.com/protected/cdowhygelund/modeling_poc.Rmd). For this case v67 data is used for modeling, and v68 is used for validation.

```{r}
# define response field
label <- 'is_release'

load_df <- function(file_path){
  df <- read.csv(file_path) %>%
  select(-c(CONTENT_PAINT_TIME_PARENT, COMPOSITE_TIME_CONTENT, COMPOSITE_TIME_PARENT, CONTENT_FRAME_TIME_PARENT)) %>% # All NAs 
  select(-e10s_enabled) %>% # All True
  mutate(default_search_engine = as.factor(normalize_search_engine(default_search_engine))) %>%
  mutate(profile_age_cat = as.factor(normalize_profile_age(profile_age))) %>%
  mutate(distro_id_norm = as.factor(normalize_distro_id(distribution_id))) %>%
  mutate(timezone_cat = as.factor(normalize_timezone(timezone_offset))) %>%
  mutate(memory_cat = as.factor(normalize_memory(memory_mb))) %>% 
  mutate(cpu_speed_cat = as.factor(normalize_cpu_speed(cpu_speed_mhz))) %>% 
  mutate(cpu_cores_cat = as.factor(normalize_cpu_cores(cpu_cores))) %>% 
  mutate(!!label := case_when(
    label == 'beta' ~ FALSE,
    TRUE ~ TRUE)) %>%
  filter(startup_ms >= 0 & profile_age >= 0)

  # complete cases (specifically targets perf metrics) and remove profiles in both Beta and Release
  df_c <- df %>% 
    na.omit() %>%
    mutate()
  return(df_c)
}

df_train <- load_df('data/Validation/df_67.csv')
df_validate <- load_df('data/Validation/df_68.csv')
```

# Sampling
Oversampling Beta by 4x and downsampling this result to 100K records.

```{r}
build_df <- function(df_c, multiple){
  df_beta <- df_c %>% filter(is_release == FALSE)
  df_rel <- df_c %>% filter(is_release == TRUE)
  n_beta <- nrow(df_beta)

  df <- df_rel %>%
    sample_n(size = round(n_beta / multiple)) %>%
    rbind(df_beta)

  return(df)
}

df_train_4x <- build_df(df_train, 4) %>% sample_n(size = 100000)
# df_validate_4x <- build_df(df_validate, 4) %>% sample_n(size = 100000)
```

Determine the number of training (v67) Beta and Release clients that are in the validation set (v68)

```{r}
mutual_clients <- df_train_4x[, c('client_id', 'label')] %>% 
  inner_join(df_validate[, c('client_id', 'label')]) %>% 
  count(label)

mutual_clients
```

Compare this to existing distribution

```{r}
df_train_4x %>% 
  count(label)
```

Okay, not bad most training clients (~70%) are in validation. See how this holds after matching.

# Modeling

```{r covariate_groups}
model_covs <- c('search_count', 'daily_max_tabs', 'daily_num_sessions_started', 'num_addons', 
                              'num_bookmarks', 'profile_age', 'timezone_offset', 'cpu_speed_mhz',
                              'memory_mb', 'cpu_cores')

holdout_covariates <- c("CONTENT_PAINT_TIME_CONTENT", "TIME_TO_DOM_CONTENT_LOADED_END_MS", 
                        "MEMORY_TOTAL", "TIME_TO_DOM_COMPLETE_MS", "FX_PAGE_LOAD_MS_2_PARENT", 
                        "FX_TAB_SWITCH_TOTAL_E10S_MS",
                        "CONTENT_FRAME_TIME_GPU", "COMPOSITE_TIME_GPU",
                        "TIME_TO_LOAD_EVENT_END_MS", 'startup_ms', 'content_crashes')

cont_log_covariates <- c('active_hours', 'daily_max_tabs', 'daily_tabs_opened', 'search_count',
                         'daily_unique_domains', 'daily_num_sessions_started', 
                         'num_bookmarks', 'num_addons', 'num_active_days', 'num_pages', 'uri_count',
                         'session_length', 'profile_age')

cat_covariates <- c('country', 'timezone_cat', 'distro_id_norm', 'profile_age_cat', 'cpu_cores_cat',
                    'memory_cat', 'cpu_speed_cat', 'default_search_engine')

```

The best model from previous work:

```{r model_train}
formula <- generate_formula(model_covs, label = label)

nn.ma <- matchit(formula, df_train_4x, 'nearest', distance='mahalanobis')

df_matched <- match.data(nn.ma) 
```
```{r export_model, warning=FALSE, message=FALSE, echo=FALSE}
save.image('data/Validation/analysis_09182019_corr.RData')
```

```{r summary_mean_tbl}
stats_pre <- calc_delta(df_train_4x, NULL, holdout_covariates) %>%
  select(-'content_crashes')
stats_post <- calc_delta(df_matched, NULL, holdout_covariates) %>%
  select(-'content_crashes')

stats_mean <- stats_pre[1, ] %>% 
  rbind(stats_post[1, ]) %>%
  set_rownames(c('pre-matching', 'post-matching'))

stats_median <- stats_pre[2, ] %>% 
  rbind(stats_post[2, ]) %>%
  set_rownames(c('pre-matching', 'post-matching'))

knitr::kable(stats_mean) %>%
  kable_styling() %>%
  scroll_box(width = "750px", height = "200px")

```

```{r perf_holdout, fig.width=10, fig.height=50, echo=FALSE}
df_full <- df_matched %>% 
  select(-c(distance, weights)) %>%
  filter(label == 'beta') %>%
  mutate(label =  'beta - matched') %>%
  rbind(df_train)

stats <- calc_stats(df_matched, holdout_covariates, add_1 = TRUE)

plots <- list()

for (covariate in holdout_covariates) {
  stats_rel <- stats %>% filter(label == 'release') %>% select(covariate, metric)
  means <- stats_rel[stats_rel$metric == 'mean', covariate]
  medians <- stats_rel[stats_rel$metric == 'median', covariate]
  ho_means <- stats %>% filter(label == 'beta' & metric == 'mean') %>% select(covariate)

  plots[[covariate]] <- compare_log_cont(df_full, covariate, means, medians, as.numeric(ho_means), print=FALSE) 
}

plot_grid(plotlist = plots, ncol = 1)

# for (covariate in holdout_covariates) {
#   compare_log_cont(df_full, covariate) 
#}
```

# Validation

Subset the validation clients down to those matched

```{r}
df_validate_matched <- df_validate %>%
  filter(client_id %in% df_matched$client_id)

df_validate_matched %>%
  count(label)
```

## Holdout Covariates

```{r summary_validate_mean_tbl}
stats_pre <- calc_delta(df_validate, NULL, holdout_covariates) %>%
  select(-'content_crashes')
stats_post <- calc_delta(df_validate_matched, NULL, holdout_covariates) %>%
  select(-'content_crashes')

stats_mean <- stats_pre[1, ] %>% 
  rbind(stats_post[1, ]) %>%
  set_rownames(c('pre-matching', 'post-matching'))

stats_median <- stats_pre[2, ] %>% 
  rbind(stats_post[2, ]) %>%
  set_rownames(c('pre-matching', 'post-matching'))

knitr::kable(stats_mean) %>%
  kable_styling() %>%
  scroll_box(width = "750px", height = "200px")

```

```{r}
knitr::kable(stats_median) %>%
  kable_styling() %>%
  scroll_box(width = "750px", height = "200px")
```

```{r perf_holdout, fig.width=10, fig.height=50, echo=FALSE}
df_validate_full <- df_validate_matched %>% 
  # select(-c(distance, weights)) %>%
  filter(label == 'beta') %>%
  mutate(label =  'beta - matched') %>%
  rbind(df_validate) %>% 
  distinct()

stats <- calc_stats(df_validate_full, holdout_covariates, add_1 = TRUE)

plots <- list()

for (covariate in holdout_covariates) {
  stats_rel <- stats %>% filter(label == 'release') %>% select(covariate, metric)
  means <- stats_rel[stats_rel$metric == 'mean', covariate]
  medians <- stats_rel[stats_rel$metric == 'median', covariate]
  ho_means <- stats %>% filter(label == 'beta' & metric == 'mean') %>% select(covariate)

  plots[[covariate]] <- compare_log_cont(df_validate_full, covariate, means, medians, as.numeric(ho_means), print=FALSE) 
}

# for (covariate in holdout_covariates) {
#   compare_log_cont(df_full, covariate) 
#}
```

```{r perf_holdout, fig.width=10, fig.height=50, echo=FALSE}
plot_grid(plotlist = plots, ncol = 1)
```

## Training/Engagement Covariates

```{r summary_validate_mean_tbl}
stats_pre <- calc_delta(df_validate, NULL, cont_log_covariates) 
stats_post <- calc_delta(df_validate_matched, NULL, cont_log_covariates)

stats_mean <- stats_pre[1, ] %>% 
  rbind(stats_post[1, ]) %>%
  set_rownames(c('pre-matching', 'post-matching'))

stats_median <- stats_pre[2, ] %>% 
  rbind(stats_post[2, ]) %>%
  set_rownames(c('pre-matching', 'post-matching'))

knitr::kable(stats_mean) %>%
  kable_styling() %>%
  scroll_box(width = "750px", height = "200px")

```

```{r}
knitr::kable(stats_median) %>%
  kable_styling() %>%
  scroll_box(width = "750px", height = "200px")
```

```{r cont_log_cov_plots, fig.width=10, fig.height=50, echo=FALSE}
stats <- calc_stats(df_validate_full, cont_log_covariates, add_1 = TRUE)

plots <- list()

for (covariate in cont_log_covariates) {
  stats_rel <- stats %>% filter(label == 'release') %>% select(covariate, metric)
  means <- stats_rel[stats_rel$metric == 'mean', covariate]
  medians <- stats_rel[stats_rel$metric == 'median', covariate]
  ho_means <- stats %>% filter(label == 'beta' & metric == 'mean') %>% select(covariate)

  plots[[covariate]] <- compare_log_cont(df_validate_full, covariate, means, medians, as.numeric(ho_means), print=FALSE) 
}
```

```{r cont_log_cov_plotted, fig.width=10, fig.height=50, echo=FALSE}
plot_grid(plotlist = plots, ncol = 1)
```

Categorical

```{r cat_cov_plotted, fig.width=10, fig.height=50, echo=FALSE}
plots <- list()

for (covariate in cat_covariates){
  plots[[covariate]] <- compare_cat(df_validate_full, covariate, limit = 10, plot = FALSE)
}

plot_grid(plotlist = plots, ncol = 1)
```

### 2019-10-01 poc/report_poc.Rmd
Moving reports over

--- 2019-09-11 report_poc.Rmd
@@
 ---
-title: "Beta to Release Matching"
+title: "Beta to Release Matching: Proof-of-Concept"
 author: "Corey Dow-Hygelund, Mozilla Data Science"
@@
     - daily_unique_domains
-    - daily_num_sessions_started
     - daily_tabs_opened

### 2019-10-02 perf_release_criteria/data_prep/Beta_Release_Matching/Beta_Release_Subsetting_Data_Preparation.py
Adding initial take on data export.

@@ -1,0 +1,442 @@
+# Databricks notebook source
+# MAGIC %md # Imports
+
+# COMMAND ----------
+
+import pyspark.sql.functions as F
+import pyspark.sql.types as T
+from pyspark.sql import Window
+import datetime as dt
+from io import StringIO
+import boto3
+import pandas as pd
+
+# COMMAND ----------
+
+# MAGIC %md **TODO**
+# MAGIC 
+# MAGIC 1. Join Release and Beta pyspark Data Frames
+# MAGIC 2. Serialize as parquet rather than pandas
+# MAGIC 3. Append rather than overwrite? 
+# MAGIC 
+# MAGIC 2. Remove country filters
+# MAGIC 3. Remove locale filters
+# MAGIC    - Should this be a separate job at first?
+
+# COMMAND ----------
+
+# MAGIC %md # Configuration
+
+# COMMAND ----------
+
+# MAGIC %md
+# MAGIC * Limit to 1 week of pings per client
+# MAGIC 
+# MAGIC **TBD**
+# MAGIC * Limit to 2 week collection interval for Beta
+
+# COMMAND ----------
+
+NUM_DAYS = 7
+NUM_WEEKS  = 2
+
+DATA_BUCKET = "net-mozaws-prod-us-west-2-pipeline-analysis"
+DATA_PATH = 'cdowhygelund/beta_release_matching/perf_criteria/v0/2week_US'
+
+# COMMAND ----------
+
+cd = spark.table('clients_daily')
+ms = spark.table('main_summary')
+
+# COMMAND ----------
+
+# MAGIC %md # Metrics
+
+# COMMAND ----------
+
+sum_int_metrics = {'active_hours_sum': 'active_hours',
+                   'scalar_parent_browser_engagement_total_uri_count_sum': 'uri_count',
+                   'subsession_hours_sum': 'session_length',
+                   'search_count_all': 'search_count',
+                   'crashes_detected_content_sum': 'content_crashes'
+                  }
+
+mean_int_metrics = {'places_bookmarks_count_mean': 'num_bookmarks',                      
+                    'places_pages_count_mean': 'num_pages',            
+                    'scalar_parent_browser_engagement_unique_domains_count_mean': 'daily_unique_domains',
[…]

### 2019-10-02 perf_release_criteria/data_prep/Beta_Release_Matching/Beta_Release_Subsetting_Data_Preparation.py
Adding new covariates. Modifying engagement covariates aggregation to mean rather than sum.

@@ -15,6 +15,14 @@ import pandas as pd
 
 # MAGIC %md **TODO**
 # MAGIC 
+# MAGIC 1. Deal with summed metrics
+# MAGIC  - How can we handle a variable size window
+# MAGIC    - need to normalize by # of days (i.e. mean over days)
+# MAGIC 
+# MAGIC * Modify filtering to realistic values
+# MAGIC  - Will increase sample size
+# MAGIC  - rerun validation
+# MAGIC    
 # MAGIC 1. Join Release and Beta pyspark Data Frames
 # MAGIC 2. Serialize as parquet rather than pandas
 # MAGIC 3. Append rather than overwrite? 
@@ -22,6 +30,15 @@ import pandas as pd
 # MAGIC 2. Remove country filters
 # MAGIC 3. Remove locale filters
 # MAGIC    - Should this be a separate job at first?
+
+# COMMAND ----------
+
+# MAGIC %md Feature Additions
+# MAGIC 1. Min/max startup times
+# MAGIC 2. Full distribution of histograms
+# MAGIC 3. content crashes features
+# MAGIC 4. max search counts, etc.. of all engangement metrics
+# MAGIC 5. 
 
 # COMMAND ----------
 
@@ -54,21 +71,28 @@ ms = spark.table('main_summary')
 
 # COMMAND ----------
 
-sum_int_metrics = {'active_hours_sum': 'active_hours',
-                   'scalar_parent_browser_engagement_total_uri_count_sum': 'uri_count',
-                   'subsession_hours_sum': 'session_length',
-                   'search_count_all': 'search_count',
-                   'crashes_detected_content_sum': 'content_crashes'
-                  }
-
-mean_int_metrics = {'places_bookmarks_count_mean': 'num_bookmarks',                      
-                    'places_pages_count_mean': 'num_pages',            
-                    'scalar_parent_browser_engagement_unique_domains_count_mean': 'daily_unique_domains',
-                    'scalar_parent_browser_engagement_max_concurrent_tab_count_max': 'daily_max_tabs',
-                    'scalar_parent_browser_engagement_tab_open_event_count_sum': 'daily_tabs_opened',
-                    'first_paint_mean': 'startup_ms',
[…]

### 2019-10-02 poc/data_prep/Beta_Release_Matching/Beta_Release_Matching_Perf_Metrics_Validation_2weeks.py
Adding new covariates. Modifying engagement covariates aggregation to mean rather than sum.

@@ -1,0 +1,445 @@
+# Databricks notebook source
+# MAGIC %md # Description
+
+# COMMAND ----------
+
+# MAGIC %md This is the same as `Beta_Release_Matching_Perf_Metrics_Validation`, with the time windows reduced by half to reflect the reduced launch timeframe from 7 to 4 weeks.
+# MAGIC 
+# MAGIC In addition, the mean of the engagement metrics was taken, rather than the sum. This enables the usage of a sliding windows of differing length for Beta and Release.
+# MAGIC 
+# MAGIC Finally, additional covariates were added for potential usage. 
+
+# COMMAND ----------
+
+# MAGIC %md # Imports
+
+# COMMAND ----------
+
+import pyspark.sql.functions as F
+import pyspark.sql.types as T
+from pyspark.sql import Window
+import datetime as dt
+from io import StringIO
+import boto3
+import pandas as pd
+
+# COMMAND ----------
+
+# MAGIC %md Lots of prior art from [David Zeber's ESPER project](https://metrics.mozilla.com/~dzeber/notebooks/esper/esper-main-summary_model.html)
+
+# COMMAND ----------
+
+# MAGIC %md
+# MAGIC * Beta and Release subsets
+# MAGIC   - Training: V67
+# MAGIC   - Validation: V68
+# MAGIC   - Beta: Last two weeks 
+# MAGIC   - Release: First two weeks
+# MAGIC   - en-US, en-GB locales
+# MAGIC   - US, GB country
+
+# COMMAND ----------
+
+NUM_DAYS = 7
+NUM_WEEKS  = 2
+
+DATA_BUCKET = "net-mozaws-prod-us-west-2-pipeline-analysis"
+DATA_PATH = 'cdowhygelund/beta_release_matching/2week_US/engage_means/Validation'
+
+# COMMAND ----------
+
+cd = spark.table('clients_daily')
+ms = spark.table('main_summary')
+
+# COMMAND ----------
+
+# MAGIC %md # Metrics
+
+# COMMAND ----------
+
+sum_int_metrics = {
+  # 'active_hours_sum': 'active_hours',
+#                    'scalar_parent_browser_engagement_total_uri_count_sum': 'uri_count',
+#                    'subsession_hours_sum': 'session_length',
[…]

### 2019-10-04 perf_release_criteria/data_prep/Beta_Release_Matching/Beta_Release_Subsetting_Data_Preparation.py
Fiixing bad cut and paste errors. Adding description and TBD text.

@@ -1,4 +1,40 @@
 # Databricks notebook source
+# MAGIC %md # Description
+# MAGIC 
+# MAGIC Generates training, prediction, and validation datasets. See [PRD](https://docs.google.com/document/d/1Ygz6MkudYHZjnDnD9Z97kUyFrvV3KGWsjXyPjddhHq0/edit#heading=h.x5t09uq91x6z) for further details. 
+# MAGIC 
+# MAGIC * Handles variable size windows for Beta and Release
+# MAGIC   - Configurable:
+# MAGIC       - _maximum_ size window for submission date
+# MAGIC       - window size used for aggregating client pings
+# MAGIC   - Means w.r.t. submission date are taken
+# MAGIC   - **WARNING**: Crash counts however are summed. Therefore, comparing directly (e.g., training/validation) is not valid. 
+# MAGIC * Window size used 
+# MAGIC   * Beta     
+# MAGIC     - _startpoint_: Either Beta launch date or configured window size (whichever is first)
+# MAGIC     - _endpoint_: Release launch date 
+# MAGIC   * Release 
+# MAGIC     - _startpoint_: Release launch date 
+# MAGIC     - _endpoint_: Configured window size
+# MAGIC       - **NOTE**: This job focuses on the _most_ recent Release version. Therefore, the window can't go past the next launch date. 
+
+# COMMAND ----------
+
+# MAGIC %md # TBD
+# MAGIC The following will be flushed out as the other portions are implemented. 
+# MAGIC 
+# MAGIC * Export:
+# MAGIC   * Current: Pandas dataframe overwritten each run
+# MAGIC   * Proposed: GCP/Parquet table that is appened. This will be specified and implemented during milestone that automates this process into daily or weekly jobs. 
+# MAGIC * Splitting this process based upon countries and locales:
+# MAGIC   - Current: US/GB locale and country
+# MAGIC   - Proposed: US/GB locale/country 1 file and table, All other records another file and table?
+# MAGIC * Modifying filtering of outliers
+# MAGIC   - Current: Filters out 99.9 percentile 
[…]

### 2019-10-15 perf_release_criteria/scoring_algo_analysis.Rmd
Adding in testing out scoring methods. Cramer von Mises it is.

---
title: 'Milestone 2 Test: Scoring Algorithms'
output:
  html_document:
    df_print: paged
---

# tl;dr 
This is analysis to determine the feasibility of the various [scoring algorithms](https://docs.google.com/document/d/1SfuanvmYmvmEFAdQ7Z5djDeLezdNB1TESqVmj93O8to/edit#heading=h.w3huje1nj766) proposed in the modeling approach for this [PRD](https://docs.google.com/document/d/1Ygz6MkudYHZjnDnD9Z97kUyFrvV3KGWsjXyPjddhHq0/edit#heading=h.lvb9l8gw2nee).

```{r imports, echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(transport)
library(profmem)
```

# Method
* Utilize previous saved image from proof-of-concept validation
* Compare performance metrics of Beta to Release, without any matching. On test. 
* Benchmark computation time, and memory usage (if necessary)

```{r data_load, echo=FALSE}
load('data/milestone2/analysis_10022019_corr.RData')
```

# transport
1st, try out the `transport` library, to determine if Wasserstein distance will work with out dataset.

## Wasserstein
The relevant `transport` class appears to be a `pp`, or "discrete measures with some fixed mass at any of finitely many locations". Basically each instance corresponds to a mass = 1, and the corresponding metric values are coordinates to where that point is located.

1st, normalize each performance distributions to unit length. This puts them all on the same scale, so that the "cost" of transport is equal between the dimensions.

```{r}
perf_metrics <- c("TIME_TO_DOM_CONTENT_LOADED_END_MS","TIME_TO_DOM_COMPLETE_MS", "FX_PAGE_LOAD_MS_2_PARENT", "TIME_TO_LOAD_EVENT_END_MS")

norm <- function(x) return(x/sum(x))

df_norm <- df_train %>%
  select(perf_metrics, label) %>%
  na.omit() %>%
  mutate_at(vars(perf_metrics), norm)

beta <- df_norm %>% 
  filter(label == 'beta') %>%
  select(perf_metrics)
  # na.omit() #  %>%
  # mutate_all(norm)

release <- df_norm %>% 
  filter(label == 'release') %>% 
  select(perf_metrics)
  # na.omit() # %>%
  # mutate_all(norm)
```

Calculate the Wasserstein distance. It appears that the same number of instances must be in both distributions.
**NOTE**: Received `Error in gen_cost(x, y, 1) : std::bad_alloc` when using 85K records. Downsample to 30K.

```{r wassertstein, error=TRUE}
wd <- wasserstein(pp(beta %>% sample_n(30000)), pp(release %>% sample_n(30000)))
```

>>> Error: cannot allocate vector of size 6.7 Gb

Okay this isn't going to work. Reduce down to single dimension for the earth mover's distance. Use `FX_PAGE_LOAD_MS_2`. Utilize the original dataset values. Benchmark the time.

## EMD

### Pre-Matching
```{r emd}
beta <- df_train %>% 
  filter(label == 'beta') %>%
  select(perf_metrics) %>%
  na.omit()

release <- df_train %>% 
  filter(label == 'release') %>%
  select(perf_metrics) %>%
  na.omit()

system.time(emd <- wasserstein1d(beta$FX_PAGE_LOAD_MS_2_PARENT, release$FX_PAGE_LOAD_MS_2_PARENT))
print(emd)
```

That is reasonable for the use-case: ~10s for full dataset and all metrics. See memory usage:

```{r emd_mem}
emd_mem <- profmem(emd <- wasserstein1d(beta$FX_PAGE_LOAD_MS_2_PARENT, release$FX_PAGE_LOAD_MS_2_PARENT, p=2))
total(emd_mem)/(1024^2)
```

### Post-matching

```{r emd_matched}
beta_m <- df_matched %>% 
  filter(label == 'beta') %>%
  select(perf_metrics) %>%
  na.omit()

release_m <- df_matched %>% 
  filter(label == 'release') %>%
  select(perf_metrics) %>%
  na.omit()

system.time(emd <- wasserstein1d(beta_m$FX_PAGE_LOAD_MS_2_PARENT, release_m$FX_PAGE_LOAD_MS_2_PARENT))
print(emd)
```

## Cramér-von Mises
Try a Cramér-von Mises (`p=2`).

```{r cms}
system.time(cmd <- wasserstein1d(beta$FX_PAGE_LOAD_MS_2_PARENT, release$FX_PAGE_LOAD_MS_2_PARENT, p=2))
print(cmd)
```

This works also! Onto memory profiling.

```{r cms_mem}
cms_mem <- profmem(cmd <- wasserstein1d(beta$FX_PAGE_LOAD_MS_2_PARENT, release$FX_PAGE_LOAD_MS_2_PARENT, p=2))
total(cms_mem)/(1024^2)
```

### Post-matching

```{r cmd_matched}
system.time(cmd <- wasserstein1d(beta_m$FX_PAGE_LOAD_MS_2_PARENT, release_m$FX_PAGE_LOAD_MS_2_PARENT, p=2))
print(cmd)
```

### 2019-10-17 perf_release_criteria/scoring_algo_analysis.Rmd
Removing manual error message.
Cleaning up text.

@@
 # tl;dr 
-This is analysis to determine the feasibility of the various [scoring algorithms](https://docs.google.com/document/d/1SfuanvmYmvmEFAdQ7Z5djDeLezdNB1TESqVmj93O8to/edit#heading=h.w3huje1nj766) proposed in the modeling approach for this [PRD](https://docs.google.com/document/d/1Ygz6MkudYHZjnDnD9Z97kUyFrvV3KGWsjXyPjddhHq0/edit#heading=h.lvb9l8gw2nee).
+This analysis determines the feasibility of the various [scoring algorithms](https://docs.google.com/document/d/1SfuanvmYmvmEFAdQ7Z5djDeLezdNB1TESqVmj93O8to/edit#heading=h.w3huje1nj766) proposed in the modeling approach for this [PRD](https://docs.google.com/document/d/1Ygz6MkudYHZjnDnD9Z97kUyFrvV3KGWsjXyPjddhHq0/edit#heading=h.lvb9l8gw2nee).
+Cramér-von Mises appears to satisfy the requirements.
 
@@
 # Method
+
 * Utilize previous saved image from proof-of-concept validation
-* Compare performance metrics of Beta to Release, without any matching. On test. 
-* Benchmark computation time, and memory usage (if necessary)
+* Compare performance metrics of Beta to Release, without any matching. 
+* Compare performance metrics of Beta to Release, without matching.
+    - Observe reduction
+* Benchmark computation time, and memory usage
 
@@
 ```
-
->>> Error: cannot allocate vector of size 6.7 Gb
 

### 2019-10-17 perf_release_criteria/data_prep/subBeta_lib.py
Adding in supporting library for data preparation.

@@ -1,0 +1,188 @@
+# Databricks notebook source
+# MAGIC %md #Metrics
+
+# COMMAND ----------
+
+sum_int_metrics = {
+                    'crashes_detected_content_sum': 'content_crashes'
+                   }
+
+mean_int_metrics = {
+  'active_hours_sum': 'active_hours',
+  'scalar_parent_browser_engagement_total_uri_count_sum': 'uri_count',
+  'subsession_hours_sum': 'session_length',
+  'search_count_all': 'search_count',
+  'places_bookmarks_count_mean': 'num_bookmarks',                      
+  'places_pages_count_mean': 'num_pages',            
+  'scalar_parent_browser_engagement_unique_domains_count_mean': 'daily_unique_domains',
+  'scalar_parent_browser_engagement_max_concurrent_tab_count_max': 'daily_max_tabs',
+  'scalar_parent_browser_engagement_tab_open_event_count_sum': 'daily_tabs_opened',
+  'first_paint_mean': 'startup_ms',
+  'sessions_started_on_this_day': 'daily_num_sessions_started',
+ }
+
+max_int_metrics = {
+  'active_hours_sum': 'active_hours_max',
+  'scalar_parent_browser_engagement_total_uri_count_sum': 'uri_count_max',
+  'subsession_hours_sum': 'session_length_max',
+  'search_count_all': 'search_count_max',
+  'places_pages_count_mean': 'num_pages_max',            
+  'scalar_parent_browser_engagement_unique_domains_count_mean': 'daily_unique_domains_max',
+  'scalar_parent_browser_engagement_max_concurrent_tab_count_max': 'daily_max_tabs_max',
+  'scalar_parent_browser_engagement_tab_open_event_count_sum': 'daily_tabs_opened_max',
+  'first_paint_mean': 'startup_ms_max',
+  'sessions_started_on_this_day': 'daily_num_sessions_started_max',
+}
+
+
+probe_ms_map = {
+  # page load
+  'histogram_parent_fx_page_load_ms_2': 'FX_PAGE_LOAD_MS_2_PARENT',
+  'histogram_content_time_to_dom_complete_ms': 'TIME_TO_DOM_COMPLETE_MS',
+  'histogram_content_time_to_dom_content_loaded_end_ms': 'TIME_TO_DOM_CONTENT_LOADED_END_MS',
[…]

### 2019-10-17 perf_release_criteria/data_prep/subBeta_lib.py
Missing `locale`

@@ -123,6 +123,7 @@ def get_meta(df):
     F.when(F.isnull(df.sync_configured), False).otherwise(df.sync_configured).alias('sync_configured'),
     F.when(F.isnull(df.is_default_browser), False).otherwise(df.is_default_browser).alias('is_default_browser'),    
     # app 
+    df.locale,
     df.normalized_channel,
     df.app_version,
     F.when(F.isnull(df.distribution_id), 'mozilla-stock').otherwise(df.distribution_id).alias('distribution_id'),    

### 2019-10-18 perf_release_criteria/ms_2_dataset_generation.Rmd
Notebook for creating milestone 2 dataset and corresponding report.

---
title: 'Milestone 2: Datasets Generation'
output:
  html_document:
    df_print: paged
---

```{r imports, echo=FALSE, warning=FALSE, message=FALSE}
source('lib/supporting_funcs.R')
```

# tl;dr 
This notebook generates the training and validation datasets used to determine the model framework for this [PRD](https://docs.google.com/document/d/1Ygz6MkudYHZjnDnD9Z97kUyFrvV3KGWsjXyPjddhHq0/edit#heading=h.lvb9l8gw2nee). These datasets will be used for all steps in the process detailed out in the [document](https://docs.google.com/document/d/1SfuanvmYmvmEFAdQ7Z5djDeLezdNB1TESqVmj93O8to/edit#heading=h.nwwrif453n80).

# Dataset Preparation
The datasets were generated by this [notebook](https://dbc-caf9527b-e073.cloud.databricks.com/#notebook/210500/command/210501). The files were manually downloaded from S3 on hala.

# Covariate Generation
The following process is very similar to that used in the validation of the [proof-of-concept](https://metrics.mozilla.com/protected/cdowhygelund/beta_subset_release_validation.html). In addition:

* `na.omit` is not applied.
* OS is filtered to only Windows.

```{r var_defs, echo=FALSE}
outcomes <- c('TIME_TO_DOM_INTERACTIVE_MS', 'TIME_TO_DOM_CONTENT_LOADED_END_MS', 'TIME_TO_LOAD_EVENT_END_MS', 
              'TIME_TO_NON_BLANK_PAINT_MS', 'TIME_TO_DOM_COMPLETE_MS', 'FX_PAGE_LOAD_MS_2_PARENT')
```

```{r data_prep}
# define response field
label <- 'is_release'

load_df <- function(file_path){
  df <- read.csv(file_path) %>%
    filter(locale %in% c('en-US', 'en-GB')) %>%
    filter(country %in% c('US', 'GB')) %>%
    filter(os == 'Windows_NT') %>%
    select(-os, country, locale) %>%
    drop_na(outcomes) %>%
    mutate(default_search_engine = as.factor(normalize_search_engine(default_search_engine))) %>%
    mutate(profile_age_cat = as.factor(normalize_profile_age(profile_age))) %>%
    mutate(distro_id_norm = as.factor(normalize_distro_id(distribution_id))) %>%
    mutate(timezone_cat = as.factor(normalize_timezone(timezone_offset))) %>%
    mutate(memory_cat = as.factor(normalize_memory(memory_mb))) %>% 
    mutate(cpu_speed_cat = as.factor(normalize_cpu_speed(cpu_speed_mhz))) %>% 
    mutate(cpu_cores_cat = as.factor(normalize_cpu_cores(cpu_cores))) %>% 
    mutate(!!label := case_when(
      label == 'beta' ~ FALSE,
      TRUE ~ TRUE)) %>%
    filter(startup_ms >= 0 & profile_age >= 0)
}

df_train <- load_df('data/milestone2/df_pd_67.csv')
df_validate <- load_df('data/milestone2/df_pd_68.csv')
```

# Review

```{r summarize}
summary(df_train)
```

## Observations

* Content crashes looks strange. Always is 0. Not sure what happened there...
    - Appears to always be 0 
    - **Action**: Remove it
* Categories for `cpu_vendor`, and `os_version` have several low populated categories
    - Remap these categories to "Other"
* `city`, `geo_subdivision1`, and  `geo_subdivision2` are dominated by "other" categories.
    - **Action**: Remove them
*  `cpu_l3_cache_kb` and `cpu_stepping` have large number of NA's
    - **Action**: Remove them
*  `cpu_model` and `cpu_family` appear to be subcategories of `cpu_family`.
    - **Action**: Remove for modeling. 
    - **However**: These could (and other cpu fields) be added in for use in validation and slicing/segmentation.
* 'distribution_id` is redundant with `distro_id_norm`
    - **Action**: Remove it
* `cpu_l2_cache_kb` has a small number of NA
    - **Action**: Drop these rows as they are very small fraction. 
    - **Action**: Create a categorical variable to reflect other environment covariates.
* `install_year` and `profile_age` have unrealistic values
    - **Action**: Filter them out. `install_year` between 1990 and now. Profiles younger than 20 years. 
* `startup_ms` has crazy times
    - **Action**: The top 0.001% are being filtered already. Review to determine how these change with matching on performance metrics.
* Drop unused factors on `default_search_engine`, `is_wow64`

## Duplicate clients 
Find number of clients that are both in Beta and Release. This isn't a problem per se, it is just an interesting observation.

```{r}
df_train %>% count(client_id) %>% select(n) %>% table
```

Duplicate cients are really uncommon!

## Cleaning

Performing the proposed actions above

```{r cleaning, echo=FALSE, message=FALSE, warning=FALSE}
normalize_os_version <- function(os_version){
  levels <- c('Other', '6.1', '6.2', '6.3', '10.0')
  factor(
    case_when(
      os_version == '10.0' ~ levels[5],
      os_version == '6.3' ~ levels[4],
      os_version == '6.2' ~ levels[3],
      os_version == '6.1' ~ levels[2],
      TRUE ~ levels[1]
    ), levels = levels, ordered = TRUE
  )
}

normalize_cpu_vendor <- function(cpu_vendor){
  factor(
    case_when(
      cpu_vendor == 'AuthenticAMD' ~ 'AMD',
      cpu_vendor == 'GenuineIntel' ~ 'Intel',
      TRUE ~ 'Other'
    )
  )
}

normalize_cpu_l2_cache <- function(cpu_l2_cache){
  levels <- c('< 256', '< 512', '< 768', '< 1024', '> 1024')
  factor(
    case_when(
      cpu_l2_cache <= 256 ~ levels[1],
      cpu_l2_cache <= 512 ~ levels[2],
      cpu_l2_cache <= 768 ~ levels[3],
      cpu_l2_cache <= 1024 ~ levels[4],
      TRUE ~ levels[5]
    )
  )
}

stage_2_clean <- function(df){
  df_clean <- df %>%
    select(-c(city, geo_subdivision1, geo_subdivision2, cpu_l3_cache_kb, cpu_stepping, 
              cpu_model, cpu_family, distribution_id)) %>%
    filter(between(install_year, 1991, 2019)) %>%
    filter(profile_age <= 365 * 20 ) %>%
    na.omit() %>% 
    mutate(os_version = normalize_os_version(os_version)) %>%
    mutate(cpu_vendor = normalize_cpu_vendor(cpu_vendor)) %>%
    mutate(cpu_l2_cache_kb_cat = normalize_cpu_l2_cache(cpu_l2_cache_kb)) %>%
    droplevels()
  return(df_clean)
}

df_train_f <- stage_2_clean(df_train)
df_validate_f <- stage_2_clean(df_validate)

```

```{r}
summary(df_train_f)
```

# Serialize and push to GCP
Save the result dataset to an R image.

```{r serialize}
image_file_path <- paste('data/milestone2/df_train_validate_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
save(df_train_f, df_validate_f, file = image_file_path)
```

The push the results to GCP in the `moz-fx-dev-subbeta` bucket, under `r image_file_path`.

```{r gcp_storage_push, warning=FALSE}
Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
           "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")

library(googleCloudStorageR)

upload_try <- gcs_upload(image_file_path, name = image_file_path)
upload_try
```
```{r}
upload_try
```

### 2019-10-18 perf_release_criteria/ms_2_dataset_generation.Rmd
Cleaning up.

@@
 title: 'Milestone 2: Datasets Generation'
+date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
 output: 
   html_document:
-    df_print: paged
+    theme: cosmo
+    toc: true
+    toc_float: true
 ---
@@
 ```
-```{r}
-upload_try
-```

### 2019-10-21 perf_release_criteria/ms_2_dataset_generation.Rmd
Fixing issues with `client_id` as factor. Blows up memory.

@@
 title: 'Milestone 2: Datasets Generation'
-date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
 output:
@@
     theme: cosmo
-    toc: true
-    toc_float: true
+    toc: yes
+    toc_float: yes
+  pdf_document:
+    toc: yes
+date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
 ---
@@
   df <- read.csv(file_path) %>%
+    mutate(client_id = as.character(client_id)) %>%
     filter(locale %in% c('en-US', 'en-GB')) %>%

### 2019-10-21 perf_release_criteria/supporting_funcs.R
Initial library for calculating scores, and applying bootstrap replicates to modeling.

@@ -1,0 +1,210 @@
+library(dplyr)
+library(ggplot2)
+library(magrittr)
+library(tidyr)
+library(tidyselect)
+
+#### Helpers ####
+calc_means <- function(df.match, ho_cov, add_1 = FALSE){
+  ho_mean <- df.match %>% 
+    select(ho_cov, label) %>% 
+    mutate_all(function(x) if(is.numeric(x) && add_1) x+1 else x) %>%
+    group_by(label) %>% 
+    summarise_all(mean)
+  return(ho_mean)
+}
+
+calc_medians <- function(df.match, ho_cov, add_1 = FALSE){
+  ho_median <- df.match %>% 
+    select(ho_cov, label) %>% 
+    mutate_all(function(x) if(is.numeric(x) && add_1) x+1 else x) %>%
+    group_by(label) %>% 
+    summarise_all(median)
+  return(ho_median)
+}
+
+calc_delta <- function(df.match, tr_cov, ho_cov){
+  perc_diff <- function(x) abs(x[1]-x[2])/x[2]
+  means <- calc_means(df.match, tr_cov, ho_cov) %>%
+    select(-label) %>% 
+    summarise_all(perc_diff)
+  medians <- calc_medians(df.match, tr_cov, ho_cov) %>%
+    select(-label) %>% 
+    summarise_all(perc_diff)
+  df <- means %>% 
+    rbind(medians) %>% 
+    as.data.frame() %>%
+    set_rownames(c('means', 'medians'))
+  return(df)
+}
+
+# TODO: merge with `calc_delta`
+calc_stats <- function(df.match, ho_cov, add_1 = FALSE){
+  means <- calc_means(df.match, NULL, ho_cov, add_1 = add_1) %>%
+    mutate(metric = 'mean')
+  medians <- calc_medians(df.match, NULL, ho_cov, add_1 = add_1) %>%
+    mutate(metric = 'median')
+  df <- means %>% 
+    rbind(medians) %>% 
+    as.data.frame()
+  return(df)
+}
+
+#### Modeling Pipeline
+
+generate_formula <- function(tr_cov, label){
+  # Focus on linear and no-interactions
+  return(as.formula(paste(label, '~', paste(tr_cov, collapse="+"))))
+}
+
+#### Categorize continuous covariates
[…]

### 2019-10-21 perf_release_criteria/milestone_3/ms_2_dataset_generation.Rmd
Creating new `milestone 3` directory for analysis.

--- 2019-10-21 perf_release_criteria/ms_2_dataset_generation.Rmd
@@
 ```{r imports, echo=FALSE, warning=FALSE, message=FALSE}
-source('lib/supporting_funcs.R')
+source('../lib/supporting_funcs.R')
 ```
@@
 These datasets will be used for all steps in the process detailed out in the [document](https://docs.google.com/document/d/1SfuanvmYmvmEFAdQ7Z5djDeLezdNB1TESqVmj93O8to/edit#heading=h.nwwrif453n80).
+In addition, the bootstrap replicates for feature selection and hyperparameter tuning are created.
+These datasets are all stored in GCP under the `moz-fx-dev-cdowhyglund-subBeta` project.
 
@@
 * `na.omit` is not applied.
+* Missing values are only dropped for the performance metrics (outcomes) of concern
 * OS is filtered to only Windows.
@@
 
-df_train <- load_df('data/milestone2/df_pd_67.csv')
-df_validate <- load_df('data/milestone2/df_pd_68.csv')
+df_train <- load_df('../data/milestone2/df_pd_67.csv')
+df_validate <- load_df('../data/milestone2/df_pd_68.csv')
 ```
@@
 
-# Serialize and push to GCP
-Save the result dataset to an R image.
+# Bootstrap Samples
 
-```{r serialize}
-image_file_path <- paste('data/milestone2/df_train_validate_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
-save(df_train_f, df_validate_f, file = image_file_path)
+```{r balancing, echo=FALSE}
+channel_counts <- df_train_f %>% count(label)
+release_overcount <- channel_counts$n[channel_counts$label == 'release'] - channel_counts$n[channel_counts$label == 'beta']
 ```
 
-The push the results to GCP in the `moz-fx-dev-subbeta` bucket, under `r image_file_path`.
+The feature selection will utilize 10 boostrap replicates, which are generated as follows:
+1. The entire `df_train` dataset is sampled at 100% with replacement.
+2. A sample of Release (`is_release = TRUE`) `client_id` are taken of the same size as Beta (`r channel_counts$n[channel_counts$label == 'beta']`)
+3. The entire (resampled) Beta `client_id` are combined with this sampled Release ids. 
+    - These are the profiles that will be used for building the matching model. 
+    - The matched Beta profiles will be used for scoring the model. 
+4. The remaining Release ids will be used for scoring the model.
+
+The same set of bootstrap samples will be used for all feature selection across modeling algorithms.
+A suite of these are created to represent different levels of Beta oversampling with respect to Release.
+
+```{r bootstrap_def}
+extract_ids <- function(df_c, size, oversampling){
+  df_beta <- df_c %>% filter(is_release == FALSE)
+  df_rel <- df_c %>% filter(is_release == TRUE)
+  n_beta <- nrow(df_beta)
+
+  model_ids <- df_rel %>%
+    sample_n(size = round(n_beta / oversampling)) %>%
+    rbind(df_beta) %>%
+    pull(client_id)
+
+  # create the dataset for scoring matching model
+  test_ids <- df_rel %>% 
+    filter(!client_id %in% model_ids) %>%
+    pull(client_id)
+
+  return(list(train = model_ids, test = test_ids))
+}
+
+gen_bootstraps <- function(df_train, oversampling = 1, num_bts = 10){
+  bts <- list()
+  for (i in 1:num_bts){
+    # create a resampled version of entire dataframe
+    df_resampled <- df_train %>% sample_frac(replace = TRUE)
+    # create train/test "splits"
+    bts[[i]] <- extract_ids(df_resampled, oversampling = oversampling)
+  }
+  return(bts)
+}
+```
+
+```{r bootstrap_gen}
+bts.1x <- gen_bootstraps(df_train_f)
+bts.4x <- gen_bootstraps(df_train_f, oversampling = 4)
+bts.8x <- gen_bootstraps(df_train_f, oversampling = 8)
+bts.16x <- gen_bootstraps(df_train_f, oversampling = 16)
+```
+
+# Serialize and push to GCP
+Save the resultant dataset and bootstrap samples to an R image.
+
+```{r serialize_dataset}
+image_file_path <- paste('data/milestone2/df_train_validate_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
+save(df_train_f, df_validate_f, bts.1x, bts.4x, bts.8x, bts.16x,
+     file = image_file_path)
+```
+
+Then push the results to GCP in the `moz-fx-dev-subbeta` bucket, under `r image_file_path`.
 

### 2019-10-22 perf_release_criteria/milestone_3/ms_2_dataset_generation.Rmd
Moving bootstrap creation to this notebook.

@@
 
-df_train <- load_df('../data/milestone2/df_pd_67.csv')
-df_validate <- load_df('../data/milestone2/df_pd_68.csv')
+df_train <- load_df('data/df_pd_67.csv')
+df_validate <- load_df('data/df_pd_68.csv')
 ```
@@
 ```{r serialize_dataset}
-image_file_path <- paste('data/milestone2/df_train_validate_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
+image_file_name <- paste('df_train_validate_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
+image_file_path <- file.path('data', image_file_name)
 save(df_train_f, df_validate_f, bts.1x, bts.4x, bts.8x, bts.16x,
      file = image_file_path)
+
+gcs_file_path <- file.path('data', 'milestone2', image_file_name)
 ```
 
-Then push the results to GCP in the `moz-fx-dev-subbeta` bucket, under `r image_file_path`.
+Then push the results to GCP in the `moz-fx-dev-subbeta` bucket, under `r gcs_file_path`.
 
@@
 
-upload_try <- gcs_upload(image_file_path, name = image_file_path)
+upload_try <- gcs_upload(image_file_path, name = gcs_file_path)
 upload_try

### 2019-10-23 perf_release_criteria/milestone_3/feature_selection_boruta_initial.Rmd
Adding notebook for Boruta initial feature selection.

---
title: "Milestone 2: Feature Selection - Boruta"
output: html_notebook
---

```{r imports, echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(Boruta)
source('../lib/scoring.R')
```

# tl;dr
This analysis determines the relevant [covariates (features)](https://docs.google.com/document/d/1SfuanvmYmvmEFAdQ7Z5djDeLezdNB1TESqVmj93O8to/edit#heading=h.nwwrif453n80) to utilize for computationally intensive statistical matching algorithms proposed in the modeling approach for this [PRD](https://docs.google.com/document/d/1Ygz6MkudYHZjnDnD9Z97kUyFrvV3KGWsjXyPjddhHq0/edit#heading=h.lvb9l8gw2nee).

This analysis is focused on utilizing `Boruta` as a initial pre-filter to the covariates, to narrow the feature selection search space.

```{r data_load, echo=FALSE}
file_name = 'df_train_validate_20191021.RData'
image_file_path = file.path('data', file_name)

# Pull from GCP if necessary
# library(googleCloudStorageR)
# Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
#            "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")
# gcs_get_object(file.path('data', 'milestone2', file_name), saveToDisk = image_file_path, overwrite = TRUE)

load(image_file_path)
```

# Method

Apply `Boruta` to each performance covariate.

```{r var_def}
perf_metrics <- names(get_m2_metric_map())

set.seed(1234)
df_train_f_sm <- df_train_f %>%
   sample_n(20000)

df_fs <- df_train_f_sm %>%
   select(-perf_metrics) %>%
   select(-content_crashes) %>%
   select(-client_id) %>%
   select(-label) %>%
   select(-is_release) %>%
   select(-app_version)
```

```{r apply_boruta}
boruta_results <- list()

for (metric in perf_metrics){
  print(paste('Applying Boruta to ', metric))
   boruta.out <- Boruta(y = df_train_f_sm[[metric]], x=df_fs, doTrace=0)
  boruta_results[[metric]]  <- boruta.out
  # plot(boruta.out, cex.axis=.7, las=2, xlab="", main=metric) 
}
```

```{r boruta_plots}
for (metric in names(boruta_results)){
  plot(boruta_results[[metric]], cex.axis=.7, las=2, xlab="", main=metric) 
}
```

Find the top 5 ranking features per metric, and add to a list.

```{r aggregate_features_5}
features_top5 <- NULL
for(metric in names(boruta_results)){
  features_top5 <- c(names(sort(apply(boruta_results[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:5]), features_top5)
}

knitr::kable(data.frame(top5 = sort(c(unique(features_top5)))))
```

Increasing to 10:

```{r aggregate_features_10}
features_top10 <- NULL
for(metric in names(boruta_results)){
  features_top10 <- c(names(sort(apply(boruta_results[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:10]), features_top10)
}

knitr::kable(data.frame(top10 = sort(c(unique(features_top10)))))
```

## Equal Labels

Equalize by label, then perform the above.

```{r var_def_equal}
df_beta <- df_train_f %>% 
  filter(is_release == FALSE)
n_beta <- nrow(df_beta)
set.seed(1234)
df_rel <- df_train_f %>% 
  filter(is_release == TRUE) %>%
  sample_n(n_beta)

set.seed(1234)
df_train_f_sm_eq <- df_rel %>%
  bind_rows(df_beta) %>%
   sample_n(20000)

df_fs_eq <- df_train_f_sm_eq %>%
   select(-perf_metrics) %>%
   select(-content_crashes) %>%
   select(-client_id) %>%
   select(-label) %>%
   select(-is_release) %>%
   select(-app_version)
```

```{r apply_boruta_equal}
boruta_results_eq <- list()

for (metric in perf_metrics){
  print(paste('Applying Boruta to ', metric))
  boruta.out <- Boruta(y = df_train_f_sm_eq[[metric]], x=df_fs_eq, doTrace=0)
  boruta_results_eq[[metric]]  <- boruta.out
  # plot(boruta.out, cex.axis=.7, las=2, xlab="", main=metric) 
}
```

```{r boruta_plots_eq}
for (metric in names(boruta_results_eq)){
  plot(boruta_results_eq[[metric]], cex.axis=.7, las=2, xlab="", main=metric) 
}
```

```{r aggregate_features_5_eq}
features_top5 <- NULL
for(metric in names(boruta_results_eq)){
  features_top5 <- c(names(sort(apply(boruta_results_eq[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:5]), features_top5)
}

knitr::kable(data.frame(top5 = sort(c(unique(features_top5)))))
```

Increasing to 10:

```{r aggregate_features_10_eq}
features_top10 <- NULL
for(metric in names(boruta_results_eq)){
  features_top10 <- c(names(sort(apply(boruta_results_eq[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:10]), features_top10)
}

knitr::kable(data.frame(top10 = sort(c(unique(features_top10)))))
```

# Serialize and push to GCP
Save the resultant dataset and bootstrap samples to an R image.

```{r serialize_dataset}
image_file_name <- paste('feature_selection_boruta_initial_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
image_file_path <- file.path('data', image_file_name)
save(df_fs, df_fs_eq, boruta_results, boruta_results_eq, file = image_file_path)

gcs_file_path <- file.path('data', 'milestone2', image_file_name)
```

Then push the results to GCP in the `moz-fx-dev-subbeta` bucket, under `r gcs_file_path`.

```{r gcp_storage_push, warning=FALSE}
Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
           "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")

library(googleCloudStorageR)

upload_try <- gcs_upload(image_file_path, name = gcs_file_path)
upload_try
```

### 2019-10-23 perf_release_criteria/lib/scoring.R
Adding lib

@@ -1,0 +1,165 @@
+library(transport)
+library(dplyr)
+library(foreach)
+# library(doMC)
+library(doParallel)
+
+get_m2_metric_map = function(){
+  #' Get milestone 2 map of metrics to scoring weights
+  #'
+  #' @return A list of keys = metrics, values = weights
+  #' @export
+  #'
+  #' @examples get_m2_metric_map()
+  return(
+    c(
+      'FX_PAGE_LOAD_MS_2_PARENT' = 0.5,
+      'TIME_TO_DOM_INTERACTIVE_MS' =  0.10,
+      'TIME_TO_DOM_COMPLETE_MS' =  0.10,
+      'TIME_TO_LOAD_EVENT_END_MS' =  0.10,
+      'TIME_TO_DOM_CONTENT_LOADED_END_MS' =  0.10,
+      'TIME_TO_NON_BLANK_PAINT_MS' = 0.10
+    )
+  )
+}
+
+calc_cms <- function(metric, beta, release){
+  #' Calculate Cramér-von Mises distance 
+  #'
+  #' @param metric character. Field for distance calculation
+  #' @param beta data.frame. Contains beta measurements
+  #' @param release data.frame. Contains release measurements
+  #' @return numeric. Distance measure
+  #'
+  #' @examples get_m2_metric_map
+  cms <- wasserstein1d(beta[[metric]], release[[metric]], p=2)
+}
+
+calc_score <- function(df, metric_map){
+  #' Calculate Cramér-von Mises distance across a range of metrics, and weighted average the results
+  #' 
+  #' The metrics are normalized (min-max) before distance is calculated. 
+  #' Then the distances are averaged, with weights given by metric_map
+  #'
+  #' @param df data.frame. Contains measurements
+  #' @param label character. Field containing the various channels. 
+  #' @param metric_map list. Keys are metrics for distance calculation, values are weights for sum
+  #' @return numeric. Aggregated distance measure
+  #'
+  #' @examples calc_score(df)
+  if(missing(metric_map)) metric_map <- get_m2_metric_map()
+  metrics <- names(metric_map)
+  
+  norm <- function(x) return((x-min(x))/(max(x) - min(x)))
+  # norm <- function(x) return(x)
+  
+  df_norm <- df %>%
+    select(metrics, label) %>%
+    na.omit() %>%
+    mutate_at(vars(metrics), norm)
+  
+  beta <- df_norm %>% filter(label == 'beta')
[…]

### 2019-10-24 perf_release_criteria/milestone_3/feature_selection_nn_mahalanobis.Rmd
Adding nn experiment.

---
title: "Milestone 2: Feature Selection - Nearest Neighbors, Mahalanobis"
author: "Corey Dow-Hygelund, Mozilla Data Science"
date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_notebook:
    theme: cosmo
    toc: true
    toc_float: true
---

# tl;dr

This analysis determines the relevant [covariates (features)](https://docs.google.com/document/d/1SfuanvmYmvmEFAdQ7Z5djDeLezdNB1TESqVmj93O8to/edit#heading=h.nwwrif453n80) to utilize for computationally intensive statistical matching algorithms proposed in the modeling approach for this [PRD](https://docs.google.com/document/d/1Ygz6MkudYHZjnDnD9Z97kUyFrvV3KGWsjXyPjddhHq0/edit#heading=h.lvb9l8gw2nee).

**Matching Algorithm Tested**: Nearest-neighbors with Mahalanobis distance metric

```{r, echo=FALSE, warning=FALSE, message=FALSE}
source('../lib/supporting_funcs.R')
source('../lib/scoring.R')
library(MatchIt)
```

```{r data_load, echo=FALSE}
file_name = 'df_train_validate_20191021.RData'
image_file_path = file.path('data', file_name)

# Pull from GCP if necessary
# library(googleCloudStorageR)
# Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
#            "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")
# gcs_get_object(file.path('data', 'milestone2', file_name), saveToDisk = image_file_path, overwrite = TRUE)

load(image_file_path)
```

```{r bts, echo=FALSE}
bts = list(
  bts_1x = bts.1x,
  bts_4x = bts.4x,
  bts_8x = bts.8x,
  bts_16x = bts.16x
)

perf_metrics <- names(get_m2_metric_map())

covs <- df_train_f %>%
  select(-perf_metrics) %>%
  select(-content_crashes) %>%
  select(-client_id) %>%
  select(-label) %>%
  select(-is_release) %>%
  select(-app_version)

results_file_name <- 'feature_selection_nn_mahalanobis.RData' 
results_file_path <- file.path('data', results_file_name)
```

# Features
**NOTE**: Mahalanobis distance measure requires continuous covariates.

Feature sets:

1. Only performance metrics.
2. Performance metrics and the highest found by Boruta with original dataset.
3. Performance metrics and the highest found by Boruta with equal labels dataset.
4. Performance metrics and all covariates.
5. Only the highest covariates found by Boruta (excluding performance).
6. Only the highest covariates found by Boruta (equal labels, excluding performance).
7. Utilize all covariates (excluding performance).

Retrieve Boruta features:

```{r boruta_import}
file_name = 'feature_selection_boruta_initial_20191023.RData'
image_file_path = file.path('data', file_name)

# Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
#            "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")
# library(googleCloudStorageR)
# gcs_get_object(file.path('data', 'milestone2', file_name), saveToDisk = image_file_path, overwrite = TRUE)

load(image_file_path)
```

```{r boruta_fs}
extract_boruta_fs <- function(boruta_res, num=5){
  features <- NULL
  for(metric in names(boruta_results)){
    features <- c(names(sort(apply(boruta_res[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:num]), features)
  }
  return(sort(unique(features)))
}

features_top10 <- extract_boruta_fs(boruta_results, num=10)
features_top10_eq <- extract_boruta_fs(boruta_results_eq, num=10)

# filter out categorical
features_top10 <- df_train_f %>% select(features_top10) %>% select_if(is.numeric) %>% names()
features_top10_eq <- df_train_f %>% select(features_top10_eq) %>% select_if(is.numeric) %>% names()
```

```{r feature_sets}
fs1 <- perf_metrics
fs2 <- c(names(fs1), features_top10)
fs3 <- c(names(fs1), features_top10_eq)
fs4 <- c(names(fs1), covs)
fs5 <- features_top10
fs6 <- features_top10_eq
fs7 <- covs
```

# FS 1
Feature selection on only performance metrics

```{r fs1, error=TRUE}
res_fs1 <- list()
for (bt in names(bts)){
  res_fs1[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=50000, replace=TRUE, workers = 5)
}
save.image(results_file_path)
print(res_fs1)
```

```{r fs1_noreplace, error=TRUE}
res_fs1_noreplace <- list()
for (bt in names(bts)){
  res_fs1_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=50000, replace=FALSE, workers = 5)
}
save.image(results_file_path)
print(res_fs1_noreplace)
```

# FS 2

Performance metrics and the highest found by Boruta with original dataset.

```{r fs2, error=TRUE}
res_fs2 <- list()
for (bt in names(bts)){
  res_fs2[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=50000, replace=TRUE, workers = 5)
}
save.image(results_file_path)
print(res_fs2)
```

```{r fs2_noreplace, error=TRUE}
res_fs2_noreplace <- list()
for (bt in names(bts)){
  res_fs2_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=50000, replace=FALSE, workers = 5)
}
save.image(results_file_path)
print(res_fs2_noreplace)
```

# FS 3

Performance metrics and the highest found by Boruta with equal labels dataset.

```{r fs3, error=TRUE}
res_fs3 <- list()
for (bt in names(bts)){
  res_fs3[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=50000, replace=TRUE, workers = 5)
}
save.image(results_file_path)
print(res_fs3)
```

```{r fs3_noreplace, error=TRUE}
res_fs3_noreplace <- list()
for (bt in names(bts)){
  res_fs3_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=50000, replace=FALSE, workers = 5)
}
save.image(results_file_path)
print(res_fs3_noreplace)
```

# FS 4

Performance metrics and all covariates.

```{r fs4, error=TRUE}
res_fs4 <- list()
for (bt in names(bts)){
  res_fs4[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=50000, replace=TRUE, workers = 5)
}
save.image(results_file_path)
print(res_fs4)
```

```{r fs4_noreplace, error=TRUE}
res_fs4_noreplace <- list()
for (bt in names(bts)){
  res_fs4_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=50000, replace=FALSE, workers = 5)
}
save.image(results_file_path)
print(res_fs4_noreplace)
```

# FS 5

Only the highest covariates found by Boruta (excluding performance).

```{r fs5, error=TRUE}
res_fs5 <- list()
for (bt in names(bts)){
  res_fs5[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=50000, replace=TRUE, workers = 5)
}
save.image(results_file_path)
print(res_fs5)
```

```{r fs5_noreplace, error=TRUE}
res_fs5_noreplace <- list()
for (bt in names(bts)){
  res_fs5_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=50000, replace=FALSE, workers = 5)
}
save.image(results_file_path)
print(res_fs5_noreplace)
```

# FS 6

Only the highest covariates found by Boruta (equal labels, excluding performance).

```{r fs6, error=TRUE}
res_fs6 <- list()
for (bt in names(bts)){
  res_fs6[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=50000, replace=TRUE, workers = 5)
}
save.image(results_file_path)
print(res_fs6)
```

```{r fs6_noreplace, error=TRUE}
res_fs6_noreplace <- list()
for (bt in names(bts)){
  res_fs6_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=50000, replace=FALSE, workers = 5)
}
save.image(results_file_path)
print(res_fs6_noreplace)
```

# FS 7

Utilize all covariates (excluding performance).

```{r fs7, error=TRUE}
res_fs7 <- list()
for (bt in names(bts)){
  res_fs7[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=50000, replace=TRUE, workers = 5)
}
save.image(results_file_path)
print(res_fs7)
```

```{r fs7_noreplace, error=TRUE}
res_fs7_noreplace <- list()
for (bt in names(bts)){
  res_fs7_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=50000, replace=FALSE, workers = 5)
}
save.image(results_file_path)
print(res_fs7_noreplace)
```

### 2019-10-24 perf_release_criteria/milestone_3/ms_2_dataset_generation.Rmd
Adding nn experiment.

@@
 ```{r bootstrap_def}
-extract_ids <- function(df_c, size, oversampling){
+extract_ids <- function(df_c, oversampling){
   df_beta <- df_c %>% filter(is_release == FALSE)

### 2019-10-24 perf_release_criteria/lib/scoring.R

@@ -119,6 +119,8 @@ get_matches <- function(model, data, group = "all", distance = "distance", weigh
 
 run_matchit_sample <- function(df_train, bt, model_covs, size=50000, ...){
   # generate training and test dataset
+  if(missing(seed)) seed <- 1984
+  set.seed(1984)
   train <- df_train %>% 
     filter(client_id %in% bt$train) %>%
     sample_n(size = size)
@@ -151,8 +153,10 @@ perform_matchit_fs <- function(df_train, bts, model_covs, workers, size=50000, .
   registerDoParallel(cl)
   
   scores <- foreach(i=1:length(bts), 
-                    .packages = c('dplyr', 'MatchIt'), 
-                    .export=c('run_matchit_sample', 'generate_formula', 'get_matches', 'calc_score')) %dopar% {
+                    .packages = c('dplyr', 'MatchIt', 'transport'), 
+                    .export=c('run_matchit_sample', 'generate_formula', 'get_matches', 
+                              'calc_score', 'get_m2_metric_map',
+                              'calc_cms')) %dopar% {
     bt <- bts[[i]]
     score <- run_matchit_sample(df_train, bt, model_covs, size = size, ...)
     score

### 2019-10-25 perf_release_criteria/lib/scoring.R
Bypassing sampling of data during bootstrapping. Adding some tryCatch.

@@ -117,13 +117,16 @@ get_matches <- function(model, data, group = "all", distance = "distance", weigh
 #### Bootstramp Resampling
 # The following are for feature selection and hyperparameter tuning
 
-run_matchit_sample <- function(df_train, bt, model_covs, size=50000, ...){
+run_matchit_sample <- function(df_train, bt, model_covs, seed, size=50000, ...){
   # generate training and test dataset
-  if(missing(seed)) seed <- 1984
-  set.seed(1984)
   train <- df_train %>% 
-    filter(client_id %in% bt$train) %>%
-    sample_n(size = size)
+    filter(client_id %in% bt$train)
+  if (!is.null(size)){
+    if(missing(seed)) seed <- 1984
+    set.seed(seed)
+    df_train <- df_train %>% 
+      sample_n(size = size)
+  }
   
   test <- df_train %>% 
     filter(client_id %in% bt$train) %>%
@@ -146,24 +149,32 @@ run_matchit_sample <- function(df_train, bt, model_covs, size=50000, ...){
   return(calc_score(df_scored, get_m2_metric_map()))
 }
 
-perform_matchit_fs <- function(df_train, bts, model_covs, workers, size=50000, ...){
+perform_matchit_fs <- function(df_train, bts, model_covs, workers, seed, size=50000, ...){
   if (missing(workers)) workers = detectCores()
   # registerDoMC(workers)
   cl <- makePSOCKcluster(workers) # number of cores to use
   registerDoParallel(cl)
-  
-  scores <- foreach(i=1:length(bts), 
-                    .packages = c('dplyr', 'MatchIt', 'transport'), 
-                    .export=c('run_matchit_sample', 'generate_formula', 'get_matches', 
-                              'calc_score', 'get_m2_metric_map',
-                              'calc_cms')) %dopar% {
-    bt <- bts[[i]]
-    score <- run_matchit_sample(df_train, bt, model_covs, size = size, ...)
-    score
-    # scores[[i]] <- score
-  }
-  stopCluster(cl)
-  scores <- unlist(scores)
-  final <- c(mean = mean(scores), median = median(scores))
+  final <- tryCatch({
+    scores <- foreach(i=1:length(bts), 
+                      .packages = c('dplyr', 'MatchIt', 'transport'), 
+                      .export=c('run_matchit_sample', 'generate_formula', 'get_matches', 
+                                'calc_score', 'get_m2_metric_map',
+                                'calc_cms')) %dopar% {
+                                  bt <- bts[[i]]
[…]

### 2019-10-25 perf_release_criteria/milestone_3/feature_selection_nn_gam_logit.Rmd
Completed analysis and report for nn GAM logit.

---
title: "Milestone 2: Feature Selection - Nearest Neighbors, GAM Logit"
author: "Corey Dow-Hygelund, Mozilla Data Science"
date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_notebook:
    theme: cosmo
    toc: true
    toc_float: true
---

# tl;dr

This analysis determines the relevant [covariates (features)](https://docs.google.com/document/d/1SfuanvmYmvmEFAdQ7Z5djDeLezdNB1TESqVmj93O8to/edit#heading=h.nwwrif453n80) to utilize for computationally intensive statistical matching algorithms proposed in the modeling approach for this [PRD](https://docs.google.com/document/d/1Ygz6MkudYHZjnDnD9Z97kUyFrvV3KGWsjXyPjddhHq0/edit#heading=h.lvb9l8gw2nee).

**Matching Algorithm Tested**: Nearest-neighbors with GAM logit distance metric

```{r, echo=FALSE, warning=FALSE, message=FALSE}
source('../lib/supporting_funcs.R')
source('../lib/scoring.R')
library(MatchIt)
```

```{r data_load, echo=FALSE}
file_name = 'df_train_validate_20191021.RData'
image_file_path = file.path('data', file_name)

# Pull from GCP if necessary
# library(googleCloudStorageR)
# Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
#            "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")
# gcs_get_object(file.path('data', 'milestone2', file_name), saveToDisk = image_file_path, overwrite = TRUE)

load(image_file_path)
```

```{r bts, echo=FALSE}
bts = list(
  bts_1x = bts.1x,
  bts_4x = bts.4x,
  bts_8x = bts.8x,
  bts_16x = bts.16x
)

perf_metrics <- names(get_m2_metric_map())

covs <- df_train_f %>%
  select(-perf_metrics) %>%
  select(-content_crashes) %>%
  select(-client_id) %>%
  select(-label) %>%
  select(-is_release) %>%
  select(-app_version) %>%
  # select_if(is.numeric) %>% # Mahalanobis constraint
  names()

results_file_name <- 'feature_selection_nn_gam_logit.RData' 
results_file_path <- file.path('data', results_file_name)
```

# Features
Feature sets:

1. Only performance metrics.
2. Performance metrics and the highest found by Boruta with original dataset.
3. Performance metrics and the highest found by Boruta with equal labels dataset.
4. Performance metrics and all covariates.
5. Only the highest covariates found by Boruta (excluding performance).
6. Only the highest covariates found by Boruta (equal labels, excluding performance).
7. Utilize all covariates (excluding performance).

Retrieve Boruta features:

```{r boruta_import}
file_name = 'feature_selection_boruta_initial_20191023.RData'
image_file_path = file.path('data', file_name)

Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
           "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")
library(googleCloudStorageR)
gcs_get_object(file.path('data', 'milestone2', file_name), saveToDisk = image_file_path, overwrite = TRUE)

load(image_file_path)
```

```{r boruta_fs}
extract_boruta_fs <- function(boruta_res, num=5){
  features <- NULL
  for(metric in names(boruta_results)){
    features <- c(names(sort(apply(boruta_res[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:num]), features)
  }
  return(sort(unique(features)))
}

features_top10 <- extract_boruta_fs(boruta_results, num=10)
features_top10_eq <- extract_boruta_fs(boruta_results_eq, num=10)

# filter out categorical
features_top10 <- df_train_f %>% 
  select(features_top10) %>% 
  # select_if(is.numeric) %>% 
  names()
features_top10_eq <- df_train_f %>% 
  select(features_top10_eq) %>% 
  # select_if(is.numeric) %>% 
  names()
```

```{r feature_sets}
fs1 <- perf_metrics
fs2 <- c(names(fs1), features_top10)
fs3 <- c(names(fs1), features_top10_eq)
fs4 <- c(names(fs1), covs)
fs5 <- features_top10
fs6 <- features_top10_eq
fs7 <- covs
```

# FS 1
Feature selection on only performance metrics

```{r fs1, error=TRUE}
res_fs1 <- list()
for (bt in names(bts)){
  res_fs1[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs1)
```

```{r fs1_noreplace, error=TRUE}
res_fs1_noreplace <- list()
for (bt in names(bts)){
  res_fs1_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs1_noreplace)
```

# FS 2

Performance metrics and the highest found by Boruta with original dataset.

```{r fs2, error=TRUE}
res_fs2 <- list()
for (bt in names(bts)){
  res_fs2[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs2)
```

```{r fs2_noreplace, error=TRUE}
res_fs2_noreplace <- list()
for (bt in names(bts)){
  res_fs2_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs2_noreplace)
```

# FS 3

Performance metrics and the highest found by Boruta with equal labels dataset.

```{r fs3, error=TRUE}
res_fs3 <- list()
for (bt in names(bts)){
  res_fs3[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs3)
```

```{r fs3_noreplace, error=TRUE}
res_fs3_noreplace <- list()
for (bt in names(bts)){
  res_fs3_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs3_noreplace)
```

# FS 4

Performance metrics and all covariates.

```{r fs4, error=TRUE}
res_fs4 <- list()
for (bt in names(bts)){
  res_fs4[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs4)
```

```{r fs4_noreplace, error=TRUE}
res_fs4_noreplace <- list()
for (bt in names(bts)){
  res_fs4_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs4_noreplace)
```

# FS 5

Only the highest covariates found by Boruta (excluding performance).

```{r fs5, error=TRUE}
res_fs5 <- list()
for (bt in names(bts)){
  res_fs5[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs5)
```

```{r fs5_noreplace, error=TRUE}
res_fs5_noreplace <- list()
for (bt in names(bts)){
  res_fs5_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs5_noreplace)
```

# FS 6

Only the highest covariates found by Boruta (equal labels, excluding performance).

```{r fs6, error=TRUE}
res_fs6 <- list()
for (bt in names(bts)){
  res_fs6[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs6)
```

```{r fs6_noreplace, error=TRUE}
res_fs6_noreplace <- list()
for (bt in names(bts)){
  res_fs6_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs6_noreplace)
```

# FS 7

Utilize all covariates (excluding performance).

```{r fs7, error=TRUE}
res_fs7 <- list()
for (bt in names(bts)){
  res_fs7[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs7)
```

```{r fs7_noreplace, error=TRUE}
res_fs7_noreplace <- list()
for (bt in names(bts)){
  res_fs7_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
}
save.image(results_file_path)
print(res_fs7_noreplace)
```

# Serialize and Push to GCP
Save the resultant dataset and bootstrap samples to an R image.

```{r serialize_dataset}
save(list = ls(pattern = 'res_fs'), file = results_file_path)
```

```{r gcp_storage_push, warning=FALSE}
gcs_file_path <- file.path('data', 'milestone2', results_file_name)

Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
           "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")

library(googleCloudStorageR)

upload_try <- gcs_upload(results_file_path, name = gcs_file_path)
upload_try
```

### 2019-10-25 perf_release_criteria/milestone_3/feature_selection_nn_logit_linear.Rmd
Completed analysis for nn logit linear.

--- 2019-10-25 perf_release_criteria/milestone_3/feature_selection_nn_gam_logit.Rmd
@@
 ---
-title: "Milestone 2: Feature Selection - Nearest Neighbors, GAM Logit"
+title: "Milestone 2: Feature Selection - Nearest Neighbors, Logit w/Linear Propensity Score"
 author: "Corey Dow-Hygelund, Mozilla Data Science"
@@
 
-**Matching Algorithm Tested**: Nearest-neighbors with GAM logit distance metric
+**Matching Algorithm Tested**: Nearest-neighbors with logit distance metric transformed back to linear scale.
 
@@
 
-results_file_name <- 'feature_selection_nn_gam_logit.RData' 
+results_file_name <- 'feature_selection_nn_logit_linear.RData' 
 results_file_path <- file.path('data', results_file_name)
@@
 for (bt in names(bts)){
-  res_fs1[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
+  res_fs1[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, replace=TRUE, workers = 10, distance = 'linear.logit')
 }
@@
 for (bt in names(bts)){
-  res_fs1_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
+  res_fs1_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, replace=FALSE, workers = 10, distance = 'linear.logit')
 }
@@
 for (bt in names(bts)){
-  res_fs2[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
+  res_fs2[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, replace=TRUE, workers = 10, distance = 'linear.logit')
 }
@@
 for (bt in names(bts)){
-  res_fs2_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
+  res_fs2_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, replace=FALSE, workers = 10, distance = 'linear.logit')
 }
@@
 for (bt in names(bts)){
-  res_fs3[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
+  res_fs3[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, replace=TRUE, workers = 10, distance = 'linear.logit')
 }
@@
 for (bt in names(bts)){
-  res_fs3_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
+  res_fs3_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, replace=FALSE, workers = 10, distance = 'linear.logit')
 }
@@
 for (bt in names(bts)){
-  res_fs4[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
+  res_fs4[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, replace=TRUE, workers = 10, distance = 'linear.logit')
 }
@@
 for (bt in names(bts)){
-  res_fs4_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
+  res_fs4_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, replace=FALSE, workers = 10, distance = 'linear.logit')
 }
@@
 for (bt in names(bts)){
-  res_fs5[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
+  res_fs5[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, replace=TRUE, workers = 10, distance = 'linear.logit')
 }
@@
 for (bt in names(bts)){
-  res_fs5_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
+  res_fs5_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, replace=FALSE, workers = 10, distance = 'linear.logit')
 }
@@
 for (bt in names(bts)){
-  res_fs6[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
+  res_fs6[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, replace=TRUE, workers = 10, distance = 'linear.logit')
 }
@@
 for (bt in names(bts)){
-  res_fs6_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
+  res_fs6_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, replace=FALSE, workers = 10, distance = 'linear.logit')
 }
@@
 for (bt in names(bts)){
-  res_fs7[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
+  res_fs7[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, replace=TRUE, workers = 10, distance = 'linear.logit')
 }
@@
 for (bt in names(bts)){
-  res_fs7_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
+  res_fs7_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, replace=FALSE, workers = 10, distance = 'linear.logit')
 }

### 2019-10-25 perf_release_criteria/milestone_3/feature_selection_subclass_gam_logit.Rmd
Completed subclassing gam logit feature selection. Didn't do really anything.

--- 2019-10-25 perf_release_criteria/milestone_3/feature_selection_nn_gam_logit.Rmd
@@
 ---
-title: "Milestone 2: Feature Selection - Nearest Neighbors, GAM Logit"
+title: "Milestone 2: Feature Selection - Subclassing, GAM Logit"
 author: "Corey Dow-Hygelund, Mozilla Data Science"
@@
 
-results_file_name <- 'feature_selection_nn_gam_logit.RData' 
+results_file_name <- 'feature_selection_subclass_gam_logit.RData' 
 results_file_path <- file.path('data', results_file_name)
@@
 
-Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
-           "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")
-library(googleCloudStorageR)
-gcs_get_object(file.path('data', 'milestone2', file_name), saveToDisk = image_file_path, overwrite = TRUE)
+# Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
+#            "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")
+# library(googleCloudStorageR)
+# gcs_get_object(file.path('data', 'milestone2', file_name), saveToDisk = image_file_path, overwrite = TRUE)
 
@@
 for (bt in names(bts)){
-  res_fs1[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
+  res_fs1[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL,  workers = 10, 
+                                      method = "subclass", distance = 'GAMlogit')
 }
@@
 print(res_fs1)
-```
-
-```{r fs1_noreplace, error=TRUE}
-res_fs1_noreplace <- list()
-for (bt in names(bts)){
-  res_fs1_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
-}
-save.image(results_file_path)
-print(res_fs1_noreplace)
 ```
@@
 for (bt in names(bts)){
-  res_fs2[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
+  res_fs2[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL,  workers = 10, method = "subclass", distance = 'GAMlogit')
 }
@@
 print(res_fs2)
-```
-
-```{r fs2_noreplace, error=TRUE}
-res_fs2_noreplace <- list()
-for (bt in names(bts)){
-  res_fs2_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
-}
-save.image(results_file_path)
-print(res_fs2_noreplace)
 ```
@@
 for (bt in names(bts)){
-  res_fs3[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
+  res_fs3[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL,  workers = 10, 
+                                      method = "subclass", distance = 'GAMlogit')
 }
@@
 print(res_fs3)
-```
-
-```{r fs3_noreplace, error=TRUE}
-res_fs3_noreplace <- list()
-for (bt in names(bts)){
-  res_fs3_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
-}
-save.image(results_file_path)
-print(res_fs3_noreplace)
 ```
@@
 for (bt in names(bts)){
-  res_fs4[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
+  res_fs4[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL,  workers = 10, 
+                                      method = "subclass", distance = 'GAMlogit')
 }
@@
 print(res_fs4)
-```
-
-```{r fs4_noreplace, error=TRUE}
-res_fs4_noreplace <- list()
-for (bt in names(bts)){
-  res_fs4_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
-}
-save.image(results_file_path)
-print(res_fs4_noreplace)
 ```
@@
 for (bt in names(bts)){
-  res_fs5[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
+  res_fs5[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL,  workers = 10, 
+                                      method = "subclass", distance = 'GAMlogit')
 }
@@
 print(res_fs5)
-```
-
-```{r fs5_noreplace, error=TRUE}
-res_fs5_noreplace <- list()
-for (bt in names(bts)){
-  res_fs5_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
-}
-save.image(results_file_path)
-print(res_fs5_noreplace)
 ```
@@
 for (bt in names(bts)){
-  res_fs6[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
+  res_fs6[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL,  workers = 10, 
+                                      method = "subclass", distance = 'GAMlogit')
 }
@@
 print(res_fs6)
-```
-
-```{r fs6_noreplace, error=TRUE}
-res_fs6_noreplace <- list()
-for (bt in names(bts)){
-  res_fs6_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
-}
-save.image(results_file_path)
-print(res_fs6_noreplace)
 ```
@@
 for (bt in names(bts)){
-  res_fs7[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
+  res_fs7[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL,  workers = 10,
+                                      method = "subclass", distance = 'GAMlogit')
 }
@@
 print(res_fs7)
-```
-
-```{r fs7_noreplace, error=TRUE}
-res_fs7_noreplace <- list()
-for (bt in names(bts)){
-  res_fs7_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
-}
-save.image(results_file_path)
-print(res_fs7_noreplace)
 ```
@@
 ```
+
+# Conclusion
+
+Subclassing appeared to do very little, as the feature sets had no influence.

### 2019-10-26 perf_release_criteria/lib/scoring.R
Adding in interactions terms for `generate_formula`. Adding support for bootstrapping.

@@ -117,12 +117,11 @@ get_matches <- function(model, data, group = "all", distance = "distance", weigh
 #### Bootstramp Resampling
 # The following are for feature selection and hyperparameter tuning
 
-run_matchit_sample <- function(df_train, bt, model_covs, seed, size=50000, ...){
+run_matchit_sample <- function(df_train, bt, model_covs, seed, add_interactions, size=50000, ...){
   # generate training and test dataset
   train <- df_train %>% 
     filter(client_id %in% bt$train)
   if (!is.null(size)){
-    if(missing(seed)) seed <- 1984
     set.seed(seed)
     df_train <- df_train %>% 
       sample_n(size = size)
@@ -133,7 +132,7 @@ run_matchit_sample <- function(df_train, bt, model_covs, seed, size=50000, ...){
     filter(label == 'release')
   
   # train model 
-  formula <- generate_formula(model_covs, label = 'is_release')
+  formula <- generate_formula(model_covs, label = 'is_release', add_interactions)
   model <- matchit(formula, train, ...)
   
   # extract beta subset
@@ -149,8 +148,10 @@ run_matchit_sample <- function(df_train, bt, model_covs, seed, size=50000, ...){
   return(calc_score(df_scored, get_m2_metric_map()))
 }
 
-perform_matchit_fs <- function(df_train, bts, model_covs, workers, seed, size=50000, ...){
+perform_matchit_fs <- function(df_train, bts, model_covs, workers, seed, add_interactions=FALSE, 
+                               size=50000, ...){
   if (missing(workers)) workers = detectCores()
+  if (missing(seed)) seed <- 1984
   # registerDoMC(workers)
   cl <- makePSOCKcluster(workers) # number of cores to use
   registerDoParallel(cl)
@@ -161,7 +162,9 @@ perform_matchit_fs <- function(df_train, bts, model_covs, workers, seed, size=50
                                 'calc_score', 'get_m2_metric_map',
                                 'calc_cms')) %dopar% {
                                   bt <- bts[[i]]
-                                  score <- run_matchit_sample(df_train, bt, model_covs, size = size, ...)
+                                  score <- run_matchit_sample(df_train, bt, model_covs, seed, add_interactions,
+                                                              size = size, 
+                                                              ...)
                                   score
                                   # scores[[i]] <- score
                                 }

### 2019-10-26 perf_release_criteria/lib/supporting_funcs.R

@@ -52,9 +52,15 @@ calc_stats <- function(df.match, ho_cov, add_1 = FALSE){
 
 #### Modeling Pipeline
 
-generate_formula <- function(tr_cov, label){
-  # Focus on linear and no-interactions
-  return(as.formula(paste(label, '~', paste(tr_cov, collapse="+"))))
+generate_formula <- function(tr_cov, label, add_interactions=FALSE){
+  if (add_interactions){
+    formula <- paste(label, '~', paste(tr_cov, collapse="*"))
+  }
+  else {
+    formula <- paste(label, '~', paste(tr_cov, collapse="+"))
+  }
+  print(formula)
+  return(as.formula(formula))
 }
 
 #### Categorize continuous covariates

### 2019-10-27 perf_release_criteria/milestone_3/feature_selection_nn_mahalanobis.Rmd
NN Malahanobis report.

@@
   select(-is_release) %>%
-  select(-app_version)
+  select(-app_version) %>%
+  select_if(is.numeric) %>% # Mahalanobis constraint
+  names()
 
@@
 for (bt in names(bts)){
-  res_fs1[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=50000, replace=TRUE, workers = 5)
+  res_fs1[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, replace=TRUE, workers = 10, distance = "mahalanobis")
 }
@@
 for (bt in names(bts)){
-  res_fs1_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=50000, replace=FALSE, workers = 5)
+  res_fs1_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, replace=FALSE, workers = 10, distance = "mahalanobis")
 }
@@
 for (bt in names(bts)){
-  res_fs2[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=50000, replace=TRUE, workers = 5)
+  res_fs2[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, replace=TRUE, workers = 10, distance = "mahalanobis")
 }
@@
 for (bt in names(bts)){
-  res_fs2_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=50000, replace=FALSE, workers = 5)
+  res_fs2_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, replace=FALSE, workers = 10, distance = "mahalanobis")
 }
@@
 for (bt in names(bts)){
-  res_fs3[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=50000, replace=TRUE, workers = 5)
+  res_fs3[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, replace=TRUE, workers = 10, distance = "mahalanobis")
 }
@@
 for (bt in names(bts)){
-  res_fs3_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=50000, replace=FALSE, workers = 5)
+  res_fs3_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, replace=FALSE, workers = 10, distance = "mahalanobis")
 }
@@
 for (bt in names(bts)){
-  res_fs4[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=50000, replace=TRUE, workers = 5)
+  res_fs4[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, replace=TRUE, workers = 10, distance = "mahalanobis")
 }
@@
 for (bt in names(bts)){
-  res_fs4_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=50000, replace=FALSE, workers = 5)
+  res_fs4_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, replace=FALSE, workers = 10, distance = "mahalanobis")
 }
@@
 for (bt in names(bts)){
-  res_fs5[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=50000, replace=TRUE, workers = 5)
+  res_fs5[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, replace=TRUE, workers = 10, distance = "mahalanobis")
 }
@@
 for (bt in names(bts)){
-  res_fs5_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=50000, replace=FALSE, workers = 5)
+  res_fs5_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, replace=FALSE, workers = 10, distance = "mahalanobis")
 }
@@
 for (bt in names(bts)){
-  res_fs6[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=50000, replace=TRUE, workers = 5)
+  res_fs6[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, replace=TRUE, workers = 10, distance = "mahalanobis")
 }
@@
 for (bt in names(bts)){
-  res_fs6_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=50000, replace=FALSE, workers = 5)
+  res_fs6_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, replace=FALSE, workers = 10, distance = "mahalanobis")
 }
@@
 for (bt in names(bts)){
-  res_fs7[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=50000, replace=TRUE, workers = 5)
+  res_fs7[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, replace=TRUE, workers = 10, distance = "mahalanobis")
 }
@@
 for (bt in names(bts)){
-  res_fs7_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=50000, replace=FALSE, workers = 5)
+  res_fs7_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, replace=FALSE, workers = 10, distance = "mahalanobis")
 }
@@
 ```
+
+# FS 1 Interactions
+
+Feature selection on only performance metrics, but including interaction terms.
+
+```{r fs1_int, error=TRUE}
+res_fs1 <- list()
+for (bt in names(bts)){
+  res_fs1[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, workers = 10, add_interactions=TRUE,
+                                      replace=TRUE, distance = 'mahalanobis')
+}
+save.image(results_file_path)
+print(res_fs1)
+```
+
+# # Serialize and Push to GCP
+Save the resultant dataset and bootstrap samples to an R image.
+
+```{r serialize_dataset}
+save(list = ls(pattern = 'res_fs'), file = results_file_path)
+```
+
+```{r gcp_storage_push, warning=FALSE}
+gcs_file_path <- file.path('data', 'milestone2', results_file_name)
+
+Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
+           "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")
+
+library(googleCloudStorageR)
+
+upload_try <- gcs_upload(results_file_path, name = gcs_file_path)
+upload_try
+```

### 2019-10-28 perf_release_criteria/milestone_3/feature_selection_nn_mahalanobis.Rmd
NN Malahanobis feature selection

@@
 ```{r fs1_int, error=TRUE}
-res_fs1 <- list()
+res_fs1_int <- list()
 for (bt in names(bts)){
-  res_fs1[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, workers = 10, add_interactions=TRUE,
+  res_fs1_int[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, workers = 10, add_interactions=TRUE,
                                       replace=TRUE, distance = 'mahalanobis')
@@
 save.image(results_file_path)
-print(res_fs1)
+print(res_fs1_int)
 ```

### 2019-10-28 perf_release_criteria/milestone_3/feature_selection_nn_logit_linear.Rmd
Updating nn logit linear with interactions.

@@
 
+# FS 1 Interactions
+
+Feature selection on only performance metrics, but including interaction terms.
+
+```{r fs1_int, error=TRUE}
+res_fs1 <- list()
+for (bt in names(bts)){
+  res_fs1[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, workers = 10, add_interactions=TRUE,
+                                      replace=TRUE, distance = 'linear.logit')
+}
+save.image(results_file_path)
+print(res_fs1)
+```
+
+```{r fs1_int_noreplace, error=TRUE}
+res_fs1_noreplace <- list()
+for (bt in names(bts)){
+  res_fs1_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, add_interactions=TRUE,
+                                                replace=FALSE, workers = 10, distance = 'linear.logit')
+}
+save.image(results_file_path)
+print(res_fs1_noreplace)
+```
+
+# FS 2
+
+Performance metrics and the highest found by Boruta with original dataset, but including interaction terms
+
+```{r fs2_int, error=TRUE}
+res_fs2 <- list()
+for (bt in names(bts)){
+  res_fs2[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, add_interactions=TRUE,
+                                      replace=TRUE, workers = 10, distance = 'linear.logit')
+}
+save.image(results_file_path)
+print(res_fs2)
+```
+
+Never completed after 2.5 days. Killed it...
+
 # Serialize and Push to GCP

### 2019-10-28 perf_release_criteria/milestone_3/feature_selection/feature_selection_cem_mahalanobis.Rmd
Tidying things up for clarity

--- 2019-10-24 perf_release_criteria/milestone_3/feature_selection_nn_mahalanobis.Rmd
@@
 ---
-title: "Milestone 2: Feature Selection - Nearest Neighbors, Mahalanobis"
+title: "Milestone 2: Feature Selection - CEM, Mahalanobis"
 author: "Corey Dow-Hygelund, Mozilla Data Science"
@@
   select(-is_release) %>%
-  select(-app_version)
+  select(-app_version) %>%
+  select_if(is.numeric) %>% # Mahalanobis constraint
+  names()
 
-results_file_name <- 'feature_selection_nn_mahalanobis.RData' 
+results_file_name <- 'feature_selection_cem_mahalanobis.RData' 
 results_file_path <- file.path('data', results_file_name)
@@
 for (bt in names(bts)){
-  res_fs1[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=50000, replace=TRUE, workers = 5)
+  res_fs1[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, k2k= TRUE, workers = 10, 
+                                      method = 'cem', distance = "mahalanobis")
 }
@@
 for (bt in names(bts)){
-  res_fs1_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=50000, replace=FALSE, workers = 5)
+  res_fs1_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, k2k= FALSE, workers = 10, 
+                                                method = 'cem', distance = "mahalanobis")
 }
@@
 for (bt in names(bts)){
-  res_fs2[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=50000, replace=TRUE, workers = 5)
+  res_fs2[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, k2k= TRUE, workers = 10, 
+                                      method = 'cem', distance = "mahalanobis")
 }
@@
 for (bt in names(bts)){
-  res_fs2_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=50000, replace=FALSE, workers = 5)
+  res_fs2_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, k2k= FALSE, workers = 10, 
+                                                method = 'cem', distance = "mahalanobis")
 }
@@
 for (bt in names(bts)){
-  res_fs3[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=50000, replace=TRUE, workers = 5)
+  res_fs3[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, k2k= TRUE, workers = 10, 
+                                      method = 'cem', distance = "mahalanobis")
 }
@@
 for (bt in names(bts)){
-  res_fs3_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=50000, replace=FALSE, workers = 5)
+  res_fs3_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, k2k= FALSE, workers = 10, 
+                                                method = 'cem', distance = "mahalanobis")
 }
@@
 for (bt in names(bts)){
-  res_fs4[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=50000, replace=TRUE, workers = 5)
+  res_fs4[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, k2k= TRUE, workers = 10, 
+                                      method = 'cem', distance = "mahalanobis")
 }
@@
 for (bt in names(bts)){
-  res_fs4_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=50000, replace=FALSE, workers = 5)
+  res_fs4_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, k2k= FALSE, workers = 10, 
+                                                method = 'cem', distance = "mahalanobis")
 }
@@
 for (bt in names(bts)){
-  res_fs5[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=50000, replace=TRUE, workers = 5)
+  res_fs5[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, k2k= TRUE, workers = 10, 
+                                      method = 'cem', distance = "mahalanobis")
 }
@@
 for (bt in names(bts)){
-  res_fs5_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=50000, replace=FALSE, workers = 5)
+  res_fs5_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, k2k= FALSE, workers = 10, 
+                                                method = 'cem', distance = "mahalanobis")
 }
@@
 for (bt in names(bts)){
-  res_fs6[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=50000, replace=TRUE, workers = 5)
+  res_fs6[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, k2k= TRUE, workers = 10, 
+                                      method = 'cem', distance = "mahalanobis")
 }
@@
 for (bt in names(bts)){
-  res_fs6_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=50000, replace=FALSE, workers = 5)
+  res_fs6_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, k2k= FALSE, workers = 10, 
+                                                method = 'cem', distance = "mahalanobis")
 }
@@
 for (bt in names(bts)){
-  res_fs7[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=50000, replace=TRUE, workers = 5)
+  res_fs7[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, k2k= TRUE, workers = 10, 
+                                      method = 'cem', distance = "mahalanobis")
 }
@@
 for (bt in names(bts)){
-  res_fs7_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=50000, replace=FALSE, workers = 5)
+  res_fs7_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, k2k= FALSE, workers = 10, 
+                                                method = 'cem', distance = "mahalanobis")
 }
@@
 ```
+
+# Serialize and Push to GCP
+Save the resultant dataset and bootstrap samples to an R image.
+
+```{r serialize_dataset}
+save(list = ls(pattern = 'res_fs'), file = results_file_path)
+```
+
+```{r gcp_storage_push, warning=FALSE}
+gcs_file_path <- file.path('data', 'milestone2', results_file_name)
+
+Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
+           "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")
+
+library(googleCloudStorageR)
+
+upload_try <- gcs_upload(results_file_path, name = gcs_file_path)
+upload_try
+```

### 2019-10-28 perf_release_criteria/milestone_3/feature_selection/feature_selection_nn_probit_linear_f.Rmd
Tidying things up for clarity

--- 2019-10-25 perf_release_criteria/milestone_3/feature_selection_nn_gam_logit.Rmd
@@
 ---
-title: "Milestone 2: Feature Selection - Nearest Neighbors, GAM Logit"
+title: "Milestone 2: Feature Selection - Nearest Neighbors, Probit, with Linear Propensity Score"
 author: "Corey Dow-Hygelund, Mozilla Data Science"
@@
 
-**Matching Algorithm Tested**: Nearest-neighbors with GAM logit distance metric
+**Matching Algorithm Tested**: Nearest-neighbors with probit distance metric transformed back to linear scale.
 
@@
 
-results_file_name <- 'feature_selection_nn_gam_logit.RData' 
+results_file_name <- 'feature_selection_nn_probit_linear.RData' 
 results_file_path <- file.path('data', results_file_name)
@@
 for (bt in names(bts)){
-  res_fs1[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
+  res_fs1[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, replace=TRUE, workers = 10, distance = "linear.probit")
 }
@@
 for (bt in names(bts)){
-  res_fs1_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
+  res_fs1_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, replace=FALSE, workers = 10, distance = "linear.probit")
 }
@@
 for (bt in names(bts)){
-  res_fs2[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
+  res_fs2[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, replace=TRUE, workers = 10, distance = "linear.probit")
 }
@@
 for (bt in names(bts)){
-  res_fs2_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
+  res_fs2_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, replace=FALSE, workers = 10, distance = "linear.probit")
 }
@@
 for (bt in names(bts)){
-  res_fs3[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
+  res_fs3[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, replace=TRUE, workers = 10, distance = "linear.probit")
 }
@@
 for (bt in names(bts)){
-  res_fs3_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
+  res_fs3_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, replace=FALSE, workers = 10, distance = "linear.probit")
 }
@@
 for (bt in names(bts)){
-  res_fs4[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
+  res_fs4[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, replace=TRUE, workers = 10, distance = "linear.probit")
 }
@@
 for (bt in names(bts)){
-  res_fs4_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
+  res_fs4_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, replace=FALSE, workers = 10, distance = "linear.probit")
 }
@@
 for (bt in names(bts)){
-  res_fs5[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
+  res_fs5[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, replace=TRUE, workers = 10, distance = "linear.probit")
 }
@@
 for (bt in names(bts)){
-  res_fs5_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
+  res_fs5_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, replace=FALSE, workers = 10, distance = "linear.probit")
 }
@@
 for (bt in names(bts)){
-  res_fs6[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
+  res_fs6[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, replace=TRUE, workers = 10, distance = "linear.probit")
 }
@@
 for (bt in names(bts)){
-  res_fs6_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
+  res_fs6_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, replace=FALSE, workers = 10, distance = "linear.probit")
 }
@@
 for (bt in names(bts)){
-  res_fs7[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
+  res_fs7[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, replace=TRUE, workers = 10, distance = "linear.probit")
 }
@@
 for (bt in names(bts)){
-  res_fs7_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
+  res_fs7_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, replace=FALSE, workers = 10, distance = "linear.probit")
 }
@@
 # Serialize and Push to GCP
-Save the resultant dataset and bootstrap samples to an R image.
+Save the feature selection results to GCP.
 

### 2019-10-28 perf_release_criteria/milestone_3/feature_selection/feature_selection_subclass_mahalanobis.Rmd
Tidying things up for clarity

--- 2019-10-25 perf_release_criteria/milestone_3/feature_selection_subclass_gam_logit.Rmd
@@
 ---
-title: "Milestone 2: Feature Selection - Subclassing, GAM Logit"
+title: "Milestone 2: Feature Selection - Subclassing, Malahanobis"
 author: "Corey Dow-Hygelund, Mozilla Data Science"
@@
 
-results_file_name <- 'feature_selection_subclass_gam_logit.RData' 
+results_file_name <- 'feature_selection_subclass_mahalanobis.RData' 
 results_file_path <- file.path('data', results_file_name)
@@
   res_fs1[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL,  workers = 10, 
-                                      method = "subclass", distance = 'GAMlogit')
+                                      method = "subclass", distance = "mahalanobis")
 }
@@
 for (bt in names(bts)){
-  res_fs2[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL,  workers = 10, method = "subclass", distance = 'GAMlogit')
+  res_fs2[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL,  workers = 10, method = "subclass", distance = "mahalanobis")
 }
@@
   res_fs3[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL,  workers = 10, 
-                                      method = "subclass", distance = 'GAMlogit')
+                                      method = "subclass", distance = "mahalanobis")
 }
@@
   res_fs4[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL,  workers = 10, 
-                                      method = "subclass", distance = 'GAMlogit')
+                                      method = "subclass", distance = "mahalanobis")
 }
@@
   res_fs5[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL,  workers = 10, 
-                                      method = "subclass", distance = 'GAMlogit')
+                                      method = "subclass", distance = "mahalanobis")
 }
@@
   res_fs6[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL,  workers = 10, 
-                                      method = "subclass", distance = 'GAMlogit')
+                                      method = "subclass", distance = "mahalanobis")
 }
@@
   res_fs7[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL,  workers = 10,
-                                      method = "subclass", distance = 'GAMlogit')
+                                      method = "subclass", distance = "mahalanobis")
 }

### 2019-10-28 perf_release_criteria/lib/scoring.R
Fixing bug in bootstrapping. Not applying approporiate test sample.

@@ -128,7 +128,7 @@ run_matchit_sample <- function(df_train, bt, model_covs, seed, add_interactions,
   }
   
   test <- df_train %>% 
-    filter(client_id %in% bt$train) %>%
+    filter(client_id %in% bt$test) %>%
     filter(label == 'release')
   
   # train model 

### 2019-10-28 perf_release_criteria/lib/scoring.R
Fixing yet another bootstrap bug: properly handing "with replacement".

@@ -120,7 +120,7 @@ get_matches <- function(model, data, group = "all", distance = "distance", weigh
 run_matchit_sample <- function(df_train, bt, model_covs, seed, add_interactions, size=50000, ...){
   # generate training and test dataset
   train <- df_train %>% 
-    filter(client_id %in% bt$train)
+    right_join(data.frame(client_id = bt$train, stringsAsFactors=FALSE), by='client_id', 'right')
   if (!is.null(size)){
     set.seed(seed)
     df_train <- df_train %>% 
@@ -128,7 +128,7 @@ run_matchit_sample <- function(df_train, bt, model_covs, seed, add_interactions,
   }
   
   test <- df_train %>% 
-    filter(client_id %in% bt$test) %>%
+    right_join(data.frame(client_id = bt$test, stringsAsFactors=FALSE), by='client_id', 'right') %>%
     filter(label == 'release')
   
   # train model 

### 2019-10-28 perf_release_criteria/milestone_3/feature_selection/feature_selection_boruta_initial.Rmd

--- 2019-10-23 perf_release_criteria/milestone_3/feature_selection_boruta_initial.Rmd
@@
 # Pull from GCP if necessary
-# library(googleCloudStorageR)
 # Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
 #            "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")
+# library(googleCloudStorageR)
 # gcs_get_object(file.path('data', 'milestone2', file_name), saveToDisk = image_file_path, overwrite = TRUE)
@@
 df_train_f_sm <- df_train_f %>%
-   sample_n(20000)
+   sample_n(80000)
 
@@
   bind_rows(df_beta) %>%
-   sample_n(20000)
+   sample_n(80000)
 

### 2019-10-29 perf_release_criteria/milestone_3/hyperparameter_tuning/hyperparameter_tuning_nn_malahanobis.Rmd
Adding support for hyperparameter tuning.

--- 2019-10-28 perf_release_criteria/milestone_3/feature_selection/feature_selection_cem_mahalanobis.Rmd
@@
 ---
-title: "Milestone 2: Feature Selection - CEM, Mahalanobis"
+title: "Milestone 2: Hyperparameter Tuning - Nearest Neighbors, Mahalanobis"
 author: "Corey Dow-Hygelund, Mozilla Data Science"
@@
 
-This analysis determines the relevant [covariates (features)](https://docs.google.com/document/d/1SfuanvmYmvmEFAdQ7Z5djDeLezdNB1TESqVmj93O8to/edit#heading=h.nwwrif453n80) to utilize for computationally intensive statistical matching algorithms proposed in the modeling approach for this [PRD](https://docs.google.com/document/d/1Ygz6MkudYHZjnDnD9Z97kUyFrvV3KGWsjXyPjddhHq0/edit#heading=h.lvb9l8gw2nee).
+This analysis determines the optimal [hyperparameters] (https://docs.google.com/document/d/1SfuanvmYmvmEFAdQ7Z5djDeLezdNB1TESqVmj93O8to/edit#heading=h.yqukkyb8q4xw) to utilize for computationally intensive statistical matching algorithms proposed in the modeling approach for this [PRD](https://docs.google.com/document/d/1Ygz6MkudYHZjnDnD9Z97kUyFrvV3KGWsjXyPjddhHq0/edit#heading=h.lvb9l8gw2nee).
 
@@
 ```{r data_load, echo=FALSE}
-file_name = 'df_train_validate_20191021.RData'
+file_name = 'df_train_validate_20191025.RData'
 image_file_path = file.path('data', file_name)
@@
 
-results_file_name <- 'feature_selection_cem_mahalanobis.RData' 
+results_file_name <- 'hyperparameter_tuning_nn_mahalanobis.RData' 
 results_file_path <- file.path('data', results_file_name)
@@
 # Features
-**NOTE**: Mahalanobis distance measure requires continuous covariates.
+The optimal feature set was found in `feature_selection_nn_mahalanobis.Rmd`. At the time of this run they were:
 
-Feature sets:
+* Beta oversampling by 4x
+* FS 1: Only performance metrics
 
-1. Only performance metrics.
-2. Performance metrics and the highest found by Boruta with original dataset.
-3. Performance metrics and the highest found by Boruta with equal labels dataset.
-4. Performance metrics and all covariates.
-5. Only the highest covariates found by Boruta (excluding performance).
-6. Only the highest covariates found by Boruta (equal labels, excluding performance).
-7. Utilize all covariates (excluding performance).
+To investigate, and possible utilize, a more general model, the second highest suite of features will also be tested:
 
-Retrieve Boruta features:
+* Beta oversapmling by 16x
+* FS 3: Performance metrics and highest found by Boruta with equal labels dataset
 
-```{r boruta_import}
+```{r boruta_import, echo=FALSE, warning=FALSE, message=FALSE}
 file_name = 'feature_selection_boruta_initial_20191023.RData'
@@
 
-```{r boruta_fs}
+```{r boruta_fs, echo=FALSE, warning=FALSE, message=FALSE}
 extract_boruta_fs <- function(boruta_res, num=5){
@@
 
+# Hyperparameters
+Hyperparameters tested for nearest-neighbors are the following:
+
+* Matching order (m.order)
+* Caliper
+* of control to treatments
+
+```{r hyperparameters}
+hps <- list(
+  replace = c(TRUE, FALSE),
+  caliper = c(0, 0.25, 0.5, 1, 3),
+  calclosest = c(TRUE, FALSE),
+  ratio = c(1, 2, 4)
+)
+
+hps_grid = expand.grid(hps)
+```
+
 # FS 1
-Feature selection on only performance metrics
+Hyperparameter tuning on optimal features.
 
 ```{r fs1, error=TRUE}
-res_fs1 <- list()
-for (bt in names(bts)){
-  res_fs1[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, k2k= TRUE, workers = 10, 
-                                      method = 'cem', distance = "mahalanobis")
-}
-save.image(results_file_path)
-print(res_fs1)
+bt <- bts[['bts_4x']]
+
+perform_matchit_hp_tune(df_train_f, bt[[1]], fs1, size=5000, workers = 10, hps_grid = hps_grid, distance = "mahalanobis")
 ```
-
-```{r fs1_noreplace, error=TRUE}
-res_fs1_noreplace <- list()
-for (bt in names(bts)){
-  res_fs1_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, k2k= FALSE, workers = 10, 
-                                                method = 'cem', distance = "mahalanobis")
-}
-save.image(results_file_path)
-print(res_fs1_noreplace)
-```
-
-# FS 2
-
-Performance metrics and the highest found by Boruta with original dataset.
-
-```{r fs2, error=TRUE}
-res_fs2 <- list()
-for (bt in names(bts)){
-  res_fs2[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, k2k= TRUE, workers = 10, 
-                                      method = 'cem', distance = "mahalanobis")
-}
-save.image(results_file_path)
-print(res_fs2)
-```
-
-```{r fs2_noreplace, error=TRUE}
-res_fs2_noreplace <- list()
-for (bt in names(bts)){
-  res_fs2_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, k2k= FALSE, workers = 10, 
-                                                method = 'cem', distance = "mahalanobis")
-}
-save.image(results_file_path)
-print(res_fs2_noreplace)
-```
-
-# FS 3
-
-Performance metrics and the highest found by Boruta with equal labels dataset.
-
-```{r fs3, error=TRUE}
-res_fs3 <- list()
-for (bt in names(bts)){
-  res_fs3[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, k2k= TRUE, workers = 10, 
-                                      method = 'cem', distance = "mahalanobis")
-}
-save.image(results_file_path)
-print(res_fs3)
-```
-
-```{r fs3_noreplace, error=TRUE}
-res_fs3_noreplace <- list()
-for (bt in names(bts)){
-  res_fs3_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, k2k= FALSE, workers = 10, 
-                                                method = 'cem', distance = "mahalanobis")
-}
-save.image(results_file_path)
-print(res_fs3_noreplace)
-```
-
-# FS 4
-
-Performance metrics and all covariates.
-
-```{r fs4, error=TRUE}
-res_fs4 <- list()
-for (bt in names(bts)){
-  res_fs4[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, k2k= TRUE, workers = 10, 
-                                      method = 'cem', distance = "mahalanobis")
-}
-save.image(results_file_path)
-print(res_fs4)
-```
-
-```{r fs4_noreplace, error=TRUE}
-res_fs4_noreplace <- list()
-for (bt in names(bts)){
-  res_fs4_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, k2k= FALSE, workers = 10, 
-                                                method = 'cem', distance = "mahalanobis")
-}
-save.image(results_file_path)
-print(res_fs4_noreplace)
-```
-
-# FS 5
-
-Only the highest covariates found by Boruta (excluding performance).
-
-```{r fs5, error=TRUE}
-res_fs5 <- list()
-for (bt in names(bts)){
-  res_fs5[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, k2k= TRUE, workers = 10, 
-                                      method = 'cem', distance = "mahalanobis")
-}
-save.image(results_file_path)
-print(res_fs5)
-```
-
-```{r fs5_noreplace, error=TRUE}
-res_fs5_noreplace <- list()
-for (bt in names(bts)){
-  res_fs5_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, k2k= FALSE, workers = 10, 
-                                                method = 'cem', distance = "mahalanobis")
-}
-save.image(results_file_path)
-print(res_fs5_noreplace)
-```
-
-# FS 6
-
-Only the highest covariates found by Boruta (equal labels, excluding performance).
-
-```{r fs6, error=TRUE}
-res_fs6 <- list()
-for (bt in names(bts)){
-  res_fs6[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, k2k= TRUE, workers = 10, 
-                                      method = 'cem', distance = "mahalanobis")
-}
-save.image(results_file_path)
-print(res_fs6)
-```
-
-```{r fs6_noreplace, error=TRUE}
-res_fs6_noreplace <- list()
-for (bt in names(bts)){
-  res_fs6_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, k2k= FALSE, workers = 10, 
-                                                method = 'cem', distance = "mahalanobis")
-}
-save.image(results_file_path)
-print(res_fs6_noreplace)
-```
-
-# FS 7
-
-Utilize all covariates (excluding performance).
-
-```{r fs7, error=TRUE}
-res_fs7 <- list()
-for (bt in names(bts)){
-  res_fs7[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, k2k= TRUE, workers = 10, 
-                                      method = 'cem', distance = "mahalanobis")
-}
-save.image(results_file_path)
-print(res_fs7)
-```
-
-```{r fs7_noreplace, error=TRUE}
-res_fs7_noreplace <- list()
-for (bt in names(bts)){
-  res_fs7_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, k2k= FALSE, workers = 10, 
-                                                method = 'cem', distance = "mahalanobis")
-}
-save.image(results_file_path)
-print(res_fs7_noreplace)
-```
-
-# Serialize and Push to GCP
-Save the resultant dataset and bootstrap samples to an R image.
-
-```{r serialize_dataset}
-save(list = ls(pattern = 'res_fs'), file = results_file_path)
-```
-
-```{r gcp_storage_push, warning=FALSE}
-gcs_file_path <- file.path('data', 'milestone2', results_file_name)
-
-Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
-           "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")
-
-library(googleCloudStorageR)
-
-upload_try <- gcs_upload(results_file_path, name = gcs_file_path)
-upload_try
-```

### 2019-10-29 perf_release_criteria/lib/scoring.R

@@ -117,39 +117,47 @@ get_matches <- function(model, data, group = "all", distance = "distance", weigh
 #### Bootstramp Resampling
 # The following are for feature selection and hyperparameter tuning
 
-run_matchit_sample <- function(df_train, bt, model_covs, seed, add_interactions, size=50000, ...){
-  # generate training and test dataset
-  train <- df_train %>% 
-    right_join(data.frame(client_id = bt$train, stringsAsFactors=FALSE), by='client_id', 'right')
-  if (!is.null(size)){
-    set.seed(seed)
-    df_train <- df_train %>% 
-      sample_n(size = size)
+run_matchit_sample <- function(df_train, bt, model_covs, seed, add_interactions, size=NULL, ...){
+  score <- tryCatch({
+    # generate training and test dataset
+    train <- df_train %>% 
+      right_join(data.frame(client_id = bt$train, stringsAsFactors=FALSE), by='client_id', 'right')
+    if (!is.null(size)){
+      set.seed(seed)
+      df_train <- df_train %>% 
+        sample_n(size = size)
+    }
+    
+    test <- df_train %>% 
+      right_join(data.frame(client_id = bt$test, stringsAsFactors=FALSE), by='client_id', 'right') %>%
+      filter(label == 'release')
+    
+    # train model 
+    formula <- generate_formula(model_covs, label = 'is_release', add_interactions)
+    model <- matchit(formula, train, ...)
+    
+    # extract beta subset
+    df_matched <- get_matches(model, train) %>%
+      select(-weights, -distance) %>%
+      filter(label == 'beta')
+    
+    # build dataframe for scoring
+    df_scored <- df_matched %>%
+      bind_rows(test)
+    
+    #apply scoring
+    return(calc_score(df_scored, get_m2_metric_map()))
+  },
+  error = function(cond){
+    message(paste("Failed for bootstrap resample: ", cond))
+    return(NA)
   }
-  
-  test <- df_train %>% 
-    right_join(data.frame(client_id = bt$test, stringsAsFactors=FALSE), by='client_id', 'right') %>%
-    filter(label == 'release')
-  
-  # train model 
-  formula <- generate_formula(model_covs, label = 'is_release', add_interactions)
-  model <- matchit(formula, train, ...)
-  
-  # extract beta subset
-  df_matched <- get_matches(model, train) %>%
-    select(-weights, -distance) %>%
-    filter(label == 'beta')
-  
[…]

### 2019-10-29 perf_release_criteria/milestone_3/ms_2_validation.Rmd
Adding in final validation notebook.

---
title: 'Milestone 2: Model Validation'
output:
  html_notebook:
    theme: cosmo
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
---

# tl;dr 
This notebook determines the model framework utilized for this [PRD](https://docs.google.com/document/d/1Ygz6MkudYHZjnDnD9Z97kUyFrvV3KGWsjXyPjddhHq0/edit#heading=h.lvb9l8gw2nee). It utilizes the results from the hyperparameter tuning step, and trains the optimal model for each algorithm on the v67 dataset. The resultant predictions of these optimal models are compared to a v68 validation dataset. The framework used to generate the highest performant model (e.g., features, hyperparameters) will be used in online model training for the subsetting of Beta in production use.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
source('../lib/supporting_funcs.R')
source('../lib/scoring.R')
library(MatchIt)
```

```{r data_load, echo=FALSE}
file_name = 'df_train_validate_20191025.RData'
image_file_path = file.path('data', file_name)

# Pull from GCP if necessary
if (!file.exists(image_file_path)){
  Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
           "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")
  library(googleCloudStorageR)
  gcs_get_object(file.path('data', 'milestone2', file_name), saveToDisk = image_file_path, overwrite = TRUE)
}

load(image_file_path)
```

```{r var_def, echo=FALSE}
df_rel_val <- df_validate_f %>%
  filter(label == 'release')

df_beta_train <- df_train_f %>% filter(is_release == FALSE)
df_rel_train <- df_train_f %>% filter(is_release == TRUE)
n_beta <- nrow(df_beta_train)
```

# Features
Feature sets:

1. Only performance metrics.
2. Performance metrics and the highest found by Boruta with original dataset.
3. Performance metrics and the highest found by Boruta with equal labels dataset.
4. Performance metrics and all covariates.
5. Only the highest covariates found by Boruta (excluding performance).
6. Only the highest covariates found by Boruta (equal labels, excluding performance).
7. Utilize all covariates (excluding performance).

Retrieve Boruta features:

```{r boruta_import, echo=FALSE, warning=FALSE, message=FALSE}
file_name = 'feature_selection_boruta_initial_20191023.RData'
image_file_path = file.path('data', file_name)

if (!file.exists(image_file_path)){
  Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
           "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")
  library(googleCloudStorageR)
  gcs_get_object(file.path('data', 'milestone2', file_name), saveToDisk = image_file_path, overwrite = TRUE)
}
load(image_file_path)
```

```{r boruta_fs, echo=FALSE}
extract_boruta_fs <- function(boruta_res, num=5){
  features <- NULL
  for(metric in names(boruta_results)){
    features <- c(names(sort(apply(boruta_res[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:num]), features)
  }
  return(sort(unique(features)))
}

features_top10 <- extract_boruta_fs(boruta_results, num=10)
features_top10_eq <- extract_boruta_fs(boruta_results_eq, num=10)

# filter out categorical
features_top10 <- df_train_f %>% 
  select(features_top10) %>% 
  # select_if(is.numeric) %>% 
  names()
features_top10_eq <- df_train_f %>% 
  select(features_top10_eq) %>% 
  # select_if(is.numeric) %>% 
  names()
```

```{r feature_sets, echo=FALSE}
perf_metrics <- names(get_m2_metric_map())

covs <- df_train_f %>%
  select(-perf_metrics) %>%
  select(-content_crashes) %>%
  select(-client_id) %>%
  select(-label) %>%
  select(-is_release) %>%
  select(-app_version) %>%
  # select_if(is.numeric) %>% # Mahalanobis constraint
  names()

fs1 <- perf_metrics
fs2 <- c(names(fs1), features_top10)
fs3 <- c(names(fs1), features_top10_eq)
fs4 <- c(names(fs1), covs)
fs5 <- features_top10
fs6 <- features_top10_eq
fs7 <- covs
```

# Validation Bootstraps

30 bootstrap replicates of v68 Release will be utilized to validate the models. There are `r nrow(df_rel_val)` profiles utilized for this purpose.

```{r bts_validate}
bts = list()
for(i in 1:30){
  bts[[i]] <- df_rel_val %>% 
    sample_frac(size = 1, replace = TRUE) %>%
    pull(client_id) 
}
```

# Oversampling

The entire v67 dataset will be utilized for training. However, most of the matching algorithms are more performant with higher ratios of Beta to Release. There are `r n_beta` profiles utilized for this purpose.

```{r oversampling}
oversample <- function(oversampling, df_beta, df_rel) {
  df_x <- df_rel %>%
    sample_n(size = round(n_beta / oversampling)) %>%
    rbind(df_beta)
  return(df_x)
  }

oversamples <- c(1, 2, 4, 8, 16)
dfs <- lapply(oversamples, oversample, df_beta = df_beta_train, df_rel = df_rel_train)
names(dfs) <- as.character(oversamples)
```

# Model Training

```{r trainer}
train_matchit <- function(train, model_covs, add_interactions, ...){
  # train model
  formula <- generate_formula(model_covs, label = 'is_release', add_interactions)
  model <- matchit(formula, train, ...)

  # extract beta subset
  df_matched <- get_matches(model, train) %>%
    select(-weights, -distance) %>%
    filter(label == 'beta')

  return(list(model = model, matched = df_matched))
}

```

## Nearest-Neighbors, Malahanobis

Hyperparameters:

* Determined in `hyperparameter_tuning_nn_malahanobis.Rmd`
*

```{r nn_mal}
nn.mal <- train_matchit(dfs[['4']], fs1, add_interactions = FALSE, replace = FALSE, distance = "mahalanobis")
```

# Serialize

* The bootsraps and training datasets!

### 2019-10-29 perf_release_criteria/lib/supporting_funcs.R

@@ -59,7 +59,6 @@ generate_formula <- function(tr_cov, label, add_interactions=FALSE){
   else {
     formula <- paste(label, '~', paste(tr_cov, collapse="+"))
   }
-  print(formula)
   return(as.formula(formula))
 }
 

### 2019-10-31 perf_release_criteria/milestone_3/ms_2_scoring_algo_analysis.Rmd
Creating new `milestone 3` directory for analysis.

--- 2019-10-17 perf_release_criteria/scoring_algo_analysis.Rmd
@@
 ---
-title: 'Milestone 2 Test: Scoring Algorithms'
+title: 'Milestone 2: Scoring Algorithms Test'
 output:
-  html_document:
-    df_print: paged
+  html_notebook:
+    theme: cosmo
+    toc: yes
+    toc_float: yes
+  pdf_document:
+    toc: yes
+date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
 ---
@@
 ```{r data_load, echo=FALSE}
-load('data/milestone2/analysis_10022019_corr.RData')
+load('../data/milestone2/analysis_10022019_corr.RData')
 ```

### 2019-11-01 perf_release_criteria/milestone_3/hyperparameter_tuning/hyperparameter_tuning_nn_gam_logit.Rmd
Hyperparameter tuning GAM logit.

---
title: "Milestone 2: Hyperparameter Tuning - Nearest Neighbors, GAM Logit"
author: "Corey Dow-Hygelund, Mozilla Data Science"
date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_notebook:
    theme: cosmo
    toc: true
    toc_float: true
---

# tl;dr

This analysis determines the optimal [hyperparameters] (https://docs.google.com/document/d/1SfuanvmYmvmEFAdQ7Z5djDeLezdNB1TESqVmj93O8to/edit#heading=h.yqukkyb8q4xw) to utilize for computationally intensive statistical matching algorithms proposed in the modeling approach for this [PRD](https://docs.google.com/document/d/1Ygz6MkudYHZjnDnD9Z97kUyFrvV3KGWsjXyPjddhHq0/edit#heading=h.lvb9l8gw2nee).

**Matching Algorithm Tested**: Nearest-neighbors with GAM logit distance metric.

```{r setup, include=FALSE, echo=FALSE}
require("knitr")
knitr::opts_knit$set(root.dir = dirname(getwd()))
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
source('../lib/supporting_funcs.R')
source('../lib/scoring.R')
library(MatchIt)
```

```{r data_load, echo=FALSE}
file_name = 'df_train_validate_20191025.RData'
image_file_path = file.path('data', file_name)

# Pull from GCP if necessary
if (!file.exists(image_file_path)){
  Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
           "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")
  library(googleCloudStorageR)
  gcs_get_object(file.path('data', 'milestone2', file_name), saveToDisk = image_file_path, overwrite = TRUE)

}
load(image_file_path)
```

```{r bts, echo=FALSE}
bts = list(
  bts_1x = bts.1x,
  bts_4x = bts.4x,
  bts_8x = bts.8x,
  bts_16x = bts.16x
)

perf_metrics <- names(get_m2_metric_map())

covs <- df_train_f %>%
  select(-perf_metrics) %>%
  select(-content_crashes) %>%
  select(-client_id) %>%
  select(-label) %>%
  select(-is_release) %>%
  select(-app_version) %>%
  names()

results_file_name <- 'hyperparameter_tuning_nn_gam_logit.RData' 
results_file_path <- file.path('data', results_file_name)
```

# Features
The optimal feature set was found in `feature_selection_nn_gam_logit.Rmd`. At the time of this run they were:

* Beta oversampling by 4x
* FS 1 Interactions: Only performance metrics, with interaction terms

To investigate, and possible utilize, a more general model, the second highest suite of features will also be tested:

* Beta oversapmling by 8x
* FS 5: Only the highest covariates found by Boruta (excluding performance)

```{r boruta_import, echo=FALSE, warning=FALSE, message=FALSE}
file_name = 'feature_selection_boruta_initial_20191023.RData'
image_file_path = file.path('data', file_name)

# Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
#            "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")
# library(googleCloudStorageR)
# gcs_get_object(file.path('data', 'milestone2', file_name), saveToDisk = image_file_path, overwrite = TRUE)

load(image_file_path)
```

```{r boruta_fs, echo=FALSE, warning=FALSE, message=FALSE}
extract_boruta_fs <- function(boruta_res, num=5){
  features <- NULL
  for(metric in names(boruta_results)){
    features <- c(names(sort(apply(boruta_res[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:num]), features)
  }
  return(sort(unique(features)))
}

features_top10 <- extract_boruta_fs(boruta_results, num=10)
features_top10_eq <- extract_boruta_fs(boruta_results_eq, num=10)

# filter out categorical
features_top10 <- df_train_f %>% select(features_top10) %>% select_if(is.numeric) %>% names()
features_top10_eq <- df_train_f %>% select(features_top10_eq) %>% select_if(is.numeric) %>% names()
```

```{r feature_sets}
fs1 <- perf_metrics
fs2 <- c(names(fs1), features_top10)
fs3 <- c(names(fs1), features_top10_eq)
fs4 <- c(names(fs1), covs)
fs5 <- features_top10
fs6 <- features_top10_eq
fs7 <- covs
```

# Hyperparameters
Hyperparameters tested for nearest-neighbors are the following:

* Matching order (m.order)
* Caliper
* of control to treatments

```{r hp}
hps <- list(
  replace = c(TRUE, FALSE),
  caliper = c(0, 0.25, 0.5, 1, 3),
  calclosest = c(TRUE, FALSE),
  ratio = c(1, 2, 4)
)

hps_grid = expand.grid(hps)
```

# FS 1
## Coarse Grid
Hyperparameter tuning on optimal features.

```{r fs1, error=TRUE}
fs1_results <- perform_matchit_hp_tune(df_train_f, bts[['bts_4x']], fs1, size=NULL, workers = 64, hps_grid = hps_grid, 
                                       distance = 'GAMlogit', add_interactions=TRUE)

fs1_results_df <- fs1_results %>% bind_rows()
fs1_results_df %>% group_by_at(setdiff(names(fs1_results_df), "scores")) %>% 
  summarise(mean = mean(scores), sd = sd(scores), median = median(scores)) -> fs1_results_df
knitr::kable(fs1_results_df[order(fs1_results_df$mean), ] %>% head(20))
```

## Fine Grid

```{r hp_fine}
hps_fine <- list(
  replace = c(TRUE, FALSE),
  caliper = seq(0.5, 1.3, by=0.2),
  calclosest = c(TRUE, FALSE),
  ratio = c(1, 2, 3)
)

hps_fine_grid = expand.grid(hps_fine)
```

```{r fs1_fine, error=TRUE}
hps_fine_grid = expand.grid(hps_fine)

fs1_results_final <- perform_matchit_hp_tune(df_train_f, bts[['bts_4x']], fs1, size=NULL, workers = 64, hps_grid = hps_fine_grid, 
                                       distance = 'GAMlogit', add_interactions=TRUE)
save(list=ls(pattern = 'fs[0-9]_results'),  file = results_file_path)

fs1_results_df <- fs1_results_final %>% bind_rows()
fs1_results_df %>% group_by_at(setdiff(names(fs1_results_df), "scores")) %>% 
  summarise(mean = mean(scores), sd = sd(scores), median = median(scores)) -> fs1_results_df
knitr::kable(fs1_results_df[order(fs1_results_df$mean), ] %>% head(20))
```

# FS 5

```{r fs5, error=TRUE}
fs5_results <- perform_matchit_hp_tune(df_train_f, bts[['bts_4x']], fs5, size=NULL, workers = 64, hps_grid = hps_grid, 
                                       distance = 'GAMlogit', add_interactions=FALSE)

fs5_results_df <- fs5_results %>% bind_rows()
fs5_results_df %>% group_by_at(setdiff(names(fs5_results_df), "scores")) %>% 
  summarise(mean = mean(scores), sd = sd(scores), median = median(scores)) -> fs5_results_df
knitr::kable(fs5_results_df[order(fs5_results_df$mean), ])
```

# Push to GCP
Save the resultant dataset and bootstrap samples to an R image.

```{r gcp_storage_push, warning=FALSE}
gcs_file_path <- file.path('data', 'milestone2', results_file_name)

Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
           "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")

library(googleCloudStorageR)

upload_try <- gcs_upload(results_file_path, name = gcs_file_path)
upload_try
```

### 2019-11-06 perf_release_criteria/milestone_3/ms_2_validation.Rmd
Adding in text.

@@
   select(features_top10) %>% 
-  # select_if(is.numeric) %>% 
+  select_if(is.numeric) %>% 
   names()
@@
   select(features_top10_eq) %>% 
-  # select_if(is.numeric) %>% 
+  select_if(is.numeric) %>% 
   names()
@@
   select(-app_version) %>%
-  # select_if(is.numeric) %>% # Mahalanobis constraint
+  select_if(is.numeric) %>% # Mahalanobis constraint
   names()
@@
 
+```{r scorer}
+score_model <- function(bts, df_match, df_val, workers){
+  if (missing(workers)) workers = detectCores()
+  cl <- makePSOCKcluster(workers) 
+  registerDoParallel(cl)
+  final <- tryCatch({
+    scores <- foreach(i=1:length(bts), 
+                      .packages = c('dplyr', 'transport'), 
+                      .export=c('calc_score', 'calc_cms', 'get_m2_metric_map')) %dopar% {
+                        bt <- bts[[i]]
+                        test <- df_val %>% 
+                          right_join(data.frame(client_id = bt, stringsAsFactors=FALSE), by='client_id', 'right')
+
+                        df_scores <- test %>%
+                          bind_rows(df_match)
+
+                        score <- calc_score(df_scores, get_m2_metric_map())
+                        score
+                        }
+    scores <- unlist(scores)
+    c(mean = mean(scores), median = median(scores))
+  }, 
+  error = function(cond){
+    message(paste("Bootstrap validation failed: ", cond))
+    return(NA)
+  },
+  finally = {
+    stopCluster(cl)
+  }
+  )
+  return(final)
+}
+```
+
 # Oversampling
@@
 
+Two matching methods were ultimately tested, as CEM and subclassing were producing extremely poor results.
+
+* nearest-neighbors
+* genetic matching
+
+Feature selection and hyperparameter tuning for the nearest-neighbors models were all trained using the `MatchIt` library.  The following method trains these models using the full training dataset.
+
 ```{r trainer}
@@
 
-Hyperparameters:
+Hyperparameters: `hyperparameter_tuning_nn_malahanobis.Rmd`
 
-* Determined in `hyperparameter_tuning_nn_malahanobis.Rmd`
-*
+* `caliper` = 0.25
+* `calcloset` = TRUE
+* `ratio` = 2
+* `replace` = FALSE
 
-```{r nn_mal}
-nn.mal <- train_matchit(dfs[['4']], fs1, add_interactions = FALSE, replace = FALSE, distance = "mahalanobis")
+```{r nn_mal_fs1}
+nn.mal.fs1 <- train_matchit(dfs[['4']], fs1, add_interactions = FALSE, replace = FALSE, 
+                        caliper = 0.25, calclosest = TRUE, ratio = 2, distance = "mahalanobis")
+score_model(bts, nn.mal.fs1$matched, df_rel_val)
 ```
+
+```{r nn_mal_fs3}
+nn.mal.fs3 <- train_matchit(dfs[['16']], fs3, add_interactions = FALSE, replace = TRUE, 
+                        caliper = 0.25, calclosest = TRUE, ratio = 1, distance = "mahalanobis")
+score_model(bts, nn.mal.fs3$matched, df_rel_val)
+```
+
+```{r nn_mal_fs5}
+nn.mal.fs5 <- train_matchit(dfs[['8']], fs5, add_interactions = FALSE, replace = TRUE, 
+                        caliper = 0.25, calclosest = TRUE, ratio = 1, 
+                        distance = "mahalanobis")
+score_model(bts, nn.mal.fs3$matched, df_rel_val)
+```
+
+## GAM
+
+# TODO
+
+* Build validation methods
+    - Plots
+    - Scoring
+    - Everything I would use for dashboard
 
@@
 
-* The bootsraps and training datasets!
+* The bootstraps and training datasets!
+
+```{r}
+save(nn.mal, 
+     file = '')
+```

### 2019-11-06 perf_release_criteria/milestone_3/feature_selection/feature_selection_genmatch_linear_logit_f.Rmd

---
title: "Milestone 2: Feature Selection - Genetic Matching, Logit, with Linear Propensity Score"
author: "Corey Dow-Hygelund, Mozilla Data Science"
date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_notebook:
    theme: cosmo
    toc: true
    toc_float: true
---

# tl;dr

This analysis determines the relevant [covariates (features)](https://docs.google.com/document/d/1SfuanvmYmvmEFAdQ7Z5djDeLezdNB1TESqVmj93O8to/edit#heading=h.nwwrif453n80) to utilize for computationally intensive statistical matching algorithms proposed in the modeling approach for this [PRD](https://docs.google.com/document/d/1Ygz6MkudYHZjnDnD9Z97kUyFrvV3KGWsjXyPjddhHq0/edit#heading=h.lvb9l8gw2nee).

**Matching Algorithm Tested**: Genetic Matching with logit distance metric transformed back to linear scale

```{r setup, include=FALSE, echo=FALSE}
require("knitr")
knitr::opts_knit$set(root.dir = dirname(getwd()))
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(Matching)
source('../lib/supporting_funcs.R')
source('../lib/scoring.R')
```

```{r data_load, echo=FALSE}
file_name = 'df_train_validate_20191025.RData'
image_file_path = file.path('data', file_name)

# Pull from GCP if necessary
if (!file.exists(image_file_path)){
  Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
           "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")
  library(googleCloudStorageR)
  gcs_get_object(file.path('data', 'milestone2', file_name), saveToDisk = image_file_path, overwrite = TRUE)

}
load(image_file_path)
```

```{r bts, echo=FALSE}
bts = list(
  bts_1x = bts.1x,
  bts_4x = bts.4x,
  bts_8x = bts.8x,
  bts_16x = bts.16x
)

perf_metrics <- names(get_m2_metric_map())

covs <- df_train_f %>%
  select(-perf_metrics) %>%
  select(-content_crashes) %>%
  select(-client_id) %>%
  select(-label) %>%
  select(-is_release) %>%
  select(-app_version) %>%
  select_if(is.numeric) %>% # Mahalanobis constraint
  names()

results_file_name <- 'feature_selection_genmatch_.RData' 
results_file_path <- file.path('data', results_file_name)
```

# Features

Feature sets:

1. Only performance metrics.
2. Performance metrics and the highest found by Boruta with original dataset.
3. Performance metrics and the highest found by Boruta with equal labels dataset.
4. Performance metrics and all covariates.
5. Only the highest covariates found by Boruta (excluding performance).
6. Only the highest covariates found by Boruta (equal labels, excluding performance).
7. Utilize all covariates (excluding performance).

Retrieve Boruta features:

```{r boruta_import}
file_name = 'feature_selection_boruta_initial_20191023.RData'
image_file_path = file.path('data', file_name)

if(!file.exists(image_file_path)){
  Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
             "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")
  library(googleCloudStorageR)
  gcs_get_object(file.path('data', 'milestone2', file_name), saveToDisk = image_file_path, overwrite = TRUE)
}

load(image_file_path)
```

```{r boruta_fs}
extract_boruta_fs <- function(boruta_res, num=5){
  features <- NULL
  for(metric in names(boruta_results)){
    features <- c(names(sort(apply(boruta_res[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:num]), features)
  }
  return(sort(unique(features)))
}

features_top10 <- extract_boruta_fs(boruta_results, num=10)
features_top10_eq <- extract_boruta_fs(boruta_results_eq, num=10)

# filter out categorical
features_top10 <- df_train_f %>% select(features_top10) %>% select_if(is.numeric) %>% names()
features_top10_eq <- df_train_f %>% select(features_top10_eq) %>% select_if(is.numeric) %>% names()
```

```{r feature_sets}
fs1 <- perf_metrics
fs2 <- c(names(fs1), features_top10)
fs3 <- c(names(fs1), features_top10_eq)
fs4 <- c(names(fs1), covs)
fs5 <- features_top10
fs6 <- features_top10_eq
fs7 <- covs
```

# Dataset
Due to the computationally intensive nature of Genetic Matching, a single run for each set will be utilized. This is a compromise due to the deisre to utilize appropriately size datasets, and investigating feature sets. The training set will be equalized in size, with the excluded release profiles used for scoring.

```{r dataset_gen}
df_beta <- df_train_f %>%
  filter(label == 'beta')
set.seed(20191030)
df_rel <- df_train_f %>%
  filter(label == 'release') %>%
  sample_n(size = nrow(df_beta)-100)

set.seed(20191030)
df_train_gen <- df_beta %>%
  bind_rows(df_rel) %>%
  sample_n(size = 90000)

df_test_gen <- df_train_f %>%
  filter(label == 'release') %>%
  filter(!client_id %in% df_train_gen$client_id)
```

```{r}
run_genmatch_sample <- function(df_train, df_test, model_covs, ...){
  workers = detectCores()

  # train model 
  gen1 <- GenMatch(Tr = df_train$is_release, X = df_train[, model_covs], 
                   cluster = rep('localhost', workers), ...)
  mgen1 <- Match(Y = NULL, Tr = df_train$is_release, X = df_train[, model_covs], Weight.matrix = gen1)

  # extract matched dataframe
  df_matched <- df_train[mgen1$index.control,]

  # build dataframe for scoring
  df_scored <- df_matched %>%
    bind_rows(df_test)

  #apply scoring
  return(list(
    score = calc_score(df_scored, get_m2_metric_map()), 
    model = gen1, 
    matches = mgen1)
    )
}
```

# FS 1
Feature selection on only performance metrics

```{r}
fs1_results <- run_genmatch_sample(df_train_gen, df_test_gen, perf_metrics, pop.size = 100, ties = FALSE)
save(list=ls(pattern = 'fs[0-9]_results'),  file = results_file_path)
fs1_results$score
```

## Pop.Size = 500

```{r}
fs1_500_results <- run_genmatch_sample(df_train_gen, df_test_gen, perf_metrics, pop.size = 500, ties = FALSE)
save(list=ls(pattern = 'fs[0-9]_results'),  file = results_file_path)
fs1_500_results$score
```

## nboots = 10
```{r}
fs1_nboots_results <- run_genmatch_sample(df_train_gen, df_test_gen, perf_metrics, 
                                   pop.size = 100, nboots = 10, ties = FALSE)
# save(list=ls(pattern = 'fs[0-9]_results'),  file = results_file_path)
fs1_nboots_results$score
```

# FS 3
```{r fs_3}
fs3_results <- run_genmatch_sample(df_train_gen, df_test_gen, fs3, pop.size = 100, ties = FALSE)
save(list=ls(pattern = 'fs[0-9]_results'),  file = results_file_path)
fs3_results$score
```

# FS 5
```{r fs_5}
fs5_results <- run_genmatch_sample(df_train_gen, df_test_gen, fs5, pop.size = 100, ties = FALSE)
save(list=ls(pattern = 'fs[0-9]_results'),  file = results_file_path)
fs5_results$score
```

```{r serialize_results}
save(list=c('df_train_gen', 'df_test_gen', ls(pattern = 'fs[0-9]')),  file = results_file_path)
```

**TODO**:
1. Adding in propensity score

# Push to GCP
Save the resultant dataset and bootstrap samples to an R image.

```{r gcp_storage_push, warning=FALSE}
gcs_file_path <- file.path('data', 'milestone2', results_file_name)

Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
           "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")

library(googleCloudStorageR)

upload_try <- gcs_upload(results_file_path, name = gcs_file_path)
upload_try
```

### 2019-11-06 perf_release_criteria/milestone_3/feature_selection/feature_selection_nn_mahalanobis.Rmd

--- 2019-10-28 perf_release_criteria/milestone_3/feature_selection_nn_mahalanobis.Rmd
@@
 
+```{r setup, include=FALSE, echo=FALSE}
+require("knitr")
+knitr::opts_knit$set(root.dir = dirname(getwd()))
+```
+
 ```{r, echo=FALSE, warning=FALSE, message=FALSE}
@@
 
-```{r boruta_import}
+```{r boruta_import, echo=FALSE}
 file_name = 'feature_selection_boruta_initial_20191023.RData'
@@
 
-# # Serialize and Push to GCP
+# Serialize and Push to GCP
 Save the resultant dataset and bootstrap samples to an R image.

### 2019-11-06 perf_release_criteria/milestone_3/hyperparameter_tuning/hyperparameter_tuning_nn_logit_linear.Rmd

--- 2019-11-01 perf_release_criteria/milestone_3/hyperparameter_tuning/hyperparameter_tuning_nn_gam_logit.Rmd
@@
 ---
-title: "Milestone 2: Hyperparameter Tuning - Nearest Neighbors, GAM Logit"
+title: "Milestone 2: Hyperparameter Tuning - Nearest Neighbors, Logit w/Linear Propensity Score"
 author: "Corey Dow-Hygelund, Mozilla Data Science"
@@
 
-This analysis determines the optimal [hyperparameters] (https://docs.google.com/document/d/1SfuanvmYmvmEFAdQ7Z5djDeLezdNB1TESqVmj93O8to/edit#heading=h.yqukkyb8q4xw) to utilize for computationally intensive statistical matching algorithms proposed in the modeling approach for this [PRD](https://docs.google.com/document/d/1Ygz6MkudYHZjnDnD9Z97kUyFrvV3KGWsjXyPjddhHq0/edit#heading=h.lvb9l8gw2nee).
+This analysis determines the optimal [hyperparameters](https://docs.google.com/document/d/1SfuanvmYmvmEFAdQ7Z5djDeLezdNB1TESqVmj93O8to/edit#heading=h.yqukkyb8q4xw) to utilize for computationally intensive statistical matching algorithms proposed in the modeling approach for this [PRD](https://docs.google.com/document/d/1Ygz6MkudYHZjnDnD9Z97kUyFrvV3KGWsjXyPjddhHq0/edit#heading=h.lvb9l8gw2nee).
 
-**Matching Algorithm Tested**: Nearest-neighbors with GAM logit distance metric.
+**Matching Algorithm Tested**: Nearest-neighbors with logit distance metric transformed back to linear scale.
 
@@
 
-results_file_name <- 'hyperparameter_tuning_nn_gam_logit.RData' 
+results_file_name <- 'hyperparameter_tuning_nn_logit_linear.RData' 
 results_file_path <- file.path('data', results_file_name)
@@
 # Features
-The optimal feature set was found in `feature_selection_nn_gam_logit.Rmd`. At the time of this run they were:
+The optimal feature set was found in `feature_selection_nn_logit_linear.Rmd`. At the time of this run they were:
 
@@
 fs1_results <- perform_matchit_hp_tune(df_train_f, bts[['bts_4x']], fs1, size=NULL, workers = 64, hps_grid = hps_grid, 
-                                       distance = 'GAMlogit', add_interactions=TRUE)
+                                       distance = 'linear.logit', add_interactions=TRUE)
 
@@
   replace = c(TRUE, FALSE),
-  caliper = seq(0.5, 1.3, by=0.2),
+  caliper = seq(0.2, 0.8, by=0.2),
   calclosest = c(TRUE, FALSE),
@@
 fs1_results_final <- perform_matchit_hp_tune(df_train_f, bts[['bts_4x']], fs1, size=NULL, workers = 64, hps_grid = hps_fine_grid, 
-                                       distance = 'GAMlogit', add_interactions=TRUE)
+                                       distance = 'linear.logit', add_interactions=TRUE)
 save(list=ls(pattern = 'fs[0-9]_results'),  file = results_file_path)
@@
 ```{r fs5, error=TRUE}
-fs5_results <- perform_matchit_hp_tune(df_train_f, bts[['bts_4x']], fs5, size=NULL, workers = 64, hps_grid = hps_grid, 
-                                       distance = 'GAMlogit', add_interactions=FALSE)
+fs3_results <- perform_matchit_hp_tune(df_train_f, bts[['bts_8x']], fs5, size=NULL, workers = 64, hps_grid = hps_grid, 
+                                       distance = 'linear.logit', add_interactions=FALSE)
+save(list=ls(pattern = 'fs[0-9]_results'),  file = results_file_path)
 
-fs5_results_df <- fs5_results %>% bind_rows()
-fs5_results_df %>% group_by_at(setdiff(names(fs5_results_df), "scores")) %>% 
-  summarise(mean = mean(scores), sd = sd(scores), median = median(scores)) -> fs5_results_df
-knitr::kable(fs5_results_df[order(fs5_results_df$mean), ])
+fs3_results_df <- fs3_results %>% bind_rows()
+fs3_results_df %>% group_by_at(setdiff(names(fs3_results_df), "scores")) %>% 
+  summarise(mean = mean(scores), sd = sd(scores), median = median(scores)) -> fs3_results_df
+knitr::kable(fs3_results_df[order(fs3_results_df$mean), ] %>% head(20))
 ```
 
-# Push to GCP
+# Serialize and Push to GCP
 Save the resultant dataset and bootstrap samples to an R image.

### 2019-11-10 perf_release_criteria/milestone_3/ms_2_validation.Rmd
Validation results.

--- 2019-10-29 perf_release_criteria/milestone_3/ms_2_validation.Rmd
@@
 # tl;dr 
-This notebook determines the model framework utilized for this [PRD](https://docs.google.com/document/d/1Ygz6MkudYHZjnDnD9Z97kUyFrvV3KGWsjXyPjddhHq0/edit#heading=h.lvb9l8gw2nee).
+This notebook determines the [model framework](https://docs.google.com/document/d/1SfuanvmYmvmEFAdQ7Z5djDeLezdNB1TESqVmj93O8to/edit#heading=h.ex3kk7zd5a1y) utilized for this [PRD](https://docs.google.com/document/d/1Ygz6MkudYHZjnDnD9Z97kUyFrvV3KGWsjXyPjddhHq0/edit#heading=h.lvb9l8gw2nee).
 It utilizes the results from the hyperparameter tuning step, and trains the optimal model for each algorithm on the v67 dataset.
@@
 library(MatchIt)
+library(cowplot)
+library(ggridges)
+library(viridis)
 ```
@@
 
-Retrieve Boruta features:
-
 ```{r boruta_import, echo=FALSE, warning=FALSE, message=FALSE}
@@
 
-```{r bts_validate}
+```{r bts_validate, echo=FALSE}
+# create once
+file_name = 'validation_bts_20191106.RData'
+bts_file_path = file.path('data', file_name)
+
+if (!file.exists(bts_file_path)){
+  print('Creating validation bootstraps and saving')
   bts = list()
@@
       pull(client_id) 
+  }
+  save(bts, file = bts_file_path)
+} else {
+  print('Loading previously created bootstraps from file')
+  load(bts_file_path)
+}
+```
+
+```{r scorer, echo=FALSE}
+score_model <- function(bts, df_match, df_val, workers){
+  if (missing(workers)) workers = detectCores()
+  cl <- makePSOCKcluster(workers) 
+  registerDoParallel(cl)
+  final <- tryCatch({
+    scores <- foreach(i=1:length(bts), 
+                      .packages = c('dplyr', 'transport'), 
+                      .export=c('calc_score', 'calc_cms', 'get_m2_metric_map')) %dopar% {
+                        bt <- bts[[i]]
+                        test <- df_val %>% 
+                          right_join(data.frame(client_id = bt, stringsAsFactors=FALSE), by='client_id', 'right')
+
+                        df_scores <- test %>%
+                          bind_rows(df_match)
+
+                        score <- calc_score(df_scores, get_m2_metric_map())
+                        score
+                        }
+    scores <- unlist(scores)
+    c(mean = mean(scores), median = median(scores))
+  }, 
+  error = function(cond){
+    message(paste("Bootstrap validation failed: ", cond))
+    return(NA)
+  },
+  finally = {
+    stopCluster(cl)
+  }
+  )
+  return(final)
+}
+
+build_quantile_df <- function(validation, matched, original){
+  qqs <- list()
+  for (perf_metric in perf_metrics){
+    qq <- qqplot(validation[[perf_metric]], matched[[perf_metric]], plot.it = FALSE) %>% 
+      bind_rows() %>%
+      mutate(type = 'matched')
+    qq_full <- qqplot(validation[[perf_metric]], original[[perf_metric]], plot.it = FALSE) %>% 
+      bind_rows() %>%
+      mutate(type = 'original') %>%
+      bind_rows(qq) %>%
+      mutate(metric = perf_metric)
+    # qq_full$metric <- perf_metric
+    qqs[[perf_metric]] <- qq_full
+  }
+  qq_df <- qqs %>% bind_rows() %>% rename(release = x, beta = y)
+  return(qq_df)
+}
+
+plot_validation_results <- function(validation, matched, original, qq_df){
+  if (missing(qq_df)) qq_df <- build_quantile_df(validation, matched, original)
+
+  df <- matched %>%
+      mutate(label = 'beta - matched') %>%
+      bind_rows(validation) %>%
+      bind_rows(original) %>%
+      select(perf_metrics, label) # %>%
+      # gather(key = 'metric', value = 'measurement', -label)
+
+  plots <- list()
+  for (pmet in perf_metrics){
+    p_qq <- ggplot(qq_df %>% filter(metric == pmet), aes(x = release, y = beta)) +
+      geom_point(aes(color = type, shape = type)) + 
+      geom_abline(slope = 1, intercept = 0) + 
+      theme_bw() + 
+      theme(axis.text.x = element_text(angle = 45, hjust = 1),
+            plot.title = element_text(size=10),
+            legend.position = c(0.8, 0.2)) + 
+      ggtitle(pmet)
+
+    p_ridge <- ggplot(df, aes(x=!!sym(pmet), y=label, fill=factor(..quantile..))) +
+    stat_density_ridges(
+      geom = "density_ridges_gradient", calc_ecdf = TRUE,
+      quantiles = 10, quantile_lines = TRUE
+    ) +
+    scale_fill_viridis(discrete = TRUE, name = "Quartiles") + 
+      theme_bw() +
+      xlab(pmet) + 
+      xlim(c(0, 10000)) + 
+      guides(fill = FALSE)
+
+    plots[[paste(pmet, 'qq', sep="_")]] <- p_qq
+    plots[[paste(pmet, 'ridge', sep="_")]] <- p_ridge
+  }
+
+  print(plot_grid(plotlist = plots, ncol = 2))
 }
@@
 However, most of the matching algorithms are more performant with higher ratios of Beta to Release.
+Therefore, various levels of oversampled datasets are created for training.
 There are `r n_beta` profiles utilized for this purpose.
 
-```{r oversampling}
+```{r oversampling, echo=FALSE}
+# create once
+
+file_name = 'training_final_oversamples_20191106.RData'
+oversamples_file_path = file.path('data', file_name)
+
+if (!file.exists(oversamples_file_path)){
+  print('Creating oversampling training sets and saving')
   oversample <- function(oversampling, df_beta, df_rel) {
@@
   names(dfs) <- as.character(oversamples)
+  save(dfs, file = oversamples_file_path)
+} else {
+  print('Loading previously created oversampling training sets from file')
+  load(oversamples_file_path)
+}
 ```
@@
 
-```{r trainer}
+Two matching methods were ultimately tested, as CEM and subclassing were producing extremely poor results.
+
+* nearest-neighbors
+* genetic matching
+
+For all models the following diagnostics are reported:
+
+* mean, median score against the 30 validation replicates
+* Number of matched Beta samples
+* QQ and ridge plots of original and matched Beta samples
+
+## Nearest-Neighbors, Malahanobis
+
+Hyperparameters: `hyperparameter_tuning_nn_malahanobis.Rmd`
+
+Feature selection and hyperparameter tuning for the nearest-neighbors models were all trained using the `MatchIt` library.
+These models are trained using the full, relevantly oversampled, training dataset.
+
+```{r trainer, echo=FALSE}
 train_matchit <- function(train, model_covs, add_interactions, ...){
@@
 
-## Nearest-Neighbors, Malahanobis
+### FS 1
 
-Hyperparameters:
+* `caliper` = 0.20
+* `calcloset` = TRUE
+* `ratio` = 2
+* `replace` = FALSE
+* 4x oversampling
 
-* Determined in `hyperparameter_tuning_nn_malahanobis.Rmd`
-*
-
-```{r nn_mal}
-nn.mal <- train_matchit(dfs[['4']], fs1, add_interactions = FALSE, replace = FALSE, distance = "mahalanobis")
+```{r nn_mal_fs1, echo=FALSE}
+nn.mal.fs1 <- train_matchit(dfs[['4']], fs1, add_interactions = FALSE, replace = FALSE, 
+                        caliper = 0.25, calclosest = TRUE, ratio = 2, distance = "mahalanobis")
+nn.mal.fs1.qq <- build_quantile_df(df_rel_val, nn.mal.fs1$matched, df_beta_train)
+nn.mal.fs1.score <- score_model(bts, nn.mal.fs1$matched, df_rel_val)
+nn.mal.fs1.score
 ```
 
-# Serialize
+Number of Beta samples: `r nrow(nn.mal.fs1$matched)`
 
-* The bootsraps and training datasets!
+```{r nn_mal_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
+plot_validation_results(df_rel_val, nn.mal.fs1$matched, df_beta_train, nn.mal.fs1.qq)
+```
+
+### FS 3
+
+* `caliper` = 3.00
+* `calcloset` = TRUE
+* `ratio` = 1
+* `replace` = TRUE
+* 16x oversampling
+
+```{r nn_mal_fs3, echo=FALSE}
+nn.mal.fs3 <- train_matchit(dfs[['16']], fs3, add_interactions = FALSE, replace = TRUE, 
+                        caliper = 3.00, calclosest = TRUE, ratio = 1, distance = "mahalanobis")
+nn.mal.fs3.qq <- build_quantile_df(df_rel_val, nn.mal.fs3$matched, df_beta_train)
+nn.mal.fs3.score <- score_model(bts, nn.mal.fs3$matched, df_rel_val)
+nn.mal.fs3.score
+```
+Number of Beta samples: `r nrow(nn.mal.fs3$matched)`
+
+```{r nn_mal_fs3_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
+plot_validation_results(df_rel_val, nn.mal.fs3$matched, df_beta_train)
+```
+
+### FS 5
+
+* `caliper` = 0
+* `calcloset` = TRUE
+* `ratio` = 1
+* `replace` = FALSE
+* 8x oversampling
+
+```{r nn_mal_fs5, echo=FALSE}
+nn.mal.fs5 <- train_matchit(dfs[['8']], fs5, add_interactions = FALSE, replace = TRUE, 
+                        caliper = 0, calclosest = TRUE, ratio = 1, 
+                        distance = "mahalanobis")
+nn.mal.fs5.qq <- build_quantile_df(df_rel_val, nn.mal.fs5$matched, df_beta_train)
+nn.mal.fs5.score <- score_model(bts, nn.mal.fs5$matched, df_rel_val)
+nn.mal.fs5.score
+```
+
+Number of Beta samples: `r nrow(nn.mal.fs5$matched)`
+
+```{r nn_mal_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
+plot_validation_results(df_rel_val, nn.mal.fs5$matched, df_beta_train)
+```
+
+## Nearest-Neighbors Logit, Linear
+
+Hyperparameters: `hyperparameter_tuning_nn_logit_linear.Rmd`
+
+```{r feature_sets_nn, echo=FALSE}
+# Reload to add additional categorical covariates
+
+perf_metrics <- names(get_m2_metric_map())
+
+covs <- df_train_f %>%
+  select(-perf_metrics) %>%
+  select(-content_crashes) %>%
+  select(-client_id) %>%
+  select(-label) %>%
+  select(-is_release) %>%
+  select(-app_version) %>%
+  names()
+
+fs1 <- perf_metrics
+fs2 <- c(names(fs1), features_top10)
+fs3 <- c(names(fs1), features_top10_eq)
+fs4 <- c(names(fs1), covs)
+fs5 <- features_top10
+fs6 <- features_top10_eq
+fs7 <- covs
+```
+
+### FS 1
+
+* `caliper` = 0.4
+* `calcloset` = TRUE
+* `ratio` = 3
+* `replace` = FALSE
+* 4x oversampling
+* Interactions across covariates
+
+```{r nn_logit_fs1, warning=FALSE, error=FALSE, echo=FALSE}
+nn.linear.logit.fs1 <- train_matchit(dfs[['4']], fs1, add_interactions = TRUE, replace = FALSE, 
+                        caliper = 0.4, calclosest = TRUE, ratio = 3, distance = "linear.logit")
+nn.linear.logit.fs1.qq <- build_quantile_df(df_rel_val, nn.linear.logit.fs1$matched, df_beta_train)
+nn.linear.logit.fs1.score <- score_model(bts, nn.linear.logit.fs1$matched, df_rel_val)
+nn.linear.logit.fs1.score
+```
+
+Number of Beta samples: `r nrow(nn.linear.logit.fs1$matched)`
+
+```{r nn_logit_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
+plot_validation_results(df_rel_val, nn.linear.logit.fs1$matched, df_beta_train)
+```
+
+### FS 5
+
+* `caliper` = 0
+* `calcloset` = FALSE
+* `ratio` = 1
+* `replace` = FALSE
+* 8x oversampling
+
+```{r nn_logit_fs3, warning=FALSE, error=FALSE, echo=FALSE}
+nn.linear.logit.fs5 <- train_matchit(dfs[['8']], fs5, add_interactions = FALSE, replace = FALSE, 
+                        caliper = 0, calclosest = FALSE, ratio = 1, distance = "linear.logit")
+nn.linear.logit.fs5.qq <- build_quantile_df(df_rel_val, nn.linear.logit.fs5$matched, df_beta_train)
+nn.linear.logit.fs5.score <- score_model(bts, nn.linear.logit.fs5$matched, df_rel_val)
+nn.linear.logit.fs5.score
+```
+
+```{r nn_logit_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
+plot_validation_results(df_rel_val, nn.linear.logit.fs5$matched, df_beta_train)
+```
+
+## Nearest-Neighbors GAM, Logit
+
+Hyperparameters: `hyperparameter_tuning_nn_gam_logit.Rmd`
+
+### FS 1
+
+* `caliper` = 0.5
+* `calcloset` = FALSE
+* `ratio` = 3
+* `replace` = FALSE
+* 4x oversampling
+* Interactions across covariates
+
+```{r nn_gam_fs1, warning=FALSE, error=FALSE, echo=FALSE, message=FALSE}
+nn.gam.fs1 <- train_matchit(dfs[['4']], fs1, add_interactions = TRUE, replace = FALSE, 
+                        caliper = 0.5, calclosest = TRUE, ratio = 3, distance = "GAMlogit")
+nn.gam.fs1.qq <- build_quantile_df(df_rel_val, nn.gam.fs1$matched, df_beta_train)
+nn.gam.fs1.score <- score_model(bts, nn.gam.fs1$matched, df_rel_val)
+nn.gam.fs1.score
+```
+
+Number of Beta samples: `r nrow(nn.gam.fs1$matched)`
+
+```{r nn_gam_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
+plot_validation_results(df_rel_val, nn.gam.fs1$matched, df_beta_train)
+```
+
+### FS 5
+
+* `caliper` = 0
+* `calcloset` = FALSE
+* `ratio` = 1
+* `replace` = FALSE
+* 4x oversampling
+
+```{r nn_gam_fs5, warning=FALSE, error=FALSE, echo=FALSE}
+nn.gam.fs5 <- train_matchit(dfs[['4']], fs5, add_interactions = FALSE, replace = FALSE, 
+                        caliper = 0, calclosest = FALSE, ratio = 1, distance = "GAMlogit")
+nn.gam.fs5.qq <- build_quantile_df(df_rel_val, nn.gam.fs5$matched, df_beta_train)
+nn.gam.fs5.score <- score_model(bts, nn.gam.fs5$matched, df_rel_val)
+nn.gam.fs5.score
+```
+
+Number of Beta samples: `r nrow(nn.gam.fs1$matched)`
+
+```{r nn_gam_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
+plot_validation_results(df_rel_val, nn.gam.fs5$matched, df_beta_train)
+```
+
+## Nearest-Neighbors Probit, Linear
+
+Hyperparameters: `hyperparameter_tuning_nn_probit_linear.Rmd`
+
+### FS 1
+
+* `caliper` = 0.4
+* `calcloset` = FALSE
+* `ratio` = 3
+* `replace` = FALSE
+* 4x oversampling
+* Interactions across covariates
+
+```{r nn_probit_fs1, warning=FALSE, error=FALSE, echo=FALSE}
+nn.linear.probit.fs1 <- train_matchit(dfs[['4']], fs1, add_interactions = TRUE, replace = FALSE, 
+                        caliper = 0.4, calclosest = TRUE, ratio = 3, distance = "linear.probit")
+nn.linear.probit.fs1.qq <- build_quantile_df(df_rel_val, nn.linear.probit.fs1$matched, df_beta_train)
+nn.linear.probit.fs1.score <- score_model(bts, nn.linear.probit.fs1$matched, df_rel_val)
+nn.linear.probit.fs1.score
+```
+
+Number of Beta samples: `r nrow(nn.linear.probit.fs1$matched)`
+
+```{r nn_probit_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
+plot_validation_results(df_rel_val, nn.linear.probit.fs1$matched, df_beta_train)
+```
+
+### FS 5
+
+* `caliper` = 0
+* `calcloset` = FALSE
+* `ratio` = 1
+* `replace` = FALSE
+* 8x oversampling
+
+```{r nn_probit_fs5, warning=FALSE, error=FALSE, echo=FALSE}
+nn.linear.probit.fs5 <- train_matchit(dfs[['8']], fs5, add_interactions = FALSE, replace = FALSE, 
+                        caliper = 0, calclosest = FALSE, ratio = 1, distance = "linear.probit")
+nn.linear.probit.fs5.qq <- build_quantile_df(df_rel_val, nn.linear.probit.fs5$matched, df_beta_train)
+nn.linear.probit.fs5.score <- score_model(bts, nn.linear.probit.fs5$matched, df_rel_val)
+nn.linear.probit.fs5.score
+```
+
+Number of Beta samples: `r nrow(nn.linear.probit.fs5$matched)`
+
+```{r nn_probit_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
+plot_validation_results(df_rel_val, nn.linear.probit.fs5$matched, df_beta_train)
+```
+
+## Genetic Matching
+
+Due to the very long training times of genetic matching, feature selection and hyperparameter tuning were not performed using bootstrap sampes.
+The models were previously trained using the full training sample.
+The resultant match beta subsets were serialized and uploaded to GCP.
+
+Trained: `feature_selection_genmatch_linear.Rmd`
+
+```{r genmatch, echo=FALSE, error=FALSE, warning=FALSE}
+file_name = 'feature_selection_genmatch_.RData'
+image_file_path = file.path('data', file_name)
+
+# Pull from GCP if necessary
+if (!file.exists(image_file_path)){
+  Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
+           "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")
+  library(googleCloudStorageR)
+  gcs_get_object(file.path('data', 'milestone2', file_name), saveToDisk = image_file_path, overwrite = TRUE)
+
+}
+load(image_file_path)
+```
+
+### FS 1
+
+```{r genmatch_fs1, echo=FALSE}
+genmatch.fs1.matched <- df_train_gen[fs1_results$matches$index.control,]
+genmatch.fs1.qq <- build_quantile_df(df_rel_val, genmatch.fs1.matched, df_beta_train)
+genmatch.fs1.score <- score_model(bts, genmatch.fs1.matched, df_rel_val)
+genmatch.fs1.score
+```
+
+Number of Beta samples: `r nrow(genmatch.fs1.matched)`
+
+```{r genmatch_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
+plot_validation_results(df_rel_val, genmatch.fs1.matched, df_beta_train)
+```
+
+#### Pop.Size 500
+
+```{r genmatch_fs1_500, echo=FALSE}
+genmatch.fs1.500.matched <- df_train_gen[fs1_500_results$matches$index.control,]
+genmatch.fs1.500.qq <- build_quantile_df(df_rel_val, genmatch.fs1.500.matched, df_beta_train)
+genmatch.fs1.500.score <- score_model(bts, genmatch.fs1.500.matched, df_rel_val)
+genmatch.fs1.500.score
+```
+
+Number of Beta samples: `r nrow(genmatch.fs1.500.matched)`
+
+```{r genmatch_fs1_500_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
+plot_validation_results(df_rel_val, genmatch.fs1.500.matched, df_beta_train)
+```
+
+### FS 3
+
+```{r genmatch_fs3, echo=FALSE}
+genmatch.fs3.matched <- df_train_gen[fs3_results$matches$index.control,]
+genmatch.fs3.qq <- build_quantile_df(df_rel_val, genmatch.fs3.matched, df_beta_train)
+genmatch.fs3.score <- score_model(bts, genmatch.fs3.matched, df_rel_val)
+genmatch.fs3.score
+```
+
+Number of Beta samples: `r nrow(genmatch.fs3.matched)`
+
+```{r genmatch_fs3_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
+plot_validation_results(df_rel_val, genmatch.fs3.matched, df_beta_train)
+```
+
+### FS 5
+
+```{r genmatch_fs5, echo=FALSE}
+genmatch.fs5.matched <- df_train_gen[fs5_results$matches$index.control,]
+genmatch.fs5.qq <- build_quantile_df(df_rel_val, genmatch.fs5.matched, df_beta_train)
+genmatch.fs5.score <- score_model(bts, genmatch.fs5.matched, df_rel_val)
+genmatch.fs5.score
+```
+
+Number of Beta samples: `r nrow(genmatch.fs3.matched)`
+
+```{r genmatch_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
+plot_validation_results(df_rel_val, genmatch.fs5.matched, df_beta_train)
+```
+
+# Results
+
+Genetic matching produces the optimal matching results.
+It yields the lowest scores, without dropping large sample of the Beta profiles.
+Unsurprisingly, matching directly, and only, on the performance metrics yields the best results.
+Increasing the population size hyperparameter slightly decreased model performance, which is surprising.
+Considering this substantially increases training times, the lower value will be used.
+
+**Conclusion**: Optimal model framework
+
+* matching algorithm: Genetic Matching
+* features: Only performance metrics
+* hyperparameters: Default for `Matching` library
+
+# Push to GCP
+
+The boostrap replicates for validation, oversampled traininig datasets, resultant quantile calculations, and matched datasets are saved to an R image. Then uploaded to the project GCP bucket.
+
+```{r serialize_gcp, echo=FALSE}
+results_file_name = 'validation_results_20191106.RData'
+results_file_path = file.path('data', results_file_name)
+
+objects <- c(
+  ls(pattern = 'genmatch'),
+  ls(pattern = 'nn'),
+  ls(pattern = '^bts$'),
+  ls(pattern = '^dfs$')
+)
+
+save(list = objects, file = results_file_path)
+```
+
+```{r push_to_gcp, echo=FALSE}
+gcs_file_path <- file.path('data', 'milestone2', results_file_name)
+
+Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
+           "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")
+
+library(googleCloudStorageR)
+
+proj_files = gcs_list_objects()
+
+if (gcs_file_path %in% proj_files$name) {
+  print(paste('Previously trained results already exist:', gcs_file_path))
+} else {
+  print(paste('Uploading validation results to GCP:', gcs_file_path))
+  upload_try <- gcs_upload(results_file_path, name = gcs_file_path)
+  upload_try
+}
+```

### 2019-11-21 perf_release_criteria/milestone_3/ms_2_validation.Rmd
Fixing incorrect analysis using unmatched training Beta set for comparison, rather than validation. Updated accordingly.

@@
 df_beta_train <- df_train_f %>% filter(is_release == FALSE)
+df_beta_val <- df_validate_f %>% filter(is_release == FALSE)
 df_rel_train <- df_train_f %>% filter(is_release == TRUE)
-n_beta <- nrow(df_beta_train)
+n_beta <- nrow(df_beta_val)
 ```
@@
                         caliper = 0.25, calclosest = TRUE, ratio = 2, distance = "mahalanobis")
-nn.mal.fs1.qq <- build_quantile_df(df_rel_val, nn.mal.fs1$matched, df_beta_train)
+nn.mal.fs1.qq <- build_quantile_df(df_rel_val, nn.mal.fs1$matched, df_beta_val)
 nn.mal.fs1.score <- score_model(bts, nn.mal.fs1$matched, df_rel_val)
@@
 ```{r nn_mal_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
-plot_validation_results(df_rel_val, nn.mal.fs1$matched, df_beta_train, nn.mal.fs1.qq)
+plot_validation_results(df_rel_val, nn.mal.fs1$matched, df_beta_val, nn.mal.fs1.qq)
 ```
@@
                         caliper = 3.00, calclosest = TRUE, ratio = 1, distance = "mahalanobis")
-nn.mal.fs3.qq <- build_quantile_df(df_rel_val, nn.mal.fs3$matched, df_beta_train)
+nn.mal.fs3.qq <- build_quantile_df(df_rel_val, nn.mal.fs3$matched, df_beta_val)
 nn.mal.fs3.score <- score_model(bts, nn.mal.fs3$matched, df_rel_val)
@@
 ```{r nn_mal_fs3_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
-plot_validation_results(df_rel_val, nn.mal.fs3$matched, df_beta_train)
+plot_validation_results(df_rel_val, nn.mal.fs3$matched, df_beta_val)
 ```
@@
                         distance = "mahalanobis")
-nn.mal.fs5.qq <- build_quantile_df(df_rel_val, nn.mal.fs5$matched, df_beta_train)
+nn.mal.fs5.qq <- build_quantile_df(df_rel_val, nn.mal.fs5$matched, df_beta_val)
 nn.mal.fs5.score <- score_model(bts, nn.mal.fs5$matched, df_rel_val)
@@
 ```{r nn_mal_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
-plot_validation_results(df_rel_val, nn.mal.fs5$matched, df_beta_train)
+plot_validation_results(df_rel_val, nn.mal.fs5$matched, df_beta_val)
 ```
@@
                         caliper = 0.4, calclosest = TRUE, ratio = 3, distance = "linear.logit")
-nn.linear.logit.fs1.qq <- build_quantile_df(df_rel_val, nn.linear.logit.fs1$matched, df_beta_train)
+nn.linear.logit.fs1.qq <- build_quantile_df(df_rel_val, nn.linear.logit.fs1$matched, df_beta_val)
 nn.linear.logit.fs1.score <- score_model(bts, nn.linear.logit.fs1$matched, df_rel_val)
@@
 ```{r nn_logit_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
-plot_validation_results(df_rel_val, nn.linear.logit.fs1$matched, df_beta_train)
+plot_validation_results(df_rel_val, nn.linear.logit.fs1$matched, df_beta_val)
 ```
@@
                         caliper = 0, calclosest = FALSE, ratio = 1, distance = "linear.logit")
-nn.linear.logit.fs5.qq <- build_quantile_df(df_rel_val, nn.linear.logit.fs5$matched, df_beta_train)
+nn.linear.logit.fs5.qq <- build_quantile_df(df_rel_val, nn.linear.logit.fs5$matched, df_beta_val)
 nn.linear.logit.fs5.score <- score_model(bts, nn.linear.logit.fs5$matched, df_rel_val)
@@
 ```{r nn_logit_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
-plot_validation_results(df_rel_val, nn.linear.logit.fs5$matched, df_beta_train)
+plot_validation_results(df_rel_val, nn.linear.logit.fs5$matched, df_beta_val)
 ```
@@
                         caliper = 0.5, calclosest = TRUE, ratio = 3, distance = "GAMlogit")
-nn.gam.fs1.qq <- build_quantile_df(df_rel_val, nn.gam.fs1$matched, df_beta_train)
+nn.gam.fs1.qq <- build_quantile_df(df_rel_val, nn.gam.fs1$matched, df_beta_val)
 nn.gam.fs1.score <- score_model(bts, nn.gam.fs1$matched, df_rel_val)
@@
 ```{r nn_gam_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
-plot_validation_results(df_rel_val, nn.gam.fs1$matched, df_beta_train)
+plot_validation_results(df_rel_val, nn.gam.fs1$matched, df_beta_val)
 ```
@@
                         caliper = 0, calclosest = FALSE, ratio = 1, distance = "GAMlogit")
-nn.gam.fs5.qq <- build_quantile_df(df_rel_val, nn.gam.fs5$matched, df_beta_train)
+nn.gam.fs5.qq <- build_quantile_df(df_rel_val, nn.gam.fs5$matched, df_beta_val)
 nn.gam.fs5.score <- score_model(bts, nn.gam.fs5$matched, df_rel_val)
@@
 ```{r nn_gam_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
-plot_validation_results(df_rel_val, nn.gam.fs5$matched, df_beta_train)
+plot_validation_results(df_rel_val, nn.gam.fs5$matched, df_beta_val)
 ```
@@
                         caliper = 0.4, calclosest = TRUE, ratio = 3, distance = "linear.probit")
-nn.linear.probit.fs1.qq <- build_quantile_df(df_rel_val, nn.linear.probit.fs1$matched, df_beta_train)
+nn.linear.probit.fs1.qq <- build_quantile_df(df_rel_val, nn.linear.probit.fs1$matched, df_beta_val)
 nn.linear.probit.fs1.score <- score_model(bts, nn.linear.probit.fs1$matched, df_rel_val)
@@
 ```{r nn_probit_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
-plot_validation_results(df_rel_val, nn.linear.probit.fs1$matched, df_beta_train)
+plot_validation_results(df_rel_val, nn.linear.probit.fs1$matched, df_beta_val)
 ```
@@
                         caliper = 0, calclosest = FALSE, ratio = 1, distance = "linear.probit")
-nn.linear.probit.fs5.qq <- build_quantile_df(df_rel_val, nn.linear.probit.fs5$matched, df_beta_train)
+nn.linear.probit.fs5.qq <- build_quantile_df(df_rel_val, nn.linear.probit.fs5$matched, df_beta_val)
 nn.linear.probit.fs5.score <- score_model(bts, nn.linear.probit.fs5$matched, df_rel_val)
@@
 ```{r nn_probit_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
-plot_validation_results(df_rel_val, nn.linear.probit.fs5$matched, df_beta_train)
+plot_validation_results(df_rel_val, nn.linear.probit.fs5$matched, df_beta_val)
 ```
@@
 genmatch.fs1.matched <- df_train_gen[fs1_results$matches$index.control,]
-genmatch.fs1.qq <- build_quantile_df(df_rel_val, genmatch.fs1.matched, df_beta_train)
+genmatch.fs1.qq <- build_quantile_df(df_rel_val, genmatch.fs1.matched, df_beta_val)
 genmatch.fs1.score <- score_model(bts, genmatch.fs1.matched, df_rel_val)
@@
 ```{r genmatch_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
-plot_validation_results(df_rel_val, genmatch.fs1.matched, df_beta_train)
+plot_validation_results(df_rel_val, genmatch.fs1.matched, df_beta_val)
 ```
@@
 genmatch.fs1.500.matched <- df_train_gen[fs1_500_results$matches$index.control,]
-genmatch.fs1.500.qq <- build_quantile_df(df_rel_val, genmatch.fs1.500.matched, df_beta_train)
+genmatch.fs1.500.qq <- build_quantile_df(df_rel_val, genmatch.fs1.500.matched, df_beta_val)
 genmatch.fs1.500.score <- score_model(bts, genmatch.fs1.500.matched, df_rel_val)
@@
 ```{r genmatch_fs1_500_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
-plot_validation_results(df_rel_val, genmatch.fs1.500.matched, df_beta_train)
+plot_validation_results(df_rel_val, genmatch.fs1.500.matched, df_beta_val)
 ```
@@
 genmatch.fs3.matched <- df_train_gen[fs3_results$matches$index.control,]
-genmatch.fs3.qq <- build_quantile_df(df_rel_val, genmatch.fs3.matched, df_beta_train)
+genmatch.fs3.qq <- build_quantile_df(df_rel_val, genmatch.fs3.matched, df_beta_val)
 genmatch.fs3.score <- score_model(bts, genmatch.fs3.matched, df_rel_val)
@@
 ```{r genmatch_fs3_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
-plot_validation_results(df_rel_val, genmatch.fs3.matched, df_beta_train)
+plot_validation_results(df_rel_val, genmatch.fs3.matched, df_beta_val)
 ```
@@
 genmatch.fs5.matched <- df_train_gen[fs5_results$matches$index.control,]
-genmatch.fs5.qq <- build_quantile_df(df_rel_val, genmatch.fs5.matched, df_beta_train)
+genmatch.fs5.qq <- build_quantile_df(df_rel_val, genmatch.fs5.matched, df_beta_val)
 genmatch.fs5.score <- score_model(bts, genmatch.fs5.matched, df_rel_val)
@@
 ```{r genmatch_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
-plot_validation_results(df_rel_val, genmatch.fs5.matched, df_beta_train)
+plot_validation_results(df_rel_val, genmatch.fs5.matched, df_beta_val)
 ```

### 2019-12-05 perf_release_criteria/milestone_4/ms_4_datasets_generation.Rmd
Milestone 4: data preparation for training, actual training, subsetting beta.

--- 2019-10-24 perf_release_criteria/milestone_3/ms_2_dataset_generation.Rmd
@@
 ---
-title: 'Milestone 2: Datasets Generation'
+title: 'Milestone 4: Datasets Generation'
 output:
-  html_document:
+  html_notebook:
     theme: cosmo
@@
     toc_float: yes
-  pdf_document:
-    toc: yes
 date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
@@
 source('../lib/supporting_funcs.R')
+library(bigrquery)
+library(DBI)
 ```
@@
 # tl;dr 
-This notebook generates the training and validation datasets used to determine the model framework for this [PRD](https://docs.google.com/document/d/1Ygz6MkudYHZjnDnD9Z97kUyFrvV3KGWsjXyPjddhHq0/edit#heading=h.lvb9l8gw2nee).
-These datasets will be used for all steps in the process detailed out in the [document](https://docs.google.com/document/d/1SfuanvmYmvmEFAdQ7Z5djDeLezdNB1TESqVmj93O8to/edit#heading=h.nwwrif453n80).
-In addition, the bootstrap replicates for feature selection and hyperparameter tuning are created.
-These datasets are all stored in GCP under the `moz-fx-dev-cdowhyglund-subBeta` project.
+This notebook generates the training (Version N) and prediction (Version N+1) datasets used for measuring Release performance  [PRD](https://docs.google.com/document/d/1Ygz6MkudYHZjnDnD9Z97kUyFrvV3KGWsjXyPjddhHq0/edit#heading=h.lvb9l8gw2nee).
+The training dataset is used to train a stastical matching model, which then is used to find a subset of Beta profiles.
+These profiles are then used in the prediction dataset to calculate the various performance metrics.
 
 # Dataset Preparation
-The datasets were generated by this [notebook](https://dbc-caf9527b-e073.cloud.databricks.com/#notebook/210500/command/210501). The files were manually downloaded from S3 on hala.
+The datasets are generated by this [notebook](
+https://storage.cloud.google.com/moz-fx-data-bq-data-science-cdowhygelund/notebooks/jupyter/Beta_Release_Subsetting_Data_Preparation_GCP.ipynb
+) on a Dataproc cluster.
+These are serialized as BigQuery tables available in the `moz-fx-data-shared-prod.analysis` dataset as `cdowhygelund_subBeta_training` (Version N) and `cdowhygelund_subBeta_prediction` (Version N+1).
 
@@
 
+```{r gcp_connect, echo=FALSE}
+project <- "moz-fx-dev-cdowhyglund-subbeta"
+
+con <- dbConnect(
+  bigrquery::bigquery(),
+  project = 'moz-fx-data-shared-prod',
+  dataset = 'analysis',
+  billing = project
+)
+```
+
 ```{r var_defs, echo=FALSE}
-outcomes <- c('TIME_TO_DOM_INTERACTIVE_MS', 'TIME_TO_DOM_CONTENT_LOADED_END_MS', 'TIME_TO_LOAD_EVENT_END_MS', 
-              'TIME_TO_NON_BLANK_PAINT_MS', 'TIME_TO_DOM_COMPLETE_MS', 'FX_PAGE_LOAD_MS_2_PARENT')
+# outcomes <- c('TIME_TO_DOM_INTERACTIVE_MS', 'TIME_TO_DOM_CONTENT_LOADED_END_MS', 'TIME_TO_LOAD_EVENT_END_MS', 
+#               'TIME_TO_NON_BLANK_PAINT_MS', 'TIME_TO_DOM_COMPLETE_MS', 'FX_PAGE_LOAD_MS_2_PARENT') (FIXME)
+
+outcomes <- c('TIME_TO_DOM_CONTENT_LOADED_END_MS', 'TIME_TO_LOAD_EVENT_END_MS', 'TIME_TO_DOM_COMPLETE_MS', 'FX_PAGE_LOAD_MS_2_PARENT')
+
+# define response field
+label <- 'is_release'
 ```
@@
 ```{r data_prep}
-# define response field
-label <- 'is_release'
-
-load_df <- function(file_path){
-  df <- read.csv(file_path) %>%
-    mutate(client_id = as.character(client_id)) %>%
-    filter(locale %in% c('en-US', 'en-GB')) %>%
+load_df <- function(table){
+  df <- tbl(con, table) %>%
+#     filter(locale %in% c('en-US', 'en-GB')) %>%  (FIXME)
     filter(country %in% c('US', 'GB')) %>%
     filter(os == 'Windows_NT') %>%
-    select(-os, country, locale) %>%
+    collect() %>%
+    # mutate(client_id = as.character(client_id)) %>%
+    select(-os, country) %>%
     drop_na(outcomes) %>%
@@
 
-df_train <- load_df('data/df_pd_67.csv')
-df_validate <- load_df('data/df_pd_68.csv')
+df_train <- load_df("cdowhygelund_subBeta_training")
+df_validate <- load_df('cdowhygelund_subBeta_prediction')
 ```
@@
 
+These observations were noted previously during Milestone 2 (`ms_2_datasets_generation.Rmd`). Noting here now for completeness.
 * Content crashes looks strange. Always is 0. Not sure what happened there...
@@
 
-# Bootstrap Samples
+# Modeling Dataset
 
-```{r balancing, echo=FALSE}
-channel_counts <- df_train_f %>% count(label)
-release_overcount <- channel_counts$n[channel_counts$label == 'release'] - channel_counts$n[channel_counts$label == 'beta']
-```
+The optimal modeling dataset utilized an 4x oversampling of Beta with respect to Release.
 
-The feature selection will utilize 10 boostrap replicates, which are generated as follows:
-1. The entire `df_train` dataset is sampled at 100% with replacement.
-2. A sample of Release (`is_release = TRUE`) `client_id` are taken of the same size as Beta (`r channel_counts$n[channel_counts$label == 'beta']`)
-3. The entire (resampled) Beta `client_id` are combined with this sampled Release ids. 
-    - These are the profiles that will be used for building the matching model. 
-    - The matched Beta profiles will be used for scoring the model. 
-4. The remaining Release ids will be used for scoring the model.
-
-The same set of bootstrap samples will be used for all feature selection across modeling algorithms.
-A suite of these are created to represent different levels of Beta oversampling with respect to Release.
-
-```{r bootstrap_def}
-extract_ids <- function(df_c, oversampling){
+```{r training_oversample}
+oversample <- function(df_c, oversampling){
   df_beta <- df_c %>% filter(is_release == FALSE)
@@
 
-  # create the dataset for scoring matching model
-  test_ids <- df_rel %>% 
-    filter(!client_id %in% model_ids) %>%
-    pull(client_id)
-
-  return(list(train = model_ids, test = test_ids))
+  return(df_c %>% filter(client_id %in% model_ids))
 }
 
-gen_bootstraps <- function(df_train, oversampling = 1, num_bts = 10){
-  bts <- list()
-  for (i in 1:num_bts){
-    # create a resampled version of entire dataframe
-    df_resampled <- df_train %>% sample_frac(replace = TRUE)
-    # create train/test "splits"
-    bts[[i]] <- extract_ids(df_resampled, oversampling = oversampling)
-  }
-  return(bts)
-}
-```
-
-```{r bootstrap_gen}
-bts.1x <- gen_bootstraps(df_train_f)
-bts.4x <- gen_bootstraps(df_train_f, oversampling = 4)
-bts.8x <- gen_bootstraps(df_train_f, oversampling = 8)
-bts.16x <- gen_bootstraps(df_train_f, oversampling = 16)
+df_train_x <- oversample(df_train_f, oversampling = 4)
 ```
@@
 ```{r serialize_dataset}
-image_file_name <- paste('df_train_validate_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
+image_file_name <- paste('df_train_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
 image_file_path <- file.path('data', image_file_name)
-save(df_train_f, df_validate_f, bts.1x, bts.4x, bts.8x, bts.16x,
-     file = image_file_path)
+save(df_train_f, df_validate_f, df_train_x, file = image_file_path)
 
-gcs_file_path <- file.path('data', 'milestone2', image_file_name)
+gcs_file_path <- file.path('data', 'milestone4', image_file_name)
 ```
@@
 Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
-           "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")
+           "GCS_AUTH_FILE" = "~/certs/moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")
 

### 2019-12-05 perf_release_criteria/milestone_4/training_data_pull.Rmd
Milestone 4: data preparation for training, actual training, subsetting beta.

---
title: "R Notebook"
output: html_notebook
---

```{r}
library(bigrquery)
```

```{r}
project <- "moz-fx-dev-cdowhyglund-subbeta"
```

```{r}
# This doesn't work yields error: "Error: Don't know how to convert type numeric"

# sql <- "
# SELECT *
# from `moz-fx-data-shared-prod.analysis.cdowhygelund_subBeta_training` 
# "
#  
# train_df <- query_exec(sql, project = project, use_legacy_sql = FALSE)
```

```{r}
library(DBI)
library(dplyr)

con <- dbConnect(
  bigrquery::bigquery(),
  project = 'moz-fx-data-shared-prod',
  dataset = 'analysis',
  billing = project
)

training_tbl <- tbl(con, "cdowhygelund_subBeta_training")

df <- training_tbl %>%
  collect()
```

### 2019-12-05 perf_release_criteria/lib/modeling.R

@@ -1,0 +1,19 @@
+train_matchit <- function(train, model_covs, add_interactions, ...){
+  # train model
+  formula <- generate_formula(model_covs, label = 'is_release', add_interactions)
+  model <- matchit(formula, train, ...)
+  
+  # extract beta subset
+  df_matched <- get_matches(model, train) %>%
+    select(-weights, -distance) %>%
+    filter(label == 'beta')
+  
+  return(list(model = model, matched = df_matched))
+}
+
+extract_predictions <- function(matched, validation){
+  prediction <- validation %>%
+    filter(client_id %in% matched$client_id)
+  
+  return(prediction)
+}

### 2019-12-06 poc/EDA/EDA.Rmd
creating EDA directory + initializing R markdown

---
title: "Mozilla Data Science Project - 2019"
author: "Mariana de Oliveira Santos Silva"
date: "December 05, 2019"
output: 
  html_document:
    toc: true
    theme: united
    highlight: textmate
---

# Exploratory Data Analysis (EDA) {.tabset}

This R markdown covers the Exploratory Data Analysis (EDA) on the training dataset of the PRD.

## Setting-up

```{r message=FALSE, warning=FALSE}
## Loading the needed libraries

library(kableExtra)      # help you build common complex tables and manipulate table styles
library(tidyverse)       # for general data wrangling (includes readr and dplyr)
library(ggplot2)         # to draw statistical plots 
library(plotly)          # to construct interactive 3d plots
library(DataExplorer)    # automated data exploration
library(corrplot)        # to plot nice correlation matrix
library(caret)           # includes several functions to pre-process
library(scales)          # to determining breaks and labels for axes and legends
library(skimr)
library(funModeling) 
library(Hmisc)
```

```{r message=FALSE, warning=FALSE}
## Loading the training dataset

load("~/GitHub/ff-beta-release-matching/poc/EDA/data_milestone2_df_train_validate_20191021.RData")
```

```{r message=FALSE, warning=FALSE}
## View train dataframe

kable(head(df_train_f)) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
scroll_box(width = "100%")
```

## Step 1 : Data Inspection

To get introduced to our dataset:

```{r}
kable(introduce(df_train_f)) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
scroll_box(width = "100%")
```

Let's have a look on the basic information of the dataset.

```{r, fig.width = 10, fig.height = 5}
plot_intro(df_train_f, ggtheme = theme_minimal())
```

Sanity check on the structure and show sample data for each variable.

```{r}
str(df_train_f)
```

When we get a new dataset to analyze, is important to know if there are missing values and the data type. The `df_status` function can help us by showing these numbers in relative and percentage values.

```{r}
kable(df_status(df_train_f)) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
scroll_box(width = "100%")
```

* `q_zeros`: quantity of zeros (`p_zeros`: in percent)
* `q_inf`: quantity of infinite values (`p_inf`: in percent)
* `q_na`: quantity of NA (`p_na`: in percent)
* `type`: factor, ordered-factor, numeric, integer or character
* `unique`: quantity of unique values

> Are all the variables in the correct data type?

`to-do`

<!-- Some variables are encoded as numbers, but they are codes or categories and the models don't handle them in the same way. -->

> Any variables with lots of zeros?

Yes. Variables with lots of zeros may not be useful for modeling and, in some cases, they may dramatically bias the model.

> Any variables with lots of NAs?

None. Good news.

> Any high cardinality variable?

`to-do`
<!-- Factor/categorical variables with a high number of different values (~30) tend to do overfitting if the categories have low cardinality. -->

## Step 2 : Analyzing Categorical Variables

```{r}
df_release <- df_train_f[which(df_train_f$label == 'release'), ]
df_beta <- df_train_f[which(df_train_f$label == 'beta'), ]

freq(df_train_f$label)
```

```{r, fig.width = 15, fig.height = 15}
## Frequency distribution of all discrete variables
plot_bar(df_train_f)
```

```{r, fig.width = 15, fig.height = 15}
## Frequency distribution for release dataframe
plot_bar(df_release)
```

```{r, fig.width = 15, fig.height = 15}
## Frequency distribution beta dataframe
plot_bar(df_beta)
```

### EDA on Coninuous Variables

```{r, fig.width = 15, fig.height = 15}
## View histogram of all continuous variables
plot_histogram(df_train_f)
```

```{r, fig.width = 15, fig.height = 15}
## View histogram of all continuous variables
plot_histogram(df_release)
```

```{r, fig.width = 15, fig.height = 15}
## View histogram of all continuous variables
plot_histogram(df_beta)
```

### 2019-12-06 poc/EDA/EDA.Rmd
updating the R markdown

@@
     theme: united
-    highlight: textmate
+    highlight: tango
+    df_print: kable
 ---
@@
 ## Setting-up
-
 ```{r message=FALSE, warning=FALSE}
@@
 library(Hmisc)
+library(grid)
+library(hrbrthemes)
+library(tidyr)
+library(viridis)
+library(ggthemes)
 ```
@@
 
-To get introduced to our dataset:
+To get introduced to our dataset, et's have a look on the basic information of the dataset.
 
-```{r}
+```{r echo=FALSE}
 kable(introduce(df_train_f)) %>%
@@
 
-Let's have a look on the basic information of the dataset.
-
-```{r, fig.width = 10, fig.height = 5}
+```{r echo=FALSE, fig.height=10, fig.width=10}
 plot_intro(df_train_f, ggtheme = theme_minimal())
@@
 
-Sanity check on the structure and show sample data for each variable.
+### Observations
+
+* Most of the dataset is composed of continuous variables
+* No NAs values (were handled in preprocessing)
+
+### Structure
+
+Let's use `glimpse` function to display a vertical preview of the dataset. So we can easily preview data type and sample data.
 
 ```{r}
-str(df_train_f)
+glimpse(df_train_f)
 ```
 
-When we get a new dataset to analyze, is important to know if there are missing values and the data type.
-The `df_status` function can help us by showing these numbers in relative and percentage values.
+If we want to get some metrics about data types, zeros, infinite numbers, and missing values, we can use the `df_status` function.
 
 ```{r}
-kable(df_status(df_train_f)) %>%
+kable(df_status(df_train_f, FALSE)) %>%
 kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
@@
 
+#### Observations
+
 > Are all the variables in the correct data type?
 
-`to-do`
-
-<!-- Some variables are encoded as numbers, but they are codes or categories and the models don't handle them in the same way. -->
+None. It seems that this has already been dealt with in preprocessing.
 
@@
 
-Yes. Variables with lots of zeros may not be useful for modeling and, in some cases, they may dramatically bias the model.
+Yes. Variables with lots of zeros may not be useful for modeling and, in some cases, they may dramatically bias the model. For example, the `content_crashes` is 100% equal to zero.
 
@@
 
-`to-do`
-<!-- Factor/categorical variables with a high number of different values (~30) tend to do overfitting if the categories have low cardinality. -->
+Factor/categorical variables with a high number of different values (~30) tend to do overfitting if the categories have low cardinality.
+Besides `client_id`, it doesn't seem like there are other high cardinality variables.
 
-## Step 2 : Analyzing Categorical Variables
+## Step 2 : Beta vs Release
 
-```{r}
+```{r, fig.width = 7.5}
 df_release <- df_train_f[which(df_train_f$label == 'release'), ]
@@
 
-freq(df_train_f$label)
+f <- freq(df_train_f$label)
 ```
 
-```{r, fig.width = 15, fig.height = 15}
-## Frequency distribution of all discrete variables
-plot_bar(df_train_f)
+```{r}
+summary(df_release)
 ```
 
+```{r}
+summary(df_beta)
+```
+
+## Step 3 - Analyzing Discrete Variables
+
 ```{r, fig.width = 15, fig.height = 15}
-## Frequency distribution for release dataframe
-plot_bar(df_release)
+## Frequency distribution release dataframe
+plot_bar(df_release, ggtheme = theme_minimal(base_size = 15))
 ```
@@
 ## Frequency distribution beta dataframe
-plot_bar(df_beta)
+plot_bar(df_beta, ggtheme = theme_minimal(base_size = 15))
 ```
 
-### EDA on Coninuous Variables
+## Step 4 - Analyzing Continuos Variables
 
 ```{r, fig.width = 15, fig.height = 15}
-## View histogram of all continuous variables
-plot_histogram(df_train_f)
+## View histogram of release dataset
+plot_histogram(df_release, ggtheme = theme_minimal(base_size = 15))
 ```
@@
 ```{r, fig.width = 15, fig.height = 15}
-## View histogram of all continuous variables
-plot_histogram(df_release)
+## View histogram of beta dataset
+plot_histogram(df_beta, ggtheme = theme_minimal(base_size = 15))
 ```
 
-```{r, fig.width = 15, fig.height = 15}
-## View histogram of all continuous variables
-plot_histogram(df_beta)
+```{r message=FALSE, warning=FALSE}
+ggplot(data=df_train_f, aes(x=daily_max_tabs, group=label, fill=label)) +
+    geom_density(adjust=1.5, alpha=0.6, main="Daily Max Tabs") + xlim(0, 20) +
+    scale_fill_viridis(discrete=TRUE) +
+    scale_color_viridis(discrete=TRUE) +
+    theme_ipsum()
 ```
+
+```{r message=FALSE, warning=FALSE}
+ggplot(data=df_train_f, aes(x=startup_ms, group=label, fill=label)) +
+    geom_density(adjust=1.5, alpha=0.6, main="Startup (ms)") + xlim(0, 5) +
+    scale_fill_viridis(discrete=TRUE) +
+    scale_color_viridis(discrete=TRUE) +
+    theme_ipsum()
+```
+
+```{r message=FALSE, warning=FALSE}
+ggplot(data=df_train_f, aes(x=num_active_days, group=label, fill=label)) +
+    geom_histogram(stat = "bin", position = "identity", alpha=0.5, main="Num Active Days") +
+    scale_fill_viridis(discrete=TRUE) +
+    scale_color_viridis(discrete=TRUE) +
+    theme_ipsum()
+```
+
+```{r message=FALSE, warning=FALSE}
+ggplot(data=df_train_f, aes(x=active_hours, group=label, fill=label)) +
+    geom_density(adjust=1.5, alpha=0.6, main="Active Hours") +
+    scale_fill_viridis(discrete=TRUE) +
+    scale_color_viridis(discrete=TRUE) +
+    theme_ipsum()
+```
+
+```{r message=FALSE, warning=FALSE}
+ggplot(data=df_train_f, aes(x=num_pages, group=label, fill=label)) +
+    geom_density(adjust=1.5, alpha=0.6, main="Num Pages") + xlim(0, 50000) +
+    scale_fill_viridis(discrete=TRUE) +
+    scale_color_viridis(discrete=TRUE) +
+    theme_ipsum()
+```
+
+```{r message=FALSE, warning=FALSE}
+ggplot(data=df_train_f, aes(x=daily_num_sessions_started, group=label, fill=label)) +
+    geom_density(adjust=1.5, alpha=0.6, main="Daily Num Sessions Started") + xlim(0, 20) +
+    scale_fill_viridis(discrete=TRUE) +
+    scale_color_viridis(discrete=TRUE) +
+    theme_ipsum()
+```
+
+```{r message=FALSE, warning=FALSE}
+ggplot(data=df_train_f, aes(x=TIME_TO_DOM_INTERACTIVE_MS, group=label, fill=label)) +
+    geom_density(adjust=1.5, alpha=0.6, main="Time to DOM Interactive (ms)") +
+    scale_fill_viridis(discrete=TRUE) +
+    scale_color_viridis(discrete=TRUE) +
+    theme_ipsum()
+```
+
+```{r message=FALSE, warning=FALSE}
+ggplot(data=df_train_f, aes(x=FX_PAGE_LOAD_MS_2_PARENT, group=label, fill=label)) +
+    geom_density(adjust=1.5, alpha=0.6, main="FX Page Load (ms)") +
+    scale_fill_viridis(discrete=TRUE) +
+    scale_color_viridis(discrete=TRUE) +
+    theme_ipsum()
+```
+
+```{r message=FALSE, warning=FALSE}
+ggplot(data=df_train_f, aes(x=TIME_TO_DOM_CONTENT_LOADED_END_MS, group=label, fill=label)) +
+    geom_density(adjust=1.5, alpha=0.6, main="Time to DOM Content Loaded End (ms)") +
+    scale_fill_viridis(discrete=TRUE) +
+    scale_color_viridis(discrete=TRUE) +
+    theme_ipsum()
+```
+
+```{r message=FALSE, warning=FALSE}
+ggplot(data=df_train_f, aes(x=TIME_TO_LOAD_EVENT_END_MS, group=label, fill=label)) +
+    geom_density(adjust=1.5, alpha=0.6, main="Time to Load Event End (ms)") +
+    scale_fill_viridis(discrete=TRUE) +
+    scale_color_viridis(discrete=TRUE) +
+    theme_ipsum()
+```
+
+```{r message=FALSE, warning=FALSE}
+ggplot(data=df_train_f, aes(x=TIME_TO_NON_BLANK_PAINT_MS, group=label, fill=label)) +
+    geom_density(adjust=1.5, alpha=0.6, main="Time to Non Blank Paint (ms)") +
+    scale_fill_viridis(discrete=TRUE) +
+    scale_color_viridis(discrete=TRUE) +
+    theme_ipsum()
+```
+
+```{r message=FALSE, warning=FALSE}
+ggplot(data=df_train_f, aes(x=TIME_TO_DOM_COMPLETE_MS, group=label, fill=label)) +
+    geom_density(adjust=1.5, alpha=0.6, main="Time to DOM Complete (ms)") +
+    scale_fill_viridis(discrete=TRUE) +
+    scale_color_viridis(discrete=TRUE) +
+    theme_ipsum()
+```
+
+### Observations

### 2019-12-06 perf_release_criteria/data_prep/milestone_3.py
Adding milestone 3 modeling dataset generation notebook.

@@ -1,0 +1,271 @@
+# Databricks notebook source
+# MAGIC %md # Description
+# MAGIC 
+# MAGIC Generates training, prediction, and validation datasets to determing [modeling framework](https://docs.google.com/document/d/1SfuanvmYmvmEFAdQ7Z5djDeLezdNB1TESqVmj93O8to/edit#) for this [PRD](https://docs.google.com/document/d/1Ygz6MkudYHZjnDnD9Z97kUyFrvV3KGWsjXyPjddhHq0/edit#heading=h.x5t09uq91x6z). 
+# MAGIC 
+# MAGIC * Utilize a two-week window. During a four week release cycle, this ensures the model framework is optimal for over half the cycle.
+# MAGIC * Focuses on US/GB countries, and en-US/en-GB locales. 
+# MAGIC   - Subsequent training sets will generated in separate notebooks.
+# MAGIC   - This implies that their will be multiple modeling frameworks for full coverage of all countries and locales. 
+
+# COMMAND ----------
+
+# MAGIC %md # Imports
+
+# COMMAND ----------
+
+import pyspark.sql.functions as F
+import pyspark.sql.types as T
+from pyspark.sql import Window
+import datetime as dt
+from io import StringIO
+import boto3
+import pandas as pd
+
+# COMMAND ----------
+
+# MAGIC %md
+# MAGIC * Beta and Release subsets
+# MAGIC   - Training: V67
+# MAGIC   - Validation: V68
+# MAGIC   - Beta: Last two weeks 
+# MAGIC   - Release: First two weeks
+# MAGIC   - en-US, en-GB locales
+# MAGIC   - US, GB country
+
+# COMMAND ----------
+
+NUM_DAYS = 7
+NUM_WEEKS  = 2
+
+DATA_BUCKET = "net-mozaws-prod-us-west-2-pipeline-analysis"
+DATA_PATH = 'cdowhygelund/subBeta/US_GB_country/US_GB_locale'
+
+# COMMAND ----------
+
+cd = spark.table('clients_daily')
+ms = spark.table('main_summary')
+
+# COMMAND ----------
+
+# MAGIC %md # Metrics and Methods
+
+# COMMAND ----------
+
+# MAGIC %md Load up the notebook containing the metric (covariates and responses) and data preparation methods.
[…]

### 2019-12-11 poc/EDA/EDA.Rmd
updating EDA notebook

@@
 library(viridis)
+library(ggpubr)
 library(ggthemes)
+library(GGally)
 ```
@@
 
-load("~/GitHub/ff-beta-release-matching/poc/EDA/data_milestone2_df_train_validate_20191021.RData")
+load("~/GitHub/ff-beta-release-matching/poc/EDA/data_milestone2_df_train_validate_20191025.RData")
 ```
@@
 Factor/categorical variables with a high number of different values (~30) tend to do overfitting if the categories have low cardinality.
-Besides `client_id`, it doesn't seem like there are other high cardinality variables.
 
@@
 
+### Analysing User Engagement Metrics
+
 ```{r message=FALSE, warning=FALSE}
-ggplot(data=df_train_f, aes(x=daily_max_tabs, group=label, fill=label)) +
-    geom_density(adjust=1.5, alpha=0.6, main="Daily Max Tabs") + xlim(0, 20) +
+ggplot(data=df_train_f, aes(x=uri_count, group=label, fill=label)) +
+    geom_density(adjust=1.5, alpha=0.6) + xlim(0, 1000) +
     scale_fill_viridis(discrete=TRUE) +
     scale_color_viridis(discrete=TRUE) +
-    theme_ipsum()
-```
-
-```{r message=FALSE, warning=FALSE}
-ggplot(data=df_train_f, aes(x=startup_ms, group=label, fill=label)) +
-    geom_density(adjust=1.5, alpha=0.6, main="Startup (ms)") + xlim(0, 5) +
-    scale_fill_viridis(discrete=TRUE) +
-    scale_color_viridis(discrete=TRUE) +
-    theme_ipsum()
-```
-
-```{r message=FALSE, warning=FALSE}
-ggplot(data=df_train_f, aes(x=num_active_days, group=label, fill=label)) +
-    geom_histogram(stat = "bin", position = "identity", alpha=0.5, main="Num Active Days") +
-    scale_fill_viridis(discrete=TRUE) +
-    scale_color_viridis(discrete=TRUE) +
+    labs(title="URI Count Density Curve",x="URI Count", y = "Density") +
     theme_ipsum()
@@
 ggplot(data=df_train_f, aes(x=active_hours, group=label, fill=label)) +
-    geom_density(adjust=1.5, alpha=0.6, main="Active Hours") +
+    geom_density(adjust=1.5, alpha=0.6) +
     scale_fill_viridis(discrete=TRUE) +
     scale_color_viridis(discrete=TRUE) +
+    labs(title="Active Hours Density Curve",x="Active Hours", y = "Density") +
     theme_ipsum()
@@
 ggplot(data=df_train_f, aes(x=num_pages, group=label, fill=label)) +
-    geom_density(adjust=1.5, alpha=0.6, main="Num Pages") + xlim(0, 50000) +
+    geom_density(adjust=1.5, alpha=0.6) + xlim(0, 50000) +
     scale_fill_viridis(discrete=TRUE) +
     scale_color_viridis(discrete=TRUE) +
+    labs(title="Num Pages Density Curve",x="Num Pages", y = "Density") +
     theme_ipsum()
@@
 ```{r message=FALSE, warning=FALSE}
-ggplot(data=df_train_f, aes(x=daily_num_sessions_started, group=label, fill=label)) +
-    geom_density(adjust=1.5, alpha=0.6, main="Daily Num Sessions Started") + xlim(0, 20) +
+ggplot(data=df_train_f, aes(x=session_length, group=label, fill=label)) +
+    geom_density(adjust=1.5, alpha=0.6, main="Session Length") + xlim(0, 75) +
     scale_fill_viridis(discrete=TRUE) +
     scale_color_viridis(discrete=TRUE) +
+    labs(title="Session Length Density Curve",x="Session Length", y = "Density") +
     theme_ipsum()
@@
 
-```{r message=FALSE, warning=FALSE}
-ggplot(data=df_train_f, aes(x=TIME_TO_DOM_INTERACTIVE_MS, group=label, fill=label)) +
-    geom_density(adjust=1.5, alpha=0.6, main="Time to DOM Interactive (ms)") +
-    scale_fill_viridis(discrete=TRUE) +
-    scale_color_viridis(discrete=TRUE) +
-    theme_ipsum()
+# User Engagement Metrics {.tabset}
+
+This project will focus on user engagement metrics to ensure the most performant model possible. So, we are going to analyze the following metrics:
+
+* `num_active_days`
+* `active_hours`
+* `active_hours_max`
+* `uri_count`
+* `uri_count_max`
+* `session_length`
+* `session_length_max`
+* `search_count`
+* `search_count_max`
+* `num_bookmarks`
+* `num_pages`
+* `num_pages_max`
+* `daily_unique_domains`
+* `daily_max_tabs`
+* `daily_tabs_opened`
+* `daily_num_sessions_started`
+* `daily_unique_domains_max`
+* `daily_max_tabs_max`
+* `daily_tabs_opened_max`
+* `daily_num_sessions_started_max`
+<!-- * `fxa_configured` -->
+<!-- * `sync_configured` -->
+
+```{r include=FALSE}
+user_eng <- c("num_active_days", "active_hours", "active_hours_max", "uri_count", "uri_count_max", "session_length", "session_length_max", "search_count", "search_count_max", "num_bookmarks", "num_pages", "num_pages_max", "daily_unique_domains", "daily_max_tabs", "daily_tabs_opened", "daily_num_sessions_started", "daily_unique_domains_max", "daily_max_tabs_max", "daily_tabs_opened_max", "daily_num_sessions_started_max")
 ```
 
-```{r message=FALSE, warning=FALSE}
-ggplot(data=df_train_f, aes(x=FX_PAGE_LOAD_MS_2_PARENT, group=label, fill=label)) +
-    geom_density(adjust=1.5, alpha=0.6, main="FX Page Load (ms)") +
-    scale_fill_viridis(discrete=TRUE) +
-    scale_color_viridis(discrete=TRUE) +
-    theme_ipsum()
+```{r include=FALSE}
+df_beta_ue <- df_beta %>% select(user_eng)
+df_release_ue <- df_release %>% select(user_eng)
+df_train_ue <- df_train_f %>% select(c(user_eng, "label"))
 ```
 
-```{r message=FALSE, warning=FALSE}
-ggplot(data=df_train_f, aes(x=TIME_TO_DOM_CONTENT_LOADED_END_MS, group=label, fill=label)) +
-    geom_density(adjust=1.5, alpha=0.6, main="Time to DOM Content Loaded End (ms)") +
-    scale_fill_viridis(discrete=TRUE) +
-    scale_color_viridis(discrete=TRUE) +
-    theme_ipsum()
+## Comparing Two Distributions
+
+The QQ plot can be used to compare two continuous distributions.
+
+```{r}
+par(mfrow = c(2, 2))  ## Set up a 2 x 2 plotting space
+
+## QQ plot in R to compare two data samples
+for (i in user_eng) {
+  x <- df_beta_ue[,i]
+  y <- df_release_ue[,i]
+
+  rg <- range(x, y, na.rm=T)
+
+  qqplot(x, y, main=i, xlim=rg, ylim=rg, xlab = "Beta", ylab = "Release", pch = 1, frame = FALSE)
+}
 ```
 
-```{r message=FALSE, warning=FALSE}
-ggplot(data=df_train_f, aes(x=TIME_TO_LOAD_EVENT_END_MS, group=label, fill=label)) +
-    geom_density(adjust=1.5, alpha=0.6, main="Time to Load Event End (ms)") +
-    scale_fill_viridis(discrete=TRUE) +
-    scale_color_viridis(discrete=TRUE) +
-    theme_ipsum()
+```{r include=FALSE}
+text_tbl <- data.frame(beta_num_active_days = c(summary(df_beta_ue$num_active_days)), release_num_active_days = c(summary(df_release_ue$num_active_days)), 
+beta_active_hours = c(summary(df_beta_ue$active_hours)), release_active_hours = c(summary(df_release_ue$active_hours)), 
+beta_active_hours_max = c(summary(df_beta_ue$active_hours_max)), release_active_hours_max = c(summary(df_release_ue$active_hours_max)), 
+beta_uri_count = c(summary(df_beta_ue$uri_count)), release_uri_count = c(summary(df_release_ue$uri_count)), 
+beta_uri_count_max = c(summary(df_beta_ue$uri_count_max)), release_uri_count_max = c(summary(df_release_ue$uri_count_max)), 
+beta_session_length = c(summary(df_beta_ue$session_length)), release_session_length = c(summary(df_release_ue$session_length)), 
+beta_session_length_max = c(summary(df_beta_ue$session_length_max)), release_session_length_max = c(summary(df_release_ue$session_length_max)), 
+beta_search_count = c(summary(df_beta_ue$search_count)), release_search_count = c(summary(df_release_ue$search_count)), 
+beta_search_count_max = c(summary(df_beta_ue$search_count_max)), release_search_count_max = c(summary(df_release_ue$search_count_max)), 
+beta_num_bookmarks = c(summary(df_beta_ue$num_bookmarks)), release_num_bookmarks = c(summary(df_release_ue$num_bookmarks)), 
+beta_num_pages = c(summary(df_beta_ue$num_pages)), release_num_pages = c(summary(df_release_ue$num_pages)), 
+beta_num_pages_max = c(summary(df_beta_ue$num_pages_max)), release_num_pages_max = c(summary(df_release_ue$num_pages_max)), 
+beta_daily_unique_domains = c(summary(df_beta_ue$daily_unique_domains)), release_daily_unique_domains = c(summary(df_release_ue$daily_unique_domains)), 
+beta_daily_max_tabs = c(summary(df_beta_ue$daily_max_tabs)), release_daily_max_tabs = c(summary(df_release_ue$daily_max_tabs)), 
+beta_daily_tabs_opened = c(summary(df_beta_ue$daily_tabs_opened)), release_daily_tabs_opened = c(summary(df_release_ue$daily_tabs_opened)), 
+beta_daily_num_sessions_started = c(summary(df_beta_ue$daily_num_sessions_started)), release_daily_num_sessions_started = c(summary(df_release_ue$daily_num_sessions_started)), 
+beta_daily_unique_domains_max = c(summary(df_beta_ue$daily_unique_domains_max)), release_daily_unique_domains_max = c(summary(df_release_ue$daily_unique_domains_max)), 
+beta_daily_max_tabs_max = c(summary(df_beta_ue$daily_max_tabs_max)), release_daily_max_tabs_max = c(summary(df_release_ue$daily_max_tabs_max)), 
+beta_daily_tabs_opened_max = c(summary(df_beta_ue$daily_tabs_opened_max)), release_daily_tabs_opened_max = c(summary(df_release_ue$daily_tabs_opened_max)), 
+beta_daily_num_sessions_started_max = c(summary(df_beta_ue$daily_num_sessions_started_max)), release_daily_num_sessions_started_max = c(summary(df_release_ue$daily_num_sessions_started_max)))
 ```
 
-```{r message=FALSE, warning=FALSE}
-ggplot(data=df_train_f, aes(x=TIME_TO_NON_BLANK_PAINT_MS, group=label, fill=label)) +
-    geom_density(adjust=1.5, alpha=0.6, main="Time to Non Blank Paint (ms)") +
-    scale_fill_viridis(discrete=TRUE) +
-    scale_color_viridis(discrete=TRUE) +
-    theme_ipsum()
+```{r}
+kable(text_tbl) %>%
+kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
+scroll_box(width = "100%")
 ```
-
-```{r message=FALSE, warning=FALSE}
-ggplot(data=df_train_f, aes(x=TIME_TO_DOM_COMPLETE_MS, group=label, fill=label)) +
-    geom_density(adjust=1.5, alpha=0.6, main="Time to DOM Complete (ms)") +
-    scale_fill_viridis(discrete=TRUE) +
-    scale_color_viridis(discrete=TRUE) +
-    theme_ipsum()
-```
-
-### Observations

### 2019-12-11 perf_release_criteria/milestone_4/ms_4_training_subsetting_calculation.Rmd
Milestone 4 script for training, subsetting, and final calculations.

--- 2019-12-05 perf_release_criteria/milestone_4/ms_4_datasets_generation.Rmd
@@
 ```{r imports, echo=FALSE, warning=FALSE, message=FALSE}
+source('../lib/modeling.R')
 source('../lib/supporting_funcs.R')
+source('../lib/scoring.R')
 library(bigrquery)
 library(DBI)
+library(lubridate)
 ```
@@
 # tl;dr 
-This notebook generates the training (Version N) and prediction (Version N+1) datasets used for measuring Release performance  [PRD](https://docs.google.com/document/d/1Ygz6MkudYHZjnDnD9Z97kUyFrvV3KGWsjXyPjddhHq0/edit#heading=h.lvb9l8gw2nee).
-The training dataset is used to train a stastical matching model, which then is used to find a subset of Beta profiles.
-These profiles are then used in the prediction dataset to calculate the various performance metrics.
+This notebook generates the training (Version N) and prediction (Version N+1) datasets, trains a statistical matching model, extracts a representative subset of Beta with respect to Release, and calculates the final Release Health Metrics as described in milestone 4 of this PRD[Release performance health metrics](https://docs.google.com/document/d/1Ygz6MkudYHZjnDnD9Z97kUyFrvV3KGWsjXyPjddhHq0/edit#heading=h.lvb9l8gw2nee).
 
@@
 ) on a Dataproc cluster.
-These are serialized as BigQuery tables available in the `moz-fx-data-shared-prod.analysis` dataset as `cdowhygelund_subBeta_training` (Version N) and `cdowhygelund_subBeta_prediction` (Version N+1).
+These are serialized as BigQuery tables available in the `moz-fx-data-shared-prod.analysis` dataset as `ccd_subBeta_training` (Version N) and `ccd_subBeta_prerelease` (Version N+1).
 
@@
 # outcomes <- c('TIME_TO_DOM_INTERACTIVE_MS', 'TIME_TO_DOM_CONTENT_LOADED_END_MS', 'TIME_TO_LOAD_EVENT_END_MS', 
-#               'TIME_TO_NON_BLANK_PAINT_MS', 'TIME_TO_DOM_COMPLETE_MS', 'FX_PAGE_LOAD_MS_2_PARENT') (FIXME)
+#                'TIME_TO_NON_BLANK_PAINT_MS', 'TIME_TO_DOM_COMPLETE_MS', 'FX_PAGE_LOAD_MS_2_PARENT')
 
-outcomes <- c('TIME_TO_DOM_CONTENT_LOADED_END_MS', 'TIME_TO_LOAD_EVENT_END_MS', 'TIME_TO_DOM_COMPLETE_MS', 'FX_PAGE_LOAD_MS_2_PARENT')
+outcomes <- names(get_m2_metric_map())
+# outcomes <- c('TIME_TO_DOM_CONTENT_LOADED_END_MS', 'TIME_TO_LOAD_EVENT_END_MS', 'TIME_TO_DOM_COMPLETE_MS', 'FX_PAGE_LOAD_MS_2_PARENT')
 
@@
 
-df_train <- load_df("cdowhygelund_subBeta_training")
-df_validate <- load_df('cdowhygelund_subBeta_prediction')
+df_train <- load_df("ccd_subBeta_training")
+df_predict <- load_df('ccd_subBeta_prerelease')
 ```
@@
     - **Action**: The top 0.001% are being filtered already. Review to determine how these change with matching on performance metrics.
+* `fxa_configured` has beeen noted to be incorrectly calculated using `clients_daily`. This will be removed until a fix is in place from `main_summary`
+    - **FIXME**: Update `main_summary` to pull the data correctly
 * Drop unused factors on `default_search_engine`, `is_wow64`
@@
     select(-c(city, geo_subdivision1, geo_subdivision2, cpu_l3_cache_kb, cpu_stepping, 
-              cpu_model, cpu_family, distribution_id)) %>%
+              cpu_model, cpu_family, distribution_id, fxa_configured)) %>%
     filter(between(install_year, 1991, 2019)) %>%
@@
     mutate(cpu_l2_cache_kb_cat = normalize_cpu_l2_cache(cpu_l2_cache_kb)) %>%
-    droplevels()
+    droplevels() %>%
+    mutate(data_created = now()) # Add in a field for when this notebook was run
   return(df_clean)
@@
 
-df_train_f <- stage_2_clean(df_train)
-df_validate_f <- stage_2_clean(df_validate)
+# Add in a field for when the training and prerelease datasets were created 
+df_train_f <- stage_2_clean(df_train) %>%
+    mutate(date_created = now())
 
+df_predict_f <- stage_2_clean(df_predict) %>%
+    mutate(date_created = now())
 ```
@@
 
+# Train
+
+The statistical matching model architecture utilized was determined in [ms_2_validation](https://metrics.mozilla.com/protected/cdowhygelund/subBeta_m3_model_determination.html).
+
+Model framework:
+
+* matching algorithm: Nearest-Neighbors Probit, Linear
+* features: Only performance metrics
+* hyperparameters: 
+    * `caliper` = 0.4
+    * `calcloset` = FALSE
+    * `ratio` = 3
+    * `replace` = FALSE
+    * 4x oversampling
+    * Interactions across covariates
+
+```{r train, message=FALSE}
+# fs1 <- c('TIME_TO_DOM_CONTENT_LOADED_END_MS', 'TIME_TO_LOAD_EVENT_END_MS', 'TIME_TO_DOM_COMPLETE_MS', 'FX_PAGE_LOAD_MS_2_PARENT') 
+# fs1 <- names(get_m2_metric_map()) # FIXME
+
+model <- train_matchit(df_train_x, outcomes, add_interactions = TRUE, replace = FALSE, 
+                         caliper = 0.4, calclosest = TRUE, ratio = 3, distance = "linear.probit")
+```
+
+Subset Beta for the representative dataset
+
+```{r beta_subset}
+predictions <- extract_predictions(model$matched, df_predict_f) 
+```
+
+# Release Health Metrics
+
+Calculate the Release Health Metrics
+
 # Serialize and push to GCP
+Serialize the following:
+
+* Cleaned training and prerelease datasets
+* Statistical matching model
+* Subsetted prerelease dataset for performance calculation
+* Prerelease performance results
+
+## Storage
 Save the resultant dataset and bootstrap samples to an R image.
@@
 image_file_path <- file.path('data', image_file_name)
-save(df_train_f, df_validate_f, df_train_x, file = image_file_path)
+save(df_train_f, df_predict_f, df_train_x, file = image_file_path)
 
@@
 ```
+
+## BigQuery
+
+Training and prerelease datasets
+```{r big_query_write}
+project <- "moz-fx-dev-cdowhyglund-subbeta"
+# project <- "moz-fx-data-bq-data-science"
+
+bq_table(project = 'moz-fx-dev-cdowhyglund-subbeta',
+         dataset = "training",
+         table   = "ccd_subbeta_training_cleaned") %>%
+  bq_table_upload(values = df_train_x,
+                  create_disposition = "CREATE_IF_NEEDED",
+                  write_disposition = "WRITE_APPEND",
+                  fields = as_bq_fields(df_train_x) )
+
+bq_table(project = 'moz-fx-dev-cdowhyglund-subbeta',
+         dataset = "prerelease",
+         table   = "ccd_subbeta_prelease_cleaned") %>%
+  bq_table_upload(values = df_predict_f,
+                  create_disposition = "CREATE_IF_NEEDED",
+                  write_disposition = "WRITE_APPEND",
+                  fields = as_bq_fields(df_predict_f) )
+
+```
+
+Subsetted dataset
+```{r bq_write_subset}
+bq_table(project = 'moz-fx-dev-cdowhyglund-subbeta',
+         dataset = "prerelease",
+         table   = "ccd_subbeta_prelease_subset") %>%
+  bq_table_upload(values = df_predict_f,
+                  create_disposition = "CREATE_IF_NEEDED",
+                  write_disposition = "WRITE_APPEND",
+                  fields = as_bq_fields(df_predict_f) )
+```
+
+Release health Metrics
+```{r bq_release_health_metrics}
+
+```

### 2019-12-11 perf_release_criteria/lib/modeling.R

@@ -1,3 +1,15 @@
+library(MatchIt)
+
+generate_formula <- function(tr_cov, label, add_interactions=FALSE){
+  if (add_interactions){
+    formula <- paste(label, '~', paste(tr_cov, collapse="*"))
+  }
+  else {
+    formula <- paste(label, '~', paste(tr_cov, collapse="+"))
+  }
+  return(as.formula(formula))
+}
+
 train_matchit <- function(train, model_covs, add_interactions, ...){
   # train model
   formula <- generate_formula(model_covs, label = 'is_release', add_interactions)

### 2019-12-11 perf_release_criteria/lib/scoring.R

@@ -4,6 +4,7 @@ library(foreach)
 # library(doMC)
 library(doParallel)
 
+# FIXME: move to subBeta_supporting.R
 get_m2_metric_map = function(){
   #' Get milestone 2 map of metrics to scoring weights
   #'
@@ -240,3 +241,52 @@ perform_matchit_hp_tune <- function(df_train, bts, model_covs, workers, hps_grid
   #return(list(full = results, mean = res_mean, median = res_median))
 }
 
+score_model <- function(bts, df_match, df_val, workers){
+  if (missing(workers)) workers = detectCores()
+  cl <- makePSOCKcluster(workers) 
+  registerDoParallel(cl)
+  final <- tryCatch({
+    scores <- foreach(i=1:length(bts), 
+                      .packages = c('dplyr', 'transport'), 
+                      .export=c('calc_score', 'calc_cms', 'get_m2_metric_map')) %dopar% {
+                        bt <- bts[[i]]
+                        test <- df_val %>% 
+                          right_join(data.frame(client_id = bt, stringsAsFactors=FALSE), by='client_id', 'right')
+                        
+                        df_scores <- test %>%
+                          bind_rows(df_match)
+                        
+                        score <- calc_score(df_scores, get_m2_metric_map())
+                        score
+                      }
+    scores <- unlist(scores)
+    c(mean = mean(scores), median = median(scores))
+  }, 
+  error = function(cond){
+    message(paste("Bootstrap validation failed: ", cond))
+    return(NA)
+  },
+  finally = {
+    stopCluster(cl)
+  }
+  )
+  return(final)
+}
+
+build_quantile_df <- function(validation, matched, original, metrics){
+  qqs <- list()
+  for (metric in metrics){
+    qq <- qqplot(validation[[metric]], matched[[metric]], plot.it = FALSE) %>% 
+      bind_rows() %>%
+      mutate(type = 'matched')
+    qq_full <- qqplot(validation[[metric]], original[[metric]], plot.it = FALSE) %>% 
+      bind_rows() %>%
+      mutate(type = 'original') %>%
+      bind_rows(qq) %>%
+      mutate(metric = metric)
+    # qq_full$metric <- metric
+    qqs[[metric]] <- qq_full
+  }
+  qq_df <- qqs %>% bind_rows() %>% rename(release = x, beta = y)
+  return(qq_df)
+}

### 2019-12-11 perf_release_criteria/lib/supporting_funcs.R

@@ -52,6 +52,7 @@ calc_stats <- function(df.match, ho_cov, add_1 = FALSE){
 
 #### Modeling Pipeline
 
+## FIXME: moved to modeling.R
 generate_formula <- function(tr_cov, label, add_interactions=FALSE){
   if (add_interactions){
     formula <- paste(label, '~', paste(tr_cov, collapse="*"))

### 2019-12-11 perf_release_criteria/milestone_4/ms_4_training_subsetting_calculation.Rmd
Updated notebook with release health placeholders.

@@
 
-```{r train, message=FALSE}
-# fs1 <- c('TIME_TO_DOM_CONTENT_LOADED_END_MS', 'TIME_TO_LOAD_EVENT_END_MS', 'TIME_TO_DOM_COMPLETE_MS', 'FX_PAGE_LOAD_MS_2_PARENT') 
-# fs1 <- names(get_m2_metric_map()) # FIXME
-
+```{r train, message=FALSE, error=FALSE}
 model <- train_matchit(df_train_x, outcomes, add_interactions = TRUE, replace = FALSE, 
@@
 
-Calculate the Release Health Metrics
+Calculate the Release Health Metrics:
+**TBD**
 
@@
 
-```{r serialize_dataset}
-image_file_name <- paste('df_train_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
-image_file_path <- file.path('data', image_file_name)
-save(df_train_f, df_predict_f, df_train_x, file = image_file_path)
+```{r serialize_datasets}
+# training datasets
+train_file_name <- paste('df_train_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
+train_file_path <- file.path('data', train_file_name)
+save(df_train_f, df_predict_f, df_train_x, model, file = train_file_path)
+gcs_train_file_path <- file.path('data', 'milestone4', train_file_name)
 
-gcs_file_path <- file.path('data', 'milestone4', image_file_name)
+# final prelease subsetted dataset
+prerelease_file_name <- paste('df_prerelease_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
+prerelease_file_path <- file.path('data', prerelease_file_name)
+save(predictions, file = prerelease_file_path)
+gcs_prerelease_file_path <- file.path('data', 'milestone4', prerelease_file_name)
+
+# Release health metrics
+release_health_file_name <- paste('df_release_health_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
+release_health_file_path <- file.path('data', release_health_file_name)
+# save(df_release_health_f, df_predict_f, df_release_health_x, file = release_health_file_path)
+gcs_release_health_file_path <- file.path('data', 'milestone4', release_health_file_name)
 ```
 
-Then push the results to GCP in the `moz-fx-dev-subbeta` bucket, under `r gcs_file_path`.
+Then push the results to GCP in the `moz-fx-dev-subbeta` bucket, to the following files:
 
-```{r gcp_storage_push, warning=FALSE}
+* `r gcs_train_file_path`
+* `r gcs_prerelease_file_path`
+* `r gcs_release_health_file_path`
+
+```{r gcp_train_storage_push, warning=FALSE}
 Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
@@
 
-upload_try <- gcs_upload(image_file_path, name = gcs_file_path)
+upload_try <- gcs_upload(train_file_path, name = gcs_train_file_path)
 upload_try
+```
+
+```{r gcp_prelease_storage_push, warning=FALSE}
+upload_try <- gcs_upload(prerelease_file_path, name = gcs_prerelease_file_path)
+upload_try
+```
+
+```{r gcp_health_metrics_storage_push, warning=FALSE}
+# upload_try <- gcs_upload(gcs_release_health_file_path, name = gcs_file_path)
+# upload_try
 ```
@@
 ```{r big_query_write}
-project <- "moz-fx-dev-cdowhyglund-subbeta"
+project <- "moz-fx-dev-cdowhyglund-subBeta"
 # project <- "moz-fx-data-bq-data-science"
@@
          table   = "ccd_subbeta_training_cleaned") %>%
+  bq_table_upload(values = df_train_x,
+                  create_disposition = "CREATE_IF_NEEDED",
+                  write_disposition = "WRITE_APPEND",
+                  fields = as_bq_fields(df_train_x) )
+
+bq_table(project = 'moz-fx-dev-cdowhyglund-subbeta',
+         dataset = "training",
+         table   = "ccd_subbeta_training_final") %>%
   bq_table_upload(values = df_train_x,
@@
 ```{r bq_release_health_metrics}
-
+# bq_table(project = 'moz-fx-dev-cdowhyglund-subbeta',
+#          dataset = "prerelease",
+#          table   = "ccd_subbeta_prerelease_health_metrics") %>%
+#   bq_table_upload(values = release_health_df,
+#                   create_disposition = "CREATE_IF_NEEDED",
+#                   write_disposition = "WRITE_APPEND",
+#                   fields = as_bq_fields(release_health_df) )
 ```

### 2019-12-11 perf_release_criteria/milestone_4/ms_4_training_subsetting_calculation.Rmd
Fixing title

@@
 ---
-title: 'Milestone 4: Datasets Generation'
+title: 'Milestone 4'
 output:

### 2019-12-12 poc/EDA/EDA.Rmd
updating the EDA notebook

--- 2019-12-06 poc/EDA/EDA.Rmd
@@
     toc: true
-    theme: united
-    highlight: textmate
+    toc_float: true
+    highlight: tango
+    df_print: kable
+    code_folding: "hide"
+    theme: "flatly"
 ---
 
-# Exploratory Data Analysis (EDA) {.tabset}
+# Exploratory Data Analysis (EDA)
 
@@
 library(Hmisc)
+library(grid)
+library(hrbrthemes)
+library(tidyr)
+library(viridis)
+library(ggpubr)
+library(ggthemes)
+library(GGally)
+library(nortest)
 ```
@@
 
-load("~/GitHub/ff-beta-release-matching/poc/EDA/data_milestone2_df_train_validate_20191021.RData")
+load("~/GitHub/ff-beta-release-matching/poc/EDA/data_milestone2_df_train_validate_20191025.RData")
 ```
+
+## Training
 
@@
 
+## Validation
+
+```{r message=FALSE, warning=FALSE}
+## View train dataframe
+
+kable(head(df_validate_f)) %>%
+kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
+scroll_box(width = "100%")
+```
+
 ## Step 1 : Data Inspection
 
-To get introduced to our dataset:
+### Training
 
-```{r}
+To get introduced to our training dataset, let's have a look on the basic information of the dataset.
+
+```{r echo=FALSE}
 kable(introduce(df_train_f)) %>%
@@
 
-Sanity check on the structure and show sample data for each variable.
+### Validation
+
+To get introduced to our validation dataset, let's have a look on the basic information of the dataset.
+
+```{r echo=FALSE}
+kable(introduce(df_validate_f)) %>%
+kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
+scroll_box(width = "100%")
+```
+
+```{r echo=FALSE, fig.height=10, fig.width=10}
+plot_intro(df_validate_f, ggtheme = theme_minimal())
+```
+
+### Observations
+
+* Most of the dataset is composed of continuous variables
+* No NAs values (were handled in preprocessing)
+
+## Data Structure
+
+### Training
+
+Let's use `glimpse` function to display a vertical preview of the training dataset. So we can easily preview data type and sample data.
 
 ```{r}
-str(df_train_f)
+glimpse(df_train_f)
 ```
 
-When we get a new dataset to analyze, is important to know if there are missing values and the data type.
-The `df_status` function can help us by showing these numbers in relative and percentage values.
+If we want to get some metrics about data types, zeros, infinite numbers, and missing values, we can use the `df_status` function.
 
 ```{r}
-kable(df_status(df_train_f)) %>%
+kable(df_status(df_train_f, FALSE)) %>%
 kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
@@
 
+### Validation
+
+Let's use `glimpse` function to display a vertical preview of the validation dataset. So we can easily preview data type and sample data.
+
+```{r}
+glimpse(df_validate_f)
+```
+
+If we want to get some metrics about data types, zeros, infinite numbers, and missing values, we can use the `df_status` function.
+
+```{r}
+kable(df_status(df_train_f, FALSE)) %>%
+kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
+scroll_box(width = "100%")
+```
+
+* `q_zeros`: quantity of zeros (`p_zeros`: in percent)
+* `q_inf`: quantity of infinite values (`p_inf`: in percent)
+* `q_na`: quantity of NA (`p_na`: in percent)
+* `type`: factor, ordered-factor, numeric, integer or character
+* `unique`: quantity of unique values
+
+### Observations
+
 > Are all the variables in the correct data type?
 
-`to-do`
-
-<!-- Some variables are encoded as numbers, but they are codes or categories and the models don't handle them in the same way. -->
+None. It seems that this has already been dealt with in preprocessing.
 
@@
 
-`to-do`
-<!-- Factor/categorical variables with a high number of different values (~30) tend to do overfitting if the categories have low cardinality. -->
+Factor/categorical variables with a high number of different values (~30) tend to do overfitting if the categories have low cardinality.
 
-## Step 2 : Analyzing Categorical Variables
+## Step 2 : Beta vs Release
 
-```{r}
+### Training
+
+```{r, fig.width = 7.5}
 df_release <- df_train_f[which(df_train_f$label == 'release'), ]
@@
 
-freq(df_train_f$label)
+f <- freq(df_train_f$label)
+```
+
+```{r}
+summary(df_release)
+```
+
+```{r}
+summary(df_beta)
+```
+
+### Validation
+
+```{r, fig.width = 7.5}
+df_v_release <- df_validate_f[which(df_validate_f$label == 'release'), ]
+df_v_beta <- df_validate_f[which(df_validate_f$label == 'beta'), ]
+
+f <- freq(df_validate_f$label)
+```
+
+```{r}
+summary(df_v_release)
+```
+
+```{r}
+summary(df_v_beta)
+```
+
+## Step 3 - Analyzing Discrete Variables
+
+### Training
+
+```{r, fig.height=15, fig.width=15, message=FALSE, warning=FALSE}
+## Frequency distribution release dataframe
+plot_bar(df_release, ggtheme = theme_minimal(base_size = 15))
+```
+
+```{r, fig.height=15, fig.width=15, message=FALSE, warning=FALSE}
+## Frequency distribution beta dataframe
+plot_bar(df_beta, ggtheme = theme_minimal(base_size = 15))
+```
+
+### Validation
+
+```{r, fig.height=15, fig.width=15, message=FALSE, warning=FALSE}
+## Frequency distribution release dataframe
+plot_bar(df_v_release, ggtheme = theme_minimal(base_size = 15))
+```
+
+```{r, fig.height=15, fig.width=15, message=FALSE, warning=FALSE}
+## Frequency distribution beta dataframe
+plot_bar(df_v_beta, ggtheme = theme_minimal(base_size = 15))
+```
+
+## Step 4 - Analyzing Continuos Variables
+
+### Training
+
+```{r, fig.width = 15, fig.height = 15}
+## View histogram of release dataset
+plot_histogram(df_release, ggtheme = theme_minimal(base_size = 15))
 ```
@@
 ```{r, fig.width = 15, fig.height = 15}
-## Frequency distribution of all discrete variables
-plot_bar(df_train_f)
+## View histogram of beta dataset
+plot_histogram(df_beta, ggtheme = theme_minimal(base_size = 15))
+```
+
+### Validation
+
+```{r, fig.width = 15, fig.height = 15}
+## View histogram of release dataset
+plot_histogram(df_release, ggtheme = theme_minimal(base_size = 15))
 ```
@@
 ```{r, fig.width = 15, fig.height = 15}
-## Frequency distribution for release dataframe
-plot_bar(df_release)
+## View histogram of beta dataset
+plot_histogram(df_beta, ggtheme = theme_minimal(base_size = 15))
 ```
 
-```{r, fig.width = 15, fig.height = 15}
-## Frequency distribution beta dataframe
-plot_bar(df_beta)
+### Observations
+
+* My first impression is that **user engagement** metrics might be a good path to follow
+
+### Ploting Density Curves
+
+```{r include=FALSE}
+require(cowplot)
 ```
 
-### EDA on Coninuous Variables
+```{r, fig.width = 20, fig.height = 5, message=FALSE, warning=FALSE}
+## Training
+t <- ggplot(data=df_train_f, aes(x=uri_count, group=label, fill=label)) +
+    geom_density(adjust=1.5, alpha=0.6) + xlim(0, 1000) +
+    scale_fill_viridis(discrete=TRUE) +
+    scale_color_viridis(discrete=TRUE) +
+    labs(x="URI Count", y = "Density") +
+    theme_ipsum()
 
-```{r, fig.width = 15, fig.height = 15}
-## View histogram of all continuous variables
-plot_histogram(df_train_f)
+## Validation
+v <- ggplot(data=df_validate_f, aes(x=uri_count, group=label, fill=label)) +
+    geom_density(adjust=1.5, alpha=0.6) + xlim(0, 1000) +
+    scale_fill_viridis(discrete=TRUE) +
+    scale_color_viridis(discrete=TRUE) +
+    labs(x="URI Count", y = "Density") +
+    theme_ipsum()
+
+plot_grid(t, v, ncol=2, labels = c("Train", "Validate")) ## Set up a 2 x 2 plotting space
 ```
 
-```{r, fig.width = 15, fig.height = 15}
-## View histogram of all continuous variables
-plot_histogram(df_release)
+```{r, fig.width = 20, fig.height = 5, message=FALSE, warning=FALSE}
+## Training
+t <- ggplot(data=df_train_f, aes(x=active_hours, group=label, fill=label)) +
+    geom_density(adjust=1.5, alpha=0.6) +
+    scale_fill_viridis(discrete=TRUE) +
+    scale_color_viridis(discrete=TRUE) +
+    labs(x="Active Hours", y = "Density") +
+    theme_ipsum()
+
+## Validation
+v <- ggplot(data=df_validate_f, aes(x=active_hours, group=label, fill=label)) +
+    geom_density(adjust=1.5, alpha=0.6) +
+    scale_fill_viridis(discrete=TRUE) +
+    scale_color_viridis(discrete=TRUE) +
+    labs(x="Active Hours", y = "Density") +
+    theme_ipsum()
+
+plot_grid(t, v, ncol=2, labels = c("Train", "Validate")) ## Set up a 2 x 2 plotting space
 ```
 
-```{r, fig.width = 15, fig.height = 15}
-## View histogram of all continuous variables
-plot_histogram(df_beta)
+```{r, fig.width = 20, fig.height = 5, message=FALSE, warning=FALSE}
+## Training
+t <- ggplot(data=df_train_f, aes(x=num_pages, group=label, fill=label)) +
+    geom_density(adjust=1.5, alpha=0.6) + xlim(0, 50000) +
+    scale_fill_viridis(discrete=TRUE) +
+    scale_color_viridis(discrete=TRUE) +
+    labs(x="Num Pages", y = "Density") +
+    theme_ipsum()
+
+## Validation
+v <- ggplot(data=df_validate_f, aes(x=num_pages, group=label, fill=label)) +
+    geom_density(adjust=1.5, alpha=0.6) + xlim(0, 50000) +
+    scale_fill_viridis(discrete=TRUE) +
+    scale_color_viridis(discrete=TRUE) +
+    labs(x="Num Pages", y = "Density") +
+    theme_ipsum()
+
+plot_grid(t, v, ncol=2, labels = c("Train", "Validate")) ## Set up a 2 x 2 plotting space
 ```
+
+```{r, fig.width = 20, fig.height = 5, message=FALSE, warning=FALSE}
+## Training
+t <- ggplot(data=df_train_f, aes(x=session_length, group=label, fill=label)) +
+    geom_density(adjust=1.5, alpha=0.6) + xlim(0, 75) +
+    scale_fill_viridis(discrete=TRUE) +
+    scale_color_viridis(discrete=TRUE) +
+    labs(x="Session Length", y = "Density") +
+    theme_ipsum()
+
+## Validation
+v <- ggplot(data=df_validate_f, aes(x=session_length, group=label, fill=label)) +
+    geom_density(adjust=1.5, alpha=0.6) + xlim(0, 75) +
+    scale_fill_viridis(discrete=TRUE) +
+    scale_color_viridis(discrete=TRUE) +
+    labs(x="Session Length", y = "Density") +
+    theme_ipsum()
+
+plot_grid(t, v, ncol=2, labels = c("Train", "Validate")) ## Set up a 2 x 2 plotting space
+```
+
+# User Engagement Continuous Metrics
+
+This section will focus only on user engagement continuous metrics. So, we are going to analyze the following metrics:
+
+* `num_active_days`
+* `active_hours`
+* `active_hours_max`
+* `uri_count`
+* `uri_count_max`
+* `session_length`
+* `session_length_max`
+* `search_count`
+* `search_count_max`
+* `num_bookmarks`
+* `num_pages`
+* `num_pages_max`
+* `num_addons`
+* `daily_unique_domains`
+* `daily_unique_domains_max`
+* `daily_max_tabs`
+* `daily_max_tabs_max`
+* `daily_tabs_opened`
+* `daily_tabs_opened_max`
+* `daily_num_sessions_started`
+* `daily_num_sessions_started_max`
+* `startup_ms`
+* `install_year`
+* `profile_age`
+* `timezone_offset`
+* `memory_mb`
+* `cpu_cores`
+* `cpu_speed_mhz`
+* `cpu_l2_cache_kb`
+
+```{r include=FALSE}
+user_eng <- c("num_active_days","active_hours","active_hours_max","uri_count","uri_count_max","session_length","session_length_max","search_count","search_count_max","num_bookmarks","num_pages","num_pages_max","num_addons","daily_unique_domains","daily_unique_domains_max","daily_max_tabs","daily_max_tabs_max","daily_tabs_opened","daily_tabs_opened_max","daily_num_sessions_started","daily_num_sessions_started_max","startup_ms","install_year","profile_age","timezone_offset","memory_mb","cpu_cores","cpu_speed_mhz","cpu_l2_cache_kb")
+```
+
+```{r include=FALSE}
+df_beta_ue <- df_beta %>% select(user_eng)
+df_release_ue <- df_release %>% select(user_eng)
+df_train_ue <- df_train_f %>% select(c(user_eng, "label"))
+
+df_beta_v_ue <- df_v_beta %>% select(user_eng)
+df_release_v_ue <- df_v_release %>% select(user_eng)
+df_validate_ue <- df_validate_f %>% select(c(user_eng, "label"))
+```
+
+```{r include=FALSE}
+text_tbl <- data.frame(
+beta_num_active_days = c(summary(df_beta_ue$num_active_days)), release_num_active_days = c(summary(df_release_ue$num_active_days)), 
+beta_active_hours = c(summary(df_beta_ue$active_hours)), release_active_hours = c(summary(df_release_ue$active_hours)), 
+beta_active_hours_max = c(summary(df_beta_ue$active_hours_max)), release_active_hours_max = c(summary(df_release_ue$active_hours_max)), 
+beta_uri_count = c(summary(df_beta_ue$uri_count)), release_uri_count = c(summary(df_release_ue$uri_count)), 
+beta_uri_count_max = c(summary(df_beta_ue$uri_count_max)), release_uri_count_max = c(summary(df_release_ue$uri_count_max)), 
+beta_session_length = c(summary(df_beta_ue$session_length)), release_session_length = c(summary(df_release_ue$session_length)), 
+beta_session_length_max = c(summary(df_beta_ue$session_length_max)), release_session_length_max = c(summary(df_release_ue$session_length_max)), 
+beta_search_count = c(summary(df_beta_ue$search_count)), release_search_count = c(summary(df_release_ue$search_count)), 
+beta_search_count_max = c(summary(df_beta_ue$search_count_max)), release_search_count_max = c(summary(df_release_ue$search_count_max)), 
+beta_num_bookmarks = c(summary(df_beta_ue$num_bookmarks)), release_num_bookmarks = c(summary(df_release_ue$num_bookmarks)), 
+beta_num_pages = c(summary(df_beta_ue$num_pages)), release_num_pages = c(summary(df_release_ue$num_pages)), 
+beta_num_pages_max = c(summary(df_beta_ue$num_pages_max)), release_num_pages_max = c(summary(df_release_ue$num_pages_max)), 
+beta_daily_unique_domains = c(summary(df_beta_ue$daily_unique_domains)), release_daily_unique_domains = c(summary(df_release_ue$daily_unique_domains)), 
+beta_daily_max_tabs = c(summary(df_beta_ue$daily_max_tabs)), release_daily_max_tabs = c(summary(df_release_ue$daily_max_tabs)), 
+beta_daily_tabs_opened = c(summary(df_beta_ue$daily_tabs_opened)), release_daily_tabs_opened = c(summary(df_release_ue$daily_tabs_opened)), 
+beta_daily_num_sessions_started = c(summary(df_beta_ue$daily_num_sessions_started)), release_daily_num_sessions_started = c(summary(df_release_ue$daily_num_sessions_started)), 
+beta_daily_unique_domains_max = c(summary(df_beta_ue$daily_unique_domains_max)), release_daily_unique_domains_max = c(summary(df_release_ue$daily_unique_domains_max)), 
+beta_daily_max_tabs_max = c(summary(df_beta_ue$daily_max_tabs_max)), release_daily_max_tabs_max = c(summary(df_release_ue$daily_max_tabs_max)), 
+beta_daily_tabs_opened_max = c(summary(df_beta_ue$daily_tabs_opened_max)), release_daily_tabs_opened_max = c(summary(df_release_ue$daily_tabs_opened_max)), 
+beta_daily_num_sessions_started_max = c(summary(df_beta_ue$daily_num_sessions_started_max)), release_daily_num_sessions_started_max = c(summary(df_release_ue$daily_num_sessions_started_max)), 
+beta_startup_ms = c(summary(df_beta_ue$startup_ms)), release_startup_ms = c(summary(df_release_ue$startup_ms)), 
+beta_install_year = c(summary(df_beta_ue$install_year)), release_install_year = c(summary(df_release_ue$install_year)), 
+beta_profile_age = c(summary(df_beta_ue$profile_age)), release_profile_age = c(summary(df_release_ue$profile_age)), 
+beta_timezone_offset = c(summary(df_beta_ue$timezone_offset)), release_timezone_offset = c(summary(df_release_ue$timezone_offset)), 
+beta_memory_mb = c(summary(df_beta_ue$memory_mb)), release_memory_mb = c(summary(df_release_ue$memory_mb)), 
+beta_cpu_cores = c(summary(df_beta_ue$cpu_cores)), release_cpu_cores = c(summary(df_release_ue$cpu_cores)), 
+beta_cpu_speed_mhz = c(summary(df_beta_ue$cpu_speed_mhz)), release_cpu_speed_mhz = c(summary(df_release_ue$cpu_speed_mhz)), 
+beta_cpu_l2_cache_kb = c(summary(df_beta_ue$cpu_l2_cache_kb)), release_cpu_l2_cache_kb = c(summary(df_release_ue$cpu_l2_cache_kb))
+)
+```
+
+```{r include=FALSE}
+text_tbl_v <- data.frame(
+beta_num_active_days = c(summary(df_beta_v_ue$num_active_days)), release_num_active_days = c(summary(df_release_v_ue$num_active_days)), 
+beta_active_hours = c(summary(df_beta_v_ue$active_hours)), release_active_hours = c(summary(df_release_v_ue$active_hours)), 
+beta_active_hours_max = c(summary(df_beta_v_ue$active_hours_max)), release_active_hours_max = c(summary(df_release_v_ue$active_hours_max)), 
+beta_uri_count = c(summary(df_beta_v_ue$uri_count)), release_uri_count = c(summary(df_release_v_ue$uri_count)), 
+beta_uri_count_max = c(summary(df_beta_v_ue$uri_count_max)), release_uri_count_max = c(summary(df_release_v_ue$uri_count_max)), 
+beta_session_length = c(summary(df_beta_v_ue$session_length)), release_session_length = c(summary(df_release_v_ue$session_length)), 
+beta_session_length_max = c(summary(df_beta_v_ue$session_length_max)), release_session_length_max = c(summary(df_release_v_ue$session_length_max)), 
+beta_search_count = c(summary(df_beta_v_ue$search_count)), release_search_count = c(summary(df_release_v_ue$search_count)), 
+beta_search_count_max = c(summary(df_beta_v_ue$search_count_max)), release_search_count_max = c(summary(df_release_v_ue$search_count_max)), 
+beta_num_bookmarks = c(summary(df_beta_v_ue$num_bookmarks)), release_num_bookmarks = c(summary(df_release_v_ue$num_bookmarks)), 
+beta_num_pages = c(summary(df_beta_v_ue$num_pages)), release_num_pages = c(summary(df_release_v_ue$num_pages)), 
+beta_num_pages_max = c(summary(df_beta_v_ue$num_pages_max)), release_num_pages_max = c(summary(df_release_v_ue$num_pages_max)), 
+beta_daily_unique_domains = c(summary(df_beta_v_ue$daily_unique_domains)), release_daily_unique_domains = c(summary(df_release_v_ue$daily_unique_domains)), 
+beta_daily_max_tabs = c(summary(df_beta_v_ue$daily_max_tabs)), release_daily_max_tabs = c(summary(df_release_v_ue$daily_max_tabs)), 
+beta_daily_tabs_opened = c(summary(df_beta_v_ue$daily_tabs_opened)), release_daily_tabs_opened = c(summary(df_release_v_ue$daily_tabs_opened)), 
+beta_daily_num_sessions_started = c(summary(df_beta_v_ue$daily_num_sessions_started)), release_daily_num_sessions_started = c(summary(df_release_v_ue$daily_num_sessions_started)), 
+beta_daily_unique_domains_max = c(summary(df_beta_v_ue$daily_unique_domains_max)), release_daily_unique_domains_max = c(summary(df_release_v_ue$daily_unique_domains_max)), 
+beta_daily_max_tabs_max = c(summary(df_beta_v_ue$daily_max_tabs_max)), release_daily_max_tabs_max = c(summary(df_release_v_ue$daily_max_tabs_max)), 
+beta_daily_tabs_opened_max = c(summary(df_beta_v_ue$daily_tabs_opened_max)), release_daily_tabs_opened_max = c(summary(df_release_v_ue$daily_tabs_opened_max)), 
+beta_daily_num_sessions_started_max = c(summary(df_beta_v_ue$daily_num_sessions_started_max)), release_daily_num_sessions_started_max = c(summary(df_release_v_ue$daily_num_sessions_started_max)), 
+beta_startup_ms = c(summary(df_beta_v_ue$startup_ms)), release_startup_ms = c(summary(df_release_v_ue$startup_ms)), 
+beta_install_year = c(summary(df_beta_v_ue$install_year)), release_install_year = c(summary(df_release_v_ue$install_year)), 
+beta_profile_age = c(summary(df_beta_v_ue$profile_age)), release_profile_age = c(summary(df_release_v_ue$profile_age)), 
+beta_timezone_offset = c(summary(df_beta_v_ue$timezone_offset)), release_timezone_offset = c(summary(df_release_v_ue$timezone_offset)), 
+beta_memory_mb = c(summary(df_beta_v_ue$memory_mb)), release_memory_mb = c(summary(df_release_v_ue$memory_mb)), 
+beta_cpu_cores = c(summary(df_beta_v_ue$cpu_cores)), release_cpu_cores = c(summary(df_release_v_ue$cpu_cores)), 
+beta_cpu_speed_mhz = c(summary(df_beta_v_ue$cpu_speed_mhz)), release_cpu_speed_mhz = c(summary(df_release_v_ue$cpu_speed_mhz)), 
+beta_cpu_l2_cache_kb = c(summary(df_beta_v_ue$cpu_l2_cache_kb)), release_cpu_l2_cache_kb = c(summary(df_release_v_ue$cpu_l2_cache_kb))
+)
+```
+
+## Training
+
+```{r}
+kable(text_tbl) %>%
+kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
+scroll_box(width = "100%")
+```
+
+## Validation
+
+```{r}
+kable(text_tbl_v) %>%
+kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
+scroll_box(width = "100%")
+```
+
+## Comparing Two Continuous Distributions
+
+### Training
+
+The QQ plot can be used to compare two continuous distributions.
+
+```{r fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
+par(mfrow = c(2, 2))  ## Set up a 2 x 2 plotting space
+
+## QQ plot in R to compare two data samples
+for (i in user_eng) {
+  x <- df_beta_ue[,i]
+  y <- df_release_ue[,i]
+
+  rg <- range(x, y, na.rm=T)
+
+  test <- ks.test(x, y)$statistic
+  pvalue <- ks.test(x, y)$p.value
+
+  test <- paste("KS Test = ", round(test, 3))
+  pvalue <- paste("P-value = ", round(pvalue, 3))
+
+  qqplot(x, y, main=i, xlim=rg, ylim=rg, xlab = "Beta", ylab = "Release", pch = 1)
+  # mtext(test, side=3)
+  text(min(x), max(x), paste(pvalue, "\n", test), adj=c(0,1))
+  abline(0,1, col="red")  
+}
+```
+
+```{r message=FALSE, warning=FALSE, out.width=c('50%', '50%')}
+for (i in user_eng) {
+  x <- df_beta_ue[,i]
+  y <- df_release_ue[,i]
+
+  print(i)
+  # print(ad.test(x))
+  # print(ad.test(y))
+  print(ks.test(x, y))
+}
+```
+
+### Validation
+
+The QQ plot can be used to compare two continuous distributions.
+
+```{r fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
+par(mfrow = c(2, 2))  ## Set up a 2 x 2 plotting space
+
+## QQ plot in R to compare two data samples
+for (i in user_eng) {
+  x <- df_beta_v_ue[,i]
+  y <- df_release_v_ue[,i]
+
+  rg <- range(x, y, na.rm=T)
+
+  test <- ks.test(x, y)$statistic
+  pvalue <- ks.test(x, y)$p.value
+
+  test <- paste("KS Test = ", round(test, 3))
+  pvalue <- paste("P-value = ", round(pvalue, 3))
+
+  qqplot(x, y, main=i, xlim=rg, ylim=rg, xlab = "Beta", ylab = "Release", pch = 1)
+  # mtext(test, side=3)
+  text(min(x), max(x), paste(pvalue, "\n", test), adj=c(0,1))
+  abline(0,1, col="red")  
+}
+```
+
+```{r message=FALSE, warning=FALSE, out.width=c('50%', '50%')}
+for (i in user_eng) {
+  x <- df_beta_v_ue[,i]
+  y <- df_release_v_ue[,i]
+
+  print(i)
+  # print(ad.test(x))
+  # print(ad.test(y))
+  print(ks.test(x, y))
+}
+```
+
+### Observations
+
+* Analyzing only the plots, in general, the distributions are very similar to each other
+* Mainly the metrics related to **active hours** and **number of active days**, **search count**, **number of pages**, **daily unique domains** and **daily number of sessions started**
+* Comparing only the training and validation plots, we can notice that the variables that presented a more different behavior were: `num_active_days`, `uri_count_max` and `num_addons`
+* When I performed the KS (kolmogorov-Smirnov) test, the null hypothesis that both samples come from the same distribution was rejected for all the comparisons. *Am I doing something wrong?*
+
+# User Engagement Discrete Metrics
+
+This section will focus only on user engagement continuous metrics. So, we are going to analyze the following metrics:
+
+* `default_search_engine`
+* `is_default_browser`
+* `profile_age_cat`
+* `distro_id_norm`
+* `memory_cat`
+* `cpu_speed_cat`
+* `cpu_cores_cat`
+* `cpu_l2_cache_kb_cat`
+* `cpu_vendor`
+* `os_version`
+* `is_wow64`
+* `fxa_configured`
+* `sync_configured`
+* `locale`
+* `country`
+* `timezone_cat`
+* `label`
+* `normalized_channel`
+* `is_release`
+
+```{r include=FALSE}
+user_eng_dis <- c("default_search_engine","is_default_browser","profile_age_cat","distro_id_norm","memory_cat","cpu_speed_cat","cpu_cores_cat","cpu_l2_cache_kb_cat","cpu_vendor","os_version","is_wow64","fxa_configured","sync_configured","locale","country","timezone_cat","label","normalized_channel","is_release")
+```
+
+```{r include=FALSE}
+df_beta_ue_dis <- df_beta %>% select(user_eng_dis)
+df_release_ue_dis <- df_release %>% select(user_eng_dis)
+df_train_ue_dis <- df_train_f %>% select(c(user_eng_dis, "label"))
+
+df_beta_v_ue_dis <- df_v_beta %>% select(user_eng_dis)
+df_release_v_ue_dis <- df_v_release %>% select(user_eng_dis)
+df_validate_ue_dis <- df_validate_f %>% select(c(user_eng_dis, "label"))
+```
+
+## Comparing Two Discrete Distributions
+
+### Training
+
+```{r fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
+par(mfrow = c(2, 2))  ## Set up a 2 x 2 plotting space
+
+## QQ plot in R to compare two data samples
+for (i in user_eng_dis) {
+  x <- df_beta_ue_dis[,i]
+  y <- df_release_ue_dis[,i]
+
+  rel_beta <- table(x)/nrow(df_beta_ue_dis) #divide the frequency counts by the total
+  beta_bar <- barplot(rel_beta,
+        main = "Beta", #Give your chart a title
+        ylim=c(0,1), border=F, col = "navy",
+        xlab = i, #Label the x axis
+        ylab = "Relative Frequency" #Label the y axis
+  ) 
+  # Add the text 
+  text(beta_bar, rel_beta+0.025, paste(round(rel_beta*100), "%", sep="") ,cex=1)
+
+  rel_release <- table(y)/nrow(df_release_ue_dis) #divide the frequency counts by the total
+  release_bar <- barplot(rel_release,
+        main = "Release", #Give your chart a title
+        ylim=c(0,1), border=F, col = "navy",
+        xlab = i, #Label the x axis
+        ylab = "Relative Frequency" #Label the y axis
+  )
+
+  # Add the text 
+  text(release_bar, rel_release+0.025, paste(round(rel_release*100), "%", sep="") ,cex=1) 
+}
+```
+
+### Validation
+
+```{r fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
+par(mfrow = c(2, 2))  ## Set up a 2 x 2 plotting space
+
+## QQ plot in R to compare two data samples
+for (i in user_eng_dis) {
+  x <- df_beta_v_ue_dis[,i]
+  y <- df_release_v_ue_dis[,i]
+
+  rel_beta <- table(x)/nrow(df_beta_v_ue_dis) #divide the frequency counts by the total
+  beta_bar <- barplot(rel_beta,
+        main = "Beta", #Give your chart a title
+        ylim=c(0,1), border=F, col = "navy",
+        xlab = i, #Label the x axis
+        ylab = "Relative Frequency" #Label the y axis
+  ) 
+  # Add the text 
+  text(beta_bar, rel_beta+0.025, paste(round(rel_beta*100), "%", sep="") ,cex=1)
+
+  rel_release <- table(y)/nrow(df_release_v_ue_dis) #divide the frequency counts by the total
+  release_bar <- barplot(rel_release,
+        main = "Release", #Give your chart a title
+        ylim=c(0,1), border=F, col = "navy",
+        xlab = i, #Label the x axis
+        ylab = "Relative Frequency" #Label the y axis
+  )
+
+  # Add the text 
+  text(release_bar, rel_release+0.025, paste(round(rel_release*100), "%", sep="") ,cex=1) 
+}
+```
+
+### Observations
+
+* Analyzing only the plots, in general, the distributions are very similar to each other

### 2019-12-17 poc/EDA/EDA.Rmd
updating the EDA report
finalizing EDA and comparative analysis

@@
 
-# Exploratory Data Analysis (EDA)
+# Introduction
 
-This R markdown covers the Exploratory Data Analysis (EDA) on the training dataset of the PRD.
+The goal of this project is to utilize [statistical matching](https://en.wikipedia.org/wiki/Matching_(statistics)) techniques to search for a subset of the prerelease user population that is most representative of Release.
 
-## Setting-up
-```{r message=FALSE, warning=FALSE}
+In this first report, we will perform an exploratory analysis of the data, focusing on investigating the differences between Beta and Release users.
+
+# Loading the data
+
+```{r message=FALSE, warning=FALSE, include=FALSE}
 ## Loading the needed libraries
@@
 library(nortest)
+library(emdist)
 ```
 
-```{r message=FALSE, warning=FALSE}
+```{r echo=TRUE, message=FALSE, warning=FALSE}
 ## Loading the training dataset
@@
 ## Training
+
+* App Version 67
 
@@
 
+* App Version 68
+
 ```{r message=FALSE, warning=FALSE}
@@
 
-## Step 1 : Data Inspection
+# Data Inspection
 
-### Training
+## Training
 
@@
 
-```{r echo=FALSE, fig.height=10, fig.width=10}
-plot_intro(df_train_f, ggtheme = theme_minimal())
-```
-
-### Validation
+## Validation
 
@@
 
+------
+
+## Observations
+
 ```{r echo=FALSE, fig.height=10, fig.width=10}
-plot_intro(df_validate_f, ggtheme = theme_minimal())
+par(mfrow = c(2, 2))  ## Set up a 2 x 2 plotting space
+
+plot_intro(df_train_f, ggtheme = theme_minimal(), title = "Training")
+plot_intro(df_validate_f, ggtheme = theme_minimal(), title = "Validation")
 ```
 
-### Observations
+* In both datasets, most variables are continuous
+* No NAs value (were handled in preprocessing)
 
-* Most of the dataset is composed of continuous variables
-* No NAs values (were handled in preprocessing)
+# Data Structure
 
-## Data Structure
-
-### Training
+## Training
 
@@
 
-### Validation
+## Validation
 
-Let's use `glimpse` function to display a vertical preview of the validation dataset. So we can easily preview data type and sample data.
+Let's use `glimpse` function to display a vertical preview of the validation dataset.
 
@@
 ```
-
-If we want to get some metrics about data types, zeros, infinite numbers, and missing values, we can use the `df_status` function.
 
@@
 
-* `q_zeros`: quantity of zeros (`p_zeros`: in percent)
-* `q_inf`: quantity of infinite values (`p_inf`: in percent)
-* `q_na`: quantity of NA (`p_na`: in percent)
-* `type`: factor, ordered-factor, numeric, integer or character
-* `unique`: quantity of unique values
+------
 
-### Observations
+## Observations
 
@@
 
-## Step 2 : Beta vs Release
+# Beta vs Release
 
-### Training
-
-```{r, fig.width = 7.5}
+```{r}
+## Training
 df_release <- df_train_f[which(df_train_f$label == 'release'), ]
@@
 
+## Validation
+df_v_release <- df_validate_f[which(df_validate_f$label == 'release'), ]
+df_v_beta <- df_validate_f[which(df_validate_f$label == 'beta'), ]
+```
+
+## Training
+
+* Composition:
+
+```{r}
 f <- freq(df_train_f$label)
@@
 
-```{r}
-summary(df_release)
-```
+## Validation
+
+* Composition:
 
 ```{r}
-summary(df_beta)
-```
-
-### Validation
-
-```{r, fig.width = 7.5}
-df_v_release <- df_validate_f[which(df_validate_f$label == 'release'), ]
-df_v_beta <- df_validate_f[which(df_validate_f$label == 'beta'), ]
-
 f <- freq(df_validate_f$label)
@@
 
-```{r}
-summary(df_v_release)
-```
+# Analyzing Discrete Variables
 
-```{r}
-summary(df_v_beta)
-```
-
-## Step 3 - Analyzing Discrete Variables
-
-### Training
+## Training
 
@@
 ## Frequency distribution release dataframe
-plot_bar(df_release, ggtheme = theme_minimal(base_size = 15))
+plot_bar(df_release, ggtheme = theme_minimal(base_size = 15), title = 'Release')
 ```
@@
 ## Frequency distribution beta dataframe
-plot_bar(df_beta, ggtheme = theme_minimal(base_size = 15))
+plot_bar(df_beta, ggtheme = theme_minimal(base_size = 15), title = 'Beta')
 ```
 
-### Validation
+## Validation
 
@@
 ## Frequency distribution release dataframe
-plot_bar(df_v_release, ggtheme = theme_minimal(base_size = 15))
+plot_bar(df_v_release, ggtheme = theme_minimal(base_size = 15), title = 'Release')
 ```
@@
 ## Frequency distribution beta dataframe
-plot_bar(df_v_beta, ggtheme = theme_minimal(base_size = 15))
+plot_bar(df_v_beta, ggtheme = theme_minimal(base_size = 15), title = 'Beta')
 ```
 
-## Step 4 - Analyzing Continuos Variables
+# Analyzing Continuos Variables
 
-### Training
+## Training
 
@@
 ## View histogram of release dataset
-plot_histogram(df_release, ggtheme = theme_minimal(base_size = 15))
+plot_histogram(df_release, ggtheme = theme_minimal(base_size = 15), title = 'Release')
 ```
@@
 ## View histogram of beta dataset
-plot_histogram(df_beta, ggtheme = theme_minimal(base_size = 15))
+plot_histogram(df_beta, ggtheme = theme_minimal(base_size = 15), title = 'Beta')
 ```
 
-### Validation
+## Validation
 
@@
 ## View histogram of beta dataset
-plot_histogram(df_beta, ggtheme = theme_minimal(base_size = 15))
+plot_histogram(df_beta, ggtheme = theme_minimal(base_size = 15), title = 'Beta')
 ```
 
-### Observations
+------
+
+## Observations
 
@@
 
-### Ploting Density Curves
+## Ploting Density Curves
 
-```{r include=FALSE}
+```{r message=FALSE, warning=FALSE, include=FALSE}
 require(cowplot)
@@
 
-# User Engagement Continuous Metrics
+# User Engagement Metrics
+
+## Continuous Variables
 
@@
 
-## Training
+### Training
+
+#### Beta-Release Difference
 
@@
 
-## Validation
+### Validation
+
+#### Beta-Release Difference
 
@@
 
-## Comparing Two Continuous Distributions
+### QQ-Plots
 
-### Training
-
-The QQ plot can be used to compare two continuous distributions.
+#### Training
 
@@
   test <- ks.test(x, y)$statistic
-  pvalue <- ks.test(x, y)$p.value
+  # pvalue <- ks.test(x, y)$p.value
 
   test <- paste("KS Test = ", round(test, 3))
-  pvalue <- paste("P-value = ", round(pvalue, 3))
+  # pvalue <- paste("P-value = ", round(pvalue, 3))
 
@@
   # mtext(test, side=3)
-  text(min(x), max(x), paste(pvalue, "\n", test), adj=c(0,1))
-  abline(0,1, col="red")  
+  text(min(x), max(x), test, adj=c(0,1))
+  abline(0,1, col="red", lty=2)  
 }
@@
 
-```{r message=FALSE, warning=FALSE, out.width=c('50%', '50%')}
-for (i in user_eng) {
-  x <- df_beta_ue[,i]
-  y <- df_release_ue[,i]
-
-  print(i)
-  # print(ad.test(x))
-  # print(ad.test(y))
-  print(ks.test(x, y))
-}
-```
-
-### Validation
-
-The QQ plot can be used to compare two continuous distributions.
+#### Validation
 
@@
 
-```{r message=FALSE, warning=FALSE, out.width=c('50%', '50%')}
-for (i in user_eng) {
-  x <- df_beta_v_ue[,i]
-  y <- df_release_v_ue[,i]
-
-  print(i)
-  # print(ad.test(x))
-  # print(ad.test(y))
-  print(ks.test(x, y))
-}
-```
+------
 
@@
 
-* Analyzing only the plots, in general, the distributions are very similar to each other
-* Mainly the metrics related to **active hours** and **number of active days**, **search count**, **number of pages**, **daily unique domains** and **daily number of sessions started**
-* Comparing only the training and validation plots, we can notice that the variables that presented a more different behavior were: `num_active_days`, `uri_count_max` and `num_addons`
-* When I performed the KS (kolmogorov-Smirnov) test, the null hypothesis that both samples come from the same distribution was rejected for all the comparisons. *Am I doing something wrong?*
+```{r message=FALSE, warning=FALSE, include=FALSE}
+tbl_ks <- data.frame(
+training = c(0.071,0.045,0.044,0.047,0.054,0.099,0.073,0.014,0.019,0.026,0.055,0.054,0.601,0.029,0.033,0.094,0.080,0.035,0.032,0.119,0.116,0.129,0.018,0.042,0.208,0.075,0.064,0.046,0.025), 
+validation = c(0.166,0.058,0.077,0.071,0.095,0.076,0.040,0.045,0.059,0.042,0.082,0.082,0.292,0.040,0.054,0.075,0.051,0.036,0.053,0.098,0.117,0.130,0.017,0.035,0.235,0.109,0.087,0.062,0.035)
+)
 
-# User Engagement Discrete Metrics
+row.names(tbl_ks) <- c('num_active_days','active_hours','active_hours_max','uri_count','uri_count_max','session_length','session_length_max','search_count','search_count_max','num_bookmarks','num_pages','num_pages_max','num_addons','daily_unique_domains','daily_unique_domains_max','daily_max_tabs','daily_max_tabs_max','daily_tabs_opened','daily_tabs_opened_max','daily_num_sessions_started','daily_num_sessions_started_max','startup_ms','install_year','profile_age','timezone_offset','memory_mb','cpu_cores','cpu_speed_mhz','cpu_l2_cache_kb')
+```
 
-This section will focus only on user engagement continuous metrics. So, we are going to analyze the following metrics:
+```{r}
+kable(tbl_ks) %>%
+add_header_above(c("KS Distance" = 3)) %>%
+kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
+row_spec(c(2,18,21:26), bold = T, color = "white", background = "#c3f584")
+```
+
+* Analyzing at the plots of each dataset separately, in general, Beta-Release distributions are very similar to each other
+* For instance, metrics related to **active hours** and **number of active days**, **search count**, **number of pages**, **daily unique domains** and **daily number of sessions started**
+* Comparing only the training and validation plots, we can observe large differences between the variables. Only a few showed similar distances (marked in green)
+
+## Discrete Variables
+
+This section will focus only on user engagement discrete metrics. So, we are going to analyze the following metrics:
 
@@
 
-## Comparing Two Discrete Distributions
-
 ### Training
@@
         main = "Beta", #Give your chart a title
-        ylim=c(0,1), border=F, col = "navy",
+        ylim=c(0,1), border=F, col = "#ffd271",
         xlab = i, #Label the x axis
@@
         main = "Release", #Give your chart a title
-        ylim=c(0,1), border=F, col = "navy",
+        ylim=c(0,1), border=F, col = "#f65c78",
         xlab = i, #Label the x axis
@@
 
+------
+
 ### Observations
 
-* Analyzing only the plots, in general, the distributions are very similar to each other
+* In general, the distributions are very similar to each other for both versions

### 2020-01-06 perf_release_criteria/milestone_4/ms_4_training_subsetting_calculation.Rmd
Adding in validation dataset. Serializing everything based upon version (i.e., each version gets its own suite of tables).

@@
 library(lubridate)
+library(htmltab)
+library(stringr)
 ```
@@
 # tl;dr 
-This notebook generates the training (Version N) and prediction (Version N+1) datasets, trains a statistical matching model, extracts a representative subset of Beta with respect to Release, and calculates the final Release Health Metrics as described in milestone 4 of this PRD[Release performance health metrics](https://docs.google.com/document/d/1Ygz6MkudYHZjnDnD9Z97kUyFrvV3KGWsjXyPjddhHq0/edit#heading=h.lvb9l8gw2nee).
+This notebook generates the training (Version N), prediction (Version N+1), and validation (Version N) datasets, trains a statistical matching model, extracts a representative subset of Beta with respect to Release, and calculates the final Release Health Metrics as described in milestone 4 of this [PRD](https://docs.google.com/document/d/1Ygz6MkudYHZjnDnD9Z97kUyFrvV3KGWsjXyPjddhHq0/edit#heading=h.lvb9l8gw2nee).
 
@@
 The datasets are generated by this [notebook](
-https://storage.cloud.google.com/moz-fx-data-bq-data-science-cdowhygelund/notebooks/jupyter/Beta_Release_Subsetting_Data_Preparation_GCP.ipynb
+https://storage.cloud.google.com/moz-fx-data-bq-data-science-cdowhygelund/notebooks/jupyter/subbeta_training_prediction_data_prep.ipynb
 ) on a Dataproc cluster.
-These are serialized as BigQuery tables available in the `moz-fx-data-shared-prod.analysis` dataset as `ccd_subBeta_training` (Version N) and `ccd_subBeta_prerelease` (Version N+1).
+These are serialized as BigQuery tables available in the `moz-fx-data-shared-prod.analysis` dataset as `ccd_subBeta_training_<version N>`, `ccd_subBeta_prerelease_<version N+1>`, and `ccd_subBeta_validation_<version N>`.
+
+```{r version, echo=FALSE}
+sched <- htmltab('https://wiki.mozilla.org/Release_Management/Calendar', which=2) %>%
+  mutate('rel_dates' = ymd(sched$`Release Date`)) %>%
+  mutate('version' = as.numeric(str_match(sched$Beta, 'Firefox ([0-9]+)')[,2])) %>%
+  filter(rel_dates < now())
+
+v_n1 <- sched$version[1]
+v_n <- sched$version[2]
+```
 
@@
 
-df_train <- load_df("ccd_subBeta_training")
-df_predict <- load_df('ccd_subBeta_prerelease')
+df_train <- load_df(paste("ccd_subBeta_training", v_n, sep='_'))
+df_predict <- load_df(paste('ccd_subBeta_prerelease'), v_n1, sep='_')
+df_validate <- load_df(paste('ccd_subBeta_validation'), v_n, sep='_')
 ```
@@
 # training datasets
-train_file_name <- paste('df_train_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
+# train_file_name <- paste('df_train_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
+train_file_name <- paste('df_train_', v_n, sep='_')
 train_file_path <- file.path('data', train_file_name)
@@
 # final prelease subsetted dataset
-prerelease_file_name <- paste('df_prerelease_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
+# prerelease_file_name <- paste('df_prerelease_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
+prerelease_file_name <- paste('df_prerelease_', v_n1, sep='_')
 prerelease_file_path <- file.path('data', prerelease_file_name)
@@
 gcs_prerelease_file_path <- file.path('data', 'milestone4', prerelease_file_name)
+
+# validation dataset
+# prerelease_file_name <- paste('df_prerelease_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
+validation_file_name <- paste('df_validation_', v_n1, sep='_')
+validation_file_path <- file.path('data', validation_file_name)
+save(validation, file = validation_file_path)
+gcs_validation_file_path <- file.path('data', 'milestone4', validation_file_name)
 
@@
 * `r gcs_prerelease_file_path`
+* `r gcs_validation_file_path`
 * `r gcs_release_health_file_path`
@@
 
+```{r gcp_validation_storage_push, warning=FALSE}
+upload_try <- gcs_upload(validation_file_path, name = gcs_validation_file_path)
+upload_try
+```
+
 ```{r gcp_health_metrics_storage_push, warning=FALSE}
@@
          dataset = "training",
-         table   = "ccd_subbeta_training_cleaned") %>%
+         table   = paste("ccd_subbeta_training_cleaned", v_n, sep = '_')) %>%
   bq_table_upload(values = df_train_x,
                   create_disposition = "CREATE_IF_NEEDED",
-                  write_disposition = "WRITE_APPEND",
+                  write_disposition = "WRITE_TRUNCATE",
                   fields = as_bq_fields(df_train_x) )
@@
          dataset = "training",
-         table   = "ccd_subbeta_training_final") %>%
+         table   = paste("ccd_subbeta_training_final", v_n, sep = '_')) %>%
   bq_table_upload(values = df_train_x,
                   create_disposition = "CREATE_IF_NEEDED",
-                  write_disposition = "WRITE_APPEND",
+                  write_disposition = "WRITE_TRUNCATE",
                   fields = as_bq_fields(df_train_x) )
@@
          dataset = "prerelease",
-         table   = "ccd_subbeta_prelease_cleaned") %>%
+         table   = paste("ccd_subbeta_prelease_cleaned", v_n1, sep = '_')) %>%
   bq_table_upload(values = df_predict_f,
                   create_disposition = "CREATE_IF_NEEDED",
-                  write_disposition = "WRITE_APPEND",
+                  write_disposition = "WRITE_TRUNCATE",
                   fields = as_bq_fields(df_predict_f) )
@@
          dataset = "prerelease",
-         table   = "ccd_subbeta_prelease_subset") %>%
+         table   = paste("ccd_subbeta_prelease_subset", v_n1, sep = '_')) %>%
+  bq_table_upload(values = df_predict_f,
+                  create_disposition = "CREATE_IF_NEEDED",
+                  write_disposition = "WRITE_APPEND",
+                  fields = as_bq_fields(df_predict_f) )
+```
+
+Validation dataset
+```{r bq_write_validate}
+bq_table(project = 'moz-fx-dev-cdowhyglund-subbeta',
+         dataset = "validation",
+         table   = paste("ccd_subbeta_validation_cleaned", v_n, sep = '_')) %>%
   bq_table_upload(values = df_predict_f,

### 2020-01-09 perf_release_criteria/lib/prediction.R
Adding in validation for processing.

@@ -1,0 +1,37 @@
+extract_health_metrics <- function(predictions, release){
+  agg_sets <- function(predictions){
+    predictions %>% 
+      select(outcomes) %>% 
+      gather("metric", "value", ) %>%
+      group_by(metric) %>%
+      summarise(
+        mean = mean(value),
+        p5 = partial(quantile, probs = .05)(value),  
+        p25 = partial(quantile, probs = .25)(value),  
+        p50 = median(value),
+        p75 = partial(quantile, probs = .75)(value),  
+        p95 = partial(quantile, probs = .95)(value),
+        p99 = partial(quantile, probs = .99)(value)
+      )
+  }
+  
+  pred_agg <- agg_sets(predictions)
+  release_agg <-  agg_sets(release)
+  
+  abs_rel_diff <- (abs(pred_agg[-1]-release_agg[-1])/release_agg[-1])
+  names(abs_rel_diff) <- paste('rel_diff_', names(abs_rel_diff), sep='')
+  abs_rel_diff <- abs_rel_diff %>%
+    mutate(metric = pred_agg$metric)
+  
+  cms_score <- sapply(outcomes, calc_cms, beta=df_predict_f, release=release)
+  cms_score <- data.frame(cms_score) %>% mutate(metric = rownames(.))
+  
+  health_metrics <- pred_agg %>% 
+    inner_join(., abs_rel_diff, by='metric') %>%
+    inner_join(., cms_score, by='metric') %>%
+    # mutate(cms_score = cms_score) %>%
+    mutate(date_created = now()) %>%
+    mutate(version = v_n1)
+  
+  return(health_metrics)
+}

### 2020-01-09 perf_release_criteria/lib/attributes.R
Moving categorical levels to own script. Fixing release health metrics ref bug.

@@ -1,0 +1,4 @@
+#### Categorical ordered levels ####
+
+cpu_cores_cat <- c('1', '2', '< 4', '< 8', '< 16', '> 16')
+cpu_speed_cat <- c("< 1GHz", "< 2GHz", "< 3GHz", "< 4GHz", "> 16GHz")

### 2020-01-09 perf_release_criteria/lib/prediction.R

@@ -1,8 +1,12 @@
-extract_health_metrics <- function(predictions, release){
+library(tidyr)
+library(purrr)
+library(lubridate)
+
+extract_health_metrics <- function(predictions, release, outcomes){
   agg_sets <- function(predictions){
     predictions %>% 
       select(outcomes) %>% 
-      gather("metric", "value", ) %>%
+      gather("metric", "value") %>%
       group_by(metric) %>%
       summarise(
         mean = mean(value),
@@ -23,7 +27,7 @@ extract_health_metrics <- function(predictions, release){
   abs_rel_diff <- abs_rel_diff %>%
     mutate(metric = pred_agg$metric)
   
-  cms_score <- sapply(outcomes, calc_cms, beta=df_predict_f, release=release)
+  cms_score <- sapply(outcomes, calc_cms, beta=predictions, release=release)
   cms_score <- data.frame(cms_score) %>% mutate(metric = rownames(.))
   
   health_metrics <- pred_agg %>% 

### 2020-01-09 perf_release_criteria/lib/supporting_funcs.R

@@ -4,6 +4,8 @@ library(magrittr)
 library(tidyr)
 library(tidyselect)
 
+source('attributes.R')
+
 #### Helpers ####
 calc_means <- function(df.match, ho_cov, add_1 = FALSE){
   ho_mean <- df.match %>% 
@@ -123,7 +125,7 @@ normalize_memory <- function(memory){
 }
 
 normalize_cpu_speed <- function(cpu_speed){
-  levels <- c("< 1GHz", "< 2GHz", "< 3GHz", "< 4GHz", "> 16GHz")
+  levels <- cpu_speed_cat 
   ghz <- cpu_speed / 1000
   factor(
     case_when(
@@ -137,7 +139,7 @@ normalize_cpu_speed <- function(cpu_speed){
 }
 
 normalize_cpu_cores <- function(cpu_cores){
-  levels <- c('1', '2', '< 4', '< 8', '< 16', '> 16')
+  levels <- cpu_cores_cat
   factor(
     case_when(
       cpu_cores <= 1 ~ levels[1],

### 2020-01-10 poc/matchIt/matching_methods.Rmd
MatchIt tutorial notebook

---
title: "Mozilla Data Science Project - 2019"
author: "Mariana de Oliveira Santos Silva"
date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    toc: true
    toc_float: true
    highlight: tango
    df_print: kable
    theme: flatly
---

# Introduction

In this second report, we will demonstrate how to get started with matching methods using R and the [MatchIt](https://cran.r-project.org/web/packages/MatchIt/MatchIt.pdf) package.

> *"Matching is a nonparametric method of preprocessing data to control for some or all of the potentially confounding influence of pretreatment control variables by reducing imbalance between the treated and control groups. After preprocessing in this way, any method of analysis that would have been used without matching can be applied to estimate causal effects."*
**- [Gary King](http://gking.harvard.edu/cem)**

# Loading the data

To begin we need to load some data. We will use as example a data set previously analyzed extensively by [Lalonde (1986)](http://business.baylor.edu/scott_cunningham/teaching/lalonde-1986.pdf) and [Dehejia and Wahba (1999)](https://www.ics.uci.edu/~sternh/courses/265/dehejiawahba_jasa1999.pdf). In this data set, there is a subsample of the data from the treated group in the National Supported Work Demonstration (NSW) and the comparison sample from the Current Population Survey (CPS).

```{r message=FALSE, warning=FALSE, include=FALSE}
## Install packages

#install.packages("MatchIt")
#install.packages("optmatch")
#install.packages("RItools")
```

```{r message=FALSE, warning=FALSE, include=FALSE}
## Loading the needed libraries

library(kableExtra)      # help you build common complex tables and manipulate table styles
library(DataExplorer)    # automated data exploration
library(tidyverse)       # for general data wrangling (includes readr and dplyr)
library(ggplot2)         # to draw statistical plots 
library(MatchIt)
library(optmatch)
library(RItools)
library(ggthemes)
library(funModeling) 
```

```{r message=FALSE, warning=FALSE}
## Loading data: a subset of the LaLonde data is loaded with the MatchIt library

data(lalonde)
```

# Data Inspection

```{r echo=FALSE}
## Examine data briefly

kable(introduce(lalonde)) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
scroll_box(width = "100%")
```

To perform matching methods, we will need a data set that consists of cases in rows and variables in columns. We will need a **dependent variable** and one or more matching variables. The dependent variable is the variable that specifies which group a case belongs to (e.g., treatment or control). In this example, our dependent variable is `treat`, where $1$ means treatment and $0$, control.

```{r message=FALSE, warning=FALSE}
## View LaLonde dataframe

kable(head(lalonde, 10)) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
scroll_box(width = "100%")
```

------

## Observations

* 614 observations: 185 treated, 429 control
* 10 variables measured for each individual:
  + Outcome (`re78`) = income in 1978, in U.S.
  + Treatment (`treat`) = participation in job training  (1 = treated, 0 = control)
  + Training Covariants: 
    - `age` is age in years
    - `educ` is education in number of years of schooling
    - `black` is an indicator for African-American (1 = African-American, 0 = not)
    - `hispan` is an indicator for being of Hispanic origin (1 = Hispanic, 0 = not)
    - `married` is an indicator for married (1 = married, 0 = not married)
    - `nodegree` is an indicator for whether the individual has a high school degree (1 = no degree, 0 = degree)
    - `re74` is income in 1974, in U.S. dollars
    - `re75` is income in 1975, in U.S. dollars

# Data Structure

```{r}
glimpse(lalonde)
```

```{r}
kable(df_status(lalonde, FALSE)) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
scroll_box(width = "100%")
```

* Composition:

```{r}
f <- freq(lalonde$treat)
```

# Propensity Score Matching

In this tutorial we'll analyze the effect of participating in job training, as opposed to not participate, on income in 1978 dollars. We will use propensity score matching to get more credible causal estimates of job training.

To examine the effect of participating in job training ("Treated") versus non-participation ("Control") on income using matching we will go through the following steps:

1. Preliminary analysis
2. Estimation of Propensity scores (the probability of being Treated given a set of pre-treatment covariates)
3. Propensity Score matching. We'll use the following matching methods:
  a) Coarsened Exact Matching (CEM)
  b) Nearest neighbor matching
  c) Nearest neighbor matching, with Mahalanobis distance measure
4. Outcome analysis
5. Sensitivity analysis

<center>
![FigName](flowchart.png)
</center>

## Preliminary Analysis (using unmatched data)

Before propensity scores are calculated, it is a good practice to determine if the two groups are balanced. The best practice to determine the covariates that influence group assignment is based on theoretical evidence. In addition, statistical tests can also be used to determine if the covariates are imbalanced across groups. The package [RItools](https://cran.r-project.org/web/packages/RItools/index.html) includes the routine `XBalance` that estimates a chi-square test to which checks if there is at least one variable in the selection model for which the two groups are different.

### Computing indices of covariate imbalance before matching

#### 1. Standardized difference

```{r}
treated <- (lalonde$treat==1)
cov <- lalonde[,2:9]
std.diff <- apply(cov,2,function(x) 100*(mean(x[treated])- mean(x[!treated]))/(sqrt(0.5*(var(x[treated]) + var(x[!treated])))))
sort(abs(std.diff))
```

For the standardized difference, absolute scores higher than $25%$ are considered suspect, and may indicate an imbalance for that specific variable [(Stuart & Rubin, 2008)](http://citeseerx.ist.psu.edu/viewdoc/download;jsessionid=F52F07E838B6B1B9DB8B05FB10AAE7CB?doi=10.1.1.584.1057&rep=rep1&type=pdf). That is, `hispan`, `re75`, `re74`, `married` and `black`.

#### 2. Check initial balance

* *How similar are treatment/control groups on X?*

```{r}
xBalance(treat ~ . - (re78 + treat), data=lalonde, report=c("all"))
```

A statistically significant chi-square will indicate that at least one of the variables included in the model is creating an imbalance between the two groups. Variables that create imbalance should be included in the selection model. Also as part of the preliminary analysis it is a good practice to assess the effects of the treatment on the outcome variable by running the outcome model. This assessment can be based on the treatment variable only (using a t-test), or include covariates (using a regression model).

### Treatment effect without matching: difference of means

```{r}
unmatched <- lm(re78 ~ treat, data=lalonde)
summary(unmatched)
```

```{r}
effect <- unmatched$coeff[2]
effect
```

### Treatment effect without matching: regression

```{r}
unmatched <- lm(re78 ~ treat + age + educ + nodegree + re74 + re75 + married + black + hispan, data = lalonde)
summary(unmatched)
```

## Propensity Score Estimation

Packages such as MatchIt estimates propensity scores using logistic regression as the default option. However, when estimating propensity scores using the default option, the fit of the model cannot be assessed. Therefore, it is recommended that a logistic regression is run to determine the model fit.

### Calculates the propensity score

```{r}
ps <- glm(treat ~ age + educ + nodegree + re74 + re75, data=lalonde, family=binomial())
summary(ps)
```

Statistically significant estimates are identified by low (i.e., $< 0.05$) p-values. There are no clear suggestions as to whether to include in the final model all the variables (even non-significant). Some authors suggest that the final model should include not only statistically significant variables, but also variables known to be associated with selection.

Once the propensity scores have been calculated, a graphical approach can be used to assess the distributional similarity between score distributions. This graphical approach uses back to back histograms such as those created through the package Hmisc. Back to back histograms cannot be used with Mahalanobis distance, because it is a multidimensional technique.

* Attach the predicted propensity score to the datafile

```{r}
lalonde$psvalue <- predict(ps, type="response")
```

### Back to back histogram

```{r fig.height=5, fig.width=10}
out <- histbackback(split(lalonde$psvalue, lalonde$treat), main="Propensity score before matching", xlab=c("control", "treatment"))
#! just adding color
barplot(-out$left, col="#111d5e" , horiz=TRUE, space=0, add=TRUE, axes=FALSE)
barplot(out$right, col="#b21f66", horiz=TRUE, space=0, add=TRUE, axes=FALSE)
```

Important parameters to determine the fit are not only the shape, but also degree of overlap between the two distributions (known as the common support region). Matching is best when there is a common support region.

## Propensity Score Matching

Packages such as MatchIt provide summary tables that include means and standard deviations for the two groups both before and after the matching was completed. It also includes percent improvement, and finally, it provides a summary of the number of individuals included in the final sample, and cases that were not matched. The number of matched and unmatched cases is usually dependent on the match ratio imposed by the user, and the number of cases in the treatment group.

### Match using Coarsened Exact Matching (CEM)

Coarsened Exact Matching (CEM) is a Monotonic Imbalance Bounding (MIB) matching method - which means that the balance between the treated and control groups is chosen by the user ex-ante rather than discovered through the usual laborious process of checking after the fact and repeatedly reestimating, and so that adjusting the imbalance on one variable has no effect on the maximum imbalance of any other. CEM also strictly bounds through ex-ante user choice both the degree of model dependence and the average treatment effect estimation error, eliminates the need for a separate procedure to restrict data to common empirical support, meets the congruence principle, is robust to measurement error, works well with multiple imputation methods for missing data, and is extremely fast computationally even with very large data sets. CEM also works well for multicategory treatments, determining blocks in experimental designs, and evaluating extreme counterfactuals.

```{r}
m.cem <- matchit(treat ~ age + educ + nodegree + re74 + re75, data=lalonde, method="cem")
summary(m.cem)
match.data.1 = match.data(m.cem)
```

### Match using Nearest neighbor matching

Nearest neighbor matching selects the $r$ (default=1) best control matches for each individual in the treatment group (excluding those discarded using the `discard` option). Matching is done using a distance measure specified by the `distance` option (default=logit). Matches are chosen for each treated unit one at a time, with the order specified by the `m.order` command (default=largest to smallest). At each matching step, we choose the control unit that is not yet matched but is closest to the treated unit on the distance measure.

```{r}
m.nn <- matchit(treat ~ age + educ + nodegree + re74 + re75, data=lalonde, method="nearest", ratio = 1)
summary(m.nn)
match.data.2 = match.data(m.nn)
```

### Match using Nearest neighbor matching, with Mahalanobis distance measure

```{r}
m.nnm <- matchit(treat ~ age + educ + nodegree + re74 + re75, data=lalonde, method="nearest", ratio=1, distance="mahalanobis")
summary(m.nnm)
match.data.3 = match.data(m.nnm)
```

Graphical approaches (such as the jitter type in the package MatchIt), will help the user get some idea of whether the individuals not matched are in some specific part of the propensity-score continuum. The jitter plot shows the overall distribution of propensity scores in the treated and control groups.

```{r fig.height=5, fig.width=10}
plot(m.cem, type = "jitter", col = "#111d5e")
plot(m.nn, type = "jitter", col = "#111d5e")
#plot(m.nnm, type = "jitter", col = "#111d5e") ## Not appropriate for pure Mahalanobis matching. No plots generated.
```

As can be observed in this figure, the section labeled "Unmatched control Units" shows that most of the non-matched individuals were in the lower (0.0 to 0.4) part of the propensity scores. However, there were a few cases in a higher range (0.5-0.6).

It is important to determine that the groups are balanced, thus eliminating (or substantially reducing) the initial selection bias. In step 1 in this section (preliminary analysis) it was mentioned that there are both statistical as well as graphical approaches that can be used to determine the degree of imbalance. After the match has been conducted, both techniques are used again to determine that all the critical variables have been balanced.

### Computing indices of covariate imbalance after matching

```{r}
### 1. Standardized difference
treated1 <- (match.data.2$treat==1)
cov1 <- match.data.2[,2:9]
std.diff1 <- apply(cov1,2,function(x) 100*(mean(x[treated1])- mean(x[!treated1]))/(sqrt(0.5*(var(x[treated1]) + var(x[!treated1])))))
abs(std.diff1)
```

```{r}
### 2. chi-square test
xBalance(treat ~ age + educ + nodegree + re74 + re75, data = match.data.2, report = c("chisquare.test"))
```

Although the chi-square test indicates no significance, thus suggesting equivalence between the groups, the standardized difference test shows that there are some variables with a large difference (i.e., black, hispan, married) that can still be improved. Potential suggestions might include the use of interactions terms, or polynomial terms to try to reduce their imbalance. A graphical approach that can be used to determine the match between groups is the back to back histograms.

```{r fig.height=5, fig.width=10}
out <- histbackback(split(match.data.1$psvalue, match.data.1$treat), main= "Propensity score after matching (CEM)", xlab=c("control", "treatment"))
barplot(-out$left, col="#111d5e" , horiz=TRUE, space=0, add=TRUE, axes=FALSE)
barplot(out$right, col="#b21f66", horiz=TRUE, space=0, add=TRUE, axes=FALSE)
```

```{r fig.height=5, fig.width=10}
out <- histbackback(split(match.data.2$psvalue, match.data.2$treat), main= "Propensity score after matching (NN)", xlab=c("control", "treatment"))
barplot(-out$left, col="#111d5e" , horiz=TRUE, space=0, add=TRUE, axes=FALSE)
barplot(out$right, col="#b21f66", horiz=TRUE, space=0, add=TRUE, axes=FALSE)
```

```{r fig.height=5, fig.width=10}
out <- histbackback(split(match.data.3$psvalue, match.data.3$treat), main= "Propensity score after matching (NN w/ Mahalanobis)", xlab=c("control", "treatment"))
barplot(-out$left, col="#111d5e" , horiz=TRUE, space=0, add=TRUE, axes=FALSE)
barplot(out$right, col="#b21f66", horiz=TRUE, space=0, add=TRUE, axes=FALSE)
```

As can be observed above, there is a remarkable improvement in the match between the two distributions of propensity scores after the match (compared to the histograms for the same data before the match). This match suggests that the two groups are much more similar in terms of their propensity scores, and thus, the selection bias has been reduced substantially.

## Outcomes Analysis

Once the researcher is satisfied with the propensity score matching, it is time to proceed with the outcome model. Several of the more frequently used techniques such as near neighbor, and Mahalanobis distances, can be used with analytic techniques such as linear regression models, ANCOVA, or even matched t-tests. However, the selection of any analytic approach to estimate the treatment effect and statistical significance should take into account the fact that the propensity score creates matched samples.

### Outcome analysis using paired t-test

```{r}
# saving the data matched
matches <- data.frame(m.nn$match.matrix)

# finding the matches. one for group 1 one for group 2
group1 <- match(row.names(matches), row.names(match.data.2))
group2 <- match(matches$X1, row.names(match.data.2))

# extracting the outcome value for the matches
yT  <- match.data.2$re78[group1]
yC  <- match.data.2$re78[group2]

# binding
matched.cases <- cbind(matches, yT, yC)

#Paired t-test
t.test(matched.cases$yT, matched.cases$yC, paired = TRUE)
```

The simplicity of these outcomes analysis make them easy to complete and their implications are usually easy to understand. For optimal and full matching however, the outcome analyses are more complex. Under optimal and full matching, it is possible to have the same individual matched against more than one individual from the other group. And for full matching, this can be the case not only for individuals in the control group, but also for individuals in the treatment group. Given that individuals can be used more than once in both the treatment and control groups, multivariate techniques should not be used.

### 2020-01-10 poc/matchIt/report.Rmd
create the report file to start modeling our problem

---
title: "Beta to Release Matching: Proof-of-Concept"
author: "Mariana de Oliveira Santos Silva"
date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    theme: flatly
    toc: true
    toc_float: true
    df_print: kable
---

## Introduction

The goal of this project is to utilize [statistical matching](https://en.wikipedia.org/wiki/Matching_(statistics)) techniques to search for a subset of the prerelease user population that is most representative of Release.

The specific use-case of this proof-of-concept was to utilize engagement, configuration, and environment client fields (covariates) for matching. Validation of the matching was performed on a hold-out set of **user engagement** covariates, as an illustration of a potential real-world use-case.

## Problem Statement

It is highly desirable to utilize the telemetry from Beta versions of Firefox to determine critical aspects of Release behavior before it is launched to the general user base. However, it is well known that the Beta population has distinctly different characteristics than Release, such as the distribution of country of origin of its users, and have higher incidents of crashes. Therefore, directly utilizing Beta telemetry to inform Release is not statistically valid.

One possible approach to deal with this discrepancy is to use statistical matching techniques to find a subset of Beta that is representative of Release. What connotates "representative" depends upon the desired use-case (outcome), such as user engagement, performance characteristics, or crash rates. In this work, we focus on the application of **user engagement** metrics.

## Methodology
### Data Preparation

### Covariates

#### Training

#### Holdout

### Covariate Selection

## Models

## Results

## Discussion

### 2020-01-10 perf_release_criteria/lib/attributes.R
Validation dashboard.

@@ -2,3 +2,5 @@
 
 cpu_cores_cat <- c('1', '2', '< 4', '< 8', '< 16', '> 16')
 cpu_speed_cat <- c("< 1GHz", "< 2GHz", "< 3GHz", "< 4GHz", "> 16GHz")
+mem_cat <- c('< 1GB', '< 2GB', '< 4GB', '< 6GB', '< 16GB', '> 16GB')
+profile_age_cat <- c("< 1 week",  "< 1 month", "< 6 months", "< 2 years", "< 5 years", "> 5 years")

### 2020-01-10 perf_release_criteria/lib/supporting_funcs.R

@@ -92,7 +92,7 @@ normalize_distro_id <- function(distro_id){
 }
 
 normalize_profile_age <- function(profile_age){
-  levels <- c("< 1 week",  "< 1 month", "< 6 months", "< 2 years", "< 5 years", "> 5 years")
+  levels <- profile_age_cat
   factor(
     case_when(
       profile_age < 7 ~ levels[1],
@@ -110,7 +110,7 @@ normalize_timezone <- function(timezone){
 }
 
 normalize_memory <- function(memory){
-  levels <- c('< 1GB', '< 2GB', '< 4GB', '< 6GB', '< 16GB', '> 16GB')
+  levels <- mem_cat 
   gb <- memory / 1024
   factor(
     case_when(

### 2020-01-10 perf_release_criteria/milestone_5/dashboard/app.R

@@ -1,0 +1,457 @@
+library(shiny)
+library(shinydashboard)
+library(shinycssloaders)
+library(dplyr)
+
+source('plotters.R')
+# source('prepare_dashboard.R')
+
+ui <- dashboardPage(
+  dashboardHeader(title = "subBeta"),
+  dashboardSidebar(
+    sidebarMenu(
+      menuItem("Perf: Prediction",
+               tabName = "performance_prediction",
+               icon = icon("dashboard")),
+      menuItem("Perf: Method Validation",
+               tabName = "performance_validation",
+               icon = icon("dashboard")),
+      menuItem('Environment Covariates',
+               menuSubItem(
+                 selectInput(
+                   'cpu_cores_cat',
+                   '# of Cores',
+                   cpu_cores_cat,
+                   multiple = TRUE,
+                   selectize = TRUE
+                 )
+               ),
+               menuSubItem(
+                 selectInput(
+                   'cpu_speed_cat',
+                   'CPU Speed',
+                   cpu_speed_cat,
+                   multiple = TRUE,
+                   selectize = TRUE
+                 )
+               ),
+               menuSubItem(
+                 selectInput(
+                   'mem_cat',
+                   'Memory Size',
+                   mem_cat,
+                   multiple = TRUE,
+                   selectize = TRUE
+                 )
+               )
+      ),
+      menuItem('Profile Covariates',
+               menuSubItem(
+                 selectInput(
+                   'profile_age_cat',
+                   'Profile Age',
+                   profile_age_cat,
+                   multiple = TRUE,
+                   selectize = TRUE
+                 )
+               ),
+               menuSubItem(
+                 selectInput(
+                   'country_cat',
+                   'Country',
+                   sort(unique(predictions$country)),
+                   multiple = TRUE,
+                   selectize = TRUE
+                 )
+               ),
+               menuSubItem(
+                 selectInput(
+                   'timezone_cat',
+                   'Timezone Offset',
+                   sort(unique(predictions$timezone_cat)),
+                   multiple = TRUE,
+                   selectize = TRUE
+                 )
+               )
+      )
+    )
+  ),
+  dashboardBody(
+    tabItems(
+      #### Sidbar Tab: Prediction #### 
+      tabItem(tabName = 'performance_prediction',
+              fluidRow(box(
+                column(
+                  width = 12,
+                  # dataTableOutput('summ_valid_tbl'),
+                  tableOutput('release_health_tbl'),
[…]

### 2020-01-10 perf_release_criteria/milestone_5/dashboard/plotters.R

@@ -1,0 +1,59 @@
+library(ggplot2)
+library(ggridges)
+library(viridis)
+
+apply_filters <- function(df, input){
+  resp.df <- df %>%
+    filter(case_when(!is.null(input$cpu_cores_cat) ~ cpu_cores_cat %in% input$cpu_cores_cat,
+                     TRUE ~ cpu_cores_cat == cpu_cores_cat)) %>%
+    filter(case_when(!is.null(input$cpu_speed_cat) ~ cpu_speed_cat %in% input$cpu_speed_cat,
+                     TRUE ~ cpu_speed_cat == cpu_speed_cat))
+  return(resp.df)
+}
+
+build_quantile_df <- function(validation, matched, original, metrics){
+  qqs <- list()
+  for (perf_metric in metrics){
+    qq <- qqplot(validation[[perf_metric]], matched[[perf_metric]], plot.it = FALSE) %>% 
+      bind_rows() %>%
+      mutate(type = 'matched')
+    qq_full <- qqplot(validation[[perf_metric]], original[[perf_metric]], plot.it = FALSE) %>% 
+      bind_rows() %>%
+      mutate(type = 'original') %>%
+      bind_rows(qq) %>%
+      mutate(metric = perf_metric)
+    # qq_full$metric <- perf_metric
+    qqs[[perf_metric]] <- qq_full
+  }
+  qq_df <- qqs %>% bind_rows() %>% rename(release = x, beta = y)
+  return(qq_df)
+}
+
+  
+plot.qq <- function(qq.df, response){
+  p_qq <- ggplot(qq.df %>% filter(metric == response), aes(x = release, y = beta)) +
+    geom_point(aes(color = type, shape = type)) + 
+    geom_abline(slope = 1, intercept = 0) + 
+    theme_bw() + 
+    theme(axis.text.x = element_text(angle = 45, hjust = 1),
+          plot.title = element_text(size=10),
+          legend.position = c(0.8, 0.2)) + 
+    ggtitle(response) 
+  return(p_qq)
+  
+}
+
+plot.ridges <- function(resp.df, response){
+
+  p_ridge <- ggplot(resp.df, aes(x=!!sym(response), y=label, fill=factor(..quantile..))) +
+    stat_density_ridges(
+      geom = "density_ridges_gradient", calc_ecdf = TRUE,
+      quantiles = 10, quantile_lines = TRUE
+    ) +
[…]

### 2020-01-10 perf_release_criteria/milestone_5/dashboard/prepare_dashboard.R

@@ -1,0 +1,82 @@
+# prepare_dashboard.R
+
+library(bigrquery)
+library(stringr)
+library(dplyr)
+library(dbplyr)
+source('../../lib/prediction.R')
+source(file = '../../lib/scoring.R')
+
+#### Config ####
+project <- "moz-fx-dev-cdowhyglund-subbeta"
+pred_tbl_prefix <- 'ccd_subbeta_prelease_subset_'
+beta_tbl_prefix <- 'ccd_subbeta_prelease_cleaned_'
+valid_tbl_prefix <- 'ccd_subbeta_validation_cleaned_'
+
+#### Funcs ####
+import_data <- function(tbl_prefix, version, dataset) {
+  tbl <- paste(tbl_prefix, version, sep='')
+  
+  con <- dbConnect(
+    bigrquery::bigquery(),
+    project = project,
+    dataset = dataset,
+    billing = project
+  )
+  
+  df <- tbl(con, tbl) %>%
+    collect()
+  
+  return(df)
+}
+
+#### Step 1 ####
+# query subbeta tables to get current version 
+v_n1 <- max(
+  as.numeric(
+    str_match(list_tables(project, 'prerelease'), 
+              paste(tbl_prefix, '([0-9]+)', sep='' ))[, 2]),
+  na.rm = TRUE
+)
+
+#### Step 2 ####
+# pull current predictions from DB
+pred_v_n1 <- import_data(pred_tbl_prefix, v_n1, 'prerelease')
+
+#### Step 3 ####
+# extract levels for use in dashboard
+source('../../lib/attributes.R')
+
+# os_version <- c('Other', '6.1', '6.2', '6.3', '10.0')
+# cpu_cores_cat <- c("1",  "2", '< 4',  '< 8', "> 16" "< 8"  "< 4"  "< 16") # levels(predictions$cpu_cores_cat)
+# cpu_speed_cat <- unique(predictions$cpu_speed_cat) # levels(predictions$cpu_speed_cat)
+
+#### Step 4 ####
+v_n <- v_n1 - 1
+
+# pull previous predictions 
+pred_v_n <- import_data(pred_tbl_prefix, v_n, 'prerelease')
+
+# pull current validation (this is used for both Health metrics and validating)
+valid_v_n <- import_data(valid_tbl_prefix, v_n, 'validation')
+
+# pull all of current Beta
+beta_v_n <- import_data(beta_tbl_prefix, v_n, 'prerelease')
+
[…]

### 2020-01-10 perf_release_criteria/milestone_5/dashboard/app.R
MVP

@@ -89,113 +89,113 @@ ui <- dashboardPage(
                 ),
                 width = 12
                 # height = 12
-              ))
-              # tabBox(
-              #   # title = 'Metric',
-              #   width = 12,
-              #   tabPanel('FX_PAGE_LOAD_MS_2',
-              #            fluidRow(box(withSpinner(
-              #              plotOutput(
-              #                "fxpglms_qq",
-              #                height = 300,
-              #                width = "100%"
-              #              )),
-              #              width = 12
-              #            )),
-              #            fluidRow(box(withSpinner(
-              #              plotOutput(
-              #                "fxpglms_ridges",
-              #                height = 300,
-              #                width = "100%"
-              #              )),
-              #              width = 12
-              #            ))),
-              #   tabPanel('TIME_TO_DOM_INTERACTIVE_MS',
-              #            fluidRow(box(withSpinner(
-              #              plotOutput(
-              #                "ttdims_qq",
-              #                height = 300,
-              #                width = "100%"
-              #              )),
-              #              width = 12
-              #            )),
-              #            fluidRow(box(withSpinner(
-              #              plotOutput(
-              #                "ttdims_ridges",
-              #                height = 300,
-              #                width = "100%"
-              #              )),
-              #              width = 12
-              #            ))),
-              #   tabPanel('TIME_TO_DOM_COMPLETE_MS',
-              #            fluidRow(box(withSpinner(
-              #              plotOutput(
-              #                "ttdcms_qq",
-              #                height = 300,
-              #                width = "100%"
-              #              )),
-              #              width = 12
-              #            )),
-              #            fluidRow(box(withSpinner(
-              #              plotOutput(
-              #                "ttdcms_ridges",
-              #                height = 300,
-              #                width = "100%"
-              #              )),
-              #              width = 12
-              #            ))),
-              #   tabPanel('TIME_TO_LOAD_EVENT_END_MS',
-              #            fluidRow(box(withSpinner(
-              #              plotOutput(
-              #                "ttleems_qq",
-              #                height = 300,
-              #                width = "100%"
[…]

### 2020-01-10 perf_release_criteria/milestone_5/dashboard/plotters.R

@@ -7,7 +7,16 @@ apply_filters <- function(df, input){
     filter(case_when(!is.null(input$cpu_cores_cat) ~ cpu_cores_cat %in% input$cpu_cores_cat,
                      TRUE ~ cpu_cores_cat == cpu_cores_cat)) %>%
     filter(case_when(!is.null(input$cpu_speed_cat) ~ cpu_speed_cat %in% input$cpu_speed_cat,
-                     TRUE ~ cpu_speed_cat == cpu_speed_cat))
+                     TRUE ~ cpu_speed_cat == cpu_speed_cat)) %>%
+    filter(case_when(!is.null(input$mem_cat) ~ memory_cat %in% input$mem_cat,
+                     TRUE ~ memory_cat == memory_cat)) %>%
+    filter(case_when(!is.null(input$profile_age_cat) ~ profile_age_cat %in% input$profile_age_cat,
+                     TRUE ~ profile_age_cat == profile_age_cat)) %>%
+    filter(case_when(!is.null(input$country_cat) ~ country %in% input$country_cat,
+                     TRUE ~ country == country)) %>%
+    filter(case_when(!is.null(input$timezone_cat) ~ timezone_cat %in% input$timezone_cat,
+                     TRUE ~ timezone_cat == timezone_cat))
+  
   return(resp.df)
 }
 

### 2020-01-10 perf_release_criteria/milestone_5/dashboard/app.R
Updating to run as prep as script.

@@ -4,7 +4,7 @@ library(shinycssloaders)
 library(dplyr)
 
 source('plotters.R')
-# source('prepare_dashboard.R')
+source('prepare_dashboard.R')
 
 ui <- dashboardPage(
   dashboardHeader(title = "subBeta"),

### 2020-01-10 perf_release_criteria/milestone_5/dashboard/prepare_dashboard.R

@@ -35,7 +35,7 @@ import_data <- function(tbl_prefix, version, dataset) {
 v_n1 <- max(
   as.numeric(
     str_match(list_tables(project, 'prerelease'), 
-              paste(tbl_prefix, '([0-9]+)', sep='' ))[, 2]),
+              paste(pred_tbl_prefix, '([0-9]+)', sep='' ))[, 2]),
   na.rm = TRUE
 )
 

### 2020-01-12 perf_release_criteria/lib/prediction.R
Dealing with extract_health_metrics masking bug with save.image.

@@ -1,8 +1,9 @@
 library(tidyr)
 library(purrr)
 library(lubridate)
+source('../../lib/scoring.R')
 
-extract_health_metrics <- function(predictions, release, outcomes){
+extract_health_metrics <- function(predictions, release, outcomes, v_n1){
   agg_sets <- function(predictions){
     predictions %>% 
       select(outcomes) %>% 
@@ -30,11 +31,13 @@ extract_health_metrics <- function(predictions, release, outcomes){
   cms_score <- sapply(outcomes, calc_cms, beta=predictions, release=release)
   cms_score <- data.frame(cms_score) %>% mutate(metric = rownames(.))
   
+  if (missing(v_n1)) v_n1 <- unique(predictions$app_version)[1]
+  
   health_metrics <- pred_agg %>% 
     inner_join(., abs_rel_diff, by='metric') %>%
     inner_join(., cms_score, by='metric') %>%
     # mutate(cms_score = cms_score) %>%
-    mutate(date_created = now()) %>%
+    mutate(date_created = now())  %>%
     mutate(version = v_n1)
   
   return(health_metrics)

### 2020-01-12 perf_release_criteria/milestone_5/dashboard/app.R

@@ -2,9 +2,13 @@ library(shiny)
 library(shinydashboard)
 library(shinycssloaders)
 library(dplyr)
+library(tidyr)
+library(purrr)
 
+# source('prepare_dashboard.R')
+load('data/dashboard_prepped.RData')
 source('plotters.R')
-source('prepare_dashboard.R')
+source('../../lib/prediction.R')
 
 ui <- dashboardPage(
   dashboardHeader(title = "subBeta"),
@@ -59,7 +63,7 @@ ui <- dashboardPage(
                  selectInput(
                    'country_cat',
                    'Country',
-                   sort(unique(predictions$country)),
+                   sort(unique(pred_v_n1$country)),
                    multiple = TRUE,
                    selectize = TRUE
                  )
@@ -68,7 +72,7 @@ ui <- dashboardPage(
                  selectInput(
                    'timezone_cat',
                    'Timezone Offset',
-                   sort(unique(predictions$timezone_cat)),
+                   sort(unique(pred_v_n1$timezone_cat)),
                    multiple = TRUE,
                    selectize = TRUE
                  )

### 2020-01-12 perf_release_criteria/milestone_5/dashboard/plotters.R

@@ -37,7 +37,6 @@ build_quantile_df <- function(validation, matched, original, metrics){
   qq_df <- qqs %>% bind_rows() %>% rename(release = x, beta = y)
   return(qq_df)
 }
-
   
 plot.qq <- function(qq.df, response){
   p_qq <- ggplot(qq.df %>% filter(metric == response), aes(x = release, y = beta)) +

### 2020-01-12 perf_release_criteria/milestone_5/dashboard/prepare_dashboard.R

@@ -80,3 +80,7 @@ df <- pred_v_n1 %>%
 #### Step 7 ####
 # Calculate health metrics
 health_metrics <- extract_health_metrics(pred_v_n1, valid_v_n, metrics)
+
+#### Step 8 ####
+# Save image for later loading when dashboard initializes
+save(v_n1, v_n, pred_v_n1, pred_v_n, valid_v_n, beta_v_n, metrics, df, file='data/dashboard_prepped.RData')

### 2020-01-12 perf_release_criteria/milestone_5/dashboard/app.R
Directly referencing `attributes.R` file.

@@ -9,6 +9,7 @@ library(purrr)
 load('data/dashboard_prepped.RData')
 source('plotters.R')
 source('../../lib/prediction.R')
+source('../../lib/attributes.R')
 
 ui <- dashboardPage(
   dashboardHeader(title = "subBeta"),

### 2020-01-16 perf_release_criteria/milestone_5/dashboard/app.R
Now we zoom.

@@ -103,7 +103,10 @@ ui <- dashboardPage(
                            plotOutput(
                              "fxpglms_pred_qq",
                              height = 300,
-                             width = "100%"
+                             width = "100%",
+                             dblclick = "metric_dblclick",
+                             brush = brushOpts(id = "metric_brush",
+                                               resetOnNew = TRUE)
                            )),
                            width = 12
                          )),
@@ -120,7 +123,10 @@ ui <- dashboardPage(
                            plotOutput(
                              "ttdims_pred_qq",
                              height = 300,
-                             width = "100%"
+                             width = "100%",
+                             dblclick = "metric_dblclick",
+                             brush = brushOpts(id = "metric_brush",
+                                               resetOnNew = TRUE)
                            )),
                            width = 12
                          )),
@@ -128,7 +134,7 @@ ui <- dashboardPage(
                            plotOutput(
                              "ttdims_pred_ridges",
                              height = 300,
-                             width = "100%"
+                             width = "100%",
                            )),
                            width = 12
                          ))),
@@ -137,7 +143,10 @@ ui <- dashboardPage(
                            plotOutput(
                              "ttdcms_pred_qq",
                              height = 300,
-                             width = "100%"
+                             width = "100%",
+                             dblclick = "metric_dblclick",
+                             brush = brushOpts(id = "metric_brush",
+                                               resetOnNew = TRUE)
                            )),
                            width = 12
                          )),
@@ -154,7 +163,10 @@ ui <- dashboardPage(
                            plotOutput(
                              "ttleems_pred_qq",
                              height = 300,
-                             width = "100%"
[…]

### 2020-01-16 perf_release_criteria/milestone_5/dashboard/plotters.R

@@ -20,38 +20,42 @@ apply_filters <- function(df, input){
   return(resp.df)
 }
 
-build_quantile_df <- function(validation, matched, original, metrics){
-  qqs <- list()
-  for (perf_metric in metrics){
-    qq <- qqplot(validation[[perf_metric]], matched[[perf_metric]], plot.it = FALSE) %>% 
-      bind_rows() %>%
-      mutate(type = 'matched')
-    qq_full <- qqplot(validation[[perf_metric]], original[[perf_metric]], plot.it = FALSE) %>% 
-      bind_rows() %>%
-      mutate(type = 'original') %>%
-      bind_rows(qq) %>%
-      mutate(metric = perf_metric)
-    # qq_full$metric <- perf_metric
-    qqs[[perf_metric]] <- qq_full
-  }
-  qq_df <- qqs %>% bind_rows() %>% rename(release = x, beta = y)
+calc_qq <- function(validation, matched, original, response){
+  qq <- qqplot(validation[[response]], matched[[response]], plot.it = FALSE) %>% 
+    bind_rows() %>%
+    mutate(type = 'matched')
+  qq_full <- qqplot(validation[[response]], original[[response]], plot.it = FALSE) %>% 
+    bind_rows() %>%
+    mutate(type = 'original') %>%
+    bind_rows(qq) %>%
+    mutate(metric = response)
+  # qq_full$metric <- perf_metric
+  # qq_df <- qqs %>% bind_rows() %>% rename(release = x, beta = y)
+  qq_df <- qq_full %>% rename(release = x, beta = y)
   return(qq_df)
 }
   
-plot.qq <- function(qq.df, response){
+plot.qq <- function(qq.df, response, ranges=NULL){
   p_qq <- ggplot(qq.df %>% filter(metric == response), aes(x = release, y = beta)) +
     geom_point(aes(color = type, shape = type)) + 
     geom_abline(slope = 1, intercept = 0) + 
     theme_bw() + 
     theme(axis.text.x = element_text(angle = 45, hjust = 1),
           plot.title = element_text(size=10),
-          legend.position = c(0.8, 0.2)) + 
+          legend.position = c(0.8, 0.2)) +
+    # scale_x_continuous(limits = ranges$x) + 
+    coord_cartesian(xlim = ranges$x)+
     ggtitle(response) 
   return(p_qq)
   
 }
 
[…]

### 2020-01-17 perf_release_criteria/milestone_5/dashboard/lib/prediction.R
Scaling QQ plot. Commenting out bootstrapping.

@@ -1,6 +1,7 @@
 library(tidyr)
 library(purrr)
 library(lubridate)
+# library(boot)
 source('lib/scoring.R')
 
 extract_health_metrics <- function(predictions, release, outcomes, v_n1){
@@ -42,3 +43,29 @@ extract_health_metrics <- function(predictions, release, outcomes, v_n1){
   
   return(health_metrics)
 }
+
+# bootstrap_mean <- function(predictions, release, metrics){
+#   agg_sets <- function(predictions){
+#     predictions %>% 
+#       select(metrics) %>% 
+#       gather("metric", "value") %>%
+#       group_by(metric) %>%
+#       summarise(
+#         mean = mean(value)
+#       ) %>%
+#       pull(mean)
+#   }
+#   
+#   bs_stat <- function(df, indices) {
+#     df_trim <- df[indices, ]
+#     predictions <- df_trim %>% filter(label == 'beta')
+#     release <- df_trim %>% filter(label == 'release')
+#     pred_agg <- agg_sets(predictions)
+#     # release_agg <- agg_sets(release[indices,])
+#     release_agg <- agg_sets(release)
+#     rel_diff <- (abs(pred_agg-release_agg)/release_agg)
+#     return(rel_diff)
+#   } 
+#   return(boot(data=predictions %>% bind_rows(release), statistic=bs_stat, 
+#               R=100, parallel = "multicore", ncpus = 2))
+# }

### 2020-01-17 perf_release_criteria/milestone_5/dashboard/plotters.R

@@ -43,8 +43,9 @@ plot.qq <- function(qq.df, response, ranges=NULL){
     theme(axis.text.x = element_text(angle = 45, hjust = 1),
           plot.title = element_text(size=10),
           legend.position = c(0.8, 0.2)) +
-    # scale_x_continuous(limits = ranges$x) + 
-    coord_cartesian(xlim = ranges$x)+
+    scale_x_continuous(limits = ranges$x) + 
+    scale_y_continuous(limits = ranges$x) + 
+    # coord_cartesian(xlim = ranges$x)+
     ggtitle(response) 
   return(p_qq)
   

### 2020-01-17 poc/matchIt/modeling.Rmd
initial modeling

---
title: "Beta to Release Matching: Modeling"
author: "Mariana de Oliveira Santos Silva"
date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    theme: "flatly"
    toc: true
    toc_float: true
    code_folding: "hide"
    highlight: tango
---

# Introduction

The goal of this project is to utilize [statistical matching](https://en.wikipedia.org/wiki/Matching_(statistics)) methods to search for a subset of Beta clients that are representative of Release. The specific use-case of this proof-of-concept is utilizing performance, configuration, and environment covariates of the clients for matching. Validation of the matching is performed on a hold-out set of Firefox **user engagement** covariates.

# Loading the data

```{r message=FALSE, warning=FALSE, include=FALSE}
## Loading the needed libraries

library(kableExtra)      # help you build common complex tables and manipulate table styles
library(DataExplorer)    # automated data exploration
library(tidyverse)       # for general data wrangling (includes readr and dplyr)
library(ggplot2)         # to draw statistical plots 
library(ggthemes)
library(funModeling) 
library(corrplot)
library(MatchIt)
library(optmatch)
library(RItools)
library(magrittr)
library(tidyr)
library(tidyselect)
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
## Loading the training dataset

load("~/GitHub/ff-beta-release-matching/poc/EDA/data_milestone2_df_train_validate_20191025.RData")
```

```{r echo=FALSE}
## Examine data briefly

kable(introduce(df_train_f)) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
scroll_box(width = "100%")
```

```{r}
f <- freq(df_train_f$label)

levels(df_train_f$label) <- c(FALSE,TRUE)
df_train_f$label <- as.logical(df_train_f$label)
```

------

## Observations

* 302,819 observations: 59,627 beta ("treated") and 243,192 release ("control")
* Covariants: 
  + Environment
      - cpu_cores
      - cpu_cores_cat
      - cpu_speed_mhz
      - cpu_speed_cat
      - cpu_vendor
      - cpu_l2_cache_kb
      - cpu_l2_cache_kb_cat
      - memory_mb
      - memory_cat
      - os_version
      - is_wow64
      - distro_id_norm
      - install_year
  + Geo
      - country
      - timezone_offset
      - timezone_cat
      - locale
  + Settings
      - num_bookmarks
      - num_addons
      - sync_configured
      - fxa_configured
      - is_default_browser
      - default_search_engine
  + Page Load
      - FX_PAGE_LOAD_MS_2_PARENT
      - TIME_TO_DOM_COMPLETE_MS
      - TIME_TO_DOM_CONTENT_LOADED_END_MS
      - TIME_TO_LOAD_EVENT_END_MS
      - TIME_TO_DOM_INTERACTIVE_MS
      - TIME_TO_NON_BLANK_PAINT_MS
  + Startup
      - startup_ms
      - startup_ms_max
  + Stability
      - content_crashes
  + Browser engagement
      - active_hours
      - active_hours_max
      - uri_count
      - uri_count_max
      - search_count
      - search_count_max
      - num_pages
      - num_pages_max
      - daily_max_tabs
      - daily_max_tabs_max
      - daily_unique_domains
      - daily_unique_domains_max
      - daily_tabs_opened
      - daily_tabs_opened_max
  + Frequency of Browser Usage
      - num_active_days
      - daily_num_sessions_started
      - daily_num_sessions_started_max
      - session_length
      - session_length_max
      - profile_age
      - profile_age_cat

```{r}
df_release <- df_train_f %>% filter(label == TRUE)
df_beta <- df_train_f %>% filter(label == FALSE)
```

```{r}
# sampling for beta overrepresentation
n_beta <- nrow(df_beta)
build_df <- function(multiple){
  df <- df_release %>%
    sample_n(size = round(n_beta / multiple)) %>%
    rbind(df_beta)
}

df_1x <- build_df(1)
df_2x <- build_df(2)
df_4x <- build_df(4)
```

```{r}
# downsampling
df_1x_sm <- df_1x %>% sample_n(size = 70000)
df_2x_sm <- df_2x %>% sample_n(size = 70000)
df_4x_sm <- df_4x %>% sample_n(size = 70000)
```

```{r}
f <- freq(as.factor(df_1x_sm$label)) # ~ 50% - 50%
f <- freq(as.factor(df_2x_sm$label)) # ~ 70% - 30%
f <- freq(as.factor(df_4x_sm$label)) # ~ 80% - 20%
```

# Covariates

```{r}
engagement <- c('active_hours','active_hours_max','uri_count','uri_count_max','search_count','search_count_max','num_pages','num_pages_max','daily_max_tabs','daily_max_tabs_max','daily_unique_domains','daily_unique_domains_max','daily_tabs_opened','daily_tabs_opened_max')

usage <- c('num_active_days','daily_num_sessions_started','daily_num_sessions_started_max','session_length','session_length_max','profile_age')

environment <- c('cpu_cores','cpu_speed_mhz','cpu_l2_cache_kb','memory_mb','timezone_offset','num_bookmarks','num_addons')

page_load <- c('FX_PAGE_LOAD_MS_2_PARENT','TIME_TO_DOM_COMPLETE_MS','TIME_TO_DOM_CONTENT_LOADED_END_MS','TIME_TO_LOAD_EVENT_END_MS','TIME_TO_DOM_INTERACTIVE_MS','TIME_TO_NON_BLANK_PAINT_MS')

startup <- c('startup_ms','startup_ms_max')

stability <- c('content_crashes')
```

# Modeling

Before propensity scores are calculated, it is a good practice to determine if the two groups are balanced.

## 1. Standardized difference

The standardized difference can be used to compare the mean of continuous and binary variables between treatment groups. The standardized difference compares the difference in means in units of the pooled standard deviation and allows for the comparison of the relative balance of variables measured in different units. Although there is no universally agreed-upon criterion as to what threshold of the standardized difference can be used to indicate an important imbalance, a standard difference that is less than $0.1$ has been taken to indicate a negligible difference in the mean or prevalence of a covariate between treatment groups.

### 1x Oversampling
```{r}
cov <- df_1x_sm %>% select(c(engagement, usage, environment, page_load, startup, stability))
treated <- (df_1x_sm$label==FALSE)
std.diff <- apply(cov,2,function(x) 100*(mean(x[treated])- mean(x[!treated]))/(sqrt(0.5*(var(x[treated]) + var(x[!treated])))))
sort(abs(std.diff))
```

### 2x Oversampling
```{r}
cov <- df_2x_sm %>% select(c(engagement, usage, environment, page_load, startup, stability))
treated <- (df_2x_sm$label==FALSE)
std.diff <- apply(cov,2,function(x) 100*(mean(x[treated])- mean(x[!treated]))/(sqrt(0.5*(var(x[treated]) + var(x[!treated])))))
sort(abs(std.diff))
```

### 4x Oversampling
```{r}
cov <- df_4x_sm %>% select(c(engagement, usage, environment, page_load, startup, stability))
treated <- (df_4x_sm$label==FALSE)
std.diff <- apply(cov,2,function(x) 100*(mean(x[treated])- mean(x[!treated]))/(sqrt(0.5*(var(x[treated]) + var(x[!treated])))))
sort(abs(std.diff))
```

------

### Observations

* As we can see, all standardized differences at the individual variable level were greater than *0.1*. These significant imbalances highlight the need for an effective matching strategy to create a release group that more closely resembles the beta group.
* For the standardized difference, absolute scores higher than *25%* are considered suspect, and may indicate an imbalance for that specific variable.
  + That is, `TIME_TO_DOM_INTERACTIVE_MS`, `TIME_TO_DOM_COMPLETE_MS`, `TIME_TO_LOAD_EVENT_END_MS`, `timezone_offset`, `num_addons` and `session_length` (only for the 2x Oversampling).

## 2. Check initial balance

The package [RItools](https://cran.r-project.org/web/packages/RItools/index.html) includes the routine `XBalance` that estimates a chi-square test to which checks if there is at least one variable in the selection model for which the two groups are different.

* *How similar are treatment/control groups on X?*

### 1x Oversampling
```{r}
xBalance(label ~ (active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes), data=df_1x_sm, report=c("chisquare.test"))
```

### 2x Oversampling
```{r}
xBalance(label ~ (active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes), data=df_2x_sm, report=c("chisquare.test"))
```

### 4x Oversampling
```{r}
xBalance(label ~ (active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes), data=df_4x_sm, report=c("chisquare.test"))
```

------

### Observations

* A statistically significant chi-square will indicate that at least one of the variables included in the model is creating an imbalance between the two groups. Variables that create imbalance should be included in the selection model.

## 3. Propensity Score Estimation

Packages such as MatchIt estimates propensity scores using logistic regression as the default option. However, when estimating propensity scores using the default option, the fit of the model cannot be assessed. Therefore, it is recommended that a logistic regression is run to determine the model fit.

### Calculates the propensity score

#### 1x Oversampling

```{r}
ps <- glm(label ~ active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes, data=df_1x_sm, family=binomial())
summary(ps)
```

Statistically significant estimates are identified by low (i.e., $< 0.05$) p-values. There are no clear suggestions as to whether to include in the final model all the variables (even non-significant). Some authors suggest that the final model should include not only statistically significant variables, but also variables known to be associated with selection.

Once the propensity scores have been calculated, a graphical approach can be used to assess the distributional similarity between score distributions. This graphical approach uses back to back histograms such as those created through the package Hmisc. Back to back histograms cannot be used with Mahalanobis distance, because it is a multidimensional technique.

* Attach the predicted propensity score to the datafile

```{r}
df_1x_sm$psvalue <- predict(ps, type="response")
```

## Back to back histogram

```{r fig.height=5, fig.width=10}
out <- histbackback(split(df_1x_sm$psvalue, df_1x_sm$label), main="Propensity score before matching", xlab=c("release", "beta"))
#! just adding color
barplot(-out$left, col="#111d5e" , horiz=TRUE, space=0, add=TRUE, axes=FALSE)
barplot(out$right, col="#b21f66", horiz=TRUE, space=0, add=TRUE, axes=FALSE)
```

#### 2x Oversampling

```{r}
ps <- glm(label ~ active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes, data=df_2x_sm, family=binomial())
summary(ps)
```

* Attach the predicted propensity score to the datafile

```{r}
df_2x_sm$psvalue <- predict(ps, type="response")
```

## Back to back histogram

```{r fig.height=5, fig.width=10}
out <- histbackback(split(df_2x_sm$psvalue, df_2x_sm$label), main="Propensity score before matching", xlab=c("release", "beta"))
#! just adding color
barplot(-out$left, col="#111d5e" , horiz=TRUE, space=0, add=TRUE, axes=FALSE)
barplot(out$right, col="#b21f66", horiz=TRUE, space=0, add=TRUE, axes=FALSE)
```

#### 4x Oversampling

```{r}
ps <- glm(label ~ active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes, data=df_4x_sm, family=binomial())
summary(ps)
```

* Attach the predicted propensity score to the datafile

```{r}
df_4x_sm$psvalue <- predict(ps, type="response")
```

## Back to back histogram

```{r fig.height=5, fig.width=10}
out <- histbackback(split(df_4x_sm$psvalue, df_4x_sm$label), main="Propensity score before matching", xlab=c("release", "beta"))
#! just adding color
barplot(-out$left, col="#111d5e" , horiz=TRUE, space=0, add=TRUE, axes=FALSE)
barplot(out$right, col="#b21f66", horiz=TRUE, space=0, add=TRUE, axes=FALSE)
```

------

#### Observations

* Important parameters to determine the fit are not only the shape, but also degree of overlap between the two distributions (known as the common support region). By definition, matching only utilizes observations in the region of common support where we are able to obtain matched observations.  That is, unmatched observations are excluded from the analysis. 
* As can be seen from the figures above, an interval of propensity scores exists, containing both release and beta groups, so that further matching analysis is valid.

## 4. Propensity Score Matching

### Match using Coarsened Exact Matching (CEM)

#### 1x Oversampling

```{r}
m.cem <- matchit(label ~ active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes, data=df_1x_sm, method="cem")
summary(m.cem)
m.cem.1 = match.data(m.cem)
```

```{r fig.height=5, fig.width=10}
plot(m.cem, type = "jitter", col = "#111d5e")
```

```{r fig.height=5, fig.width=10}
plot(m.cem, type = "hist", col = "#111d5e")
```

#### 2x Oversampling

```{r}
m.cem <- matchit(label ~ active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes, data=df_2x_sm, method="cem")
summary(m.cem)
m.cem.2 = match.data(m.cem)
```

```{r fig.height=5, fig.width=10}
plot(m.cem, type = "jitter", col = "#111d5e")
```

```{r fig.height=5, fig.width=10}
plot(m.cem, type = "hist", col = "#111d5e")
```

#### 4x Oversampling

```{r}
m.cem <- matchit(label ~ active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes, data=df_4x_sm, method="cem")
summary(m.cem)
m.cem.4 = match.data(m.cem)
```

```{r fig.height=5, fig.width=10}
plot(m.cem, type = "jitter", col = "#111d5e")
```

```{r fig.height=5, fig.width=10}
plot(m.cem, type = "hist", col = "#111d5e")
```

### Match using Nearest Neighbor matching

#### 1x Oversampling

```{r}
m.nn <- matchit(label ~ active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes, data=df_1x_sm, method="nearest", replace = TRUE)
summary(m.nn)
m.nn.1 = match.data(m.nn)
```

```{r fig.height=5, fig.width=10}
plot(m.nn, type = "jitter", col = "#111d5e")
```

```{r fig.height=5, fig.width=10}
plot(m.nn, type = "hist", col = "#111d5e")
```

#### 2x Oversampling

```{r}
m.nn <- matchit(label ~ active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes, data=df_2x_sm, method="nearest", replace = TRUE)
summary(m.nn)
m.nn.2 = match.data(m.nn)
```

```{r fig.height=5, fig.width=10}
plot(m.nn, type = "jitter", col = "#111d5e")
```

```{r fig.height=5, fig.width=10}
plot(m.nn, type = "hist", col = "#111d5e")
```

#### 4x Oversampling

```{r}
m.nn <- matchit(label ~ active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes, data=df_4x_sm, method="nearest", replace = TRUE)
summary(m.nn)
m.nn.4 = match.data(m.nn)
```

```{r fig.height=5, fig.width=10}
plot(m.nn, type = "jitter", col = "#111d5e")
```

```{r fig.height=5, fig.width=10}
plot(m.nn, type = "hist", col = "#111d5e")
```

---

### Observations

* What we want to see is that the Matched Treated (beta) and Matched Control (release) distributions are roughly similar. So, we can do better.

## 5. Computing indices of covariate imbalance after matching

### 1x Oversampling

#### CEM

```{r}
### 1. Standardized difference
cov1 <- m.cem.1 %>% select(c(engagement, usage, environment, page_load, startup, stability))
treated1 <- (m.cem.1$label==FALSE)
std.diff1 <- apply(cov1,2,function(x) 100*(mean(x[treated1])- mean(x[!treated1]))/(sqrt(0.5*(var(x[treated1]) + var(x[!treated1])))))
sort(abs(std.diff1))
```

```{r}
### 2. chi-square test
xBalance(label ~ (active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes), data=m.cem.1, report=c("chisquare.test"))
```

```{r fig.height=5, fig.width=10}
out <- histbackback(split(m.cem.1$psvalue, m.cem.1$label), main= "Propensity score after matching (CEM)", xlab=c("release", "beta"))
barplot(-out$left, col="#111d5e" , horiz=TRUE, space=0, add=TRUE, axes=FALSE)
barplot(out$right, col="#b21f66", horiz=TRUE, space=0, add=TRUE, axes=FALSE)
```

#### NN

```{r}
### 1. Standardized difference
cov1 <- m.nn.1 %>% select(c(engagement, usage, environment, page_load, startup, stability))
treated1 <- (m.nn.1$label==FALSE)
std.diff1 <- apply(cov1,2,function(x) 100*(mean(x[treated1])- mean(x[!treated1]))/(sqrt(0.5*(var(x[treated1]) + var(x[!treated1])))))
sort(abs(std.diff1))
```

```{r}
### 2. chi-square test
xBalance(label ~ (active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes), data=m.nn.1, report=c("chisquare.test"))
```

```{r fig.height=5, fig.width=10}
out <- histbackback(split(m.nn.1$psvalue, m.nn.1$label), main= "Propensity score after matching (NN)", xlab=c("release", "beta"))
barplot(-out$left, col="#111d5e" , horiz=TRUE, space=0, add=TRUE, axes=FALSE)
barplot(out$right, col="#b21f66", horiz=TRUE, space=0, add=TRUE, axes=FALSE)
```

### 2x Oversampling

#### CEM

```{r}
### 1. Standardized difference
cov1 <- m.cem.2 %>% select(c(engagement, usage, environment, page_load, startup, stability))
treated1 <- (m.cem.2$label==FALSE)
std.diff1 <- apply(cov1,2,function(x) 100*(mean(x[treated1])- mean(x[!treated1]))/(sqrt(0.5*(var(x[treated1]) + var(x[!treated1])))))
sort(abs(std.diff1))
```

```{r}
### 2. chi-square test
xBalance(label ~ (active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes), data=m.cem.2, report=c("chisquare.test"))
```

```{r fig.height=5, fig.width=10}
out <- histbackback(split(m.cem.2$psvalue, m.cem.2$label), main= "Propensity score after matching (CEM)", xlab=c("release", "beta"))
barplot(-out$left, col="#111d5e" , horiz=TRUE, space=0, add=TRUE, axes=FALSE)
barplot(out$right, col="#b21f66", horiz=TRUE, space=0, add=TRUE, axes=FALSE)
```

#### NN

```{r}
### 1. Standardized difference
cov1 <- m.nn.2 %>% select(c(engagement, usage, environment, page_load, startup, stability))
treated1 <- (m.nn.2$label==FALSE)
std.diff1 <- apply(cov1,2,function(x) 100*(mean(x[treated1])- mean(x[!treated1]))/(sqrt(0.5*(var(x[treated1]) + var(x[!treated1])))))
sort(abs(std.diff1))
```

```{r}
### 2. chi-square test
xBalance(label ~ (active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes), data=m.nn.2, report=c("chisquare.test"))
```

```{r fig.height=5, fig.width=10}
out <- histbackback(split(m.nn.2$psvalue, m.nn.2$label), main= "Propensity score after matching (NN)", xlab=c("release", "beta"))
barplot(-out$left, col="#111d5e" , horiz=TRUE, space=0, add=TRUE, axes=FALSE)
barplot(out$right, col="#b21f66", horiz=TRUE, space=0, add=TRUE, axes=FALSE)
```

### 4x Oversampling

#### CEM

```{r}
### 1. Standardized difference
cov1 <- m.cem.4 %>% select(c(engagement, usage, environment, page_load, startup, stability))
treated1 <- (m.cem.4$label==FALSE)
std.diff1 <- apply(cov1,2,function(x) 100*(mean(x[treated1])- mean(x[!treated1]))/(sqrt(0.5*(var(x[treated1]) + var(x[!treated1])))))
sort(abs(std.diff1))
```

```{r}
### 2. chi-square test
xBalance(label ~ (active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes), data=m.cem.4, report=c("chisquare.test"))
```

```{r fig.height=5, fig.width=10}
out <- histbackback(split(m.cem.4$psvalue, m.cem.4$label), main= "Propensity score after matching (CEM)", xlab=c("release", "beta"))
barplot(-out$left, col="#111d5e" , horiz=TRUE, space=0, add=TRUE, axes=FALSE)
barplot(out$right, col="#b21f66", horiz=TRUE, space=0, add=TRUE, axes=FALSE)
```

#### NN

```{r}
### 1. Standardized difference
cov1 <- m.nn.4 %>% select(c(engagement, usage, environment, page_load, startup, stability))
treated1 <- (m.nn.4$label==FALSE)
std.diff1 <- apply(cov1,2,function(x) 100*(mean(x[treated1])- mean(x[!treated1]))/(sqrt(0.5*(var(x[treated1]) + var(x[!treated1])))))
sort(abs(std.diff1))
```

```{r}
### 2. chi-square test
xBalance(label ~ (active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes), data=m.nn.4, report=c("chisquare.test"))
```

```{r fig.height=5, fig.width=10}
out <- histbackback(split(m.nn.4$psvalue, m.nn.4$label), main= "Propensity score after matching (NN)", xlab=c("release", "beta"))
barplot(-out$left, col="#111d5e" , horiz=TRUE, space=0, add=TRUE, axes=FALSE)
barplot(out$right, col="#b21f66", horiz=TRUE, space=0, add=TRUE, axes=FALSE)
```

### 2020-02-17 poc/matchIt/feature_engineering.Rmd
adding feature engineering and selection

---
title: "Feature Engineering"
author: "Mariana de Oliveira Santos Silva"
date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    theme: "flatly"
    toc: true
    toc_float: true
    code_folding: "hide"
    highlight: tango
---

# tl;dr

Often combining variables to generate a new variable, a process known as *feature engineering*, can make a model infinitely better. In this notebook we will try to engineer some features in case some of them turn out to be determinant factors when imputing other variables.

```{r imports, echo=FALSE, warning=FALSE, message=FALSE}
library(kableExtra)      # help you build common complex tables and manipulate table styles
library(DataExplorer)    # automated data exploration
library(tidyverse)       # for general data wrangling (includes readr and dplyr)
library(ggplot2)         # to draw statistical plots 
library(ggthemes)
library(tidyr)
library(tidyselect)
library(caret)           # includes several functions to pre-process
library(scales)          # to determining breaks and labels for axes and legends
library(vtreat)          # to variable preparation for ML
library(semTools)        # useful tools for structural equation modeling
library(onehot)
library(mltools)
library(data.table)
load("~/GitHub/ff-beta-release-matching/poc/EDA/data_milestone2_df_train_validate_20191025.RData")
```

```{r echo=FALSE}
## Examine data briefly
glimpse(df_train_f)
```

```{r, fig.height=15, fig.width=15, message=FALSE, warning=FALSE}
## Frequency distribution release dataframe
plot_bar(df_train_f, ggtheme = theme_minimal(base_size = 15), title = 'Categorical Variables')
```

# Converting Categorical Features

* Most values of `default_search_engine` are equal to **Google**. That is, for better modeling, we could just create a variable that represents *Google* and set the remainder to *Other*. 
* The same can be done for `distro_id_norm`. We could just create a variable that represents *Mozilla* and set the remainder to *Other*.

```{r}
# Training
df_train_f$google_default <- (df_train_f$default_search_engine == 'Google') * 1
df_train_f$mozilla_distro <- (df_train_f$distro_id_norm == 'Mozilla') * 1

# Validation
df_validate_f$google_default <- (df_validate_f$default_search_engine == 'Google') * 1
df_validate_f$mozilla_distro <- (df_validate_f$distro_id_norm == 'Mozilla') * 1
```

```{r}
plot_bar(df_train_f$google_default, ggtheme = theme_minimal(base_size = 15), title = 'Google default seach engine')
plot_bar(df_train_f$mozilla_distro, ggtheme = theme_minimal(base_size = 15), title = 'Mozilla distro id norm')
```

* In addition, we could map numerical values to the categorical variables.

```{r message=FALSE, warning=FALSE}
require(plyr) # to use mapvalues function

# Training
df_train_f$new_os_version <- mapvalues(df_train_f$os_version,
          from=c('Other', '10.0', '6.1', '6.3', '6.2'), 
          to=c(0,1,2,3,4))
df_train_f$new_os_version <- as.numeric(as.character(df_train_f$new_os_version))

df_train_f$new_cpu_vendor <- mapvalues(df_train_f$cpu_vendor,
          from=c('Other', 'Intel', 'AMD'), 
          to=c(0,1,2))
df_train_f$new_cpu_vendor <- as.numeric(as.character(df_train_f$new_cpu_vendor))

# Validation
df_validate_f$new_os_version <- mapvalues(df_validate_f$os_version,
          from=c('Other', '10.0', '6.1', '6.3', '6.2'), 
          to=c(0,1,2,3,4))
df_validate_f$new_os_version <- as.numeric(as.character(df_validate_f$new_os_version))

df_validate_f$new_cpu_vendor <- mapvalues(df_validate_f$cpu_vendor,
          from=c('Other', 'Intel', 'AMD'), 
          to=c(0,1,2))
df_validate_f$new_cpu_vendor <- as.numeric(as.character(df_validate_f$new_cpu_vendor))
```

```{r}
plot_histogram(df_train_f$new_os_version, ggtheme = theme_minimal(base_size = 15), title = 'OS Version')
plot_histogram(df_train_f$new_cpu_vendor, ggtheme = theme_minimal(base_size = 15), title = 'CPU Vendor')
```

# One Hot Encoding

To convert all the nominal or factor variables to numeric, we need to create a dummy variable for each category of the categorical variables. Only one dummy variable is coded with a one for each set of categories.

## Training
```{r}
df_train_encoder <- one_hot(as.data.table(df_train_f))
```

```{r}
numericVarNames <- which(sapply(df_train_encoder, is.numeric))
df_num <- df_train_encoder %>% select(numericVarNames)
df_cat <- df_train_encoder  %>% select(-numericVarNames)

cat('There are', length(df_num), 'numeric variables, and', length(df_cat), 'factor variables')
```

## Validation
```{r}
df_validate_encoder <- one_hot(as.data.table(df_validate_f))
```

```{r}
numericVarNames <- which(sapply(df_validate_encoder, is.numeric))
df_num <- df_validate_encoder %>% select(numericVarNames)
df_cat <- df_validate_encoder  %>% select(-numericVarNames)

cat('There are', length(df_num), 'numeric variables, and', length(df_cat), 'factor variables')
```

# Saving

```{r}
save.image(file = "feature_engineering.RData")
```

### 2020-02-17 poc/matchIt/feature_selection.Rmd
adding feature engineering and selection

---
title: "Feature Selection - Boruta"
author: "Mariana de Oliveira Santos Silva"
date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    theme: "flatly"
    toc: true
    toc_float: true
    code_folding: "hide"
    highlight: tango
---

```{r libraries, message=FALSE, warning=FALSE, include=FALSE}
## Loading the needed libraries

library(kableExtra)      # help you build common complex tables and manipulate table styles
library(DataExplorer)    # automated data exploration
library(tidyverse)       # for general data wrangling (includes readr and dplyr)
library(ggplot2)         # to draw statistical plots 
library(Boruta)          # to use relevant feature selection wrapper algorithm
library(ggthemes)
library(funModeling) 
library(corrplot)
library(MatchIt)
library(optmatch)
library(RItools)
library(magrittr)
library(tidyr)
library(tidyselect)
```

```{r data_load, echo=FALSE}
load("~/GitHub/ff-beta-release-matching/poc/matchIt/feature_engineering.RData")
```

# tl;dr

This analysis is focused on utilizing `Boruta` as a initial pre-filter to the covariates, to narrow the feature selection search space.

# Method

Apply `Boruta` to each performance covariate.

```{r var_def}
engagement <- c('active_hours','active_hours_max','uri_count','uri_count_max','search_count','search_count_max','num_pages','num_pages_max','daily_max_tabs','daily_max_tabs_max','daily_unique_domains','daily_unique_domains_max','daily_tabs_opened','daily_tabs_opened_max')

set.seed(1234)
df_train_sm <- df_train_encoder %>%
   sample_n(1000)

df_fs <- df_train_sm %>%
   select(-engagement) %>%
   select(-content_crashes) %>%
   select(-client_id) %>%
   select(-label_beta) %>%
   select(-label_release) %>%
   select(-is_release) %>%
   select(-app_version)
```

Boruta is a feature selection algorithm based on the random forest algorithm. In the process of deciding if a feature is important or not, some features may be marked as *Tentative*. Sometimes increasing the `maxRuns` can help resolve the *Tentativeness* of the feature.

```{r apply_boruta}
boruta_results <- list()
for (metric in engagement){
  print(paste('Applying Boruta to ', metric))
  boruta.out <- Boruta(y = df_train_sm[[metric]], x=df_fs, doTrace=0)
  boruta_results[[metric]]  <- boruta.out
  # plot(boruta.out, cex.axis=.7, las=2, xlab="", main=metric) 
}
```

```{r boruta_plots}
for (metric in names(boruta_results)){
  plot(boruta_results[[metric]], cex.axis=.7, las=2, xlab="", main=metric) 
}
```

Find the top 5 ranking features per metric, and add to a list.

```{r aggregate_features_5}
features_top5 <- NULL
for(metric in names(boruta_results)){
  features_top5 <- c(names(sort(apply(boruta_results[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:5]), features_top5)
}
knitr::kable(data.frame(top5 = sort(c(unique(features_top5)))))
```

Increasing to 10:

```{r aggregate_features_10}
features_top10 <- NULL
for(metric in names(boruta_results)){
  features_top10 <- c(names(sort(apply(boruta_results[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:10]), features_top10)
}
knitr::kable(data.frame(top10 = sort(c(unique(features_top10)))))
```

## Equal Labels

Equalize by label, then perform the above.

```{r var_def_equal}
df_beta <- df_train_encoder %>% 
  filter(label_beta == 1)
n_beta <- nrow(df_beta)
set.seed(1234)
df_rel <- df_train_encoder %>% 
  filter(label_beta == 0) %>%
  sample_n(n_beta)
set.seed(1234)
df_train_f_sm_eq <- df_rel %>%
  bind_rows(df_beta) %>%
   sample_n(1000)
df_fs_eq <- df_train_f_sm_eq %>%
   select(-engagement) %>%
   select(-content_crashes) %>%
   select(-client_id) %>%
   select(-label_beta) %>%
   select(-label_release) %>%
   select(-is_release) %>%
   select(-app_version)
```

```{r apply_boruta_equal}
boruta_results_eq <- list()
for (metric in engagement){
  print(paste('Applying Boruta to ', metric))
  boruta.out <- Boruta(y = df_train_f_sm_eq[[metric]], x=df_fs_eq, doTrace=0)
  boruta_results_eq[[metric]]  <- boruta.out
  # plot(boruta.out, cex.axis=.7, las=2, xlab="", main=metric) 
}
```

```{r boruta_plots_eq}
for (metric in names(boruta_results_eq)){
  plot(boruta_results_eq[[metric]], cex.axis=.7, las=2, xlab="", main=metric) 
}
```

```{r aggregate_features_5_eq}
features_top5 <- NULL
for(metric in names(boruta_results_eq)){
  features_top5 <- c(names(sort(apply(boruta_results_eq[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:5]), features_top5)
}
knitr::kable(data.frame(top5 = sort(c(unique(features_top5)))))
```

Increasing to 10:

```{r aggregate_features_10_eq}
features_top10 <- NULL
for(metric in names(boruta_results_eq)){
  features_top10 <- c(names(sort(apply(boruta_results_eq[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:10]), features_top10)
}
knitr::kable(data.frame(top10 = sort(c(unique(features_top10)))))
```

# Saving

```{r}
save.image(file = "feature_selection.RData")
```

### 2020-02-20 poc/matchIt/feature_selection.Rmd
udating feature selection

@@
 
+```{r}
+filter_features <- function(df_train_sm){
+  df_fs <- df_train_sm %>%
+   select(-engagement) %>%
+   select(-content_crashes) %>%
+   select(-client_id) %>%
+   select(-label_beta) %>%
+   select(-label_release) %>%
+   select(-is_release) %>%
+   select(-app_version)
+  return(df_fs)
+}
+```
+
 # tl;dr
@@
 
-set.seed(1234)
-df_train_sm <- df_train_encoder %>%
+df_train_sm_1 <- df_train_encoder %>%
    sample_n(1000)
+df_train_sm_2 <- df_train_encoder %>%
+   sample_n(1000)
+df_train_sm_3 <- df_train_encoder %>%
+   sample_n(1000)
+#df_train_sm_4 <- df_train_encoder %>% sample_n(1000)
+#df_train_sm_5 <- df_train_encoder %>% sample_n(1000)
 
-df_fs <- df_train_sm %>%
-   select(-engagement) %>%
-   select(-content_crashes) %>%
-   select(-client_id) %>%
-   select(-label_beta) %>%
-   select(-label_release) %>%
-   select(-is_release) %>%
-   select(-app_version)
+df_fs_1 <- filter_features(df_train_sm_1)
+df_fs_2 <- filter_features(df_train_sm_2)
+df_fs_3 <- filter_features(df_train_sm_3)
+#df_fs_4 <- filter_features(df_train_sm_4)
+#df_fs_5 <- filter_features(df_train_sm_5)
+
 ```
@@
 ```{r apply_boruta}
-boruta_results <- list()
+boruta_results_1 <- list()
+boruta_results_2 <- list()
+boruta_results_3 <- list()
+#boruta_results_4 <- list()
+#boruta_results_5 <- list()
+
 for (metric in engagement){
   print(paste('Applying Boruta to ', metric))
-  boruta.out <- Boruta(y = df_train_sm[[metric]], x=df_fs, doTrace=0)
-  boruta_results[[metric]]  <- boruta.out
-  # plot(boruta.out, cex.axis=.7, las=2, xlab="", main=metric) 
+  boruta.out <- Boruta(y = df_train_sm_1[[metric]], x=df_fs_1, doTrace=0)
+  boruta_results_1[[metric]]  <- boruta.out
+
+  boruta.out <- Boruta(y = df_train_sm_2[[metric]], x=df_fs_2, doTrace=0)
+  boruta_results_2[[metric]]  <- boruta.out
+
+  boruta.out <- Boruta(y = df_train_sm_3[[metric]], x=df_fs_3, doTrace=0)
+  boruta_results_3[[metric]]  <- boruta.out
+  #boruta.out <- Boruta(y = df_train_sm_4[[metric]], x=df_fs_4, doTrace=0)
+  #boruta_results_4[[metric]]  <- boruta.out
+  #boruta.out <- Boruta(y = df_train_sm_5[[metric]], x=df_fs_5, doTrace=0)
+  #boruta_results_5[[metric]]  <- boruta.out
 }
@@
 
-```{r boruta_plots}
-for (metric in names(boruta_results)){
-  plot(boruta_results[[metric]], cex.axis=.7, las=2, xlab="", main=metric) 
+```{r boruta_plots, fig.height=7, fig.width=15}
+for (metric in engagement){
+  plot(boruta_results_1[[metric]], cex.axis=.7, las=2, xlab="", main=metric)
+  plot(boruta_results_2[[metric]], cex.axis=.7, las=2, xlab="", main=metric)
+  plot(boruta_results_3[[metric]], cex.axis=.7, las=2, xlab="", main=metric)
 }
@@
 ```{r aggregate_features_5}
-features_top5 <- NULL
-for(metric in names(boruta_results)){
-  features_top5 <- c(names(sort(apply(boruta_results[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:5]), features_top5)
+features_top5_1 <- NULL
+features_top5_2 <- NULL
+features_top5_3 <- NULL
+
+for(metric in engagement){
+  features_top5_1 <- c(names(sort(apply(boruta_results_1[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:5]), features_top5_1)
+  features_top5_2 <- c(names(sort(apply(boruta_results_2[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:5]), features_top5_2)
+  features_top5_3 <- c(names(sort(apply(boruta_results_3[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:5]), features_top5_3)
 }
-knitr::kable(data.frame(top5 = sort(c(unique(features_top5)))))
+
+top5_1 <- sort(c(unique(features_top5_1)))
+top5_2 <- sort(c(unique(features_top5_2)))
+top5_3 <- sort(c(unique(features_top5_3)))
+
+n <- max(length(top5_1), length(top5_2), length(top5_3))
+length(top5_1) <- n 
+length(top5_2) <- n 
+length(top5_3) <- n
+
+x <- data.frame(top5_1, top5_2, top5_3)
+kable(x) %>%
+kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
+scroll_box(width = "100%")
 ```
@@
 ```{r aggregate_features_10}
-features_top10 <- NULL
-for(metric in names(boruta_results)){
-  features_top10 <- c(names(sort(apply(boruta_results[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:10]), features_top10)
+features_top10_1 <- NULL
+features_top10_2 <- NULL
+features_top10_3 <- NULL
+
+for(metric in engagement){
+  features_top10_1 <- c(names(sort(apply(boruta_results_1[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:10]), features_top10_1)
+  features_top10_2 <- c(names(sort(apply(boruta_results_2[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:10]), features_top10_2)
+  features_top10_3 <- c(names(sort(apply(boruta_results_3[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:10]), features_top10_3)
 }
-knitr::kable(data.frame(top10 = sort(c(unique(features_top10)))))
+
+top10_1 <- sort(c(unique(features_top10_1)))
+top10_2 <- sort(c(unique(features_top10_2)))
+top10_3 <- sort(c(unique(features_top10_3)))
+
+n <- max(length(top10_1), length(top10_2), length(top10_3))
+length(top10_1) <- n 
+length(top10_2) <- n 
+length(top10_3) <- n
+
+x <- data.frame(top10_1, top10_2, top10_3)
+kable(x) %>%
+kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
+scroll_box(width = "100%")
 ```
@@
 
+As we can see, using different samples hardly changes the result. Therefore, we can use only one df with 1000 samples.
 Equalize by label, then perform the above.
@@
 }
-knitr::kable(data.frame(top5 = sort(c(unique(features_top5)))))
+
+x <- data.frame(top5 = sort(c(unique(features_top5))))
+kable(x) %>%
+kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
+scroll_box(width = "100%")
 ```
@@
 }
-knitr::kable(data.frame(top10 = sort(c(unique(features_top10)))))
+
+x <- data.frame(top10 = sort(c(unique(features_top10))))
+kable(x) %>%
+kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
+scroll_box(width = "100%")
 ```

### 2020-03-10 poc/matchIt/modeling.Rmd
update the modeling

@@
 library(ggplot2)         # to draw statistical plots 
+library(dplyr)           # for data frame manipulation
 library(ggthemes)
@@
 library(optmatch)
+library(cem)
 library(RItools)
@@
 library(tidyselect)
+library(grt)
+library(tableone)
 ```
@@
 ## Loading the training dataset
+#load("~/GitHub/ff-beta-release-matching/poc/EDA/data_milestone2_df_train_validate_20191025.RData")
+load('~/ff-beta-release-matching/poc/matchIt/feature_selection.RData')
+```
 
-load("~/GitHub/ff-beta-release-matching/poc/EDA/data_milestone2_df_train_validate_20191025.RData")
+```{r include=FALSE}
+colnames(df_train_encoder)[which(names(df_train_encoder) == "cpu_l2_cache_kb_cat_< 1024")] <- "cpu_l2_cache_kb_cat_l1024"
+colnames(df_train_encoder)[which(names(df_train_encoder) == "cpu_l2_cache_kb_cat_< 256")] <- "cpu_l2_cache_kb_cat_l256"
+colnames(df_train_encoder)[which(names(df_train_encoder) == "cpu_l2_cache_kb_cat_< 512")] <- "cpu_l2_cache_kb_cat_l512"
+colnames(df_train_encoder)[which(names(df_train_encoder) == "cpu_l2_cache_kb_cat_> 1024")] <- "cpu_l2_cache_kb_cat_g1024"
+
+colnames(df_train_encoder)[which(names(df_train_encoder) == "default_search_engine_other (bundled)")] <- "default_search_engine_other_bundled"
+colnames(df_train_encoder)[which(names(df_train_encoder) == "default_search_engine_other (non-bundled)")] <- "default_search_engine_other_nonbundled"
+
+colnames(df_train_encoder)[which(names(df_train_encoder) == "locale_en-GB")] <- "locale_enGB"
+colnames(df_train_encoder)[which(names(df_train_encoder) == "locale_en-US")] <- "locale_enUS"
+
+colnames(df_train_encoder)[which(names(df_train_encoder) == "timezone_cat_[-12,-10]")] <- "timezone_cat_m12_m10"
+colnames(df_train_encoder)[which(names(df_train_encoder) == "timezone_cat_(-10,-8]")] <- "timezone_cat_m10_m8"
+colnames(df_train_encoder)[which(names(df_train_encoder) == "timezone_cat_(-8,-6]")] <- "timezone_cat_m8_m6"
+colnames(df_train_encoder)[which(names(df_train_encoder) == "timezone_cat_(-6,-4]")] <- "timezone_cat_m6_m4"
+colnames(df_train_encoder)[which(names(df_train_encoder) == "timezone_cat_(-4,-2]")] <- "timezone_cat_m4_m2"
+colnames(df_train_encoder)[which(names(df_train_encoder) == "timezone_cat_(-2,0]")] <- "timezone_cat_m2_0"
+colnames(df_train_encoder)[which(names(df_train_encoder) == "timezone_cat_(0,2]")] <- "timezone_cat_0_2"
+colnames(df_train_encoder)[which(names(df_train_encoder) == "timezone_cat_(2,4]")] <- "timezone_cat_2_4"
+colnames(df_train_encoder)[which(names(df_train_encoder) == "timezone_cat_(4,6]")] <- "timezone_cat_4_6"
+colnames(df_train_encoder)[which(names(df_train_encoder) == "timezone_cat_(6,8]")] <- "timezone_cat_6_8"
+colnames(df_train_encoder)[which(names(df_train_encoder) == "timezone_cat_(8,10]")] <- "timezone_cat_8_10"
+colnames(df_train_encoder)[which(names(df_train_encoder) == "timezone_cat_(10,12]")] <- "timezone_cat_10_12"
+colnames(df_train_encoder)[which(names(df_train_encoder) == "timezone_cat_(12,14]")] <- "timezone_cat_12_14"
+```
+
+```{r include=FALSE}
+generate_formula <- function(tr_cov, label){
+  # Focus on linear and no-interactions
+  return(as.formula(paste(label, '~', paste(tr_cov, collapse="+"))))
+}
+
+calc_means <- function(df.match, ho_cov, add_1 = FALSE){
+  # Validation
+  ## Means: holdout
+  ho_mean <- df.match %>% 
+    select(ho_cov, label) %>% 
+    mutate_all(function(x) if(is.numeric(x) && add_1) x+1 else x) %>%
+    group_by(label) %>% 
+    summarise_all(mean)
+  return(ho_mean)
+}
+
+calc_medians <- function(df.match, ho_cov, add_1 = FALSE){
+  # Validation
+  ## medians: holdout
+  ho_median <- df.match %>% 
+    select(ho_cov, label) %>% 
+    mutate_all(function(x) if(is.numeric(x) && add_1) x+1 else x) %>%
+    group_by(label) %>% 
+    summarise_all(median)
+  # print(ho_median)
+  # return(list(train = tr_median, ho = ho_median))
+  return(ho_median)
+}
+
+calc_delta <- function(df.match, ho_cov){
+  perc_diff <- function(x) abs(x[1]-x[2])/x[2]
+  means <- calc_means(df.match, ho_cov) %>%
+    select(-label) %>% 
+    summarise_all(perc_diff)
+  medians <- calc_medians(df.match, ho_cov) %>%
+    select(-label) %>% 
+    summarise_all(perc_diff)
+  # return(list(means = means, medians = medians))
+  df <- means %>% 
+    rbind(medians) %>% 
+    as.data.frame() %>%
+    set_rownames(c('means', 'medians'))
+  return(df)
+}
 ```
@@
 ```{r echo=FALSE}
+# define response field
+label <- 'is_release'
+
 ## Examine data briefly
-
-kable(introduce(df_train_f)) %>%
+kable(introduce(df_train_encoder)) %>%
 kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
@@
 ```{r}
-f <- freq(df_train_f$label)
-
-levels(df_train_f$label) <- c(FALSE,TRUE)
-df_train_f$label <- as.logical(df_train_f$label)
+f <- freq(df_train_encoder$label_beta)
 ```
@@
 
-* 302,819 observations: 59,627 beta ("treated") and 243,192 release ("control")
-* Covariants: 
+* $302,819$ observations: $59,627$ beta ("treated") and $243,192$ release ("control")
+* $95$ covariants: 
   + Environment
@@
 ```{r}
-df_release <- df_train_f %>% filter(label == TRUE)
-df_beta <- df_train_f %>% filter(label == FALSE)
+df_beta <- df_train_encoder %>% filter(label_beta == 1)
+df_rel <- df_train_encoder %>% filter(label_beta == 0)
 ```
@@
 build_df <- function(multiple){
-  df <- df_release %>%
+  df <- df_rel %>%
     sample_n(size = round(n_beta / multiple)) %>%
@@
 ```{r}
-f <- freq(as.factor(df_1x_sm$label)) # ~ 50% - 50%
-f <- freq(as.factor(df_2x_sm$label)) # ~ 70% - 30%
-f <- freq(as.factor(df_4x_sm$label)) # ~ 80% - 20%
+f <- freq(as.factor(df_1x_sm$label_beta)) # ~ 50% - 50%
+f <- freq(as.factor(df_2x_sm$label_beta)) # ~ 70% - 30%
+f <- freq(as.factor(df_4x_sm$label_beta)) # ~ 80% - 20%
 ```
@@
 
-environment <- c('cpu_cores','cpu_speed_mhz','cpu_l2_cache_kb','memory_mb','timezone_offset','num_bookmarks','num_addons')
+environment <- c('cpu_cores','cpu_speed_mhz','cpu_vendor_AMD','cpu_vendor_Intel','cpu_vendor_Other','cpu_l2_cache_kb','cpu_l2_cache_kb_cat_l1024','cpu_l2_cache_kb_cat_l256','cpu_l2_cache_kb_cat_l512','cpu_l2_cache_kb_cat_g1024','memory_mb','is_wow64_True','distro_id_norm_acer','distro_id_norm_Mozilla','distro_id_norm_other','distro_id_norm_Yahoo','install_year')
+
+geo <- c('country_US','timezone_offset','timezone_cat_m12_m10','timezone_cat_m10_m8','timezone_cat_m8_m6','timezone_cat_m6_m4','timezone_cat_m4_m2','timezone_cat_m2_0','timezone_cat_0_2','timezone_cat_2_4','timezone_cat_4_6','timezone_cat_6_8','timezone_cat_8_10','timezone_cat_10_12','timezone_cat_12_14','locale_enGB','locale_enUS')
+
+settings <- c('num_bookmarks','num_addons','sync_configured_True','fxa_configured_True','is_default_browser_True','default_search_engine_Bing','default_search_engine_DuckDuckGo','default_search_engine_Google','default_search_engine_other_bundled','default_search_engine_other_nonbundled','default_search_engine_Yahoo')
 
@@
 stability <- c('content_crashes')
+```
+
+## Variable Selection
+The Boruta method was performed.
+
+## Experiments
+Groups of models to train.
+
+```{r}
+exp_1 <- c('daily_num_sessions_started', 'daily_num_sessions_started_max', 'FX_PAGE_LOAD_MS_2_PARENT', 'fxa_configured_True', 'memory_mb', 'num_active_days', 'num_addons', 'num_bookmarks', 'profile_age','session_length','session_length_max','TIME_TO_DOM_COMPLETE_MS','TIME_TO_DOM_CONTENT_LOADED_END_MS','TIME_TO_DOM_INTERACTIVE_MS','TIME_TO_LOAD_EVENT_END_MS','TIME_TO_NON_BLANK_PAINT_MS','timezone_cat_0_2')
+
+exp_2 <- c('country_US', 'daily_num_sessions_started', 'daily_num_sessions_started_max', 'default_search_engine_other_nonbundled', 'FX_PAGE_LOAD_MS_2_PARENT', 'fxa_configured_True', 'memory_mb', 'num_active_days', 'num_addons', 'num_bookmarks', 'profile_age', 'session_length','session_length_max', 'startup_ms', 'startup_ms_max', 'sync_configured_True', 'TIME_TO_DOM_COMPLETE_MS','TIME_TO_DOM_CONTENT_LOADED_END_MS','TIME_TO_DOM_INTERACTIVE_MS','TIME_TO_LOAD_EVENT_END_MS','TIME_TO_NON_BLANK_PAINT_MS','timezone_cat_0_2')
+
+exp_3 <- c('daily_num_sessions_started', 'daily_num_sessions_started_max', 'FX_PAGE_LOAD_MS_2_PARENT', 'memory_mb', 'num_active_days', 'num_addons', 'num_bookmarks', 'profile_age', 'session_length', 'session_length_max','TIME_TO_DOM_COMPLETE_MS','TIME_TO_DOM_CONTENT_LOADED_END_MS','TIME_TO_DOM_INTERACTIVE_MS','TIME_TO_LOAD_EVENT_END_MS','TIME_TO_NON_BLANK_PAINT_MS')
+
+exp_4 <- c('cpu_speed_mhz', 'daily_num_sessions_started', 'daily_num_sessions_started_max', 'default_search_engine_other_nonbundled', 'FX_PAGE_LOAD_MS_2_PARENT', 'memory_mb', 'num_active_days', 'num_addons', 'num_bookmarks', 'profile_age','session_length','session_length_max','startup_ms','startup_ms_max','TIME_TO_DOM_COMPLETE_MS','TIME_TO_DOM_CONTENT_LOADED_END_MS','TIME_TO_DOM_INTERACTIVE_MS','TIME_TO_LOAD_EVENT_END_MS','TIME_TO_NON_BLANK_PAINT_MS')
 ```
@@
 The standardized difference compares the difference in means in units of the pooled standard deviation and allows for the comparison of the relative balance of variables measured in different units.
-Although there is no universally agreed-upon criterion as to what threshold of the standardized difference can be used to indicate an important imbalance, a standard difference that is less than $0.1$ has been taken to indicate a negligible difference in the mean or prevalence of a covariate between treatment groups.
+Although there is no universally agreed-upon criterion as to what threshold of the standardized difference can be used to indicate an important imbalance, a standard difference that is less than 10% (or $0.1$) has been taken to indicate a negligible difference in the mean or prevalence of a covariate between treatment groups.
 
 ### 1x Oversampling
-```{r}
-cov <- df_1x_sm %>% select(c(engagement, usage, environment, page_load, startup, stability))
-treated <- (df_1x_sm$label==FALSE)
+```{r message=FALSE, warning=FALSE}
+cov <- df_1x_sm %>% dplyr::select(c(engagement, usage, environment, geo, settings, page_load, startup, stability))
+treated <- (df_1x_sm$label_beta == 1)
 std.diff <- apply(cov,2,function(x) 100*(mean(x[treated])- mean(x[!treated]))/(sqrt(0.5*(var(x[treated]) + var(x[!treated])))))
-sort(abs(std.diff))
+cov_df_1x <- sort(abs(std.diff))
+cov_df_1x
 ```
@@
 ```{r}
-cov <- df_2x_sm %>% select(c(engagement, usage, environment, page_load, startup, stability))
-treated <- (df_2x_sm$label==FALSE)
+cov <- df_2x_sm %>% dplyr::select(c(engagement, usage, environment, geo, settings, page_load, startup, stability))
+treated <- (df_2x_sm$label_beta == 1)
 std.diff <- apply(cov,2,function(x) 100*(mean(x[treated])- mean(x[!treated]))/(sqrt(0.5*(var(x[treated]) + var(x[!treated])))))
-sort(abs(std.diff))
+cov_df_2x <- sort(abs(std.diff))
+cov_df_2x
 ```
@@
 ```{r}
-cov <- df_4x_sm %>% select(c(engagement, usage, environment, page_load, startup, stability))
-treated <- (df_4x_sm$label==FALSE)
+cov <- df_4x_sm %>% dplyr::select(c(engagement, usage, environment, geo, settings, page_load, startup, stability))
+treated <- (df_4x_sm$label_beta == 1)
 std.diff <- apply(cov,2,function(x) 100*(mean(x[treated])- mean(x[!treated]))/(sqrt(0.5*(var(x[treated]) + var(x[!treated])))))
-sort(abs(std.diff))
+cov_df_4x <- sort(abs(std.diff))
+cov_df_4x
 ```
@@
 
-* As we can see, all standardized differences at the individual variable level were greater than *0.1*.
+* As we can see, all standardized differences at the individual variable level were greater than *0.1* (except for the `timezone_cat_10_12`,`timezone_cat_m10_m8`,`cpu_l2_cache_kb_cat_l512` variables).
 These significant imbalances highlight the need for an effective matching strategy to create a release group that more closely resembles the beta group.
-* For the standardized difference, absolute scores higher than *25%* are considered suspect, and may indicate an imbalance for that specific variable.
-  + That is, `TIME_TO_DOM_INTERACTIVE_MS`, `TIME_TO_DOM_COMPLETE_MS`, `TIME_TO_LOAD_EVENT_END_MS`, `timezone_offset`, `num_addons` and `session_length` (only for the 2x Oversampling).
+Variables that create imbalance *should* be included in the selection model:
 
-## 2. Check initial balance
-
-The package [RItools](https://cran.r-project.org/web/packages/RItools/index.html) includes the routine `XBalance` that estimates a chi-square test to which checks if there is at least one variable in the selection model for which the two groups are different.
-
-* *How similar are treatment/control groups on X?*
-
-### 1x Oversampling
 ```{r}
-xBalance(label ~ (active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes), data=df_1x_sm, report=c("chisquare.test"))
+exp_5  <- c(setdiff(names(cov_df_1x[3:73]), engagement))
+exp_6  <- c(setdiff(names(cov_df_2x), engagement)) 
+exps <- list(exp_1 = exp_1, exp_2 = exp_2, exp_3 = exp_3, exp_4 = exp_4, exp_5 = exp_5, exp_6 = exp_6)
 ```
 
-### 2x Oversampling
-```{r}
-xBalance(label ~ (active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes), data=df_2x_sm, report=c("chisquare.test"))
-```
-
-### 4x Oversampling
-```{r}
-xBalance(label ~ (active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes), data=df_4x_sm, report=c("chisquare.test"))
-```
-
-------
-
-### Observations
-
-* A statistically significant chi-square will indicate that at least one of the variables included in the model is creating an imbalance between the two groups.
-Variables that create imbalance should be included in the selection model.
-
-## 3. Propensity Score Estimation
+## 2. Propensity Score Estimation
 
@@
 
-```{r}
-ps <- glm(label ~ active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes, data=df_1x_sm, family=binomial())
-summary(ps)
+```{r, collapse=TRUE}
+ps_1x <- list()
+for (exp in names(exps)){
+  ps <- glm(generate_formula(exps[[exp]], label), data=df_1x_sm, family=binomial())
+  ps_1x[[exp]] <- ps
+  print(summary(ps))
+}
 ```
@@
 
-```{r}
+```{r fig.height=7, fig.width=14}
+par(mfrow=c(2,3))
+for (ps in ps_1x){
   df_1x_sm$psvalue <- predict(ps, type="response")
-```
-
-## Back to back histogram
-
-```{r fig.height=5, fig.width=10}
-out <- histbackback(split(df_1x_sm$psvalue, df_1x_sm$label), main="Propensity score before matching", xlab=c("release", "beta"))
-#! just adding color
+  out <- histbackback(split(df_1x_sm$psvalue, df_1x_sm$label_release), main="Propensity score before matching", xlab=c("release", "beta"))
+  # just adding color
   barplot(-out$left, col="#111d5e" , horiz=TRUE, space=0, add=TRUE, axes=FALSE)
   barplot(out$right, col="#b21f66", horiz=TRUE, space=0, add=TRUE, axes=FALSE)
+}
 ```
@@
 
-```{r}
-ps <- glm(label ~ active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes, data=df_2x_sm, family=binomial())
-summary(ps)
+```{r, collapse=TRUE}
+ps_2x <- list()
+for (exp in names(exps)){
+  ps <- glm(generate_formula(exps[[exp]], label), data=df_2x_sm, family=binomial())
+  ps_2x[[exp]] <- ps
+  print(summary(ps))
+}
 ```
@@
 
-```{r}
+```{r fig.height=7, fig.width=14}
+par(mfrow=c(2,3))
+for (ps in ps_2x){
   df_2x_sm$psvalue <- predict(ps, type="response")
-```
-
-## Back to back histogram
-
-```{r fig.height=5, fig.width=10}
-out <- histbackback(split(df_2x_sm$psvalue, df_2x_sm$label), main="Propensity score before matching", xlab=c("release", "beta"))
-#! just adding color
+  out <- histbackback(split(df_2x_sm$psvalue, df_2x_sm$label_release), main="Propensity score before matching", xlab=c("release", "beta"))
+  # just adding color
   barplot(-out$left, col="#111d5e" , horiz=TRUE, space=0, add=TRUE, axes=FALSE)
   barplot(out$right, col="#b21f66", horiz=TRUE, space=0, add=TRUE, axes=FALSE)
+}
 ```
@@
 
-```{r}
-ps <- glm(label ~ active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes, data=df_4x_sm, family=binomial())
-summary(ps)
+```{r, collapse=TRUE}
+ps_4x <- list()
+for (exp in names(exps)){
+  ps <- glm(generate_formula(exps[[exp]], label), data=df_4x_sm, family=binomial())
+  ps_4x[[exp]] <- ps
+  print(summary(ps))
+}
 ```
@@
 
-```{r}
+```{r, fig.height=7, fig.width=14}
+par(mfrow=c(2,3))
+for (ps in ps_4x){
   df_4x_sm$psvalue <- predict(ps, type="response")
-```
-
-## Back to back histogram
-
-```{r fig.height=5, fig.width=10}
-out <- histbackback(split(df_4x_sm$psvalue, df_4x_sm$label), main="Propensity score before matching", xlab=c("release", "beta"))
-#! just adding color
+  out <- histbackback(split(df_4x_sm$psvalue, df_4x_sm$label_release), main="Propensity score before matching", xlab=c("release", "beta"))
+  # just adding color
   barplot(-out$left, col="#111d5e" , horiz=TRUE, space=0, add=TRUE, axes=FALSE)
   barplot(out$right, col="#b21f66", horiz=TRUE, space=0, add=TRUE, axes=FALSE)
+}
 ```
@@
 
-## 4. Propensity Score Matching
+## 3. Propensity Score Matching
 
-### Match using Coarsened Exact Matching (CEM)
+### Match using Coarsened Exact Matching (CEM): Small Dataset
 
@@
 
-```{r}
-m.cem <- matchit(label ~ active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes, data=df_1x_sm, method="cem")
-summary(m.cem)
-m.cem.1 = match.data(m.cem)
-```
-
-```{r fig.height=5, fig.width=10}
-plot(m.cem, type = "jitter", col = "#111d5e")
-```
-
-```{r fig.height=5, fig.width=10}
-plot(m.cem, type = "hist", col = "#111d5e")
+```{r, collapse=TRUE}
+cem_results_1x <- list()
+cem_models_1x <- list()
+for (exp in names(exps)){
+  cem <- matchit(formula = generate_formula(exps[[exp]], label), df_1x_sm, 'cem')
+  res <- match.data(cem)
+  cem_models_1x[[exp]] <- cem
+  cem_results_1x[[exp]] <- res
+  #print(summary(cem))
+}
 ```
@@
 
-```{r}
-m.cem <- matchit(label ~ active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes, data=df_2x_sm, method="cem")
-summary(m.cem)
-m.cem.2 = match.data(m.cem)
-```
-
-```{r fig.height=5, fig.width=10}
-plot(m.cem, type = "jitter", col = "#111d5e")
-```
-
-```{r fig.height=5, fig.width=10}
-plot(m.cem, type = "hist", col = "#111d5e")
+```{r, collapse=TRUE}
+cem_results_2x <- list()
+cem_models_2x <- list()
+for (exp in names(exps)){
+  cem <- matchit(formula = generate_formula(exps[[exp]], label), df_2x_sm, 'cem')
+  res <- match.data(cem)
+  cem_models_2x[[exp]] <- cem
+  cem_results_2x[[exp]] <- res
+  #print(summary(cem))
+}
 ```
@@
 
-```{r}
-m.cem <- matchit(label ~ active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes, data=df_4x_sm, method="cem")
-summary(m.cem)
-m.cem.4 = match.data(m.cem)
+```{r, collapse=TRUE}
+cem_results_4x <- list()
+cem_models_4x <- list()
+for (exp in names(exps)){
+  cem <- matchit(formula = generate_formula(exps[[exp]], label), df_4x_sm, 'cem')
+  res <- match.data(cem)
+  cem_models_4x[[exp]] <- cem
+  cem_results_4x[[exp]] <- res
+  #print(summary(cem))
+}
 ```
 
-```{r fig.height=5, fig.width=10}
-plot(m.cem, type = "jitter", col = "#111d5e")
-```
-
-```{r fig.height=5, fig.width=10}
-plot(m.cem, type = "hist", col = "#111d5e")
-```
-
-### Match using Nearest Neighbor matching
+### Match using Nearest Neighbor matching: Small
 
@@
 
-```{r}
-m.nn <- matchit(label ~ active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes, data=df_1x_sm, method="nearest", replace = TRUE)
-summary(m.nn)
-m.nn.1 = match.data(m.nn)
-```
-
-```{r fig.height=5, fig.width=10}
-plot(m.nn, type = "jitter", col = "#111d5e")
-```
-
-```{r fig.height=5, fig.width=10}
-plot(m.nn, type = "hist", col = "#111d5e")
+```{r, collapse=TRUE}
+nn_results_1x <- list()
+nn_models_1x <- list()
+for (exp in names(exps)){
+  nn <- matchit(formula = generate_formula(exps[[exp]], label), df_1x_sm, 'nearest', replace = TRUE)
+  res <- match.data(nn)
+  nn_models_1x[[exp]] <- nn
+  nn_results_1x[[exp]] <- res
+  #print(summary(nn))
+}
 ```
@@
 
-```{r}
-m.nn <- matchit(label ~ active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes, data=df_2x_sm, method="nearest", replace = TRUE)
-summary(m.nn)
-m.nn.2 = match.data(m.nn)
-```
-
-```{r fig.height=5, fig.width=10}
-plot(m.nn, type = "jitter", col = "#111d5e")
-```
-
-```{r fig.height=5, fig.width=10}
-plot(m.nn, type = "hist", col = "#111d5e")
+```{r, collapse=TRUE}
+nn_results_2x <- list()
+nn_models_2x <- list()
+for (exp in names(exps)){
+  nn <- matchit(formula = generate_formula(exps[[exp]], label), df_2x_sm, 'nearest', replace = TRUE)
+  res <- match.data(nn)
+  nn_models_2x[[exp]] <- nn
+  nn_results_2x[[exp]] <- res
+  #print(summary(nn))
+}
 ```
@@
 
-```{r}
-m.nn <- matchit(label ~ active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes, data=df_4x_sm, method="nearest", replace = TRUE)
-summary(m.nn)
-m.nn.4 = match.data(m.nn)
+```{r, collapse=TRUE}
+nn_results_4x <- list()
+nn_models_4x <- list()
+for (exp in names(exps)){
+  nn <- matchit(formula = generate_formula(exps[[exp]], label), df_4x_sm, 'nearest', replace = TRUE)
+  res <- match.data(nn)
+  nn_models_4x[[exp]] <- nn
+  nn_results_4x[[exp]] <- res
+  #print(summary(nn))
+}
+```
+
+### Match using CEM: Full
+
+#### 1x Oversampling
+
+```{r, collapse=TRUE}
+cem_full_results_1x <- list()
+cem_full_models_1x <- list()
+for (exp in names(exps)){
+  nn <- matchit(formula = generate_formula(exps[[exp]], label), df_1x, 'cem')
+  res <- match.data(nn)
+  cem_full_models_1x[[exp]] <- nn
+  cem_full_results_1x[[exp]] <- res
+  #print(summary(nn))
+}
+```
+
+#### 2x Oversampling
+
+```{r, collapse=TRUE}
+cem_full_results_2x <- list()
+cem_full_models_2x <- list()
+for (exp in names(exps)){
+  nn <- matchit(formula = generate_formula(exps[[exp]], label), df_2x, 'cem')
+  res <- match.data(nn)
+  cem_full_models_2x[[exp]] <- nn
+  cem_full_results_2x[[exp]] <- res
+  #print(summary(nn))
+}
+```
+
+#### 4x Oversampling
+
+```{r, collapse=TRUE}
+cem_full_results_4x <- list()
+cem_full_models_4x <- list()
+for (exp in names(exps)){
+  nn <- matchit(formula = generate_formula(exps[[exp]], label), df_4x, 'cem')
+  res <- match.data(nn)
+  cem_full_models_4x[[exp]] <- nn
+  cem_full_results_4x[[exp]] <- res
+  #print(summary(nn))
+}
+```
+
+---
+
+#### Graphical Comparison
+
+* Note that we want to see if the Matched Treated (beta) and Matched Control (release) distributions are roughly similar.
+
+##### (CEM): Small Dataset
+
+###### 1x Oversampling
+
+```{r fig.height=7, fig.width=14}
+counter <- 0
+par(mfrow=c(2,2))
+for (m.cem in cem_models_1x){
+  counter <- counter + 1 
+  print(paste("Experiment ", counter))
+  plot(m.cem, type = "hist", col = "#111d5e")
+}
+```
+
+###### 2x Oversampling
+
+```{r fig.height=7, fig.width=14}
+par(mfrow=c(2,3))
+for (m.cem in cem_models_2x){
+  plot(m.cem, type = "hist", col = "#611e62")
+}
+```
+
+###### 4x Oversampling
+
+```{r fig.height=7, fig.width=14}
+par(mfrow=c(2,3))
+for (m.cem in cem_models_4x){
+  plot(m.cem, type = "hist", col = "#b21f66")
+}
+```
+
+##### Nearest Neighbor matching: Small Dataset
+
+###### 1x Oversampling
+
+```{r fig.height=7, fig.width=14}
+par(mfrow=c(2,3))
+for (m.nn in nn_models_1x){
+  plot(m.nn, type = "hist", col = "#111d5e")
+}
+```
+
+###### 2x Oversampling
+
+```{r fig.height=7, fig.width=14}
+par(mfrow=c(2,3))
+for (m.nn in nn_models_2x){
+  plot(m.nn, type = "hist", col = "#611e62")
+}
+```
+
+###### 4x Oversampling
+
+```{r fig.height=7, fig.width=14}
+par(mfrow=c(2,3))
+for (m.nn in nn_models_4x){
+  plot(m.nn, type = "hist", col = "#b21f66")
+}
+```
+
+##### CEM: Full Dataset
+
+###### 1x Oversampling
+
+```{r fig.height=7, fig.width=14}
+par(mfrow=c(2,3))
+for (m.cem in cem_full_models_1x){
+  plot(m.cem, type = "hist", col = "#111d5e")
+}
+```
+
+###### 2x Oversampling
+
+```{r fig.height=7, fig.width=14}
+par(mfrow=c(2,3))
+for (m.cem in cem_full_models_2x){
+  plot(m.cem, type = "hist", col = "#611e62")
+}
+```
+
+###### 4x Oversampling
+
+```{r fig.height=7, fig.width=14}
+par(mfrow=c(2,3))
+for (m.cem in cem_full_models_4x){
+  plot(m.cem, type = "hist", col = "#b21f66")
+}
+```
+
+---
+
+##### Observations
+
+* From the results above, we can see that the model using *Nearest Neighbor matching* with balanced sampling outperforms the other models.
+
+* Furthermore, experiments $3$ and $4$ (referring to the results of the feature selection, considering the top 10) were the ones that presented the best results, for most of the tested models.
+
+```{r fig.height=7, fig.width=14}
+plot(nn_models_1x$exp_3, type = "QQ", col = "#111d5e")
+```
+
+```{r fig.height=7, fig.width=14}
+plot(nn_models_1x$exp_4, type = "QQ", col = "#111d5e")
+```
+
+* Control unit quantile values are plotted on the x-axis, and treated unit quantile values are plotted on the y-axis.
+If values fall below the 45 degree line, control units generally take lower values of the covariate.
+
+* Data points that fall exactly on the 45 degree line indicate that the marginal distributions are identical, that is, the empirical distributions are the same in the treated and control groups.
+
+* Deviations from the 45 degree line indicate differences in the empirical distribution.
+Therefore, despite the promising results of the previous analysis, we still have some variables with different distributions after matching.
+
+## 4. Computing indices of covariate imbalance after matching
+
+### Experiment 3
+
+```{r message=FALSE, warning=FALSE}
+### 1. Standardized difference
+match.data_3 = match.data(nn_models_1x$exp_3)
+treated1 <- (match.data_3$label_beta==1)
+cov1 <- match.data_3 %>% dplyr::select(exp_3)
+std.diff1 <- apply(cov1,2,function(x) 100*(mean(x[treated1])- mean(x[!treated1]))/(sqrt(0.5*(var(x[treated1]) + var(x[!treated1])))))
+sort(abs(std.diff1))
 ```
@@
 ```{r fig.height=5, fig.width=10}
-plot(m.nn, type = "jitter", col = "#111d5e")
+par(mfrow=c(1,2))
+
+# before matching
+df_1x_sm$psvalue <- predict(ps_1x$exp_3, type="response")
+out <- histbackback(split(df_1x_sm$psvalue, df_1x_sm$label_release), main="Propensity score before matching", xlab=c("release", "beta"))
+# just adding color
+barplot(-out$left, col="#111d5e" , horiz=TRUE, space=0, add=TRUE, axes=FALSE)
+barplot(out$right, col="#b21f66", horiz=TRUE, space=0, add=TRUE, axes=FALSE)
+
+# after matching
+out <- histbackback(split(match.data_3$psvalue, match.data_3$label_release), main="Propensity score after matching (NN)", xlab=c("release", "beta"))
+# just adding color
+barplot(-out$left, col="#111d5e" , horiz=TRUE, space=0, add=TRUE, axes=FALSE)
+barplot(out$right, col="#b21f66", horiz=TRUE, space=0, add=TRUE, axes=FALSE)
+```
+
+### Experiment 4
+
+```{r message=FALSE, warning=FALSE}
+### 1. Standardized difference
+match.data_4 = match.data(nn_models_1x$exp_4)
+treated1 <- (match.data_4$label_beta==1)
+cov1 <- match.data_4 %>% dplyr::select(exp_4)
+std.diff1 <- apply(cov1,2,function(x) 100*(mean(x[treated1])- mean(x[!treated1]))/(sqrt(0.5*(var(x[treated1]) + var(x[!treated1])))))
+sort(abs(std.diff1))
 ```
@@
 ```{r fig.height=5, fig.width=10}
-plot(m.nn, type = "hist", col = "#111d5e")
+par(mfrow=c(1,2))
+
+# before matching
+df_1x_sm$psvalue <- predict(ps_1x$exp_4, type="response")
+out <- histbackback(split(df_1x_sm$psvalue, df_1x_sm$label_release), main="Propensity score before matching", xlab=c("release", "beta"))
+# just adding color
+barplot(-out$left, col="#111d5e" , horiz=TRUE, space=0, add=TRUE, axes=FALSE)
+barplot(out$right, col="#b21f66", horiz=TRUE, space=0, add=TRUE, axes=FALSE)
+
+# after matching
+out <- histbackback(split(match.data_4$psvalue, match.data_4$label_release), main="Propensity score after matching (NN)", xlab=c("release", "beta"))
+# just adding color
+barplot(-out$left, col="#111d5e" , horiz=TRUE, space=0, add=TRUE, axes=FALSE)
+barplot(out$right, col="#b21f66", horiz=TRUE, space=0, add=TRUE, axes=FALSE)
 ```
@@
 
-* What we want to see is that the Matched Treated (beta) and Matched Control (release) distributions are roughly similar. So, we can do better.
+* As can be seen from the figures above, there is a notable improvement in the match between the two distributions of propensity scores after the match (compared to the results before to match).
+This match suggests the two groups (beta and release) are much more similar in terms of their propensity scores and, therefore, the selection bias has been reduced substantially.
 
-## 5. Computing indices of covariate imbalance after matching
+* Comparing the two experiments, we can see that *Experiment 3* showed better results. We confirm this below:
 
-### 1x Oversampling
+```{r out.width=c('50%', '50%')}
+# Experiment 3
+table_match_3 <- CreateTableOne(vars = exp_3, strata = "label_beta", data = match.data_3, test = FALSE, smd = TRUE)
 
-#### CEM
+kable(print(table_match_3, smd = TRUE)) %>%
+kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
+scroll_box(width = "100%")
 
-```{r}
-### 1. Standardized difference
-cov1 <- m.cem.1 %>% select(c(engagement, usage, environment, page_load, startup, stability))
-treated1 <- (m.cem.1$label==FALSE)
-std.diff1 <- apply(cov1,2,function(x) 100*(mean(x[treated1])- mean(x[!treated1]))/(sqrt(0.5*(var(x[treated1]) + var(x[!treated1])))))
-sort(abs(std.diff1))
+# Experiment 4
+table_match <- CreateTableOne(vars = exp_4, strata = "label_beta", data = match.data_4, test = FALSE, smd = TRUE)
+
+kable(print(table_match, smd = TRUE)) %>%
+kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
+scroll_box(width = "100%")
 ```
@@
 ```{r}
-### 2. chi-square test
-xBalance(label ~ (active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes), data=m.cem.1, report=c("chisquare.test"))
+summary(nn_models_1x$exp_3)
 ```
-
-```{r fig.height=5, fig.width=10}
-out <- histbackback(split(m.cem.1$psvalue, m.cem.1$label), main= "Propensity score after matching (CEM)", xlab=c("release", "beta"))
-barplot(-out$left, col="#111d5e" , horiz=TRUE, space=0, add=TRUE, axes=FALSE)
-barplot(out$right, col="#b21f66", horiz=TRUE, space=0, add=TRUE, axes=FALSE)
-```
-
-#### NN
-
-```{r}
-### 1. Standardized difference
-cov1 <- m.nn.1 %>% select(c(engagement, usage, environment, page_load, startup, stability))
-treated1 <- (m.nn.1$label==FALSE)
-std.diff1 <- apply(cov1,2,function(x) 100*(mean(x[treated1])- mean(x[!treated1]))/(sqrt(0.5*(var(x[treated1]) + var(x[!treated1])))))
-sort(abs(std.diff1))
-```
-
-```{r}
-### 2. chi-square test
-xBalance(label ~ (active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes), data=m.nn.1, report=c("chisquare.test"))
-```
-
-```{r fig.height=5, fig.width=10}
-out <- histbackback(split(m.nn.1$psvalue, m.nn.1$label), main= "Propensity score after matching (NN)", xlab=c("release", "beta"))
-barplot(-out$left, col="#111d5e" , horiz=TRUE, space=0, add=TRUE, axes=FALSE)
-barplot(out$right, col="#b21f66", horiz=TRUE, space=0, add=TRUE, axes=FALSE)
-```
-
-### 2x Oversampling
-
-#### CEM
-
-```{r}
-### 1. Standardized difference
-cov1 <- m.cem.2 %>% select(c(engagement, usage, environment, page_load, startup, stability))
-treated1 <- (m.cem.2$label==FALSE)
-std.diff1 <- apply(cov1,2,function(x) 100*(mean(x[treated1])- mean(x[!treated1]))/(sqrt(0.5*(var(x[treated1]) + var(x[!treated1])))))
-sort(abs(std.diff1))
-```
-
-```{r}
-### 2. chi-square test
-xBalance(label ~ (active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes), data=m.cem.2, report=c("chisquare.test"))
-```
-
-```{r fig.height=5, fig.width=10}
-out <- histbackback(split(m.cem.2$psvalue, m.cem.2$label), main= "Propensity score after matching (CEM)", xlab=c("release", "beta"))
-barplot(-out$left, col="#111d5e" , horiz=TRUE, space=0, add=TRUE, axes=FALSE)
-barplot(out$right, col="#b21f66", horiz=TRUE, space=0, add=TRUE, axes=FALSE)
-```
-
-#### NN
-
-```{r}
-### 1. Standardized difference
-cov1 <- m.nn.2 %>% select(c(engagement, usage, environment, page_load, startup, stability))
-treated1 <- (m.nn.2$label==FALSE)
-std.diff1 <- apply(cov1,2,function(x) 100*(mean(x[treated1])- mean(x[!treated1]))/(sqrt(0.5*(var(x[treated1]) + var(x[!treated1])))))
-sort(abs(std.diff1))
-```
-
-```{r}
-### 2. chi-square test
-xBalance(label ~ (active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes), data=m.nn.2, report=c("chisquare.test"))
-```
-
-```{r fig.height=5, fig.width=10}
-out <- histbackback(split(m.nn.2$psvalue, m.nn.2$label), main= "Propensity score after matching (NN)", xlab=c("release", "beta"))
-barplot(-out$left, col="#111d5e" , horiz=TRUE, space=0, add=TRUE, axes=FALSE)
-barplot(out$right, col="#b21f66", horiz=TRUE, space=0, add=TRUE, axes=FALSE)
-```
-
-### 4x Oversampling
-
-#### CEM
-
-```{r}
-### 1. Standardized difference
-cov1 <- m.cem.4 %>% select(c(engagement, usage, environment, page_load, startup, stability))
-treated1 <- (m.cem.4$label==FALSE)
-std.diff1 <- apply(cov1,2,function(x) 100*(mean(x[treated1])- mean(x[!treated1]))/(sqrt(0.5*(var(x[treated1]) + var(x[!treated1])))))
-sort(abs(std.diff1))
-```
-
-```{r}
-### 2. chi-square test
-xBalance(label ~ (active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes), data=m.cem.4, report=c("chisquare.test"))
-```
-
-```{r fig.height=5, fig.width=10}
-out <- histbackback(split(m.cem.4$psvalue, m.cem.4$label), main= "Propensity score after matching (CEM)", xlab=c("release", "beta"))
-barplot(-out$left, col="#111d5e" , horiz=TRUE, space=0, add=TRUE, axes=FALSE)
-barplot(out$right, col="#b21f66", horiz=TRUE, space=0, add=TRUE, axes=FALSE)
-```
-
-#### NN
-
-```{r}
-### 1. Standardized difference
-cov1 <- m.nn.4 %>% select(c(engagement, usage, environment, page_load, startup, stability))
-treated1 <- (m.nn.4$label==FALSE)
-std.diff1 <- apply(cov1,2,function(x) 100*(mean(x[treated1])- mean(x[!treated1]))/(sqrt(0.5*(var(x[treated1]) + var(x[!treated1])))))
-sort(abs(std.diff1))
-```
-
-```{r}
-### 2. chi-square test
-xBalance(label ~ (active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes), data=m.nn.4, report=c("chisquare.test"))
-```
-
-```{r fig.height=5, fig.width=10}
-out <- histbackback(split(m.nn.4$psvalue, m.nn.4$label), main= "Propensity score after matching (NN)", xlab=c("release", "beta"))
-barplot(-out$left, col="#111d5e" , horiz=TRUE, space=0, add=TRUE, axes=FALSE)
-barplot(out$right, col="#b21f66", horiz=TRUE, space=0, add=TRUE, axes=FALSE)
-```

### 2020-03-10 poc/matchIt/modeling.Rmd
update the modeling

@@
 
-* Furthermore, experiments $3$ and $4$ (referring to the results of the feature selection, considering the top 10) were the ones that presented the best results, for most of the tested models.
+* Furthermore, experiments $3$ and $4$ (referring to the results of the feature selection with the stratified sampling, considering the top 5 and top 10, respectly) were the ones that presented the best results, for most of the tested models.
 

### 2020-03-11 poc/matchIt/modeling.Rmd
updating the model selection

@@
 
-```{r}
+```{r echo=TRUE}
 # downsampling
@@
 f <- freq(as.factor(df_1x_sm$label_beta)) # ~ 50% - 50%
+print(paste('50% - 50%'))
+
 f <- freq(as.factor(df_2x_sm$label_beta)) # ~ 70% - 30%
+print(paste('70% - 30%'))
+
 f <- freq(as.factor(df_4x_sm$label_beta)) # ~ 80% - 20%
+print(paste('80% - 20%'))
 ```
@@
 
-```{r}
+```{r echo=TRUE}
 engagement <- c('active_hours','active_hours_max','uri_count','uri_count_max','search_count','search_count_max','num_pages','num_pages_max','daily_max_tabs','daily_max_tabs_max','daily_unique_domains','daily_unique_domains_max','daily_tabs_opened','daily_tabs_opened_max')
@@
 
-```{r}
+```{r echo=TRUE}
 exp_1 <- c('daily_num_sessions_started', 'daily_num_sessions_started_max', 'FX_PAGE_LOAD_MS_2_PARENT', 'fxa_configured_True', 'memory_mb', 'num_active_days', 'num_addons', 'num_bookmarks', 'profile_age','session_length','session_length_max','TIME_TO_DOM_COMPLETE_MS','TIME_TO_DOM_CONTENT_LOADED_END_MS','TIME_TO_DOM_INTERACTIVE_MS','TIME_TO_LOAD_EVENT_END_MS','TIME_TO_NON_BLANK_PAINT_MS','timezone_cat_0_2')
@@
 
-```{r}
+```{r echo=TRUE}
 exp_5  <- c(setdiff(names(cov_df_1x[3:73]), engagement))
@@
 
-```{r, collapse=TRUE}
+```{r message=FALSE, warning=FALSE}
 ps_1x <- list()
@@
   ps_1x[[exp]] <- ps
+  print(paste(exp))
   print(summary(ps))
@@
 
-```{r, collapse=TRUE}
+```{r message=FALSE, warning=FALSE}
 ps_2x <- list()
@@
   ps_2x[[exp]] <- ps
+  print(paste(exp))
   print(summary(ps))
@@
 
-```{r, collapse=TRUE}
+```{r message=FALSE, warning=FALSE}
 ps_4x <- list()
@@
   ps_4x[[exp]] <- ps
+  print(paste(exp))
   print(summary(ps))
@@
 
-```{r, collapse=TRUE}
+```{r message=FALSE, warning=FALSE}
 cem_results_1x <- list()
@@
 
-```{r, collapse=TRUE}
+```{r message=FALSE, warning=FALSE}
 cem_results_2x <- list()
@@
 
-```{r, collapse=TRUE}
+```{r message=FALSE, warning=FALSE}
 cem_results_4x <- list()
@@
 
-```{r, collapse=TRUE}
+```{r message=FALSE, warning=FALSE}
 nn_results_1x <- list()
@@
 
-```{r, collapse=TRUE}
+```{r message=FALSE, warning=FALSE}
 nn_results_2x <- list()
@@
 
-```{r, collapse=TRUE}
+```{r message=FALSE, warning=FALSE}
 nn_results_4x <- list()
@@
   nn_results_4x[[exp]] <- res
-  #print(summary(nn))
-}
-```
-
-### Match using CEM: Full
-
-#### 1x Oversampling
-
-```{r, collapse=TRUE}
-cem_full_results_1x <- list()
-cem_full_models_1x <- list()
-for (exp in names(exps)){
-  nn <- matchit(formula = generate_formula(exps[[exp]], label), df_1x, 'cem')
-  res <- match.data(nn)
-  cem_full_models_1x[[exp]] <- nn
-  cem_full_results_1x[[exp]] <- res
-  #print(summary(nn))
-}
-```
-
-#### 2x Oversampling
-
-```{r, collapse=TRUE}
-cem_full_results_2x <- list()
-cem_full_models_2x <- list()
-for (exp in names(exps)){
-  nn <- matchit(formula = generate_formula(exps[[exp]], label), df_2x, 'cem')
-  res <- match.data(nn)
-  cem_full_models_2x[[exp]] <- nn
-  cem_full_results_2x[[exp]] <- res
-  #print(summary(nn))
-}
-```
-
-#### 4x Oversampling
-
-```{r, collapse=TRUE}
-cem_full_results_4x <- list()
-cem_full_models_4x <- list()
-for (exp in names(exps)){
-  nn <- matchit(formula = generate_formula(exps[[exp]], label), df_4x, 'cem')
-  res <- match.data(nn)
-  cem_full_models_4x[[exp]] <- nn
-  cem_full_results_4x[[exp]] <- res
   #print(summary(nn))
@@
 
-##### CEM: Full Dataset
-
-###### 1x Oversampling
-
-```{r fig.height=7, fig.width=14}
-par(mfrow=c(2,3))
-for (m.cem in cem_full_models_1x){
-  plot(m.cem, type = "hist", col = "#111d5e")
-}
-```
-
-###### 2x Oversampling
-
-```{r fig.height=7, fig.width=14}
-par(mfrow=c(2,3))
-for (m.cem in cem_full_models_2x){
-  plot(m.cem, type = "hist", col = "#611e62")
-}
-```
-
-###### 4x Oversampling
-
-```{r fig.height=7, fig.width=14}
-par(mfrow=c(2,3))
-for (m.cem in cem_full_models_4x){
-  plot(m.cem, type = "hist", col = "#b21f66")
-}
-```
-
 ---
@@
 * Furthermore, experiments $3$ and $4$ (referring to the results of the feature selection with the stratified sampling, considering the top 5 and top 10, respectly) were the ones that presented the best results, for most of the tested models.
-
-```{r fig.height=7, fig.width=14}
-plot(nn_models_1x$exp_3, type = "QQ", col = "#111d5e")
-```
-
-```{r fig.height=7, fig.width=14}
-plot(nn_models_1x$exp_4, type = "QQ", col = "#111d5e")
-```
-
-* Control unit quantile values are plotted on the x-axis, and treated unit quantile values are plotted on the y-axis.
-If values fall below the 45 degree line, control units generally take lower values of the covariate.
-
-* Data points that fall exactly on the 45 degree line indicate that the marginal distributions are identical, that is, the empirical distributions are the same in the treated and control groups.
-
-* Deviations from the 45 degree line indicate differences in the empirical distribution.
-Therefore, despite the promising results of the previous analysis, we still have some variables with different distributions after matching.
 
@@
 ```
+
+# Saving
+
+```{r}
+save(list=c("df_1x","df_1x_sm","exp_3","exp_4"), file="modeling.RData")
+```

### 2020-03-15 poc/matchIt/model_validation.Rmd
performing the model validation

---
title: "Beta to Release Matching: Model Validation"
author: "Mariana de Oliveira Santos Silva"
date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    theme: "flatly"
    toc: true
    toc_float: true
    code_folding: "hide"
    highlight: tango
---

# Introduction

The goal of this notebook is to validate the best model identified in the [previous work](https://github.com/godelstheory/ff-beta-release-matching/blob/marianaossilva/poc/matchIt/model_selection.html). Here, we follow two different applications:

* To balance on the other covariates (e.g., environment and performance metrics), then look at the difference in the user engagement metrics between the balanced Beta and Release for that version (N). This gives us an idea of how clients with similar environments and performance resemble Release in terms of usage. 
* To balance the Beta and Release datasets to resemble each other across the covariates we are concerned with. Balancing, in this case, yields a set of `client_id` for Beta that resembles Release. Our application is then querying the current Beta data (Version N+1) for this `client_id`, and then calculate the metrics we care about from the covariates we care about. This is our outcome.

# Loading the data

```{r message=FALSE, warning=FALSE, include=FALSE}
## Loading the needed libraries

library(kableExtra)      # help you build common complex tables and manipulate table styles
library(DataExplorer)    # automated data exploration
library(tidyverse)       # for general data wrangling (includes readr and dplyr)
library(ggplot2)         # to draw statistical plots 
library(dplyr)           # for data frame manipulation
library(MatchIt)
library(optmatch)
library(cem)
library(RItools)
library(magrittr)
library(tidyr)
library(tidyselect)
library(grt)
library(tableone)
library(cobalt)
library(funModeling)
library(cowplot)
library(plyr)
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
## Loading the training dataset
#load('~/ff-beta-release-matching/poc/matchIt/feature_selection.RData')

df_train_encoder <- read.csv("df_train_encoder.csv", header = T, sep = "\t", encoding="UTF-8") 
df_validate_encoder <- read.csv("df_validate_encoder.csv", header = T, sep = "\t", encoding="UTF-8")
#df_train_encoder$default_search_engine_missing <- 0
```

```{r include=FALSE}
generate_formula <- function(tr_cov, label){
  # Focus on linear and no-interactions
  return(as.formula(paste(label, '~', paste(tr_cov, collapse="+"))))
}

calc_means <- function(df.match, ho_cov, add_1 = FALSE){
  # Validation
  ## Means: holdout
  ho_mean <- df.match %>% 
    dplyr::select(ho_cov, label) %>% 
    mutate_all(function(x) if(is.numeric(x) && add_1) x+1 else x) %>%
    group_by(label) %>% 
    summarise_all(mean)
  return(ho_mean)
}

calc_medians <- function(df.match, ho_cov, add_1 = FALSE){
  # Validation
  ## medians: holdout
  ho_median <- df.match %>% 
    dplyr::select(ho_cov, label) %>% 
    mutate_all(function(x) if(is.numeric(x) && add_1) x+1 else x) %>%
    group_by(label) %>% 
    summarise_all(median)
  return(ho_median)
}

calc_delta <- function(df.match, ho_cov){
  perc_diff <- function(x) abs(x[1]-x[2])/x[2]

  means <- calc_means(df.match, ho_cov) %>%
    dplyr::select(-label) %>% 
    summarise_all(perc_diff)

  medians <- calc_medians(df.match, ho_cov) %>%
    dplyr::select(-label) %>% 
    summarise_all(perc_diff)

  df <- means %>% 
    rbind(medians) %>% 
    as.data.frame() %>%
    set_rownames(c('means', 'medians'))
  return(df)
}

calc_stats <- function(df.match, ho_cov, add_1 = FALSE){
  means <- calc_means(df.match, ho_cov, add_1 = add_1) %>%
    mutate(metric = 'mean')
  medians <- calc_medians(df.match, ho_cov, add_1 = add_1) %>%
    mutate(metric = 'median')
  df <- means %>% 
    rbind(medians) %>% 
    as.data.frame()
  return(df)
}

#### Diagnostics ####
compare_log_cont <- function(df, covariate, tr_mean = NULL, tr_median = NULL, ho_mean = NULL, print = TRUE){
  p <- ggplot(df %>% mutate(!!covariate := get(covariate)+1), aes(label, get(covariate))) +
    geom_violin(aes(fill = label), alpha=0.5) +
    geom_boxplot(width=0.1) +
    scale_y_log10() + scale_fill_manual(values = c("#111d5e", "#b21f66","#611e62")) +
    theme_bw() +
    guides(fill = FALSE) +
    labs(x='Channel', y='Measure', title=covariate) + coord_flip()

  if(print) print(p)
  return(p)
}
```

# Data Preparation

## Training

```{r echo=FALSE}
# define response field
label <- 'is_release'

## Training set
kable(introduce(df_train_encoder)) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
scroll_box(width = "100%")
```

## Validation

```{r echo=FALSE}
## Validation set
kable(introduce(df_validate_encoder)) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
scroll_box(width = "100%")
```

```{r}
# sampling for beta overrepresentation
build_df <- function(df_c, multiple){
  df_beta <- df_c %>% filter(label_beta == 1)
  df_rel <- df_c %>% filter(label_beta == 0)
  n_beta <- nrow(df_beta)

  df <- df_rel %>%
    sample_n(size = round(n_beta / multiple)) %>%
    rbind(df_beta)

  return(df)
}

df_train_1x <- build_df(df_train_encoder, 1)
df_validate_1x <- build_df(df_validate_encoder, 1)
```

Let's check the class balance.

```{r include=FALSE}
df_validate_1x$label <- mapvalues(df_validate_1x$is_release, from=c(FALSE,TRUE), to=c('beta','release'))
df_validate_encoder$label <- mapvalues(df_validate_encoder$is_release, from=c(FALSE,TRUE), to=c('beta','release'))
df_train_1x$label <- mapvalues(df_train_1x$is_release, from=c(FALSE,TRUE), to=c('beta','release'))
```

```{r}
print(paste('Train (50% - 50%)'))
f <- freq(as.factor(df_train_1x$label)) # ~ 50% - 50%

print(paste('Validation (50% - 50%)'))
f <- freq(as.factor(df_validate_1x$label)) # ~ 50% - 50%
```

# First Application - Training Daset (V67)

In this application, we need to balance the two groups (Beta and Release) considering the other covariates (e.g., environment and performance metrics) and then look at the difference in user engagement metrics between the balanced Beta and Release for that version (N). The utility of this application is to inform us on how Beta is different concerning Release in user engagement, with all the other covariates being equal.

## Modeling

Setting the selected expirement from previous work.

```{r echo=TRUE}
covariates <- c('daily_num_sessions_started', 'daily_num_sessions_started_max', 'FX_PAGE_LOAD_MS_2_PARENT', 'memory_mb', 'num_active_days', 'num_addons', 'num_bookmarks', 'profile_age', 'session_length', 'session_length_max','TIME_TO_DOM_COMPLETE_MS','TIME_TO_DOM_CONTENT_LOADED_END_MS','TIME_TO_DOM_INTERACTIVE_MS','TIME_TO_LOAD_EVENT_END_MS','TIME_TO_NON_BLANK_PAINT_MS')

engagement <- c('active_hours','active_hours_max','uri_count','uri_count_max','search_count','search_count_max','num_pages','num_pages_max','daily_max_tabs','daily_max_tabs_max','daily_unique_domains','daily_unique_domains_max','daily_tabs_opened','daily_tabs_opened_max')
```

### Match using Nearest Neighbor matching - Mahalanobis: Full Dataset

The best model from previous work.

```{r message=FALSE, warning=FALSE}
nn.ma <- matchit(formula = generate_formula(covariates, label), df_train_1x, 'nearest', distance='mahalanobis')
df_matched <- match.data(nn.ma)
df_matched$label <- mapvalues(df_matched$is_release, from=c(FALSE,TRUE), to=c('beta','release'))
print(summary(nn.ma))
```

```{r}
table_match <- CreateTableOne(vars = covariates, strata = "is_release", data = df_matched, test = FALSE)
print(table_match, smd = TRUE)
```

```{r fig.height=5, fig.width=9, message=FALSE, warning=FALSE}
love.plot(nn.ma, binary = "std", threshold = .1, colors = c("#111d5e", "#b21f66"), abs = T) + theme_bw()
```

***
### Observations

* Both table and plot show that the matching process successfully match all instances. That is, we have no unmatched (unadjusted) samples.
* The plot shows that, for adjusted cases (after matching), the standardized mean difference is relatively small for most covariates. The smallest (that is, less than or equal to $0.1$) are: `profile_age`, `memory_mb`, `num_bookmarks` and `num_active_days`. However, some have a high absolute value, for example, `num_addons`.

### Post-matching Beta-Release Difference:

```{r message=FALSE, warning=FALSE, results = 'asis'}
stats_post_mean <- calc_means(df_matched, engagement) %>%
  dplyr::select(-label) %>%
  set_rownames(c('beta (mean)', 'release (mean)'))

stats_post_median <- calc_medians(df_matched, engagement) %>%
  dplyr::select(-label) %>%
  set_rownames(c('beta (median)', 'release (median)'))

stats_post <- calc_delta(df_matched, engagement)

stats_mean <- stats_post_mean %>%
  rbind(stats_post[1, ]) %>%
  set_rownames(c('beta (mean)', 'release (mean)', 'delta (mean)'))

stats_median <- stats_post_median %>%
  rbind(stats_post[2, ]) %>%
  set_rownames(c('beta (median)', 'release (median)', 'delta (median)'))

stats <- stats_mean %>%
  rbind(stats_median)

knitr::kable(stats) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
  row_spec(c(3,6), bold = T, color = "white", background = "#4D5686") %>%
  scroll_box(width = "100%")
```

### QQ-Plots

Q-Q plots are a handy tool for comparing distributions: the closer the values form a straight line, the higher
chance to come from a similar distribution. Here, we use Q-Q plots and the Kolmogorov-Smirnov test (KS) test to verify the differences between the balanced Beta and Release for that version (N).

```{r fig.height=9, fig.width=9, message=FALSE, warning=FALSE}
par(mfrow = c(4, 2))

df_beta <- df_matched %>% filter(label == 'beta')
df_rel <- df_matched %>% filter(label == 'release')

## QQ plot in R to compare two data samples
for (i in engagement) {

  # Training
  x_t <- df_beta[,i]
  y_t <- df_rel[,i]

  rg_t <- range(x_t, y_t, na.rm=T)

  test_t <- ks.test(x_t, y_t)$statistic
  test_t <- paste("KS Test = ", round(test_t, 3))

  ########

  title_t <- paste('V67', i, sep='\n')
  qqplot(x_t, y_t, main=title_t, xlim=rg_t, ylim=rg_t, xlab = "Beta", ylab = "Release", pch = 1)
  # mtext(test, side=3)
  text(min(x_t), (if(max(x_t) > max(y_t)) max(x_t) else max(y_t)), test_t, adj=c(0,1))
  abline(0,1, col="#fe346e", lty=2)
}
```

### Violin Plots

The following violin plots depicts distributions for the Beta and release subsets, for the version v67 (training).

```{r fig.height=5, fig.width=8, message=FALSE, warning=FALSE}
par(mfrow = c(4, 2))

## Violin plots
for (i in engagement) {
  p <- ggplot(df_matched, aes(x=label, y=eval(as.name(i)), fill=label)) + 
  geom_violin(trim=FALSE) +
  labs(title=i,x="Channel", y = "Measure") + 
  scale_y_log10() + scale_fill_manual(values=c("#111d5e", "#b21f66")) +
  geom_boxplot(width=0.1, fill="white", alpha=0.5) + 
  theme_bw() + theme(legend.position="none") + coord_flip()
  print(p)
}
```

***

### Observations

* Analysing only the Q-Q plots, the best matching variables are near the $x = y$ line (e.g., `active_hours`, `num_pages`, `search_count` and `daily_unique_domains`). However, some plots present a deviation from such a line at the high-end (e.g., `daily_max_tabs` and `daily_tabs_opened`). 
* Regarding violin plots, overall, the Beta users from V67, with all the other covariates (*experiment 3*) being equal, are quite similar concerning Release in user engagement. Only the following metrics yielded a great deviation (as already pointed by the KS test):

  - `num_pages` and `num_pages_max`
  - `daily_max_tabs` and `daily_max_tabs_max`

# Second Application - Validation dataset (V68)

In this application, we need to balance the Beta and Release datasets to resemble each other across the covariates we are concerned with, that is, the user engagement metrics. Balancing, in this case, yields a set of `client_id` for Beta that resembles Release. This gives us an idea of how these users do indeed change in time. If we see changes that are larger than anticipated, then we know that something significant is happening in user engagement that we can "forecast" in the subsequent Release.

First, we determine the number of training (v67) Beta and Release clients that are in the validation set (v68).

```{r message=FALSE, warning=FALSE, echo=FALSE}
mutual_clients <- df_train_1x[, c('client_id', 'label')] %>% 
  inner_join(df_validate_encoder[, c('client_id', 'label')]) %>%
  count('label')

mutual_clients
```

Let's compare this to existing distribution:

```{r echo=FALSE}
total <- df_train_1x %>% count('label')
cat('Percentage of beta mutual clients:',round(mutual_clients$freq[1] * 100 / total$freq[1]),'%\n')
cat('Percentage of release mutual clients:',round(mutual_clients$freq[2] * 100 / total$freq[2]),'%')
```

Hence, most training clients (65%) are in the validation set.

## Holdout Covariates

* User engagement metrics:
  - active_hours
  - active_hours_max
  - uri_count
  - uri_count_max
  - search_count
  - search_count_max
  - num_pages
  - num_pages_max
  - daily_max_tabs
  - daily_max_tabs_max
  - daily_unique_domains
  - daily_unique_domains_max
  - daily_tabs_opened
  - daily_tabs_opened_max

Subset the validation clients down to those matched:

```{r echo=FALSE}
df_validate_matched <- df_validate_1x %>%
  filter(client_id %in% df_matched$client_id)

df_validate_matched %>%
  count('label')
```

### Training and Validation Difference:

```{r}
stats_pre <- calc_delta(df_validate_1x, engagement)
stats_post <- calc_delta(df_validate_matched, engagement)

stats_mean <- stats_pre[1, ] %>%
  rbind(stats_post[1, ]) %>%
  set_rownames(c('pre-matching', 'post-matching'))

stats_median <- stats_pre[2, ] %>%
  rbind(stats_post[2, ]) %>%
  set_rownames(c('pre-matching', 'post-matching'))
```

> Mean

```{r results = 'asis'}
knitr::kable(stats_mean) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
  scroll_box(width = "100%")
```

> Median

```{r results = 'asis'}
knitr::kable(stats_median) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
  scroll_box(width = "100%")
```

***

```{r fig.width=10, fig.height=50, echo=FALSE, results = 'asis'}
df_validate_full <- df_validate_matched %>%
  filter(label == 'beta') %>%
  mutate(label =  'beta - matched') %>%
  rbind(df_validate_1x) %>% 
  distinct()

stats <- calc_stats(df_validate_full, engagement, add_1 = TRUE) %>%
  dplyr::select('metric','label', everything())

knitr::kable(stats) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
  row_spec(1:3, bold = T, color = "white", background = "#4D5686") %>%
  row_spec(4:6, bold = T, color = "white", background = "#C5578C") %>%
  scroll_box(width = "100%")
```

```{r message=FALSE, warning=FALSE}
plots <- list()

for (covariate in engagement) {
  stats_rel <- stats %>% filter(label == 'release') %>% dplyr::select(covariate, metric)
  means <- stats_rel[stats_rel$metric == 'mean', covariate]
  medians <- stats_rel[stats_rel$metric == 'median', covariate]
  ho_means <- stats %>% filter(label == 'beta' & metric == 'mean') %>% dplyr::select(covariate)

  plots[[covariate]] <- compare_log_cont(df_validate_full, covariate, means, medians, as.numeric(ho_means), print=FALSE) 
}
```

```{r echo=FALSE, fig.height=50, fig.width=10, message=FALSE, warning=FALSE}
plot_grid(plotlist = plots, ncol = 1)
```

## Training Covariates

* Experiment 3:
  - daily_num_sessions_started
  - daily_num_sessions_started_max
  - FX_PAGE_LOAD_MS_2_PARENT
  - memory_mb
  - num_active_days
  - num_addons
  - num_bookmarks
  - profile_age
  - session_length
  - session_length_max
  - TIME_TO_DOM_COMPLETE_MS
  - TIME_TO_DOM_CONTENT_LOADED_END_MS
  - TIME_TO_DOM_INTERACTIVE_MS
  - TIME_TO_LOAD_EVENT_END_MS
  - TIME_TO_NON_BLANK_PAINT_MS

```{r}
stats_pre <- calc_delta(df_validate_1x, covariates)
stats_post <- calc_delta(df_validate_matched, covariates)

stats_mean <- stats_pre[1, ] %>%
  rbind(stats_post[1, ]) %>%
  set_rownames(c('pre-matching', 'post-matching'))

stats_median <- stats_pre[2, ] %>%
  rbind(stats_post[2, ]) %>%
  set_rownames(c('pre-matching', 'post-matching'))
```

> Mean

```{r results = 'asis'}
knitr::kable(stats_mean) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
  scroll_box(width = "100%")
```

> Median

```{r results = 'asis'}
knitr::kable(stats_median) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
  scroll_box(width = "100%")
```

***

```{r fig.width=10, fig.height=50, echo=FALSE, results = 'asis'}
stats <- calc_stats(df_validate_full, covariates, add_1 = TRUE) %>%
  dplyr::select('metric','label', everything())

knitr::kable(stats) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
  row_spec(1:3, bold = T, color = "white", background = "#4D5686") %>%
  row_spec(4:6, bold = T, color = "white", background = "#C5578C") %>%
  scroll_box(width = "100%")
```

```{r message=FALSE, warning=FALSE}
plots <- list()

for (covariate in covariates) {
  stats_rel <- stats %>% filter(label == 'release') %>% dplyr::select(covariate, metric)
  means <- stats_rel[stats_rel$metric == 'mean', covariate]
  medians <- stats_rel[stats_rel$metric == 'median', covariate]
  ho_means <- stats %>% filter(label == 'beta' & metric == 'mean') %>% dplyr::select(covariate)

  plots[[covariate]] <- compare_log_cont(df_validate_full, covariate, means, medians, as.numeric(ho_means), print=FALSE) 
}
```

```{r echo=FALSE, fig.height=50, fig.width=10, message=FALSE, warning=FALSE}
plot_grid(plotlist = plots, ncol = 1)
```

### 2020-03-17 poc/matchIt/model_validation.Rmd
updating the model validation

@@
 df_validate_encoder <- read.csv("df_validate_encoder.csv", header = T, sep = "\t", encoding="UTF-8")
-#df_train_encoder$default_search_engine_missing <- 0
+df_train_encoder$default_search_engine_missing <- 0
 ```
@@
     p <- ggplot(df %>% mutate(!!covariate := get(covariate)+1), aes(label, get(covariate))) +
-    geom_violin(aes(fill = label), alpha=0.5) +
+        geom_violin(aes(fill = label), alpha = 0.5) +
         geom_boxplot(width=0.1) +
@@
         guides(fill = FALSE) +
-    labs(x='Channel', y='Measure', title=covariate) + coord_flip()
+        labs(x = 'Channel', y='Measure', title=covariate) + coord_flip()
+
+    # add in lines for treatment means/medians
+    if (!is.null(tr_mean)){
+        p <- p + 
+            geom_hline(yintercept=tr_mean, linetype="solid", lwd = .5) + 
+            geom_hline(yintercept=tr_median, linetype="dashed", lwd = .5) + 
+            geom_hline(yintercept=ho_mean, linetype="dashed", color = "#D62728B2", lwd = 1)
+    }
 
@@
 df_train_1x$label <- mapvalues(df_train_1x$is_release, from=c(FALSE,TRUE), to=c('beta','release'))
+df_train_encoder$label <- mapvalues(df_train_encoder$is_release, from=c(FALSE,TRUE), to=c('beta','release'))
 ```
@@
 
-### Match using Nearest Neighbor matching - Mahalanobis: Full Dataset
+### Match using Nearest Neighbor matching: Full Dataset
 
@@
 ```{r message=FALSE, warning=FALSE}
-nn.ma <- matchit(formula = generate_formula(covariates, label), df_train_1x, 'nearest', distance='mahalanobis')
-df_matched <- match.data(nn.ma)
+nn <- matchit(formula = generate_formula(covariates, label), df_train_1x, 'nearest', replace = TRUE)
+df_matched <- match.data(nn)
 df_matched$label <- mapvalues(df_matched$is_release, from=c(FALSE,TRUE), to=c('beta','release'))
-print(summary(nn.ma))
+print(summary(nn))
 ```
@@
 ```{r}
-table_match <- CreateTableOne(vars = covariates, strata = "is_release", data = df_matched, test = FALSE)
+table_match <- CreateTableOne(vars = covariates, strata = "label", data = df_matched, test = FALSE)
 print(table_match, smd = TRUE)
@@
 ```{r fig.height=5, fig.width=9, message=FALSE, warning=FALSE}
-love.plot(nn.ma, binary = "std", threshold = .1, colors = c("#111d5e", "#b21f66"), abs = T) + theme_bw()
+love.plot(nn, binary = "std", threshold = .1, shapes = c("triangle filled", "circle filled"), colors = c("#111d5e", "#b21f66"), abs = F, position = "top", var.order = "unadjusted") + theme_bw()
 ```
@@
 ***
-### Observations
+#### Observations
 
-* Both table and plot show that the matching process successfully match all instances. That is, we have no unmatched (unadjusted) samples.
-* The plot shows that, for adjusted cases (after matching), the standardized mean difference is relatively small for most covariates.
-The smallest (that is, less than or equal to $0.1$) are: `profile_age`, `memory_mb`, `num_bookmarks` and `num_active_days`.
-However, some have a high absolute value, for example, `num_addons`.
+* The Love plot is a summary plot of covariate balance pre and post matching.
+Each point represents the balance statistic for that covariate, colored based on whether it is calculated before or after adjustment.
+The dotted lines represent the threshold set ($0.1$); if most or all of the points after adjustment are within the threshold, that is good evidence that balance has been achieved
+* The plot shows that, for unadjusted cases (pre-matching), the standardized mean difference is not relatively large (except for `num_addons`).
+However, for adjusted cases (post-matching), the standardized mean difference is smaller.
+That is, for most cases, the absolute value is even smaller than the threshold ($0.1$)
+* Therefore, this result is a good evidence that the matching worked well, as the balance was improved on almost all variables after adjustment
 
-### Post-matching Beta-Release Difference:
+### Post-matching Beta-Release Difference
 
@@
 
-### QQ-Plots
+```{r fig.width=10, fig.height=50, echo=FALSE, results = 'asis'}
+df_training_full <- df_matched %>% 
+  dplyr::select(-weights, -distance) %>%
+  filter(label == 'beta') %>%
+  mutate(label =  'beta - matched') %>%
+  rbind(df_train_1x) %>% 
+  distinct()
 
-Q-Q plots are a handy tool for comparing distributions: the closer the values form a straight line, the higher
-chance to come from a similar distribution. Here, we use Q-Q plots and the Kolmogorov-Smirnov test (KS) test to verify the differences between the balanced Beta and Release for that version (N).
+stats <- calc_stats(df_training_full, engagement) %>%
+  dplyr::select('metric','label', everything())
+
+knitr::kable(stats) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
+  row_spec(1:3, bold = T, color = "white", background = "#4D5686") %>%
+  row_spec(4:6, bold = T, color = "white", background = "#C5578C") %>%
+  scroll_box(width = "100%")
+```
+
+### Kolmogorov-Smirnov test (KS)
+
+We can use the Kolmogorov-Smirnov test (KS) to verify the differences between the balanced Beta and Release for the v67 version.
+It is between 0 and 1, and represents how two data sets are similar.
+Smaller KS distance values indicate better balance.
 
@@
 
-## QQ plot in R to compare two data samples
+output = data.frame()
+
 for (i in engagement) {
@@
   rg_t <- range(x_t, y_t, na.rm=T)
-
-  test_t <- ks.test(x_t, y_t)$statistic
-  test_t <- paste("KS Test = ", round(test_t, 3))
-
-  ########
-
-  title_t <- paste('V67', i, sep='\n')
-  qqplot(x_t, y_t, main=title_t, xlim=rg_t, ylim=rg_t, xlab = "Beta", ylab = "Release", pch = 1)
-  # mtext(test, side=3)
-  text(min(x_t), (if(max(x_t) > max(y_t)) max(x_t) else max(y_t)), test_t, adj=c(0,1))
-  abline(0,1, col="#fe346e", lty=2)
+  ks <- ks.test(x_t, y_t)$statistic
+  output = rbind(output, data.frame(KS = ks))
 }
@@
 
-### Violin Plots
+```{r message=FALSE, warning=FALSE, echo=FALSE, results = 'asis'}
+kable(set_rownames(output, engagement)) %>%
+kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
+scroll_box(width = "100%")
+```
 
-The following violin plots depicts distributions for the Beta and release subsets, for the version v67 (training).
+### Visual inspection
 
-```{r fig.height=5, fig.width=8, message=FALSE, warning=FALSE}
-par(mfrow = c(4, 2))
+Here, we display density plots for the two groups on the given user engagement metric, so we can visually compare their distribution.
+The degree to which the densities for the two groups overlap is a good measure of group balance on the given covariate; significant differences in shape can be indicative of poor balance, even when the mean differences and variance ratios are well within thresholds.
 
-## Violin plots
-for (i in engagement) {
-  p <- ggplot(df_matched, aes(x=label, y=eval(as.name(i)), fill=label)) + 
-  geom_violin(trim=FALSE) +
-  labs(title=i,x="Channel", y = "Measure") + 
-  scale_y_log10() + scale_fill_manual(values=c("#111d5e", "#b21f66")) +
-  geom_boxplot(width=0.1, fill="white", alpha=0.5) + 
-  theme_bw() + theme(legend.position="none") + coord_flip()
+```{r echo=FALSE, fig.height=4, fig.width=7}
+par(mfrow = c(7, 2))
+for (v in engagement){
+  p <- ggplot(data=df_matched, aes(x = get(v), group = label, fill = label)) +
+    geom_density(aes(fill = label), adjust=1.5, alpha=.4) + 
+    scale_fill_manual(values = c("#111d5e", "#b21f66")) +
+    labs(y='Density', title=v) + theme_bw() + theme(legend.position="bottom") 
   print(p)
@@
 
+The following violin plots depicts distributions for the following subsets:
+
+* Beta v67: pre-matching
+* Beta v67: matched and subsetted
+* Release v67
+
+**NOTE**: Guiding lines have been added for the following:
+
+* <span style="color:black">black</span> solid: Release mean
+* <span style="color:black">black</span> dashed: Release median
+* <span style="color:#D62728B2">red</span> dashed line: subsetted Beta _mean_.
+
+```{r message=FALSE, warning=FALSE}
+plots <- list()
+
+for (covariate in engagement) {
+  stats_rel <- stats %>% filter(label == 'release') %>% dplyr::select(covariate, metric)
+  means <- stats_rel[stats_rel$metric == 'mean', covariate]
+  medians <- stats_rel[stats_rel$metric == 'median', covariate]
+  ho_means <- stats %>% filter(label == 'beta' & metric == 'mean') %>% dplyr::select(covariate)
+
+  plots[[covariate]] <- compare_log_cont(df_training_full, covariate, means, medians, as.numeric(ho_means), print=FALSE) 
+}
+```
+
+```{r echo=FALSE, fig.height=50, fig.width=10, message=FALSE, warning=FALSE}
+plot_grid(plotlist = plots, ncol = 1)
+```
+
 ***
+#### Observations
 
-### Observations
+The density and violin plots show that there are significant differences between both groups (Beta and Release) concerning some user engagement metrics, listed as follows.
 
-* Analysing only the Q-Q plots, the best matching variables are near the $x = y$ line (e.g., `active_hours`, `num_pages`, `search_count` and `daily_unique_domains`).
-However, some plots present a deviation from such a line at the high-end (e.g., `daily_max_tabs` and `daily_tabs_opened`).
-* Regarding violin plots, overall, the Beta users from V67, with all the other covariates (*experiment 3*) being equal, are quite similar concerning Release in user engagement.
-Only the following metrics yielded a great deviation (as already pointed by the KS test):
-
-  - `num_pages` and `num_pages_max`
-  - `daily_max_tabs` and `daily_max_tabs_max`
+* `num_pages`
+* `num_pages_max`
+* `active_hours`
+* `active_hours_max`
+* `uri_count`
+* `uri_count_max`
+* `daily_unique_domains`
+* `daily_unique_domains_max`
 
@@
 
-stats <- calc_stats(df_validate_full, engagement, add_1 = TRUE) %>%
+stats <- calc_stats(df_validate_full, engagement) %>%
   dplyr::select('metric','label', everything())
@@
 
-```{r echo=FALSE, fig.height=50, fig.width=10, message=FALSE, warning=FALSE}
-plot_grid(plotlist = plots, ncol = 1)
+### Kolmogorov-Smirnov test (KS)
+
+Once again, we use the KS test to verify whether any significant difference between the average user engagement metrics in the Beta and Release groups, over several versions (v67 and v68).
+*Reminder:* smaller KS distance values indicate a better balance.
+
+```{r fig.height=9, fig.width=9, message=FALSE, warning=FALSE}
+par(mfrow = c(4, 2))
+
+df_beta <- df_validate_full %>% filter(label == 'beta - matched')
+df_rel <- df_validate_full %>% filter(label == 'release')
+
+output = data.frame()
+
+for (i in engagement) {
+
+  # Training
+  x_t <- df_beta[,i]
+  y_t <- df_rel[,i]
+
+  rg_t <- range(x_t, y_t, na.rm=T)
+  ks <- ks.test(x_t, y_t)$statistic
+  output = rbind(output, data.frame(KS = ks))
+}
 ```
 
-## Training Covariates
-
-* Experiment 3:
-  - daily_num_sessions_started
-  - daily_num_sessions_started_max
-  - FX_PAGE_LOAD_MS_2_PARENT
-  - memory_mb
-  - num_active_days
-  - num_addons
-  - num_bookmarks
-  - profile_age
-  - session_length
-  - session_length_max
-  - TIME_TO_DOM_COMPLETE_MS
-  - TIME_TO_DOM_CONTENT_LOADED_END_MS
-  - TIME_TO_DOM_INTERACTIVE_MS
-  - TIME_TO_LOAD_EVENT_END_MS
-  - TIME_TO_NON_BLANK_PAINT_MS
-
-```{r}
-stats_pre <- calc_delta(df_validate_1x, covariates)
-stats_post <- calc_delta(df_validate_matched, covariates)
-
-stats_mean <- stats_pre[1, ] %>%
-  rbind(stats_post[1, ]) %>%
-  set_rownames(c('pre-matching', 'post-matching'))
-
-stats_median <- stats_pre[2, ] %>%
-  rbind(stats_post[2, ]) %>%
-  set_rownames(c('pre-matching', 'post-matching'))
-```
-
-> Mean
-
-```{r results = 'asis'}
-knitr::kable(stats_mean) %>%
+```{r message=FALSE, warning=FALSE, echo=FALSE, results = 'asis'}
+kable(set_rownames(output, engagement)) %>%
 kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
@@
 
-> Median
+### Visual inspection
 
-```{r results = 'asis'}
-knitr::kable(stats_median) %>%
-  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
-  scroll_box(width = "100%")
+```{r echo=FALSE, fig.height=4, fig.width=7}
+par(mfrow = c(7, 2))
+for (v in engagement){
+  p <- ggplot(data=df_validate_full, aes(x = get(v), group = label, fill = label)) +
+    geom_density(aes(fill = label), adjust=1.5, alpha=.4) + 
+    scale_fill_manual(values = c("#111d5e", "#b21f66","#611e62")) +
+    labs(y='Density', title=v) + theme_bw() + theme(legend.position="bottom") 
+  print(p)
+}
 ```
 
-***
+The following violin plots depicts distributions for the following subsets:
 
-```{r fig.width=10, fig.height=50, echo=FALSE, results = 'asis'}
-stats <- calc_stats(df_validate_full, covariates, add_1 = TRUE) %>%
-  dplyr::select('metric','label', everything())
+* Beta v68: pre-matching
+* Beta v68: matched and subsetted
+* Release v68
 
-knitr::kable(stats) %>%
-  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
-  row_spec(1:3, bold = T, color = "white", background = "#4D5686") %>%
-  row_spec(4:6, bold = T, color = "white", background = "#C5578C") %>%
-  scroll_box(width = "100%")
-```
+**NOTE**: Guiding lines have been added for the following:
+
+* <span style="color:black">black</span> solid: Release mean
+* <span style="color:black">black</span> dashed: Release median
+* <span style="color:#D62728B2">red</span> dashed line: subsetted Beta _mean_.
 
@@
 
-for (covariate in covariates) {
+for (covariate in engagement) {
   stats_rel <- stats %>% filter(label == 'release') %>% dplyr::select(covariate, metric)
@@
 ```
+
+***
+#### Observations
+
+Our main objective was to determine if the user engagement metrics changed in the newest Beta version concerning the previous Release version.
+The density and violin plots show that there are significant differences between both groups (Beta and Release) concerning some user engagement metrics, listed as follows.
+
+* `daily_max_tabs`
+* `daily_max_tabs_max`
+* `num_pages`
+* `num_pages_max`
+* `daily_unique_domains`
+
+```{r eval=FALSE, include=FALSE}
+# Saving
+save.image(file = "model_validation.RData")
+```

### 2020-03-18 poc/matchIt/final_report.Rmd
creating the final report

---
title: "Beta to Release Matching: Proof-of-Concept"
author: "Mariana de Oliveira Santos Silva"
date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    theme: "flatly"
    toc: true
    toc_float: true
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r imports, echo=FALSE, message=FALSE, warning=FALSE}
library(kableExtra)      # help you build common complex tables and manipulate table styles
library(DataExplorer)    # automated data exploration
library(tidyverse)       # for general data wrangling (includes readr and dplyr)
library(ggplot2)         # to draw statistical plots
library(cem)
library(RItools)
library(magrittr)
library(tidyr)
library(tidyselect)
library(grt)
library(tableone)
library(cobalt)
library(funModeling)
library(cowplot)
library(plyr)
library(pander)
library(arsenal)
library(data.table)
library(dplyr)           # for data frame manipulation

load('~/ff-beta-release-matching/poc/matchIt/final_report.RData')

df_train_encoder$default_search_engine_missing <- 0
df_validate_1x$label <- mapvalues(df_validate_1x$is_release, from=c(FALSE,TRUE), to=c('beta','release'))
df_validate_encoder$label <- mapvalues(df_validate_encoder$is_release, from=c(FALSE,TRUE), to=c('beta','release'))
df_train_1x$label <- mapvalues(df_train_1x$is_release, from=c(FALSE,TRUE), to=c('beta','release'))
df_train_encoder$label <- mapvalues(df_train_encoder$is_release, from=c(FALSE,TRUE), to=c('beta','release'))
```

```{r covariates, message=FALSE, warning=FALSE, echo=FALSE}
model_covs <- c('daily_num_sessions_started', 'daily_num_sessions_started_max', 'FX_PAGE_LOAD_MS_2_PARENT', 'memory_mb', 'num_active_days', 'num_addons', 'num_bookmarks', 'profile_age', 'session_length', 'session_length_max','TIME_TO_DOM_COMPLETE_MS','TIME_TO_DOM_CONTENT_LOADED_END_MS','TIME_TO_DOM_INTERACTIVE_MS','TIME_TO_LOAD_EVENT_END_MS','TIME_TO_NON_BLANK_PAINT_MS')

holdout_covariates <- c('active_hours','active_hours_max','uri_count','uri_count_max','search_count','search_count_max','num_pages','num_pages_max','daily_max_tabs','daily_max_tabs_max','daily_unique_domains','daily_unique_domains_max','daily_tabs_opened','daily_tabs_opened_max')
```

# tl;dr

The goal of this project is to utilize [statistical matching](https://en.wikipedia.org/wiki/Matching_(statistics)) methods to search for a subset of Beta clients that are representative of Release. The specific use-case of this proof-of-concept was to utilize *performance*, *configuration*, and *environment* covariates of the clients for matching. Validation of the matching was performed on a hold-out set of Firefox **user engagement** covariates.

The following tables represent the relative difference between the Beta and Release train (v67) and validation (v68) data sets for the mean and median respectively. These initial results are promising and suggest that such techniques could be applied to Mozilla use-cases.

```{r tldr_summary, message=FALSE, warning=FALSE, echo=FALSE}
stats_pre <- calc_delta(df_validate_1x, holdout_covariates)
stats_post <- calc_delta(df_validate_matched, holdout_covariates)

stats_pre_v67 <- calc_delta(df_train_1x, holdout_covariates)
stats_post_v67 <- calc_delta(df_matched, holdout_covariates)

rows <- c('pre-matching: v67', 'post-matching: v67', 'pre-matching: v68', 'post-matching: v68')

stats_mean <- stats_pre_v67[1, ] %>% 
  rbind(stats_post_v67[1, ]) %>%
  rbind(stats_pre[1, ]) %>%
  rbind(stats_post[1, ]) %>%
  set_rownames(rows)

stats_median <- stats_pre_v67[2, ] %>% 
  rbind(stats_post_v67[2, ]) %>%
  rbind(stats_pre[2, ]) %>%
  rbind(stats_post[2, ]) %>%
  set_rownames(rows)
```

## Beta-Release Difference: Mean
```{r tldr_summary_mean, message=FALSE, warning=FALSE, echo=FALSE, results = 'asis'}
knitr::kable(stats_mean) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  scroll_box(width = "100%", height = "200px")
```

## Beta-Release Difference: Median

```{r tldr_summary_median, message=FALSE, warning=FALSE, echo=FALSE, results = 'asis'}
knitr::kable(stats_median) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  scroll_box(width = "100%", height = "200px")
```

# Problem Statement

Each new Release version of Firefox is available as a prerelease before it is launched to the general community. It is highly desirable to utilize the telemetry from Beta versions of Firefox to determine critical aspects of Release behavior before it is launched to the general user base. However, it is well known that the Beta population has distinctly different characteristics than Release, such as the distribution of country of origin of its users, and have higher incidents of crashes. Therefore, directly utilizing Beta telemetry to inform Release is not statistically valid.

One possible approach to deal with this discrepency is to use [statistical matching](https://en.wikipedia.org/wiki/Matching_(statistics)) techniques to find a subset of Beta that is representative of Release. What connotates "representative" depends upon the desired use-case (outcome), such as performance characteristics, or crash rates. In this work, we focus on **user engagement metrics** as the chosen use-case. Here, we follow two different strategies for validate the resultant model:

1. To balance on the other covariates (e.g., environment and performance metrics), then look at the difference in the user engagement metrics between the balanced Beta and Release for that version (N). *This gives us an idea of how clients with similar environments and performance resemble Release in terms of usage*. 
2. To balance the Beta and Release data sets to resemble each other across the covariates we are concerned with. Balancing, in this case, yields a set of `client_id` for Beta that resembles Release. Our application is then querying the current Beta data (Version N+1) for this `client_id`, and then calculate the metrics we care about from the covariates we care about. *This gives us an idea of how these users do indeed change in time*.

# Methodology

Our methodology aims at defyning which aspect of Release behavior we will address with the Beta subset (e.g., start-up, user engagement, browser responsiveness) and, then, determining and focusing on the statistical matching approaches to address the chosen use-case. The methodology is summarized as follows:

1. Build and prepare training and validation data sets containing Beta and Release clients ([data preparation](#data_prep))
2. Perform feature engineering on categorical data into dummy variables ([feature engineering](#feat_eng))
3. Perform feature selection as an initial pre-filter to the covariates, to narrow the feature selection search space ([feature selection](#feat_sel))
4. Perform statistical modeling for the chosen use-case, that is, **user engagement metrics** ([modeling](#model))

## Data Preparation {#data_prep}

The following filters are applied:

* Desktop Firefox
* Two weeks of collection per profile, starting with first observed ping within date window
* en-US, en-GB locales
* US, GB countries

```{r introduce, message=FALSE, warning=FALSE, echo=FALSE}
intro_v67 <- introduce(df_train_encoder)
intro_v68 <- introduce(df_validate_encoder)
rows <- c('v67', 'v68')

intro <- intro_v67 %>% 
  rbind(intro_v68) %>%
  set_rownames(rows)
```

```{r intro_train_validate, message=FALSE, warning=FALSE, echo=FALSE, results = 'asis'}
kable(intro) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  scroll_box(width = "100%")
```

### Covariates

The following covariates were collected. These were categorized under training and hold-out. The former were used for training a statistical matching model. The latter are not included in training and are used for determining model performance. The covariates are further subcategorized as to what they measure.

#### Training
The follows makes up the training data set, used in statistical matching:

* Version 67
* $39$ covariates: 
  + Environment
      - cpu_cores
      - cpu_cores_cat
      - cpu_speed_mhz
      - cpu_speed_cat
      - cpu_vendor
      - cpu_l2_cache_kb
      - cpu_l2_cache_kb_cat
      - memory_mb
      - memory_cat
      - os_version
      - is_wow64
      - distro_id_norm
      - install_year
  + Geo
      - country
      - timezone_offset
      - timezone_cat
      - locale
  + Settings
      - num_bookmarks
      - num_addons
      - sync_configured
      - fxa_configured
      - is_default_browser
      - default_search_engine
  + Page Load
      - FX_PAGE_LOAD_MS_2_PARENT
      - TIME_TO_DOM_COMPLETE_MS
      - TIME_TO_DOM_CONTENT_LOADED_END_MS
      - TIME_TO_LOAD_EVENT_END_MS
      - TIME_TO_DOM_INTERACTIVE_MS
      - TIME_TO_NON_BLANK_PAINT_MS
  + Startup
      - startup_ms
      - startup_ms_max
  + Stability
      - content_crashes
  + Frequency of Browser Usage
      - num_active_days
      - daily_num_sessions_started
      - daily_num_sessions_started_max
      - session_length
      - session_length_max
      - profile_age
      - profile_age_cat
* Composition:

```{r freq_train, fig.width=8, fig.height=4, echo=FALSE}
f <- freq(data=df_train_1x, input = 'label')
```

#### Holdout
The followings filters constitute the validation data set:

* Version 68
* $14$ covariates: 
  + User engagement
      - active_hours
      - active_hours_max
      - uri_count
      - uri_count_max
      - search_count
      - search_count_max
      - num_pages
      - num_pages_max
      - daily_max_tabs
      - daily_max_tabs_max
      - daily_unique_domains
      - daily_unique_domains_max
      - daily_tabs_opened
      - daily_tabs_opened_max
* Composition:

```{r freq_valid, fig.width=8, fig.height=4, echo=FALSE}
f <- freq(data=df_validate_1x, input = 'label')
```

## Feature (Covariate) Engineering {#feat_eng}

In this step, we perform feature engineering on categorical data into dummy variables, in case some of them turn out to be determinant factors when imputing other variables. Specifically, we employ two widely used techniques:

* **Binning** is a common technique used to smooth noisy data by arranging numerical or categorical features into separate bins.
* **One-hot encoding** is one of the most common encoding methods in machine learning, which spreads the values in a column to multiple flag columns and assigns 0 or 1 to them.

Through these techniques, we end up with larger training and validation data sets. The following reports show the differences between those data sets pre (`df_train_f`) and post (`df_train_encoder`) feature engineering.

### Training (v67)

```{r feat_eng_train, message=FALSE, warning=FALSE, echo=FALSE}
summ <- summary(comparedf(df_train_f, df_train_encoder))
```

```{r message=FALSE, warning=FALSE, echo=FALSE, results = 'asis'}
summ$frame.summary.table$version <- c('pre-engineering','post-engineering')
colnames(summ$frame.summary.table) <- c(' ', 'data.frame', 'ncol', 'nrow')
kable(summ$frame.summary.table) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  scroll_box(width = "100%")
```

```{r message=FALSE, warning=FALSE, echo=FALSE, results = 'asis'}
vars <- summ$vars.ns.table %>%
  dplyr::select(-'version')
kable(vars) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  scroll_box(width = "100%", height = "200px")
```

### Validation (v68)

```{r feat_eng_valid, message=FALSE, warning=FALSE, echo=FALSE}
summ <- summary(comparedf(df_validate_f, df_validate_encoder))
```

```{r message=FALSE, warning=FALSE, echo=FALSE, results = 'asis'}
summ$frame.summary.table$version <- c('pre-engineering','post-engineering')
colnames(summ$frame.summary.table) <- c(' ', 'data.frame', 'ncol', 'nrow')
kable(summ$frame.summary.table) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
scroll_box(width = "100%")
```

```{r message=FALSE, warning=FALSE, echo=FALSE, results = 'asis'}
vars <- summ$vars.ns.table %>%
  dplyr::select(-'version')
kable(vars) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  scroll_box(width = "100%", height = "200px")
rm('summ')
```

## Feature (Covariate) Selection {#feat_sel}

As statistical matching typically trains a machine learning (ML) model for calculation of propensity scores, variable selection should be employed. However, the literature suggests that typical ML techniques of limiting covariates to those that best predict the response are not helpful for statistical matching. Rather, covariates that are unrelated to the exposure (i.e., Beta or Release) but related to the outcome (i.e., user engagement metrics) should always be included in a propensity score model.

Therefore, in this step, we apply the *Boruta* algorithm as an initial pre-filter to the covariates, to narrow the feature selection search space. The *Boruta* algorithm is a wrapper built around the random forest classification algorithm, which tries to capture all the important features you might have in your data set concerning an outcome variable. In short, we apply the *Boruta* algorithm for each user engagement metric as the model outcome. Thus, for each outcome, the algorithm verifies if a feature is important or not. Finally, we find the top 5 and top 10 rankings features per metric, and add to lists. We also perfom this same process to a class balanced data set.

Hence, in total, we builted four covariate sets, that we called as experiments:

```{r include=FALSE}
exp_1 <- c('daily_num_sessions_started', 'daily_num_sessions_started_max', 'FX_PAGE_LOAD_MS_2_PARENT', 'fxa_configured_True', 'memory_mb', 'num_active_days', 'num_addons', 'num_bookmarks', 'profile_age','session_length','session_length_max','TIME_TO_DOM_COMPLETE_MS','TIME_TO_DOM_CONTENT_LOADED_END_MS','TIME_TO_DOM_INTERACTIVE_MS','TIME_TO_LOAD_EVENT_END_MS','TIME_TO_NON_BLANK_PAINT_MS','timezone_cat_0_2')

exp_2 <- c('country_US', 'daily_num_sessions_started', 'daily_num_sessions_started_max', 'default_search_engine_other_nonbundled', 'FX_PAGE_LOAD_MS_2_PARENT', 'fxa_configured_True', 'memory_mb', 'num_active_days', 'num_addons', 'num_bookmarks', 'profile_age', 'session_length','session_length_max', 'startup_ms', 'startup_ms_max', 'sync_configured_True', 'TIME_TO_DOM_COMPLETE_MS','TIME_TO_DOM_CONTENT_LOADED_END_MS','TIME_TO_DOM_INTERACTIVE_MS','TIME_TO_LOAD_EVENT_END_MS','TIME_TO_NON_BLANK_PAINT_MS','timezone_cat_0_2')

exp_3 <- c('daily_num_sessions_started', 'daily_num_sessions_started_max', 'FX_PAGE_LOAD_MS_2_PARENT', 'memory_mb', 'num_active_days', 'num_addons', 'num_bookmarks', 'profile_age', 'session_length', 'session_length_max','TIME_TO_DOM_COMPLETE_MS','TIME_TO_DOM_CONTENT_LOADED_END_MS','TIME_TO_DOM_INTERACTIVE_MS','TIME_TO_LOAD_EVENT_END_MS','TIME_TO_NON_BLANK_PAINT_MS')

exp_4 <- c('cpu_speed_mhz', 'daily_num_sessions_started', 'daily_num_sessions_started_max', 'default_search_engine_other_nonbundled', 'FX_PAGE_LOAD_MS_2_PARENT', 'memory_mb', 'num_active_days', 'num_addons', 'num_bookmarks', 'profile_age','session_length','session_length_max','startup_ms','startup_ms_max','TIME_TO_DOM_COMPLETE_MS','TIME_TO_DOM_CONTENT_LOADED_END_MS','TIME_TO_DOM_INTERACTIVE_MS','TIME_TO_LOAD_EVENT_END_MS','TIME_TO_NON_BLANK_PAINT_MS')

exps <- list('experient 1' = exp_1, 'experient 2' = exp_2, 'experient 3' = exp_3, 'experient 4' = exp_4)
```

* **experient 1**: 
	+ _daily_num_sessions_started_
	+ _daily_num_sessions_started_max_
	+ _FX_PAGE_LOAD_MS_2_PARENT_
	+ _fxa_configured_True_
	+ _memory_mb_
	+ _num_active_days_
	+ _num_addons_
	+ _num_bookmarks_
	+ _profile_age_
	+ _session_length_
	+ _session_length_max_
	+ _TIME_TO_DOM_COMPLETE_MS_
	+ _TIME_TO_DOM_CONTENT_LOADED_END_MS_
	+ _TIME_TO_DOM_INTERACTIVE_MS_
	+ _TIME_TO_LOAD_EVENT_END_MS_
	+ _TIME_TO_NON_BLANK_PAINT_MS_ 
	+ _timezone_cat_0_2_
* **experient 2**: 
	+ _country_US_
	+ _daily_num_sessions_started_
	+ _daily_num_sessions_started_max_
	+ _default_search_engine_other_nonbundled_
	+ _FX_PAGE_LOAD_MS_2_PARENT_
	+ _fxa_configured_True_
	+ _memory_mb_
	+ _num_active_days_
	+ _num_addons_
	+ _num_bookmarks_
	+ _profile_age_
	+ _session_length_
	+ _session_length_max_
	+ _startup_ms_
	+ _startup_ms_max_
	+ _sync_configured_True_
	+ _TIME_TO_DOM_COMPLETE_MS_
	+ _TIME_TO_DOM_CONTENT_LOADED_END_MS_
	+ _TIME_TO_DOM_INTERACTIVE_MS_
	+ _TIME_TO_LOAD_EVENT_END_MS_
	+ _TIME_TO_NON_BLANK_PAINT_MS_
	+ _timezone_cat_0_2_
* **experient 3**: 
	+ _daily_num_sessions_started_
	+ _daily_num_sessions_started_max_
	+ _FX_PAGE_LOAD_MS_2_PARENT_
	+ _memory_mb_
	+ _num_active_days_
	+ _num_addons_
	+ _num_bookmarks_
	+ _profile_age_
	+ _session_length_
	+ _session_length_max_
	+ _TIME_TO_DOM_COMPLETE_MS_
	+ _TIME_TO_DOM_CONTENT_LOADED_END_MS_
	+ _TIME_TO_DOM_INTERACTIVE_MS_
	+ _TIME_TO_LOAD_EVENT_END_MS_
	+ _TIME_TO_NON_BLANK_PAINT_MS_
* **experient 4**: 
	+ _cpu_speed_mhz_
	+ _daily_num_sessions_started_
	+ _daily_num_sessions_started_max_
	+ _default_search_engine_other_nonbundled_
	+ _FX_PAGE_LOAD_MS_2_PARENT_
	+ _memory_mb_
	+ _num_active_days_
	+ _num_addons_
	+ _num_bookmarks_
	+ _profile_age_
	+ _session_length_
	+ _session_length_max_
	+ _startup_ms_
	+ _startup_ms_max_
	+ _TIME_TO_DOM_COMPLETE_MS_
	+ _TIME_TO_DOM_CONTENT_LOADED_END_MS_
	+ _TIME_TO_DOM_INTERACTIVE_MS_
	+ _TIME_TO_LOAD_EVENT_END_MS_
	+ _TIME_TO_NON_BLANK_PAINT_MS_

## Models {#model}

For the last step of our methodology, we use [statistical matching](https://en.wikipedia.org/wiki/Matching_(statistics)) methods to search for a subset of Beta clients that are representative of Release. To do that, a range of statistical matching models were [reviewed](https://github.com/godelstheory/ff-beta-release-matching/blob/marianaossilva/poc/matchIt/modeling.Rmd), using the R library [Matchit](https://cran.r-project.org/web/packages/MatchIt/index.html):

* **Coarsened Exact Matching (CEM).** In CEM, instead of matching based on a composite propensity to be in either treatment or control, one simply coarsens each variable to a reasonable degree of clustering for each variable and then performs an exact match on these coarsened variables.
* **Nearest neighbor matching.** This method selects the $r$ (`default = 1`) best control matches for each individual in the treatment group, by using a distance measure specified by the distance option (`default = logit`). In short, at each matching step the method chooses the control unit that is not yet matched but is closest to the treated unit on the distance measure.
* Nearest neighbor matching, with **Mahalanobis** distance measure
* **Subclassification matching.** The goal of subclassification is to form subclasses, such that in each the distribution of covariates for the Beta and Release user groups are as similar as possible.

Before propensity scores are calculated, we define six covariate sets (experiments) to be utilized in the model selection. The first four experiments were obtained under the conditions described [above](#cov_sel). One of the remaining experiments was included according to statistical tests. That is, we compute the estimation of a normalized difference, a traditional statistical approach, which calculates the difference between the control and treatment group for every variable included in the selection model. In this case, absolute scores higher than 25% are considered suspect, and may indicate an imbalance for that specific variable. Variables that create imbalance should be included in the selection model. For the last experiment, we considered all the variables present in the data set (except for user engagement).

```{r include=FALSE}
exp_5 <- c('timezone_cat_10_12','timezone_cat_m10_m8','cpu_l2_cache_kb_cat_l512','num_pages_max','num_pages','profile_age','uri_count','timezone_cat_12_14','active_hours','uri_count_max','search_count','cpu_vendor_Intel','active_hours_max','daily_unique_domains','default_search_engine_other_bundled','daily_unique_domains_max','timezone_cat_m4_m2','cpu_vendor_AMD','default_search_engine_Bing','search_count_max','timezone_cat_m12_m10','timezone_cat_8_10','cpu_l2_cache_kb_cat_l1024','install_year','is_default_browser_True','cpu_speed_mhz','cpu_l2_cache_kb_cat_g1024','cpu_vendor_Other','default_search_engine_DuckDuckGo','cpu_l2_cache_kb_cat_l256','memory_mb','cpu_l2_cache_kb','startup_ms_max','default_search_engine_Yahoo','startup_ms','num_bookmarks','timezone_cat_m2_0','num_active_days','distro_id_norm_Yahoo','cpu_cores','default_search_engine_Google','daily_tabs_opened_max','daily_tabs_opened','timezone_cat_m8_m6','daily_max_tabs_max','distro_id_norm_other','daily_max_tabs','default_search_engine_other_nonbundled','distro_id_norm_acer','sync_configured_True','fxa_configured_True','daily_num_sessions_started','timezone_cat_6_8','timezone_cat_2_4','session_length_max','daily_num_sessions_started_max','TIME_TO_DOM_CONTENT_LOADED_END_MS','TIME_TO_NON_BLANK_PAINT_MS','locale_enUS','locale_enGB','distro_id_norm_Mozilla','FX_PAGE_LOAD_MS_2_PARENT','session_length','timezone_cat_4_6','timezone_cat_0_2','TIME_TO_DOM_INTERACTIVE_MS','TIME_TO_DOM_COMPLETE_MS','timezone_cat_m6_m4','TIME_TO_LOAD_EVENT_END_MS','country_US','timezone_offset','is_wow64_True','num_addons')
```

* **experient 5**:
	+ timezone_cat_10_12
	+ timezone_cat_m10_m8
	+ cpu_l2_cache_kb_cat_l512
	+ num_pages_max
	+ num_pages
	+ profile_age
	+ uri_count
	+ timezone_cat_12_14
	+ active_hours
	+ uri_count_max
	+ search_count
	+ cpu_vendor_Intel
	+ active_hours_max
	+ daily_unique_domains
	+ default_search_engine_other_bundled
	+ daily_unique_domains_max
	+ timezone_cat_m4_m2
	+ cpu_vendor_AMD
	+ default_search_engine_Bing
	+ search_count_max
	+ timezone_cat_m12_m10
	+ timezone_cat_8_10
	+ cpu_l2_cache_kb_cat_l1024
	+ install_year
	+ is_default_browser_True
	+ cpu_speed_mhz
	+ cpu_l2_cache_kb_cat_g1024
	+ cpu_vendor_Other
	+ default_search_engine_DuckDuckGo
	+ cpu_l2_cache_kb_cat_l256
	+ memory_mb
	+ cpu_l2_cache_kb
	+ startup_ms_max
	+ default_search_engine_Yahoo
	+ startup_ms
	+ num_bookmarks
	+ timezone_cat_m2_0
	+ num_active_days
	+ distro_id_norm_Yahoo
	+ cpu_cores
	+ default_search_engine_Google
	+ daily_tabs_opened_max
	+ daily_tabs_opened
	+ timezone_cat_m8_m6
	+ daily_max_tabs_max
	+ distro_id_norm_other
	+ daily_max_tabs
	+ default_search_engine_other_nonbundled
	+ distro_id_norm_acer
	+ sync_configured_True
	+ fxa_configured_True
	+ daily_num_sessions_started
	+ timezone_cat_6_8
	+ timezone_cat_2_4
	+ session_length_max
	+ daily_num_sessions_started_max
	+ TIME_TO_DOM_CONTENT_LOADED_END_MS
	+ TIME_TO_NON_BLANK_PAINT_MS
	+ locale_enUS
	+ locale_enGB
	+ distro_id_norm_Mozilla
	+ FX_PAGE_LOAD_MS_2_PARENT
	+ session_length
	+ timezone_cat_4_6
	+ timezone_cat_0_2
	+ TIME_TO_DOM_INTERACTIVE_MS
	+ TIME_TO_DOM_COMPLETE_MS
	+ timezone_cat_m6_m4
	+ TIME_TO_LOAD_EVENT_END_MS
	+ country_US
	+ timezone_offset
	+ is_wow64_True
	+ num_addons

Finally, a range of Beta overrepresentations were tested. In the following, 2x means there were twice as many Beta samples as Release.

```{r include=FALSE}
df_beta <- df_train_encoder %>% filter(label == 'beta')
df_rel <- df_train_encoder %>% filter(label == 'release')
n_beta <- nrow(df_beta)
build_df <- function(multiple){
  df <- df_rel %>%
    sample_n(size = round(n_beta / multiple)) %>%
    rbind(df_beta)
}

df_1x <- build_df(1)
df_2x <- build_df(2)
df_4x <- build_df(4)

# downsampling
df_1x_sm <- df_1x %>% sample_n(size = 70000)
df_2x_sm <- df_2x %>% sample_n(size = 70000)
df_4x_sm <- df_4x %>% sample_n(size = 70000)
```

> 1x Beta to Release (50% - 50%)

```{r freq_1x, fig.width=8, fig.height=4, echo=FALSE}
f <- freq(data=df_1x_sm, input = 'label')
```

> 2x Beta to Release (70% - 30%)

```{r freq_2x, fig.width=8, fig.height=4, echo=FALSE}
f <- freq(data=df_2x_sm, input = 'label')
```

> 4x Beta to Release (80% - 20%)

```{r freq_4x, fig.width=8, fig.height=4, echo=FALSE}
f <- freq(data=df_4x_sm, input = 'label')
```

# Results

The [highest performant model](https://github.com/godelstheory/ff-beta-release-matching/blob/marianaossilva/poc/matchIt/model_selection.Rmd) was trained on the v67 data set and has the following properties:

* Matching method: Nearest Neighbor
* Beta oversampling: 1x Beta to Release
* Covariates (Model Features): `experiment 3`

```{r balancing, echo=FALSE, fig.height=5, fig.width=9, message=FALSE, warning=FALSE}
love.plot(nn, binary = "std", threshold = .1, shapes = c("triangle filled", "circle filled"), colors = c("#111d5e", "#b21f66"), abs = F, position = "top", var.order = "unadjusted") + theme_bw()
```

## First Application - Training Set (V67) {#first}

In this application, we need to balance the two groups (Beta and Release) considering the other covariates (e.g., environment and performance metrics) and then look at the difference in user engagement metrics between the balanced Beta and Release for that version (N). The utility of this application is to inform us on how Beta is different concerning Release in user engagement, with all the other covariates being equal.

### Holdout Covariates

* active_hours
* active_hours_max
* uri_count
* uri_count_max
* search_count
* search_count_max
* num_pages
* num_pages_max
* daily_max_tabs
* daily_max_tabs_max
* daily_unique_domains
* daily_unique_domains_max
* daily_tabs_opened
* daily_tabs_opened_max

#### Post-matching Beta-Release Difference

```{r message=FALSE, warning=FALSE, echo=FALSE, results = 'asis'}
stats_post_mean <- calc_means(df_matched, engagement) %>%
  dplyr::select(-label) %>%
  set_rownames(c('beta (mean)', 'release (mean)'))

stats_post_median <- calc_medians(df_matched, engagement) %>%
  dplyr::select(-label) %>%
  set_rownames(c('beta (median)', 'release (median)'))

stats_post <- calc_delta(df_matched, engagement)

stats_mean <- stats_post_mean %>%
  rbind(stats_post[1, ]) %>%
  set_rownames(c('beta (mean)', 'release (mean)', 'delta (mean)'))

stats_median <- stats_post_median %>%
  rbind(stats_post[2, ]) %>%
  set_rownames(c('beta (median)', 'release (median)', 'delta (median)'))

stats <- stats_mean %>%
  rbind(stats_median)

knitr::kable(stats) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  row_spec(c(3,6), bold = T, color = "white", background = "#4D5686") %>%
  scroll_box(width = "100%")
```

```{r first_app, echo=FALSE, results = 'asis'}
df_train_full <- df_matched %>%
  dplyr::select(-weights, -distance) %>%
  filter(label == 'beta') %>%
  mutate(label = 'beta - matched') %>%
  rbind(df_train_1x) %>% 
  distinct()

stats <- calc_stats(df_train_full, engagement) %>%
  dplyr::select('metric','label', everything())

knitr::kable(stats) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  row_spec(1:3, bold = T, color = "white", background = "#4D5686") %>%
  row_spec(4:6, bold = T, color = "white", background = "#C5578C") %>%
  scroll_box(width = "100%")
```

#### Wilcoxon test

In short, we want to know if there is any significant difference between the average user engagement metrics in the Beta and Release groups, for the same version (v67). Here, we use the unpaired two-samples *Wilcoxon test*, which is a non-parametric alternative to the unpaired two-samples t-test used to compare two independent groups of samples. Our question is: *Is there any significant difference between Beta (v67) and Release (v67) user engagement metrics?*

If the resultatns p-values are less than the significance level $alpha = 0.05$, we can conclude that Beta's user engagement metrics, in average, are significantly different from Release users.

```{r message=FALSE, warning=FALSE, echo=FALSE}
set.seed(0)
df <- df_matched %>%
  dplyr::select(-weights, -distance) %>%
  sample_n(size = 5000)

# if the p-value is less than the significance level (0.05), 
# we can conclude that there are significant differences between both groups
df_tests <- data.frame(p_value = 0, diff = 0)
for (covariate in engagement) {
  wt <- wilcox.test(get(covariate) ~ label, data = df, exact = FALSE)
  df_tests = rbind(df_tests, data.frame(p_value = wt$p.value, diff = wt$p.value < 0.05))
}

df_tests <- df_tests[-1,] %>%
  set_rownames(engagement)

df_tests$diff <- lapply(df_tests$diff, as.logical)
```

```{r message=FALSE, warning=FALSE, echo=FALSE, results = 'asis'}
kable(df_tests) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  row_spec(c(1:4,7,8,11,12), bold = T, color = "white", background = "#4D5686") %>%
  scroll_box(width = "100%", height = "400px")
```

#### Visual inspection

For a graphical comparison, we plot the holdout covariate distributions for the following subsets:

* Beta v67: pre-matching [<span style="color:#111d5e">blue</span>]
* Beta v67: matched and subsetted [<span style="color:#b21f66">pink</span>]
* Release v67 [<span style="color:#611e62">purple</span>]

**NOTE**: Guiding lines have been added for the following:

* <span style="color:black">black</span> solid: Release mean
* <span style="color:black">black</span> dashed: Release median
* <span style="color:#D62728B2">red</span> dashed line: subsetted Beta _mean_.

```{r include=FALSE}
plots <- list()

for (covariate in engagement) {
  stats_rel <- stats %>% filter(label == 'release') %>% dplyr::select(covariate, metric)
  means <- stats_rel[stats_rel$metric == 'mean', covariate]
  medians <- stats_rel[stats_rel$metric == 'median', covariate]
  ho_means <- stats %>% filter(label == 'beta' & metric == 'mean') %>% dplyr::select(covariate)

  plots[[covariate]] <- compare_log_cont(df_train_full, covariate, means, medians, as.numeric(ho_means), print=FALSE) 
}
```

```{r violin_train, echo=FALSE, fig.height=50, fig.width=10, message=FALSE, warning=FALSE}
plot_grid(plotlist = plots, ncol = 1)
rm('plots')
```

### Training Covariates

* daily_num_sessions_started
* daily_num_sessions_started_max
* FX_PAGE_LOAD_MS_2_PARENT
* memory_mb
* num_active_days
* num_addons
* num_bookmarks
* profile_age
* session_length
* session_length_max
* TIME_TO_DOM_COMPLETE_MS
* TIME_TO_DOM_CONTENT_LOADED_END_MS
* TIME_TO_DOM_INTERACTIVE_MS
* TIME_TO_LOAD_EVENT_END_MS
* TIME_TO_NON_BLANK_PAINT_MS

#### Post-matching Beta-Release Difference

```{r message=FALSE, warning=FALSE, echo=FALSE, results = 'asis'}
stats_post_mean <- calc_means(df_matched, exp_3) %>%
  dplyr::select(-label) %>%
  set_rownames(c('beta (mean)', 'release (mean)'))

stats_post_median <- calc_medians(df_matched, exp_3) %>%
  dplyr::select(-label) %>%
  set_rownames(c('beta (median)', 'release (median)'))

stats_post <- calc_delta(df_matched, exp_3)

stats_mean <- stats_post_mean %>%
  rbind(stats_post[1, ]) %>%
  set_rownames(c('beta (mean)', 'release (mean)', 'delta (mean)'))

stats_median <- stats_post_median %>%
  rbind(stats_post[2, ]) %>%
  set_rownames(c('beta (median)', 'release (median)', 'delta (median)'))

stats <- stats_mean %>%
  rbind(stats_median)

knitr::kable(stats) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  row_spec(c(3,6), bold = T, color = "white", background = "#4D5686") %>%
  scroll_box(width = "100%")
```

```{r first_app_2, echo=FALSE, results = 'asis'}
df_train_full <- df_matched %>%
  dplyr::select(-weights, -distance) %>%
  filter(label == 'beta') %>%
  mutate(label = 'beta - matched') %>%
  rbind(df_train_1x) %>% 
  distinct()

stats <- calc_stats(df_train_full, exp_3) %>%
  dplyr::select('metric','label', everything())

knitr::kable(stats) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  row_spec(1:3, bold = T, color = "white", background = "#4D5686") %>%
  row_spec(4:6, bold = T, color = "white", background = "#C5578C") %>%
  scroll_box(width = "100%")
```

#### Wilcoxon test

```{r message=FALSE, warning=FALSE, echo=FALSE}
set.seed(0)
df <- df_matched %>%
  dplyr::select(-weights, -distance) %>%
  sample_n(size = 5000)

# if the p-value is less than the significance level (0.05), 
# we can conclude that there are significant differences between both groups
df_tests <- data.frame(p_value = 0, diff = 0)
for (covariate in exp_3) {
  wt <- wilcox.test(get(covariate) ~ label, data = df, exact = FALSE)
  df_tests = rbind(df_tests, data.frame(p_value = wt$p.value, diff = wt$p.value < 0.05))
}

df_tests <- df_tests[-1,] %>%
  set_rownames(exp_3)

df_tests$diff <- lapply(df_tests$diff, as.logical)
```

```{r message=FALSE, warning=FALSE, echo=FALSE, results = 'asis'}
kable(df_tests) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  row_spec(c(1:3,6,7,9,11:15), bold = T, color = "white", background = "#4D5686") %>%
  scroll_box(width = "100%", height = "400px")
```

#### Visual inspection

**NOTE**: Guiding lines have been added for the following:

* <span style="color:black">black</span> solid: Release mean
* <span style="color:black">black</span> dashed: Release median
* <span style="color:#D62728B2">red</span> dashed line: subsetted Beta _mean_

```{r include=FALSE}
plots <- list()

for (covariate in exp_3) {
  stats_rel <- stats %>% filter(label == 'release') %>% dplyr::select(covariate, metric)
  means <- stats_rel[stats_rel$metric == 'mean', covariate]
  medians <- stats_rel[stats_rel$metric == 'median', covariate]
  ho_means <- stats %>% filter(label == 'beta' & metric == 'mean') %>% dplyr::select(covariate)

  plots[[covariate]] <- compare_log_cont(df_train_full, covariate, means, medians, as.numeric(ho_means), print=FALSE) 
}
```

```{r violin_train_cov, echo=FALSE, fig.height=50, fig.width=10, message=FALSE, warning=FALSE}
plot_grid(plotlist = plots, ncol = 1)
rm('plots')
```

### Discussion

Our main objective was to inform how users Beta are different concerning Release in terms of user engagement, with all the other covariates being equal. From these prior analysis, we can see that there are significant differences between both groups (Beta and Release) concerning some user engagement metrics, listed as follows.

* `num_pages`
* `num_pages_max`
* `active_hours`
* `active_hours_max`
* `uri_count`
* `uri_count_max`
* `daily_unique_domains`
* `daily_unique_domains_max`

In addition, by analyzing the distributions of the training covariates, we can see exactly which were the variables that presented the biggest discrepancies. That is, in which aspects the matching was not able to balance the datasets efficiently. The most different covariates are listed as follows.

* `num_addons`
* `daily_num_sessions_started_max`
* `daily_num_sessions_started`

## Second Application - Validation Set (V68) {#second}

In this application, we need to balance the Beta and Release data sets to resemble each other across the covariates we are concerned with, that is, the user engagement metrics. Balancing, in this case, yields a set of `client_id` for Beta that resembles Release. This gives us an idea of how these users do indeed change in time. If we see changes that are larger than anticipated, then we know that something significant is happening in user engagement that we can "forecast" in the subsequent Release.

The next step is to subset the _validation_ v68 set by these matched Beta profiles. This reduces the Beta sample size used in the subsequent analysis:

* v67 Beta subset: `r df_matched %>% filter(label == 'beta') %>% count('label') %>% dplyr::select(freq)` distinct profiles
* v68 Beta subset: `r df_validate_matched %>% filter(label == 'beta') %>% count('label') %>% dplyr::select(freq)` distinct profiles

### Holdout Covariates

* active_hours
* active_hours_max
* uri_count
* uri_count_max
* search_count
* search_count_max
* num_pages
* num_pages_max
* daily_max_tabs
* daily_max_tabs_max
* daily_unique_domains
* daily_unique_domains_max
* daily_tabs_opened
* daily_tabs_opened_max

#### Training and Validation Difference:

```{r echo=FALSE, results = 'asis'}
stats_pre <- calc_delta(df_validate_1x, engagement)
stats_post <- calc_delta(df_validate_matched, engagement)

stats_mean <- stats_pre[1, ] %>%
  rbind(stats_post[1, ]) %>%
  set_rownames(c('pre-matching', 'post-matching'))

stats_median <- stats_pre[2, ] %>%
  rbind(stats_post[2, ]) %>%
  set_rownames(c('pre-matching', 'post-matching'))
```

> Mean

```{r echo=FALSE, results = 'asis'}
knitr::kable(stats_mean) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  scroll_box(width = "100%")
```

> Median

```{r echo=FALSE, results = 'asis'}
knitr::kable(stats_median) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  scroll_box(width = "100%")
```

```{r fig.width=10, fig.height=50, echo=FALSE, results = 'asis'}
df_validate_full <- df_validate_matched %>%
  filter(label == 'beta') %>%
  mutate(label =  'beta - matched') %>%
  rbind(df_validate_1x) %>% 
  distinct()

stats <- calc_stats(df_validate_full, engagement) %>%
  dplyr::select('metric','label', everything())

knitr::kable(stats) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  row_spec(1:3, bold = T, color = "white", background = "#4D5686") %>%
  row_spec(4:6, bold = T, color = "white", background = "#C5578C") %>%
  scroll_box(width = "100%")
```

#### Wilcoxon test

Now, we want to know if there is any significant difference between the average user engagement metrics in the Beta and Release groups, over several versions (v67 and v68). Once again, we use the *Wilcoxon test* with the following question: *Is there any significant difference between Beta-matched (v68) and Release (v68) user engagement metrics?*

```{r message=FALSE, warning=FALSE, echo=FALSE}
set.seed(0)
df <- df_validate_full %>%
  filter(label == 'beta - matched' | label == "release") %>%
  sample_n(size = 5000)

# if the p-value is less than the significance level (0.05), 
# we can conclude that there are significant differences between both groups
df_tests <- data.frame(p_value = 0, diff = 0)
for (covariate in engagement) {
  wt <- wilcox.test(get(covariate) ~ label, data = df, exact = FALSE)
  df_tests = rbind(df_tests, data.frame(p_value = wt$p.value, diff = wt$p.value < 0.05))
}

df_tests <- df_tests[-1,] %>%
  set_rownames(engagement)

df_tests$diff <- lapply(df_tests$diff, as.logical)
```

```{r message=FALSE, warning=FALSE, echo=FALSE, results = 'asis'}
kable(df_tests) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  row_spec(c(7:8), bold = T, color = "white", background = "#4D5686") %>%
  scroll_box(width = "100%", height = "400px")
```

#### Visual inspection

For a graphical comparison, we plot the covariate distributions for the following subsets:

* Beta v68: pre-matching [<span style="color:#111d5e">blue</span>]
* Beta v68: matched and subsetted [<span style="color:#b21f66">pink</span>]
* Release v68 [<span style="color:#611e62">purple</span>]

**NOTE**: Guiding lines have been added for the following:

* <span style="color:black">black</span> solid: Release mean
* <span style="color:black">black</span> dashed: Release median
* <span style="color:#D62728B2">red</span> dashed line: subsetted Beta _mean_

```{r message=FALSE, warning=FALSE}
plots <- list()

for (covariate in engagement) {
  stats_rel <- stats %>% filter(label == 'release') %>% dplyr::select(covariate, metric)
  means <- stats_rel[stats_rel$metric == 'mean', covariate]
  medians <- stats_rel[stats_rel$metric == 'median', covariate]
  ho_means <- stats %>% filter(label == 'beta' & metric == 'mean') %>% dplyr::select(covariate)

  plots[[covariate]] <- compare_log_cont(df_validate_full, covariate, means, medians, as.numeric(ho_means), print=FALSE) 
}
```

```{r violin_valid, echo=FALSE, fig.height=50, fig.width=10, message=FALSE, warning=FALSE}
plot_grid(plotlist = plots, ncol = 1)
rm('plots')
```

### Training Covariates

* daily_num_sessions_started
* daily_num_sessions_started_max
* FX_PAGE_LOAD_MS_2_PARENT
* memory_mb
* num_active_days
* num_addons
* num_bookmarks
* profile_age
* session_length
* session_length_max
* TIME_TO_DOM_COMPLETE_MS
* TIME_TO_DOM_CONTENT_LOADED_END_MS
* TIME_TO_DOM_INTERACTIVE_MS
* TIME_TO_LOAD_EVENT_END_MS
* TIME_TO_NON_BLANK_PAINT_MS

#### Training and Validation Difference:

```{r echo=FALSE, results = 'asis'}
stats_pre <- calc_delta(df_validate_1x, exp_3)
stats_post <- calc_delta(df_validate_matched, exp_3)

stats_mean <- stats_pre[1, ] %>%
  rbind(stats_post[1, ]) %>%
  set_rownames(c('pre-matching', 'post-matching'))

stats_median <- stats_pre[2, ] %>%
  rbind(stats_post[2, ]) %>%
  set_rownames(c('pre-matching', 'post-matching'))
```

> Mean

```{r echo=FALSE, results = 'asis'}
knitr::kable(stats_mean) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  scroll_box(width = "100%")
```

> Median

```{r echo=FALSE, results = 'asis'}
knitr::kable(stats_median) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  scroll_box(width = "100%")
```

```{r fig.width=10, fig.height=50, echo=FALSE, results = 'asis'}
df_validate_full <- df_validate_matched %>%
  filter(label == 'beta') %>%
  mutate(label =  'beta - matched') %>%
  rbind(df_validate_1x) %>% 
  distinct()

stats <- calc_stats(df_validate_full, exp_3) %>%
  dplyr::select('metric','label', everything())

knitr::kable(stats) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  row_spec(1:3, bold = T, color = "white", background = "#4D5686") %>%
  row_spec(4:6, bold = T, color = "white", background = "#C5578C") %>%
  scroll_box(width = "100%")
```

#### Wilcoxon test

Now, we want to know if there is any significant difference between the average user engagement metrics in the Beta and Release groups, over several versions (v67 and v68). Once again, we use the *Wilcoxon test* with the following question: *Is there any significant difference between Beta-matched (v68) and Release (v68) user engagement metrics?*

```{r message=FALSE, warning=FALSE, echo=FALSE}
set.seed(0)
df <- df_validate_full %>%
  filter(label == 'beta - matched' | label == "release") %>%
  sample_n(size = 5000)

# if the p-value is less than the significance level (0.05), 
# we can conclude that there are significant differences between both groups
df_tests <- data.frame(p_value = 0, diff = 0)
for (covariate in exp_3) {
  wt <- wilcox.test(get(covariate) ~ label, data = df, exact = FALSE)
  df_tests = rbind(df_tests, data.frame(p_value = wt$p.value, diff = wt$p.value < 0.05))
}

df_tests <- df_tests[-1,] %>%
  set_rownames(exp_3)

df_tests$diff <- lapply(df_tests$diff, as.logical)
```

```{r message=FALSE, warning=FALSE, echo=FALSE, results = 'asis'}
kable(df_tests) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  row_spec(c(5:8, 11, 12, 14), bold = T, color = "white", background = "#4D5686") %>%
  scroll_box(width = "100%", height = "400px")
```

#### Visual inspection

For a graphical comparison, we plot the covariate distributions for the following subsets:

* Beta v68: pre-matching [<span style="color:#111d5e">blue</span>]
* Beta v68: matched and subsetted [<span style="color:#b21f66">pink</span>]
* Release v68 [<span style="color:#611e62">purple</span>]

**NOTE**: Guiding lines have been added for the following:

* <span style="color:black">black</span> solid: Release mean
* <span style="color:black">black</span> dashed: Release median
* <span style="color:#D62728B2">red</span> dashed line: subsetted Beta _mean_

```{r message=FALSE, warning=FALSE}
plots <- list()

for (covariate in exp_3) {
  stats_rel <- stats %>% filter(label == 'release') %>% dplyr::select(covariate, metric)
  means <- stats_rel[stats_rel$metric == 'mean', covariate]
  medians <- stats_rel[stats_rel$metric == 'median', covariate]
  ho_means <- stats %>% filter(label == 'beta' & metric == 'mean') %>% dplyr::select(covariate)

  plots[[covariate]] <- compare_log_cont(df_validate_full, covariate, means, medians, as.numeric(ho_means), print=FALSE) 
}
```

```{r violin_valid_cov, echo=FALSE, fig.height=50, fig.width=10, message=FALSE, warning=FALSE}
plot_grid(plotlist = plots, ncol = 1)
rm('plots')
```

### Discussion

Our main objective was to determine if the user engagement metrics changed in the newest Beta version concerning the previous Release version. From these prior analysis, we can see that there are significant differences between both groups (Beta and Release) concerning only two user engagement metrics, listed as follows.

* `num_pages`
* `num_pages_max `

In addition, by analyzing the distributions of the training covariates, the most different covariates are listed as follows.

* `num_addons`
* `profile_age`
* `num_bookmarks`
* `num_active_days`

# Overall Considerations

In this project, we employ [statistical matching](https://en.wikipedia.org/wiki/Matching_(statistics)) methods to find subsets of Beta users that can be used to inform how Release in the general user community will behave. Particularly, statistical matching is used to evaluate the effect of a treatment by comparing treated and untreated units in an observational study. The purpose of _matching_ is, for each treated unit, to find one (or more) untreated unit(s) with similar observable characteristics against which the effect of the treatment can be assessed. By matching treated samples to similar untreated ones, matching enables a comparison of outcomes among treated and untreated samples to evaluate the effect of the treatment.

Here, we use statistical matching methods in a non-traditional way. In particular, our goal is to search for a subset of Beta representative clients of Release. In our application, we still have two cohorts, i.e., Beta and Release data sets for a given Firefox version (N). However, we do not have a single outcome, as we do not have a _treatment_. Rather, we are trying to equate (or _balance_) the Beta and Release data sets to resemble each other across the covariates we are concerned with. This is our outcome, so to speak.

In this current work, we focus on **user engagement metrics** as the chosen use-case. Also to validate the resultant matching model, we follow two different strategies. First, we balance the data sets on a set of training covariates (i.e., environment, machine configuration, performance  and usage metrics), then look at the difference in the user engagement metrics between the balanced Beta and Release for a same Firefox version (v67). *This gives us an idea of how clients with similar environments and performance resemble Release in terms of usage*. In the second, we are more interested in balancing the data sets to resemble each other across the covariates we are concerned with, but now over several versions (v67 and v68). *This gives us an idea of how these users do indeed change in time*.

For both strategies, we apply the same experimental setup. The only difference is in the considered Firefox version we were comparing. In the [first strategy](#first), our main objective was to inform how users Beta are different concerning Release in terms of user engagement, with all the other training covariates being equal. Our findings show the matching worked well, in general. However, for a subset of covariates, the difference between channels actually increased (e.g., `num_pages`, `num_pages_max`, `daily_unique_domains` and `daily_unique_domains_max`), or are relatevly different than Release before and after matching, namely `active_hours`, `active_hours_max`, `uri_count`, and `uri_count_max`. Besides, we observe that these Beta users are very similar to Release ones regarding search count and daily tabs opened.

In the [second strategy](#second), our main objective was to determine if the user engagement metrics changed in the newest Beta version concerning the previous Release version. Overall, the matching yielded a subset that was similarly representative to v67 as to v68 for most of the covariates reviewed. However, for a subset of covariates, the difference between channels actually decreased (`num_pages`, `num_pages_max`, `daily_unique_domains` and `daily_max_tabs`).

```{r eval=FALSE, include=FALSE}
save.image(file = "final_report.RData", compress=TRUE)
```

### 2020-04-09 poc/EDA/EDA.Rmd

@@
 library(emdist)
+library(ggridges)
+library(cowplot)
 ```
@@
 
-#### Training
-
-```{r fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
-par(mfrow = c(2, 2))  ## Set up a 2 x 2 plotting space
+```{r fig.height=9, fig.width=9, message=FALSE, warning=FALSE}
+par(mfrow = c(4, 2))  ## Set up a 2 x 3 plotting space
 
@@
 for (i in user_eng) {
-  x <- df_beta_ue[,i]
-  y <- df_release_ue[,i]
 
-  rg <- range(x, y, na.rm=T)
+  # Training
+  x_t <- df_beta_ue[,i]
+  y_t <- df_release_ue[,i]
 
-  test <- ks.test(x, y)$statistic
-  # pvalue <- ks.test(x, y)$p.value
+  rg_t <- range(x_t, y_t, na.rm=T)
 
-  test <- paste("KS Test = ", round(test, 3))
-  # pvalue <- paste("P-value = ", round(pvalue, 3))
+  test_t <- ks.test(x_t, y_t)$statistic
+  test_t <- paste("KS Test = ", round(test_t, 3))
 
-  qqplot(x, y, main=i, xlim=rg, ylim=rg, xlab = "Beta", ylab = "Release", pch = 1)
+  # Validation
+
+  x_v <- df_beta_v_ue[,i]
+  y_v <- df_release_v_ue[,i]
+
+  rg_v <- range(x_v, y_v, na.rm=T)
+
+  test_v <- ks.test(x_v, y_v)$statistic
+  test_v <- paste("KS Test = ", round(test_v, 3))
+
+  ########
+
+  title_t <- paste('V67', i, sep='\n')
+  qqplot(x_t, y_t, main=title_t, xlim=rg_t, ylim=rg_t, xlab = "Beta", ylab = "Release", pch = 1)
   # mtext(test, side=3)
-  text(min(x), max(x), test, adj=c(0,1))
-  abline(0,1, col="red", lty=2)  
+  text(min(x_t), (if(max(x_t) > max(y_t)) max(x_t) else max(y_t)), test_t, adj=c(0,1))
+  abline(0,1, col="#fe346e", lty=2)
+
+  title_v <- paste('V68', i, sep='\n')
+  qqplot(x_v, y_v, main=title_v, xlim=rg_v, ylim=rg_v, xlab = "Beta", ylab = "Release", pch = 1)
+  # mtext(test, side=3)
+  text(min(x_v), (if(max(x_v) > max(y_v)) max(x_v) else max(y_v)), test_v, adj=c(0,1))
+  abline(0,1, col="#fe346e", lty=2)  
 }
 ```
-
-#### Validation
-
-```{r fig.height=8, fig.width=8, message=FALSE, warning=FALSE}
-par(mfrow = c(2, 2))  ## Set up a 2 x 2 plotting space
-
-## QQ plot in R to compare two data samples
-for (i in user_eng) {
-  x <- df_beta_v_ue[,i]
-  y <- df_release_v_ue[,i]
-
-  rg <- range(x, y, na.rm=T)
-
-  test <- ks.test(x, y)$statistic
-  # pvalue <- ks.test(x, y)$p.value
-
-  test <- paste("KS Test = ", round(test, 3))
-  # pvalue <- paste("P-value = ", round(pvalue, 3))
-
-  qqplot(x, y, main=i, xlim=rg, ylim=rg, xlab = "Beta", ylab = "Release", pch = 1)
-  # mtext(test, side=3)
-  text(min(x), max(x), test, adj=c(0,1))
-  abline(0,1, col="red", lty=2)  
-}
-```
-
-------
 
@@
 * Comparing only the training and validation plots, we can observe large differences between the variables. Only a few showed similar distances (marked in green)
+
+### Violin Plots
+
+The following violin plots depicts distributions for the beta and release subsets, for both versions v67 and v68.
+Violin plot is a powerful data visualization technique since it allows to compare both the **ranking** of several groups and their **distribution**.
+
+**NOTE:** Guiding lines have been added for the following:
+
+* <span style="color:red">red</span> dashed: Release mean
+* <span style="color:blue">blue</span> dashed: Beta mean
+* <span style="color:red">red</span> solid: Release median
+* <span style="color:blue">blue</span> solid: Beta median
+
+```{r fig.height=10, fig.width=15, message=FALSE, warning=FALSE}
+
+## Violin plots
+for (i in user_eng) {
+  df_validate_means <- df_validate_ue %>%
+  group_by(label) %>%
+  summarise(value = mean(eval(as.name(i))))
+
+  df_validate_medians <- df_validate_ue %>%
+  group_by(label) %>%
+  summarise(value = median(eval(as.name(i))))
+
+  df_train_means <- df_train_ue %>%
+  group_by(label) %>%
+  summarise(value = mean(eval(as.name(i))))
+
+  df_train_medians <- df_train_ue %>%
+  group_by(label) %>%
+  summarise(value = median(eval(as.name(i))))
+
+  ###########
+
+  violin_train <- ggplot(df_train_ue, aes(x=label, y=eval(as.name(i)), fill=label)) + 
+  geom_violin(trim=FALSE) +
+  labs(title=i,x="Channel", y = "Measure") + 
+  scale_fill_manual(values=c("#111d5e", "#b21f66")) +
+  geom_hline(
+    data = df_train_means,
+    aes(yintercept = value, colour = label),
+    linetype = "dashed",
+    size = 1
+  ) +
+  geom_hline(
+    data = df_train_medians,
+    aes(yintercept = value, colour = label),
+    linetype = "solid",
+    size = 1
+  ) + scale_colour_manual(values=c("blue", "red")) +
+  geom_boxplot(width=0.1, fill="white", alpha=0.5) + 
+  theme_minimal() + theme(legend.position="none") + coord_flip()
+
+  violin_valid <- ggplot(df_validate_ue, aes(x=label, y=eval(as.name(i)), fill=label)) + 
+  geom_violin(trim=FALSE) +
+  labs(title=i,x="Channel", y = "Measure") + 
+  scale_fill_manual(values=c("#111d5e", "#b21f66")) +
+  geom_hline(
+    data = df_validate_means,
+    aes(yintercept = value, colour = label),
+    linetype = "dashed",
+    size = 1
+  ) +
+  geom_hline(
+    data = df_validate_medians,
+    aes(yintercept = value, colour = label),
+    linetype = "solid",
+    size = 1
+  ) + scale_colour_manual(values=c("blue", "red")) +
+  geom_boxplot(width=0.1, fill="white", alpha=0.5) + 
+  theme_minimal() + theme(legend.position="none") + coord_flip()
+
+  print(plot_grid(violin_train, violin_valid, ncol = 1,labels = c('V67','V68')))
+}
+```
+
+### Observations
+
+The violin plots above show the relationship of channel type to user engagement metrics.
+Overall, the results were quite similar comparing the two versions (v67 and v68).
+Only the following metrics yielded different results:
+
+* `active_hours_max`
+* `daily_unique_domains_max`
+
+Now, let's take a closer look at the similar comparative results:
+
+> Which variables presented **similar/equal** means and medians for beta and release users?
+
+* `uri_count`
+* `uri_count_max`
+* `session_length_max`
+* `search_count`
+* `search_count_max`
+* `daily_unique_domains`
+* `daily_tabs_opened_max`
+* `install_year`
+* `profile_age`
+* `memory_mb`
+* `cpu_speed_mhz`
+
+> Which variables presented **higher** release users means and/or medians than betas?
+
+* `num_active_days`
+* `active_hours`
+* `num_pages`
+* `num_pages_max`
+* `daily_num_sessions_started`
+* `daily_num_sessions_started_max`
+* `cpu_cores`
+
+> Which variables presented **lower** release users means and/or medians than betas?
+
+* `session_length`
+* `num_addons`
+* `daily_tabs_opened`
+* `timezone_offset`
+* `cpu_l2_cache_kb`
+
+Four variables became difficult to visualize through the violin plot. So we will plot ridgeline charts.
+
+```{r fig.height=10, fig.width=15, message=FALSE, warning=FALSE}
+vlist <- c('num_bookmarks','daily_max_tabs','daily_max_tabs_max','startup_ms')
+
+## Ridgeline  plots
+for (i in vlist) {
+  ridge_train <- ggplot(df_train_ue, aes(x = eval(as.name(i)), y = label, fill = label)) +
+  geom_density_ridges(alpha=0.6, stat="binline", bins=20) +
+  labs(title=i,x="Channel", y = "Measure") + 
+  theme_ridges() + 
+  scale_fill_manual(values=c("#111d5e", "#b21f66")) +
+  theme(legend.position = "none")
+
+  ridge_valid <- ggplot(df_validate_ue, aes(x = eval(as.name(i)), y = label, fill = label)) +
+  geom_density_ridges(alpha=0.6, stat="binline", bins=20) +
+  labs(title=i,x="Channel", y = "Measure") + 
+  theme_ridges() + 
+  scale_fill_manual(values=c("#111d5e", "#b21f66")) +
+  theme(legend.position = "none")
+
+  print(plot_grid(ridge_train, ridge_valid, ncol = 1,labels = c('V67','V68')))
+}
+```
 
@@
         main = "Beta", #Give your chart a title
-        ylim=c(0,1), border=F, col = "#ffd271",
+        ylim=c(0,1), border=F, col = "#111d5e",
         xlab = i, #Label the x axis
@@
         main = "Release", #Give your chart a title
-        ylim=c(0,1), border=F, col = "#f65c78",
+        ylim=c(0,1), border=F, col = "#b21f66",
         xlab = i, #Label the x axis

### 2020-04-09 poc/matchIt/feature_selection.Rmd

--- 2020-02-17 poc/matchIt/feature_selection.Rmd
@@
 ```{r data_load, echo=FALSE}
-load("~/GitHub/ff-beta-release-matching/poc/matchIt/feature_engineering.RData")
+load("~/ff-beta-release-matching/poc/matchIt/feature_selection.RData")
+```
+
+```{r}
+filter_features <- function(df_train_sm){
+  df_fs <- df_train_sm %>%
+   select(-engagement) %>%
+   select(-content_crashes) %>%
+   select(-client_id) %>%
+   select(-label_beta) %>%
+   select(-label_release) %>%
+   select(-is_release) %>%
+   select(-app_version)
+  return(df_fs)
+}
 ```
@@
 set.seed(1234)
-df_train_sm <- df_train_encoder %>%
-   sample_n(1000)
-
-df_fs <- df_train_sm %>%
-   select(-engagement) %>%
-   select(-content_crashes) %>%
-   select(-client_id) %>%
-   select(-label_beta) %>%
-   select(-label_release) %>%
-   select(-is_release) %>%
-   select(-app_version)
+df_train_sm <- df_train_encoder %>% sample_n(10000)
+df_fs <- filter_features(df_train_sm)
 ```
@@
 boruta_results <- list()
+
 for (metric in engagement){
@@
   boruta_results[[metric]]  <- boruta.out
-  # plot(boruta.out, cex.axis=.7, las=2, xlab="", main=metric) 
 }
@@
 
-```{r boruta_plots}
-for (metric in names(boruta_results)){
+```{r boruta_plots, fig.height=7, fig.width=15}
+for (metric in engagement){
   plot(boruta_results[[metric]], cex.axis=.7, las=2, xlab="", main=metric)
@@
 
-Find the top 5 ranking features per metric, and add to a list.
+> Find the top 5 ranking features per metric, and add to a list.
 
@@
 features_top5 <- NULL
-for(metric in names(boruta_results)){
+
+for(metric in engagement){
   features_top5 <- c(names(sort(apply(boruta_results[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:5]), features_top5)
 }
-knitr::kable(data.frame(top5 = sort(c(unique(features_top5)))))
+
+top5 <- sort(c(unique(features_top5)))
+x <- data.frame(top5)
+kable(x) %>%
+kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
+scroll_box(width = "100%")
 ```
 
-Increasing to 10:
+> Increasing to 10:
 
@@
 features_top10 <- NULL
-for(metric in names(boruta_results)){
+
+for(metric in engagement){
   features_top10 <- c(names(sort(apply(boruta_results[[metric]]$ImpHistory, 2, median), decreasing = TRUE)[1:10]), features_top10)
 }
-knitr::kable(data.frame(top10 = sort(c(unique(features_top10)))))
+
+top10 <- sort(c(unique(features_top10)))
+x <- data.frame(top10)
+kable(x) %>%
+kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
+scroll_box(width = "100%")
 ```
@@
   bind_rows(df_beta) %>%
-   sample_n(1000)
+   sample_n(10000)
 df_fs_eq <- df_train_f_sm_eq %>%
@@
   boruta_results_eq[[metric]]  <- boruta.out
-  # plot(boruta.out, cex.axis=.7, las=2, xlab="", main=metric) 
 }
@@
 
+> Find the top 5 ranking features per metric, and add to a list.
+
 ```{r aggregate_features_5_eq}
@@
 }
-knitr::kable(data.frame(top5 = sort(c(unique(features_top5)))))
+
+x <- data.frame(top5 = sort(c(unique(features_top5))))
+kable(x) %>%
+kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
+scroll_box(width = "100%")
 ```
 
-Increasing to 10:
+> Increasing to 10:
 

### 2020-04-09 poc/matchIt/model_selection.Rmd

---
title: "Beta to Release Matching: Model Selection"
author: "Mariana de Oliveira Santos Silva"
date: 'Last Updated: `r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    theme: "flatly"
    toc: true
    toc_float: true
    code_folding: "hide"
    highlight: tango
---

```{r include=FALSE}
generate_formula <- function(tr_cov, label){
  # Focus on linear and no-interactions
  return(as.formula(paste(label, '~', paste(tr_cov, collapse="+"))))
}
```

# Introduction

The main objective of this notebook is to perform several different matching methods in experiment 3 (which was the experiment that presented the best results in the previous work) to select the best model.

# Loading the data

```{r message=FALSE, warning=FALSE, include=FALSE}
## Loading the needed libraries

library(kableExtra)      # help you build common complex tables and manipulate table styles
library(DataExplorer)    # automated data exploration
library(tidyverse)       # for general data wrangling (includes readr and dplyr)
library(ggplot2)         # to draw statistical plots 
library(dplyr)           # for data frame manipulation
library(MatchIt)
library(optmatch)
library(cem)
library(RItools)
library(magrittr)
library(tidyr)
library(tidyselect)
library(grt)
library(tableone)
library(cobalt)

label <- 'is_release'
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
## Loading the training dataset
load('~/ff-beta-release-matching/poc/matchIt/modeling.RData')
```

# Model Selection

In short, the prior results showed that the model using *Nearest Neighbor matching* with stratified sampling outperformed the other models. In particular, the `experiment 3` (regarding to the results of feature selection with stratified sampling, considering the top 5 features) presented the best results for most of the tested models. However, the results could be further improved. So, before move on to the last phase (the model validation), we can try using other matching strategies. Now that we have selected the best expirement.

## Match using Coarsened Exact Matching (CEM): Small Dataset

```{r message=FALSE, warning=FALSE}
cem <- matchit(formula = generate_formula(exp_3, label), df_1x_sm, 'cem')
res <- match.data(cem)
cem_models_1x <- cem
cem_results_1x <- res
print(summary(cem))
```

## Match using Coarsened Exact Matching (CEM): Full Dataset

```{r message=FALSE, warning=FALSE}
cem_full <- matchit(formula = generate_formula(exp_3, label), df_1x, 'cem')
res_full <- match.data(cem_full)
cem_full_models_1x <- cem_full
cem_full_results_1x <- res_full
print(summary(cem_full))
```

## Match using Nearest Neighbor matching: Small Dataset

```{r message=FALSE, warning=FALSE}
nn <- matchit(formula = generate_formula(exp_3, label), df_1x_sm, 'nearest', replace = TRUE)
res <- match.data(nn)
nn_models_1x <- nn
nn_results_1x <- res
print(summary(nn))
```

## Match using Nearest Neighbor matching: Full Dataset

```{r message=FALSE, warning=FALSE}
nn_full <- matchit(formula = generate_formula(exp_3, label), df_1x, 'nearest', replace = TRUE)
res <- match.data(nn_full)
nn_full_models_1x <- nn_full
nn_full_results_1x <- res
print(summary(nn_full))
```

## Match using Nearest Neighbor matching: Small Dataset - Mahalanobis

```{r message=FALSE, warning=FALSE}
nn.ma <- matchit(formula = generate_formula(exp_3, label), df_1x_sm, 'nearest', distance='mahalanobis')
res <- match.data(nn.ma)
nn.ma_models_1x <- nn.ma
nn.ma_results_1x <- res
print(summary(nn.ma))
```

## Match using Nearest Neighbor matching: Full Dataset - Mahalanobis

```{r message=FALSE, warning=FALSE}
nn.ma_full <- matchit(formula = generate_formula(exp_3, label), df_1x, 'nearest', distance='mahalanobis')
res <- match.data(nn.ma_full)
nn.ma_full_models_1x <- nn.ma_full
nn.ma_full_results_1x <- res
print(summary(nn.ma_full))
```

## Match using Subclassification matching: Small Dataset

```{r message=FALSE, warning=FALSE}
sub <- matchit(formula = generate_formula(exp_3, label), df_1x_sm, 'subclass')
res <- match.data(sub)
sub_models_1x <- sub
sub_results_1x <- res
print(summary(sub))
```

## Match using Subclassification matching: Full Dataset

```{r message=FALSE, warning=FALSE}
sub_full <- matchit(formula = generate_formula(exp_3, label), df_1x, 'subclass')
res <- match.data(sub_full)
sub_full_models_1x <- sub_full
sub_full_results_1x <- res
print(summary(sub_full))
```

---

## Graphical Comparison

```{r}
small <- list(cem_models_1x = cem_models_1x, nn_models_1x = nn_models_1x, nn.ma_models_1x = nn.ma_models_1x, sub_models_1x = sub_models_1x)

full <- list(cem_full_models_1x = cem_full_models_1x, nn_full_models_1x = nn_full_models_1x, nn.ma_full_models_1x = nn.ma_full_models_1x, sub_full_models_1x = sub_full_models_1x)
```

* Note that we want to see if the Matched Treated (beta) and Matched Control (release) distributions are roughly similar.

### Small Dataset

```{r fig.height=7, fig.width=14}
for (model in names(small)){
  print(paste(model))
  if (model != "nn.ma_models_1x"){
    plot(small[[model]], type = "hist", col = "#111d5e")
    plot(small[[model]], type = "jitter", col = "#111d5e", interactive = F)
  } else {
    print(paste("Not appropriate for pure Mahalanobis matching. No plots generated."))
  }
}
```

### Full Dataset

```{r fig.height=7, fig.width=14}
for (model in names(full)){
  print(paste(model))
  if (model != "nn.ma_full_models_1x"){
    plot(full[[model]], type = "hist", col = "#111d5e")
    plot(full[[model]], type = "jitter", col = "#111d5e", interactive = F)
  } else {
    print(paste("Not appropriate for pure Mahalanobis matching. No plots generated."))
  }
}
```

---

### Observations

* Although it was not possible to graphically compare the results using the Nearest Neighbor matching with Mahalanobis distance, from the summary, we can see that those models outperformed the others. Analyzing each of the covariates, we have:

#### Small Dataset

```{r fig.height=7, fig.width=14}
for (v in exp_3){
  p <- bal.plot(nn.ma_models_1x, var.name = v, colors = c("#111d5e", "#611e62"))
  print(p)
}
```

#### Full Dataset

```{r fig.height=7, fig.width=14}
for (v in exp_3){
  p <- bal.plot(nn.ma_full_models_1x, var.name = v, colors = c("#111d5e", "#611e62"))
  print(p)
}
```

* The figures show that the model containing the entire dataset was better than sampling. 
* In addition, the main problem is displayed mainly in pageload metrics.

### 2021-11-04 perf_release_criteria/milestone_3/feature_selection/feature_selection_nn_gam_logit_f.Rmd

--- 2019-10-25 perf_release_criteria/milestone_3/feature_selection_nn_gam_logit.Rmd
@@
 
-```{r data_load, echo=FALSE}
-file_name = 'df_train_validate_20191021.RData'
+```{r data_load, echo=FALSE, message=FALSE}
+file_name = 'df_train_validate_20191025.RData'
 image_file_path = file.path('data', file_name)
@@
 # Pull from GCP if necessary
-# library(googleCloudStorageR)
-# Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
-#            "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")
-# gcs_get_object(file.path('data', 'milestone2', file_name), saveToDisk = image_file_path, overwrite = TRUE)
+if (!file.exists(image_file_path)){
+  Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
+           "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")
+  library(googleCloudStorageR)
+  gcs_get_object(file.path('data', 'milestone2', file_name), saveToDisk = image_file_path, overwrite = TRUE)
+}
 
@@
 print(res_fs1_noreplace)
+```
+
+# FS 1 Interactions
+
+Feature selection on only performance metrics, but including interaction terms.
+
+```{r fs1_int, error=TRUE}
+res_fs1_int <- list()
+for (bt in names(bts)){
+  res_fs1_int[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, workers = 10, add_interactions=TRUE,
+                                      replace=TRUE, distance = 'linear.logit')
+}
+save.image(results_file_path)
+print(res_fs1_int)
+```
+
+```{r fs1_int_noreplace, error=TRUE}
+res_fs1_int_noreplace <- list()
+for (bt in names(bts)){
+  res_fs1_int_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, add_interactions=TRUE,
+                                                replace=FALSE, workers = 10, distance = 'linear.logit')
+}
+save.image(results_file_path)
+print(res_fs1_int_noreplace)
 ```

### 2021-11-04 perf_release_criteria/milestone_3/feature_selection/feature_selection_nn_logit.Rmd

--- 2019-10-25 perf_release_criteria/milestone_3/feature_selection_nn_gam_logit.Rmd
@@
 ---
-title: "Milestone 2: Feature Selection - Nearest Neighbors, GAM Logit"
+title: "Milestone 2: Feature Selection - Nearest Neighbors, Logit"
 author: "Corey Dow-Hygelund, Mozilla Data Science"
@@
 
-**Matching Algorithm Tested**: Nearest-neighbors with GAM logit distance metric
+**Matching Algorithm Tested**: Nearest-neighbors with logit distance metric
 
@@
 
-results_file_name <- 'feature_selection_nn_gam_logit.RData' 
+results_file_name <- 'feature_selection_nn_logit.RData' 
 results_file_path <- file.path('data', results_file_name)
@@
 for (bt in names(bts)){
-  res_fs1[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
+  res_fs1[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, replace=TRUE, workers = 10, distance = 'logit')
 }
@@
 for (bt in names(bts)){
-  res_fs1_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
+  res_fs1_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs1, size=NULL, replace=FALSE, workers = 10, distance = 'logit')
 }
@@
 for (bt in names(bts)){
-  res_fs2[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
+  res_fs2[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, replace=TRUE, workers = 10, distance = 'logit')
 }
@@
 for (bt in names(bts)){
-  res_fs2_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
+  res_fs2_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, replace=FALSE, workers = 10, distance = 'logit')
 }
@@
 for (bt in names(bts)){
-  res_fs3[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
+  res_fs3[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, replace=TRUE, workers = 10, distance = 'logit')
 }
@@
 for (bt in names(bts)){
-  res_fs3_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
+  res_fs3_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs3, size=NULL, replace=FALSE, workers = 10, distance = 'logit')
 }
@@
 for (bt in names(bts)){
-  res_fs4[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
+  res_fs4[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, replace=TRUE, workers = 10, distance = 'logit')
 }
@@
 for (bt in names(bts)){
-  res_fs4_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
+  res_fs4_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs4, size=NULL, replace=FALSE, workers = 10, distance = 'logit')
 }
@@
 for (bt in names(bts)){
-  res_fs5[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
+  res_fs5[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, replace=TRUE, workers = 10, distance = 'logit')
 }
@@
 for (bt in names(bts)){
-  res_fs5_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
+  res_fs5_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs5, size=NULL, replace=FALSE, workers = 10, distance = 'logit')
 }
@@
 for (bt in names(bts)){
-  res_fs6[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
+  res_fs6[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, replace=TRUE, workers = 10, distance = 'logit')
 }
@@
 for (bt in names(bts)){
-  res_fs6_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
+  res_fs6_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs6, size=NULL, replace=FALSE, workers = 10, distance = 'logit')
 }
@@
 for (bt in names(bts)){
-  res_fs7[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, replace=TRUE, workers = 10, distance = 'GAMlogit')
+  res_fs7[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, replace=TRUE, workers = 10, distance = 'logit')
 }
@@
 for (bt in names(bts)){
-  res_fs7_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, replace=FALSE, workers = 10, distance = 'GAMlogit')
+  res_fs7_noreplace[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs7, size=NULL, replace=FALSE, workers = 10, distance = 'logit')
 }

### 2021-11-04 perf_release_criteria/milestone_3/feature_selection/feature_selection_nn_logit_linear.Rmd

--- 2019-10-28 perf_release_criteria/milestone_3/feature_selection_nn_logit_linear.Rmd
@@
 ```{r fs2_int, error=TRUE}
-res_fs2 <- list()
-for (bt in names(bts)){
-  res_fs2[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, add_interactions=TRUE,
-                                      replace=TRUE, workers = 10, distance = 'linear.logit')
-}
-save.image(results_file_path)
-print(res_fs2)
+# res_fs2 <- list()
+# for (bt in names(bts)){
+#   res_fs2[[bt]] <- perform_matchit_fs(df_train_f, bts[[bt]], fs2, size=NULL, add_interactions=TRUE,
+#                                       replace=TRUE, workers = 10, distance = 'linear.logit')
+# }
+# save.image(results_file_path)
+# print(res_fs2)
 ```

### 2021-11-04 perf_release_criteria/milestone_3/hyperparameter_tuning/hyperparameter_tuning_nn_malahanobis.Rmd

@@
 # Pull from GCP if necessary
-# library(googleCloudStorageR)
-# Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
-#            "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")
-# gcs_get_object(file.path('data', 'milestone2', file_name), saveToDisk = image_file_path, overwrite = TRUE)
+if (!file.exists(image_file_path)){
+  Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
+           "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")
+  library(googleCloudStorageR)
+  gcs_get_object(file.path('data', 'milestone2', file_name), saveToDisk = image_file_path, overwrite = TRUE)
 
+}
 load(image_file_path)
@@
 
-To investigate, and possible utilize, a more general model, the second highest suite of features will also be tested:
+To investigate, and possible utilize, a more general model, two other suite of high scoring features will also be tested:
 
+1. Contains performance metrics
     * Beta oversapmling by 16x
     * FS 3: Performance metrics and highest found by Boruta with equal labels dataset
+2. No performance metrics: 
+    * Beta oversapmling by 8x
+    * FS 5: Highest found by Boruta
 
@@
 
-* Matching order (m.order)
-* Caliper
-* of control to treatments
+* `replace`: Can each control unit be matched to more than one treated unit?
+* `caliper`:  The number of standard deviations of the distance measure within which to draw control units.
+* `calclosest`: Whether to take the nearest available match if no matches are available within the `caliper`.
+* `ratio`: #  of control units to match to each test.
 
@@
 # FS 1
+## Coarse Grid
 Hyperparameter tuning on optimal features.
@@
 
-perform_matchit_hp_tune(df_train_f, bt[[1]], fs1, size=5000, workers = 10, hps_grid = hps_grid, distance = "mahalanobis")
+fs1_results <- perform_matchit_hp_tune(df_train_f, bt, fs1, size=NULL, workers = 64, hps_grid = hps_grid, distance = "mahalanobis")
+save(list=ls(pattern = 'fs[0-9]_results'),  file = results_file_path)
+
+fs1_results_df <- fs1_results %>% bind_rows()
+fs1_results_df %>% group_by_at(setdiff(names(fs1_results_df), "scores")) %>% 
+  summarise(mean = mean(scores), sd = sd(scores), median = median(scores)) -> fs1_results_df
+knitr::kable(fs1_results_df[order(fs1_results_df$mean), ] %>% head(n=20))
+
 ```
+
+## Fine Grid
+
+```{r hp_fine}
+hps_fine <- list(
+  replace = c(FALSE),
+  caliper = seq(0, 3, by=0.2),
+  calclosest = c(TRUE, FALSE),
+  ratio = c(1, 2)
+)
+
+hps_fine_grid = expand.grid(hps_fine)
+```
+
+```{r fs1_fine, error=TRUE}
+hps_fine_grid = expand.grid(hps_fine)
+
+fs1_results_final <- perform_matchit_hp_tune(df_train_f, bts[['bts_4x']], fs1, size=NULL, workers = 64, hps_grid = hps_fine_grid, 
+                                       distance = "mahalanobis", add_interactions=FALSE)
+save(list=ls(pattern = 'fs[0-9]_results'),  file = results_file_path)
+
+fs1_results_df <- fs1_results_final %>% bind_rows()
+fs1_results_df %>% group_by_at(setdiff(names(fs1_results_df), "scores")) %>% 
+  summarise(mean = mean(scores), sd = sd(scores), median = median(scores)) -> fs1_results_df
+knitr::kable(fs1_results_df[order(fs1_results_df$median), ] %>% head(20))
+```
+
+# FS 3
+
+```{r fs3, error=TRUE}
+fs3_results <- perform_matchit_hp_tune(df_train_f, bts[['bts_16x']], fs3, size=NULL, workers = 64, hps_grid = hps_grid, distance = "mahalanobis")
+save(list=ls(pattern = 'fs[0-9]_results'),  file = results_file_path)
+
+fs3_results_df <- fs3_results %>% bind_rows()
+fs3_results_df %>% group_by_at(setdiff(names(fs3_results_df), "scores")) %>% 
+  summarise(mean = mean(scores), sd = sd(scores), median = median(scores)) -> fs3_results_df
+knitr::kable(fs3_results_df[order(fs3_results_df$median), ] %>% head(n=20))
+```
+
+# FS 5
+
+```{r fs5, error=TRUE}
+fs5_results <- perform_matchit_hp_tune(df_train_f, bts[['bts_8x']], fs5, size=NULL, workers = 64, hps_grid = hps_grid, distance = "mahalanobis")
+save(list=ls(pattern = 'fs[0-9]_results'),  file = results_file_path)
+
+fs5_results_df <- fs5_results %>% bind_rows()
+fs5_results_df %>% group_by_at(setdiff(names(fs5_results_df), "scores")) %>% 
+  summarise(mean = mean(scores), sd = sd(scores), median = median(scores)) -> fs5_results_df
+knitr::kable(fs5_results_df[order(fs5_results_df$median), ])
+```
+
+# Push to GCP
+Save the resultant dataset and bootstrap samples to an R image.
+
+```{r gcp_storage_push, warning=FALSE}
+gcs_file_path <- file.path('data', 'milestone2', results_file_name)
+
+Sys.setenv("GCS_DEFAULT_BUCKET" = "moz-fx-dev-subbeta",
+           "GCS_AUTH_FILE" = "moz-fx-dev-cdowhyglund-subBeta-788f8f0d4627.json")
+
+library(googleCloudStorageR)
+
+upload_try <- gcs_upload(results_file_path, name = gcs_file_path)
+upload_try
+```

### 2021-11-04 perf_release_criteria/milestone_3/ms_2_dataset_generation.Rmd

@@
 
-df_train <- load_df('data/df_pd_67.csv')
-df_validate <- load_df('data/df_pd_68.csv')
+df_train <- load_df('data/df_pd_67_20191026.csv')
+df_validate <- load_df('data/df_pd_68_20191026.csv')
 ```
@@
 The feature selection will utilize 10 boostrap replicates, which are generated as follows:
+
 1. The entire `df_train` dataset is sampled at 100% with replacement.
 2. A sample of Release (`is_release = TRUE`) `client_id` are taken of the same size as Beta (`r channel_counts$n[channel_counts$label == 'beta']`)
-3. The entire (resampled) Beta `client_id` are combined with this sampled Release ids. 
+3. The entire (resampled) Beta `client_id` are combined with these sampled Release ids. 
     - These are the profiles that will be used for building the matching model. 

### 2021-11-04 perf_release_criteria/milestone_3/ms_2_validation.Rmd

@@
 
+extract_predictions <- function(matched, validation){
+  prediction <- validation %>%
+    filter(client_id %in% matched$client_id)
+
+  return(prediction)
+}
 ```
@@
 ```{r nn_mal_fs1, echo=FALSE}
-nn.mal.fs1 <- train_matchit(dfs[['4']], fs1, add_interactions = FALSE, replace = FALSE, 
-                        caliper = 0.25, calclosest = TRUE, ratio = 2, distance = "mahalanobis")
-nn.mal.fs1.qq <- build_quantile_df(df_rel_val, nn.mal.fs1$matched, df_beta_val)
-nn.mal.fs1.score <- score_model(bts, nn.mal.fs1$matched, df_rel_val)
-nn.mal.fs1.score
+# nn.mal.fs1 <- train_matchit(dfs[['4']], fs1, add_interactions = FALSE, replace = FALSE, 
+#                         caliper = 0.25, calclosest = TRUE, ratio = 2, distance = "mahalanobis")
+nn.mal.fs1.predictions <- extract_predictions(nn.mal.fs1$matched, df_beta_val)
+nn.mal.fs1.qq <- build_quantile_df(df_rel_val, nn.mal.fs1.predictions, df_beta_val)
+nn.mal.fs1.score <- score_model(bts, nn.mal.fs1.predictions, df_rel_val)
+# nn.mal.fs1.score
 ```
 
-Number of Beta samples: `r nrow(nn.mal.fs1$matched)`
+Resultant scores: `r nn.mal.fs1.score`
+
+* Number of matched Beta training samples: `r nrow(nn.mal.fs1$matched)`
+* Number of matched Beta validation samples: `r nrow(nn.mal.fs1.predictions)`
 
 ```{r nn_mal_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
-plot_validation_results(df_rel_val, nn.mal.fs1$matched, df_beta_val, nn.mal.fs1.qq)
+plot_validation_results(df_rel_val, nn.mal.fs1.predictions, df_beta_val, nn.mal.fs1.qq)
 ```
@@
 ```{r nn_mal_fs3, echo=FALSE}
-nn.mal.fs3 <- train_matchit(dfs[['16']], fs3, add_interactions = FALSE, replace = TRUE, 
-                        caliper = 3.00, calclosest = TRUE, ratio = 1, distance = "mahalanobis")
-nn.mal.fs3.qq <- build_quantile_df(df_rel_val, nn.mal.fs3$matched, df_beta_val)
-nn.mal.fs3.score <- score_model(bts, nn.mal.fs3$matched, df_rel_val)
-nn.mal.fs3.score
+# nn.mal.fs3 <- train_matchit(dfs[['16']], fs3, add_interactions = FALSE, replace = TRUE, 
+#                         caliper = 3.00, calclosest = TRUE, ratio = 1, distance = "mahalanobis")
+nn.mal.fs3.predictions <- extract_predictions(nn.mal.fs3$matched, df_beta_val)
+nn.mal.fs3.qq <- build_quantile_df(df_rel_val, nn.mal.fs3.predictions, df_beta_val)
+nn.mal.fs3.score <- score_model(bts, nn.mal.fs3.predictions, df_rel_val)
+# nn.mal.fs3.score
 ```
-Number of Beta samples: `r nrow(nn.mal.fs3$matched)`
+
+Resultant scores: `r nn.mal.fs3.score`
+
+* Number of matched Beta training samples: `r nrow(nn.mal.fs3$matched)`
+* Number of matched Beta validation samples: `r nrow(nn.mal.fs3.predictions)`
 
 ```{r nn_mal_fs3_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
-plot_validation_results(df_rel_val, nn.mal.fs3$matched, df_beta_val)
+plot_validation_results(df_rel_val, nn.mal.fs3.predictions, df_beta_val)
 ```
@@
 ```{r nn_mal_fs5, echo=FALSE}
-nn.mal.fs5 <- train_matchit(dfs[['8']], fs5, add_interactions = FALSE, replace = TRUE, 
-                        caliper = 0, calclosest = TRUE, ratio = 1, 
-                        distance = "mahalanobis")
-nn.mal.fs5.qq <- build_quantile_df(df_rel_val, nn.mal.fs5$matched, df_beta_val)
-nn.mal.fs5.score <- score_model(bts, nn.mal.fs5$matched, df_rel_val)
-nn.mal.fs5.score
+# nn.mal.fs5 <- train_matchit(dfs[['8']], fs5, add_interactions = FALSE, replace = TRUE, 
+#                         caliper = 0, calclosest = TRUE, ratio = 1, 
+#                         distance = "mahalanobis")
+nn.mal.fs5.predictions <- extract_predictions(nn.mal.fs5$matched, df_beta_val)
+nn.mal.fs5.qq <- build_quantile_df(df_rel_val, nn.mal.fs5.predictions, df_beta_val)
+nn.mal.fs5.score <- score_model(bts, nn.mal.fs5.predictions, df_rel_val)
+# nn.mal.fs5.score
 ```
 
-Number of Beta samples: `r nrow(nn.mal.fs5$matched)`
+Resultant scores: `r nn.mal.fs5.score`
+
+* Number of matched Beta training samples: `r nrow(nn.mal.fs5$matched)`
+* Number of matched Beta validation samples: `r nrow(nn.mal.fs5.predictions)`
 
 ```{r nn_mal_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
-plot_validation_results(df_rel_val, nn.mal.fs5$matched, df_beta_val)
+plot_validation_results(df_rel_val, nn.mal.fs5.predictions, df_beta_val)
 ```
@@
 ```{r nn_logit_fs1, warning=FALSE, error=FALSE, echo=FALSE}
-nn.linear.logit.fs1 <- train_matchit(dfs[['4']], fs1, add_interactions = TRUE, replace = FALSE, 
-                        caliper = 0.4, calclosest = TRUE, ratio = 3, distance = "linear.logit")
-nn.linear.logit.fs1.qq <- build_quantile_df(df_rel_val, nn.linear.logit.fs1$matched, df_beta_val)
-nn.linear.logit.fs1.score <- score_model(bts, nn.linear.logit.fs1$matched, df_rel_val)
-nn.linear.logit.fs1.score
+# nn.linear.logit.fs1 <- train_matchit(dfs[['4']], fs1, add_interactions = TRUE, replace = FALSE, 
+#                         caliper = 0.4, calclosest = TRUE, ratio = 3, distance = "linear.logit")
+nn.linear.logit.fs1.predictions <- extract_predictions(nn.linear.logit.fs1$matched, df_beta_val)
+nn.linear.logit.fs1.qq <- build_quantile_df(df_rel_val, nn.linear.logit.fs1.predictions, df_beta_val)
+nn.linear.logit.fs1.score <- score_model(bts, nn.linear.logit.fs1.predictions, df_rel_val)
+# nn.linear.logit.fs1.score
 ```
 
-Number of Beta samples: `r nrow(nn.linear.logit.fs1$matched)`
+Resultant scores: `r nn.linear.logit.fs1.score`
+
+* Number of matched Beta training samples: `r nrow(nn.linear.logit.fs1$matched)`
+* Number of matched Beta validation samples: `r nrow(nn.linear.logit.fs1.predictions)`
 
 ```{r nn_logit_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
-plot_validation_results(df_rel_val, nn.linear.logit.fs1$matched, df_beta_val)
+plot_validation_results(df_rel_val, nn.linear.logit.fs1.predictions, df_beta_val)
 ```
@@
 ```{r nn_logit_fs3, warning=FALSE, error=FALSE, echo=FALSE}
-nn.linear.logit.fs5 <- train_matchit(dfs[['8']], fs5, add_interactions = FALSE, replace = FALSE, 
-                        caliper = 0, calclosest = FALSE, ratio = 1, distance = "linear.logit")
-nn.linear.logit.fs5.qq <- build_quantile_df(df_rel_val, nn.linear.logit.fs5$matched, df_beta_val)
-nn.linear.logit.fs5.score <- score_model(bts, nn.linear.logit.fs5$matched, df_rel_val)
-nn.linear.logit.fs5.score
+# nn.linear.logit.fs5 <- train_matchit(dfs[['8']], fs5, add_interactions = FALSE, replace = FALSE, 
+#                         caliper = 0, calclosest = FALSE, ratio = 1, distance = "linear.logit")
+nn.linear.logit.fs5.predictions <- extract_predictions(nn.linear.logit.fs5$matched, df_beta_val)
+nn.linear.logit.fs5.qq <- build_quantile_df(df_rel_val, nn.linear.logit.fs5.predictions, df_beta_val)
+nn.linear.logit.fs5.score <- score_model(bts, nn.linear.logit.fs5.predictions, df_rel_val)
+# nn.linear.logit.fs5.score
 ```
 
+Resultant scores: `r nn.linear.logit.fs5.score`
+
+* Number of matched Beta training samples: `r nrow(nn.linear.logit.fs5$matched)`
+* Number of matched Beta validation samples: `r nrow(nn.linear.logit.fs5.predictions)`
+
 ```{r nn_logit_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
-plot_validation_results(df_rel_val, nn.linear.logit.fs5$matched, df_beta_val)
+plot_validation_results(df_rel_val, nn.linear.logit.fs5.predictions, df_beta_val)
 ```
@@
 ```{r nn_gam_fs1, warning=FALSE, error=FALSE, echo=FALSE, message=FALSE}
-nn.gam.fs1 <- train_matchit(dfs[['4']], fs1, add_interactions = TRUE, replace = FALSE, 
-                        caliper = 0.5, calclosest = TRUE, ratio = 3, distance = "GAMlogit")
-nn.gam.fs1.qq <- build_quantile_df(df_rel_val, nn.gam.fs1$matched, df_beta_val)
-nn.gam.fs1.score <- score_model(bts, nn.gam.fs1$matched, df_rel_val)
-nn.gam.fs1.score
+# nn.gam.fs1 <- train_matchit(dfs[['4']], fs1, add_interactions = TRUE, replace = FALSE, 
+#                         caliper = 0.5, calclosest = TRUE, ratio = 3, distance = "GAMlogit")
+nn.gam.fs1.predictions <- extract_predictions(nn.gam.fs1$matched, df_beta_val)
+nn.gam.fs1.qq <- build_quantile_df(df_rel_val, nn.gam.fs1.predictions, df_beta_val)
+nn.gam.fs1.score <- score_model(bts, nn.gam.fs1.predictions, df_rel_val)
+# nn.gam.fs1.score
 ```
 
-Number of Beta samples: `r nrow(nn.gam.fs1$matched)`
+Resultant scores: `r nn.gam.fs1.score`
+
+* Number of matched Beta training samples: `r nrow(nn.gam.fs1$matched)`
+* Number of matched Beta validation samples: `r nrow(nn.gam.fs1.predictions)`
 
 ```{r nn_gam_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
-plot_validation_results(df_rel_val, nn.gam.fs1$matched, df_beta_val)
+plot_validation_results(df_rel_val, nn.gam.fs1.predictions, df_beta_val)
 ```
@@
 ```{r nn_gam_fs5, warning=FALSE, error=FALSE, echo=FALSE}
-nn.gam.fs5 <- train_matchit(dfs[['4']], fs5, add_interactions = FALSE, replace = FALSE, 
-                        caliper = 0, calclosest = FALSE, ratio = 1, distance = "GAMlogit")
-nn.gam.fs5.qq <- build_quantile_df(df_rel_val, nn.gam.fs5$matched, df_beta_val)
-nn.gam.fs5.score <- score_model(bts, nn.gam.fs5$matched, df_rel_val)
-nn.gam.fs5.score
+# nn.gam.fs5 <- train_matchit(dfs[['4']], fs5, add_interactions = FALSE, replace = FALSE, 
+#                         caliper = 0, calclosest = FALSE, ratio = 1, distance = "GAMlogit")
+nn.gam.fs5.predictions <- extract_predictions(nn.gam.fs5$matched, df_beta_val)
+nn.gam.fs5.qq <- build_quantile_df(df_rel_val, nn.gam.fs5.predictions, df_beta_val)
+nn.gam.fs5.score <- score_model(bts, nn.gam.fs5.predictions, df_rel_val)
+# nn.gam.fs5.score
 ```
 
-Number of Beta samples: `r nrow(nn.gam.fs1$matched)`
+Resultant scores: `r nn.gam.fs5.score`
+
+* Number of matched Beta training samples: `r nrow(nn.gam.fs5$matched)`
+* Number of matched Beta validation samples: `r nrow(nn.gam.fs5.predictions)`
 
 ```{r nn_gam_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
-plot_validation_results(df_rel_val, nn.gam.fs5$matched, df_beta_val)
+plot_validation_results(df_rel_val, nn.gam.fs5.predictions, df_beta_val)
 ```
@@
 ```{r nn_probit_fs1, warning=FALSE, error=FALSE, echo=FALSE}
-nn.linear.probit.fs1 <- train_matchit(dfs[['4']], fs1, add_interactions = TRUE, replace = FALSE, 
-                        caliper = 0.4, calclosest = TRUE, ratio = 3, distance = "linear.probit")
-nn.linear.probit.fs1.qq <- build_quantile_df(df_rel_val, nn.linear.probit.fs1$matched, df_beta_val)
-nn.linear.probit.fs1.score <- score_model(bts, nn.linear.probit.fs1$matched, df_rel_val)
-nn.linear.probit.fs1.score
+# nn.linear.probit.fs1 <- train_matchit(dfs[['4']], fs1, add_interactions = TRUE, replace = FALSE, 
+#                         caliper = 0.4, calclosest = TRUE, ratio = 3, distance = "linear.probit")
+nn.linear.probit.fs1.predictions <- extract_predictions(nn.linear.probit.fs1$matched, df_beta_val)
+nn.linear.probit.fs1.qq <- build_quantile_df(df_rel_val, nn.linear.probit.fs1.predictions, df_beta_val)
+nn.linear.probit.fs1.score <- score_model(bts, nn.linear.probit.fs1.predictions, df_rel_val)
+# nn.linear.probit.fs1.score
 ```
 
-Number of Beta samples: `r nrow(nn.linear.probit.fs1$matched)`
+Resultant scores: `r nn.linear.probit.fs1.score`
+
+* Number of matched Beta training samples: `r nrow(nn.linear.probit.fs1$matched)`
+* Number of matched Beta validation samples: `r nrow(nn.linear.probit.fs1.predictions)`
 
 ```{r nn_probit_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
-plot_validation_results(df_rel_val, nn.linear.probit.fs1$matched, df_beta_val)
+plot_validation_results(df_rel_val, nn.linear.probit.fs1.predictions, df_beta_val)
 ```
@@
 ```{r nn_probit_fs5, warning=FALSE, error=FALSE, echo=FALSE}
-nn.linear.probit.fs5 <- train_matchit(dfs[['8']], fs5, add_interactions = FALSE, replace = FALSE, 
-                        caliper = 0, calclosest = FALSE, ratio = 1, distance = "linear.probit")
-nn.linear.probit.fs5.qq <- build_quantile_df(df_rel_val, nn.linear.probit.fs5$matched, df_beta_val)
-nn.linear.probit.fs5.score <- score_model(bts, nn.linear.probit.fs5$matched, df_rel_val)
-nn.linear.probit.fs5.score
+# nn.linear.probit.fs5 <- train_matchit(dfs[['8']], fs5, add_interactions = FALSE, replace = FALSE, 
+#                         caliper = 0, calclosest = FALSE, ratio = 1, distance = "linear.probit")
+nn.linear.probit.fs5.predictions <- extract_predictions(nn.linear.probit.fs5$matched, df_beta_val)
+nn.linear.probit.fs5.qq <- build_quantile_df(df_rel_val, nn.linear.probit.fs5.predictions, df_beta_val)
+nn.linear.probit.fs5.score <- score_model(bts, nn.linear.probit.fs5.predictions, df_rel_val)
+# nn.linear.probit.fs5.score
 ```
 
-Number of Beta samples: `r nrow(nn.linear.probit.fs5$matched)`
+Resultant scores: `r nn.linear.probit.fs5.score`
+
+* Number of matched Beta training samples: `r nrow(nn.linear.probit.fs5$matched)`
+* Number of matched Beta validation samples: `r nrow(nn.linear.probit.fs5.predictions)`
 
 ```{r nn_probit_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
-plot_validation_results(df_rel_val, nn.linear.probit.fs5$matched, df_beta_val)
+plot_validation_results(df_rel_val, nn.linear.probit.fs5.predictions, df_beta_val)
 ```
@@
 genmatch.fs1.matched <- df_train_gen[fs1_results$matches$index.control,]
-genmatch.fs1.qq <- build_quantile_df(df_rel_val, genmatch.fs1.matched, df_beta_val)
-genmatch.fs1.score <- score_model(bts, genmatch.fs1.matched, df_rel_val)
-genmatch.fs1.score
+genmatch.fs1.predictions <- extract_predictions(genmatch.fs1.matched, df_beta_val)
+genmatch.fs1.qq <- build_quantile_df(df_rel_val, genmatch.fs1.predictions, df_beta_val)
+genmatch.fs1.score <- score_model(bts, genmatch.fs1.predictions, df_rel_val)
+# genmatch.fs1.score
 ```
 
-Number of Beta samples: `r nrow(genmatch.fs1.matched)`
+Resultant scores: `r genmatch.fs1.score`
+
+* Number of matched Beta training samples: `r length(unique(genmatch.fs1.matched$client_id))`
+* Number of matched Beta validation samples: `r nrow(genmatch.fs1.predictions)`
 
 ```{r genmatch_fs1_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
-plot_validation_results(df_rel_val, genmatch.fs1.matched, df_beta_val)
+plot_validation_results(df_rel_val, genmatch.fs1.predictions, df_beta_val)
 ```
@@
 genmatch.fs1.500.matched <- df_train_gen[fs1_500_results$matches$index.control,]
-genmatch.fs1.500.qq <- build_quantile_df(df_rel_val, genmatch.fs1.500.matched, df_beta_val)
-genmatch.fs1.500.score <- score_model(bts, genmatch.fs1.500.matched, df_rel_val)
-genmatch.fs1.500.score
+genmatch.fs1.500.predictions <- extract_predictions(genmatch.fs1.500.matched, df_beta_val)
+genmatch.fs1.500.qq <- build_quantile_df(df_rel_val, genmatch.fs1.500.predictions, df_beta_val)
+genmatch.fs1.500.score <- score_model(bts, genmatch.fs1.500.predictions, df_rel_val)
+# genmatch.fs1.500.score
 ```
 
-Number of Beta samples: `r nrow(genmatch.fs1.500.matched)`
+Resultant scores: `r genmatch.fs1.500.score`
 
-```{r genmatch_fs1_500_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
-plot_validation_results(df_rel_val, genmatch.fs1.500.matched, df_beta_val)
+* Number of matched Beta training samples: `r length(unique(genmatch.fs1.500.matched$client_id))`
+* Number of matched Beta validation samples: `r nrow(genmatch.fs1.500.predictions)`
+
+```{r genmatch_fs1.500_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
+plot_validation_results(df_rel_val, genmatch.fs1.500.predictions, df_beta_val)
 ```
@@
 genmatch.fs3.matched <- df_train_gen[fs3_results$matches$index.control,]
-genmatch.fs3.qq <- build_quantile_df(df_rel_val, genmatch.fs3.matched, df_beta_val)
-genmatch.fs3.score <- score_model(bts, genmatch.fs3.matched, df_rel_val)
-genmatch.fs3.score
+genmatch.fs3.predictions <- extract_predictions(genmatch.fs3.matched, df_beta_val)
+genmatch.fs3.qq <- build_quantile_df(df_rel_val, genmatch.fs3.predictions, df_beta_val)
+genmatch.fs3.score <- score_model(bts, genmatch.fs3.predictions, df_rel_val)
+# genmatch.fs3.score
 ```
 
-Number of Beta samples: `r nrow(genmatch.fs3.matched)`
+Resultant scores: `r genmatch.fs3.score`
+
+* Number of matched Beta training samples: `r length(unique(genmatch.fs3.matched$client_id))`
+* Number of matched Beta validation samples: `r nrow(genmatch.fs3.predictions)`
 
 ```{r genmatch_fs3_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
-plot_validation_results(df_rel_val, genmatch.fs3.matched, df_beta_val)
+plot_validation_results(df_rel_val, genmatch.fs3.predictions, df_beta_val)
 ```
@@
 genmatch.fs5.matched <- df_train_gen[fs5_results$matches$index.control,]
-genmatch.fs5.qq <- build_quantile_df(df_rel_val, genmatch.fs5.matched, df_beta_val)
-genmatch.fs5.score <- score_model(bts, genmatch.fs5.matched, df_rel_val)
-genmatch.fs5.score
+genmatch.fs5.predictions <- extract_predictions(genmatch.fs5.matched, df_beta_val)
+genmatch.fs5.qq <- build_quantile_df(df_rel_val, genmatch.fs5.predictions, df_beta_val)
+genmatch.fs5.score <- score_model(bts, genmatch.fs5.predictions, df_rel_val)
+#genmatch.fs5.score
 ```
 
-Number of Beta samples: `r nrow(genmatch.fs3.matched)`
+Resultant scores: `r genmatch.fs5.score`
+
+* Number of matched Beta training samples: `r length(unique(genmatch.fs5.matched$client_id))`
+* Number of matched Beta validation samples: `r nrow(genmatch.fs5.predictions)`
 
 ```{r genmatch_fs5_val_plt, fig.width=15,fig.height=25, warning=FALSE, message=FALSE, echo=FALSE}
-plot_validation_results(df_rel_val, genmatch.fs5.matched, df_beta_val)
+plot_validation_results(df_rel_val, genmatch.fs5.predictions, df_beta_val)
 ```
@@
 
-Genetic matching produces the optimal matching results.
+Nearest-Neighbors Probit, Linear produces the optimal matching results.
 It yields the lowest scores, without dropping large sample of the Beta profiles.
 Unsurprisingly, matching directly, and only, on the performance metrics yields the best results.
-Increasing the population size hyperparameter slightly decreased model performance, which is surprising.
-Considering this substantially increases training times, the lower value will be used.
+Interestingly, it appears that interactions across covariates greatly help.
+Fortunately, this model architecture is relatively cheap from a computational perspective.
+
+Balancing on additional covariates (e.g, FS3 or FS5), outside of the performance metrics, yields sub-optimal results.
+Nearest-Neighbors Probit, Linear again yields the lowest score (`r nn.linear.probit.fs5.score`); however, this is at the expense of a greatly reduced Beta samples size (`r nrow(nn.linear.probit.fs5.predictions)`).
+Genetic matching is able to retain a much larger sample size (`r nrow(genmatch.fs3.predictions)`), at the expense of greater error (`r genmatch.fs3.score`).
 
@@
 
-* matching algorithm: Genetic Matching
+* matching algorithm: Nearest-Neighbors Probit, Linear
 * features: Only performance metrics
-* hyperparameters: Default for `Matching` library
+* hyperparameters: 
+    * `caliper` = 0.4
+    * `calcloset` = FALSE
+    * `ratio` = 3
+    * `replace` = FALSE
+    * 4x oversampling
+    * Interactions across covariates
 
@@
 ```{r serialize_gcp, echo=FALSE}
-results_file_name = 'validation_results_20191106.RData'
+results_file_name = 'validation_results_20191121.RData'
 results_file_path = file.path('data', results_file_name)

### 2021-11-04 perf_release_criteria/milestone_4/ms_4_training_subsetting_calculation.Rmd

@@
 library(stringr)
+library(purrr)
 ```
@@
 sched <- htmltab('https://wiki.mozilla.org/Release_Management/Calendar', which=2) %>%
-  mutate('rel_dates' = ymd(sched$`Release Date`)) %>%
-  mutate('version' = as.numeric(str_match(sched$Beta, 'Firefox ([0-9]+)')[,2])) %>%
+  mutate('rel_dates' = ymd(`Release Date`)) %>%
+  mutate('version' = as.numeric(str_match(Beta, 'Firefox ([0-9]+)')[,2])) %>%
   filter(rel_dates < now())
@@
 df_train <- load_df(paste("ccd_subBeta_training", v_n, sep='_'))
-df_predict <- load_df(paste('ccd_subBeta_prerelease'), v_n1, sep='_')
-df_validate <- load_df(paste('ccd_subBeta_validation'), v_n, sep='_')
+df_predict <- load_df(paste('ccd_subBeta_prerelease', v_n1, sep='_'))
+# df_validate <- load_df(paste('ccd_subBeta_validation', v_n, sep='_'))
+df_validate <- load_df(paste('ccd_subset_validation', v_n, sep='_'))
 ```
@@
     mutate(date_created = now())
+
+df_validate_f <- stage_2_clean(df_validate) %>%
+    mutate(date_created = now())
 ```
@@
 
-Calculate the Release Health Metrics:
-**TBD**
+Calculate the Release Health Metrics, by comparing the performance metrics of the subsetted Beta dataset to the current validation (version N) Release dataset:
+
+* Beta mean 
+* Beta quantiles
+* relative difference in mean
+* relative difference in deciles
+* Cramér-von Mises score
+
+```{r release_health}
+agg_sets <- function(predictions){
+  predictions %>% 
+  select(outcomes) %>% 
+  gather("metric", "value", ) %>%
+  group_by(metric) %>%
+  summarise(
+    mean = mean(value),
+    p5 = partial(quantile, probs = .05)(value),  
+    p25 = partial(quantile, probs = .25)(value),  
+    p50 = median(value),
+    p75 = partial(quantile, probs = .75)(value),  
+    p95 = partial(quantile, probs = .95)(value),
+    p99 = partial(quantile, probs = .99)(value)
+  )
+}
+
+pred_agg <- agg_sets(predictions)
+release_agg <-  agg_sets(df_validate_f)
+
+abs_rel_diff <- (abs(pred_agg[-1]-release_agg[-1])/release_agg[-1])
+names(abs_rel_diff) <- paste('rel_diff_', names(abs_rel_diff), sep='')
+abs_rel_diff <- abs_rel_diff %>%
+  mutate(metric = pred_agg$metric)
+
+# cms_score <- calc_score(
+#   predictions %>% 
+#     select(label, outcomes) %>%
+#     bind_rows(
+#       select(df_validate_f, label, outcomes)
+#   ))
+
+cms_score <- sapply(outcomes, calc_cms, beta=df_predict_f, release=df_validate_f)
+cms_score <- data.frame(cms_score) %>% mutate(metric = rownames(.))
+
+health_metrics <- pred_agg %>% 
+  inner_join(., abs_rel_diff, by='metric') %>%
+  inner_join(., cms_score, by='metric') %>%
+  # mutate(cms_score = cms_score) %>%
+  mutate(date_created = now()) %>%
+  mutate(version = v_n1)
+```
 
@@
 # train_file_name <- paste('df_train_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
-train_file_name <- paste('df_train_', v_n, sep='_')
+train_file_name <- paste('df_train_', v_n, '.RData', sep='')
 train_file_path <- file.path('data', train_file_name)
@@
 # prerelease_file_name <- paste('df_prerelease_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
-prerelease_file_name <- paste('df_prerelease_', v_n1, sep='_')
+prerelease_file_name <- paste('df_prerelease_', v_n1, '.RData', sep='')
 prerelease_file_path <- file.path('data', prerelease_file_name)
@@
 # prerelease_file_name <- paste('df_prerelease_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
-validation_file_name <- paste('df_validation_', v_n1, sep='_')
+validation_file_name <- paste('df_validation_', v_n1, '.RData', sep='')
 validation_file_path <- file.path('data', validation_file_name)
-save(validation, file = validation_file_path)
+save(df_validate_f, file = validation_file_path)
 gcs_validation_file_path <- file.path('data', 'milestone4', validation_file_name)
@@
 # Release health metrics
-release_health_file_name <- paste('df_release_health_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
+# release_health_file_name <- paste('df_release_health_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
+release_health_file_name <- paste('df_release_health_', v_n1, '_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
 release_health_file_path <- file.path('data', release_health_file_name)
-# save(df_release_health_f, df_predict_f, df_release_health_x, file = release_health_file_path)
+save(health_metrics, file = release_health_file_path)
 gcs_release_health_file_path <- file.path('data', 'milestone4', release_health_file_name)
@@
 ```{r gcp_health_metrics_storage_push, warning=FALSE}
-# upload_try <- gcs_upload(gcs_release_health_file_path, name = gcs_file_path)
-# upload_try
+upload_try <- gcs_upload(release_health_file_path, name = gcs_release_health_file_path)
+upload_try
 ```
@@
 ```{r big_query_write}
-project <- "moz-fx-dev-cdowhyglund-subBeta"
+project <- "moz-fx-dev-cdowhyglund-subbeta"
 # project <- "moz-fx-data-bq-data-science"
 
-bq_table(project = 'moz-fx-dev-cdowhyglund-subbeta',
+bq_table(project = project,
          dataset = "training",
@@
 
-bq_table(project = 'moz-fx-dev-cdowhyglund-subbeta',
+bq_table(project = project,
          dataset = "training",
          table   = paste("ccd_subbeta_training_final", v_n, sep = '_')) %>%
-  bq_table_upload(values = df_train_x,
+  bq_table_upload(values = df_train_f,
                   create_disposition = "CREATE_IF_NEEDED",
                   write_disposition = "WRITE_TRUNCATE",
-                  fields = as_bq_fields(df_train_x) )
+                  fields = as_bq_fields(df_train_f) )
 
-bq_table(project = 'moz-fx-dev-cdowhyglund-subbeta',
+bq_table(project = project,
          dataset = "prerelease",
@@
 ```{r bq_write_subset}
-bq_table(project = 'moz-fx-dev-cdowhyglund-subbeta',
+bq_table(project = project,
          dataset = "prerelease",
          table   = paste("ccd_subbeta_prelease_subset", v_n1, sep = '_')) %>%
-  bq_table_upload(values = df_predict_f,
+  bq_table_upload(values = predictions,
                   create_disposition = "CREATE_IF_NEEDED",
-                  write_disposition = "WRITE_APPEND",
-                  fields = as_bq_fields(df_predict_f) )
+                  write_disposition = "WRITE_TRUNCATE",
+                  fields = as_bq_fields(predictions) )
 ```
@@
 ```{r bq_write_validate}
-bq_table(project = 'moz-fx-dev-cdowhyglund-subbeta',
+bq_table(project = project,
          dataset = "validation",
          table   = paste("ccd_subbeta_validation_cleaned", v_n, sep = '_')) %>%
-  bq_table_upload(values = df_predict_f,
+  bq_table_upload(values = df_validate_f,
                   create_disposition = "CREATE_IF_NEEDED",
                   write_disposition = "WRITE_APPEND",
-                  fields = as_bq_fields(df_predict_f) )
+                  fields = as_bq_fields(df_validate_f) )
 ```
@@
 ```{r bq_release_health_metrics}
-# bq_table(project = 'moz-fx-dev-cdowhyglund-subbeta',
-#          dataset = "prerelease",
-#          table   = "ccd_subbeta_prerelease_health_metrics") %>%
-#   bq_table_upload(values = release_health_df,
-#                   create_disposition = "CREATE_IF_NEEDED",
-#                   write_disposition = "WRITE_APPEND",
-#                   fields = as_bq_fields(release_health_df) )
+bq_table(project = project,
+         dataset = "prerelease",
+         table   = "ccd_subbeta_prerelease_health_metrics") %>%
+  bq_table_upload(values = health_metrics,
+                  create_disposition = "CREATE_IF_NEEDED",
+                  write_disposition = "WRITE_APPEND",
+                  fields = as_bq_fields(health_metrics) )
 ```
